### 2024-01-14 index.qmd
init commit

---
title: Solar wind discontinuities spatial evolution
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
  - name: Shi Chen
    orcid: 0000-0002-2582-7085
    affiliation: University of California, Los Angeles
affiliations:
  - id: ucla
    name: University of California, Los Angeles
bibliography: files/references.bib
execute: 
  eval: false
---

## Background

'Discontinuities' are discontinuous spatial changes in plasma parameters/characteristics and magnetic fields [@colburn1966].

They are observed across the heliosphere from inner heliosphere [@liu2022] to the heliosheath [@burlaga2011].

::: {#fig-ids_examples .column-page layout-ncol="2"}
![Current sheets in the heliosheath: Voyager 1, 2009](images/jgra21162-fig-0009.png){fig-alt="Hodograms produced by means of a minimum variance analysis for the current sheets associated with the sector boundaries in Figures 8 and 10. (b, d, and f) The value of the component of B along the minimum variance direction (Bm) as a function of time, N. (a, c, and e) The components of B along the intermediate variance direction (Bi) and maximum variance direction (BM)."}

![A rotational discontinuity (RD) detected at 0.126 AU](https://agupubs.onlinelibrary.wiley.com/cms/asset/8e244339-32cf-4703-9101-c1d9b4a3fa7c/jgra57047-fig-0002-m.jpg){fig-alt="The properties of a rotational discontinuity (RD) detected at 0.126 AU on 28 January 2020. (a) The magnetic field magnitude and three components in Radial‐Tangential‐Normal (RTN) coordinate system, (b) the magnetic field in local magnetic normal (LMN) coordinate system, (c and d) the proton velocity in RTN and LMN coordinate systems, (e) the proton density, (f) the proton thermal pressure, the magnetic pressure and the sum, (g) the tangential components of the electric field in LMN coordinate system in the RD rest frame, (h) the position, orientation, and motion of the RD, (i–k) the distributions of BL, JM, and J · E across the RD, (l and m) the jump conditions across the RD. In (h), the cyan plane and arrow represent the RD and its motion vector, and the yellow curve shows the PSP orbit. In (j), both the colors and the curve correspond to the values of JM, and two vertical dashed lines indicate the area of |JM|>13max|JM| $\\vert {J}_{M}\\vert > \\frac{1}{3}\\text{max}\\left(\\vert {J}_{M}\\vert \\right)$ whose width is defined as the half thickness of the discontinuity. In (m), the solid lines present the actual upstream and downstream velocities, while the dashed lines show the theoretical downstream velocity to satisfy the Walén relation."}

Discontinuities examples across the heliosphere
:::

@söding2001 studied the radial distribution of discontinuities in the solar wind between 0.3 and 19 AU during solar activity minimum. @liu2021 studied the spatial evolution of the discontinuities from 0.13-0.9 AU, using measurements from the Parker Solar Probe. [Typical rate of occurrence is about 50 per day at 1AU]{.aside}

::: {#fig-ids_distribution .column-page layout-ncol="2"}
[![Discontinuities between 0.3 and 19 AU](images/söding2001_fig4.png){fig-alt="Distribution of DD per day over r with a bin size of 0.1 AU and the standard deviations as error bars on logarithmic scale; TS criterion at the top and B at the bottom; darker lines represent intervals in the ecliptic which are used for the given fit and lighter ones are out of the ecliptic; right Voyager 2 in detail on linear scale."}](https://www.researchgate.net/figure/Distribution-of-DD-per-day-over-r-with-a-bin-size-of-01-AU-and-the-standard-deviations_fig4_29624789)

![Discontinuities between 0.13–0.9 AU](images/liu2021_fig2.png){fig-alt="Histograms as a function of heliocentric distance of (a) the number of events, (b) the PSP detection time, and (c)–(e) the occurrence rates of the total IDs, RDs and TDs. Panel (f) shows the ratio of RD occurrence rate to TD occurrence rate. The orange curves in panels (c) and (d) are the power-function fittings of ID and RD occurrence rates, with the coefficient of determination R2 being 0.983 and 0.985, respectively. The uncertainties of the power-law indices correspond to 95% confidence bounds."}

Spatial distribution of the discontinuities
:::

### Importance

-   Contribution of Strong Discontinuities to the Power Spectrum

    > The strong discontinuities produce a power-law spectrum in the 'inertial subrange' with a spectral index near the Kolmogorov -5/3 index. The discontinuity spectrum contains about half of the power of the full solar-wind magnetic ﬁeld over this 'inertial subrange'. [@borovsky2010]

### Motivations

Studying the radial distribution of occurrence rate, as well as the properties of solar wind discontinuities may help answer the following questions:

-   How does the discontinuities change with the radial distance from the Sun?
-   How is solar wind discontinuities formed? What is the physical mechanisms?
    -   Generated at or near the sun?
    -   Locally generated in the interplanetary space by turbulence?

Joint observations of JUNO & ARTEMIS & Other missions really provides a unique opportunity!!!

::: {#fig-juno_traj .column-page layout-ncol="2"}
![](https://www.nasa.gov/wp-content/uploads/2023/03/575573main_Juno20110727-3-43_full.jpg)

{{< video https://www.youtube.com/watch?v=sYp5p2oL51g title='Juno spacecraft trajectory animation' >}}

Juno Spacecraft Cruise Trajectory
:::

-   Five-year cruise to Jupiter from 2011 to 2016
-   One earth flyby in 2013
-   Nearly the same Heliographic latitude as Earth

To eliminate the effect of the solar wind structure, we use data from other missions (mainly at 1AU) to provide a way of normalization.

| Mission       | r \[AU\]  | $\delta t_B$        | $\delta t_{plasma}$                  | Data availability         |
|---------------|---------------|---------------|---------------|---------------|
| JUNO          | 1-5.5     | 1s averaged (64 Hz) | 1h **model** [\*](#solar-wind-model) | **2011 - 2016** - Today   |
| ARTEMIS       | 1         | 1s averaged (8 Hz)  | 1h averaged                          | 2009 - Today (solar wind) |
| STEREO-A      | 1         | 1s averaged (8 Hz)  | 1h averaged                          | 2006 - Today              |
| STEREO-B      | 1         | 1s averaged (8 Hz)  | 1h averaged                          | 2006 - 2016.09            |
| Wind          | 1         | 11 Hz               | 1h averaged                          | 1994 - 2004 -2020 - Today |
| Solar Orbiter | 0.28-0.91 |                     |                                      | 2020 - Today              |
| Ulysis        |           |                     |                                      |                           |

## Methods

- We use [@liu2022a] method to identify IDs, which has better compatibility for the IDs with minor field changes.
- Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features.

### ID identification (limited feature extraction / anomaly detection)

Traditional methods for ID identiﬁcation, such as the criteria of

-   Burlaga & Ness (1969; B-criterion) : a directional change of the magnetic ﬁeld larger than 30° during 60 s
-   Tsurutani & Smith (1979; TS-criterion) : $|ΔB|/|B| \geq 0.5$ within 3 minutes

Mostly rely on magnetic ﬁeld variations with a certain time lag. B-criterion has, as its main condition.

In their methods, the IDs below the thresholds are artiﬁcially abandoned. Therefore, identiﬁcation criteria may affect the statistical results, and there is likely to be a discrepancy between the ﬁndings via B-criterion and TS- criterion.

Liu's method : The first two conditions guarantee that the field changes of the IDs identiﬁed are large enough to be distinguished from the stochastic fluctuations on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition.

$$ \textrm{Index}_1 = \frac{\sigma(\vec{B})}{Max(\sigma(\vec{B}_-),\sigma(\vec{B}_+))} $$

$$ \textrm{Index}_2 = \frac{\sigma(\vec{B}_- + \vec{B}_+)} {\sigma(\vec{B}_-) + \sigma(\vec{B}_+)} $$

$$ \textrm{Index}_3 = \frac{| \Delta \vec{B} |}{|B_{bg}|} $$

$$ \textrm{Index}_1 \ge 2, \textrm{Index}_2 \ge 1, \textrm{Index}_3 \ge 0.1 $$

### Solar Wind Model {#solar-wind-model}

Sadly, JUNO does not provide plasma data during the cruise phase, so to estimate the plasma state we will use MHD model.

We are using [Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/), which models the solar wind propagation in 2D using the BATSRUS MHD solver. [@keebler2022]

Some key points about the model

-   Representing the solar wind in the ecliptic plane from 1 to 75 AU
-   2D MHD model, using the BATSRUS MHD solver
-   Inclusion of neutral hydrogen (important for the outer heliosphere)
-   Inner boundary is filled by time-shifting in situ data from multiple spacecraft

For model validation part, please see [JUNO Model Report](notebooks/analysis/20_model.ipynb).

## Results

For all results, see [results page](notebooks/analysis/index.qmd).

### Occurrence rates

[For code, see [noteboook](notebooks/analysis/01_occurence_rate.ipynb).]{.aside}

::: {#fig-ocr_time layout-ncol="2"}
![](figures/ocr/ocr_time_cleaned)

![](figures/ocr/ocr_time_N2_cleaned)

Occurrence rates with time
:::

::: {#fig-ocr_r layout-ncol="2"}
![](figures/ocr/ocr_r_cleaned)

![](figures/ocr/ocr_r_N2_cleaned)

Occurrence rates with radial distance
:::

### Properties

::: {#fig-thickness-distribution .column-page layout-ncol="2"}
![MN thickness](figures/thickness/thickness_mn_dist)

![MN current](figures/current/current_mn_dist)

![MN normalized thickness](figures/thickness/thickness_mn_N1_dist)

![MN normalized current](figures/current/current_mn_N1_dist)

Thickness and current density distribution
:::

## Conclusion

-   We have collected 5 years of solar wind discontinuities from JUNO, ARTEMIS and STEREO.
-   We have developed a pipeline to identify solar wind discontinuities. (Modular, Performant, Scalable)
-   The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
-   The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs decreases.
-   The current intensity of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current intensity of IDs increases.

### 2024-01-15 index.qmd
move file locations

@@
   eval: false
+
 ---
@@
 
-![A rotational discontinuity (RD) detected at 0.126 AU](https://agupubs.onlinelibrary.wiley.com/cms/asset/8e244339-32cf-4703-9101-c1d9b4a3fa7c/jgra57047-fig-0002-m.jpg){fig-alt="The properties of a rotational discontinuity (RD) detected at 0.126 AU on 28 January 2020.
+![A rotational discontinuity (RD) detected at 0.126 AU](images/jgra57047-fig-0002-m.jpg){fig-alt="The properties of a rotational discontinuity (RD) detected at 0.126 AU on 28 January 2020.
 (a) The magnetic field magnitude and three components in Radial‐Tangential‐Normal (RTN) coordinate system, (b) the magnetic field in local magnetic normal (LMN) coordinate system, (c and d) the proton velocity in RTN and LMN coordinate systems, (e) the proton density, (f) the proton thermal pressure, the magnetic pressure and the sum, (g) the tangential components of the electric field in LMN coordinate system in the RD rest frame, (h) the position, orientation, and motion of the RD, (i–k) the distributions of BL, JM, and J · E across the RD, (l and m) the jump conditions across the RD.

### 2024-01-15 notebooks/analysis/utils.R

@@ -1,0 +1,139 @@
+if (!requireNamespace("ggdensity", quietly = TRUE)) {
+  pak::pkg_install("ggdensity")
+}
+if (!requireNamespace("gaussplotR", quietly = TRUE)) {
+  pak::pkg_install("gaussplotR")
+}
+
+if (!requireNamespace("ggmagnify", quietly = TRUE)) {
+  pak::pkg_install("hughjonesd/ggmagnify")
+}
+
+library(dplyr)
+
+library(ggplot2)
+library(ggdensity)
+library(ggpubr)
+library(patchwork)
+library(see)
+
+library(glue)
+library(arrow)
+library(gaussplotR)
+library(scales)
+
+# Save the plot, if filename is provided
+save_plot <- function(filename = NULL) {
+  if (!is.null(filename)) {
+    ggsave(filename = glue("../figures/{filename}.png"))
+    ggsave(filename = glue("../figures/{filename}.pdf"))
+  }
+}
+
+
+# Plotting function for Level 1 data.
+# Similar to the `geom_bin2d` function, but with added functionality
+# - Normalize the data to every x-axis value
+# - Add peak values
+# - Add mean values with error bars
+
+library(scales)
+# Helper function to calculate summary statistics for x-binned data
+calculate_summary <- function(data, x_col, y_col, x_seq) {
+  data %>%
+    mutate(!!x_col := x_seq[findInterval(data[[x_col]], x_seq, rightmost.closed = TRUE)]) %>%
+    group_by(.data[[x_col]]) %>%
+    summarise(
+      mean_y = mean(.data[[y_col]], na.rm = TRUE),
+      sd_y = sd(.data[[y_col]], na.rm = TRUE),
+      # se_y = sd_y / sqrt(n())
+    )
+}
+
+
+plot_binned_data <- function(data, x_col, y_col, x_bins, y_bins, y_lim = NULL, log_y = FALSE) {
+  # If y_lim is provided, filter the data
+  if (!is.null(y_lim)) {
+    data <- data %>%
+      filter(.data[[y_col]] >= y_lim[1], .data[[y_col]] <= y_lim[2])
+  }
+
+  # If transform_log_y is TRUE, transform y_col to log scale
+  if (log_y) {
+    data[[y_col]] <- log10(data[[y_col]])
+    if (!is.null(y_lim)) {
[…]

### 2024-01-15 index.qmd
update figures

@@
   eval: false
-
+code-links:
+  - repo
+  - href: https://app.tana.inc?nodeid=Kmdzbyj-36NM
+    text: Tana
 ---
@@
 
-For all results, see [results page](notebooks/analysis/index.qmd).
+For all results, see [results page](notebooks/results.qmd).
 

### 2024-01-20 notebooks/utils.py
update omni figures

@@ -1,0 +1,53 @@
+from pydantic import constr, BaseModel, root_validator
+from datetime import datetime, date
+
+
+class TplotConfig(BaseModel):
+    tvar: str
+    trans: list[str] = None
+
+
+class PanelConfig(BaseModel):
+
+    timerange: list[datetime | date] = None
+    
+    id: str = None
+    name: str = None
+    units: str = None
+    
+    satellite: constr(to_lower=True)
+    instrument: constr(to_lower=True)
+    datatype: str = None
+    probe: str = None
+    
+    tplot: TplotConfig = None
+
+
+class OutputConfig(BaseModel):
+    path : str = None
+    filename: str = None
+    
+    formats: list[str] = list()
+    display: bool = False
+
+
+class Config(BaseModel):
+    panels: list[PanelConfig]
+    timerange: list[datetime | date] = None
+    output: OutputConfig = None
+    backend: str = None
+    
+    @root_validator(pre=True)
+    def set_default_timerange(cls, values):
+        timerange = values.get('timerange', None)
+        panels = values.get('panels', [])
+        
+        if timerange:
+            for panel in panels:
+                if not panel.get('timerange'):
+                    panel['timerange'] = timerange
+        return values
+
+class GraphicalConfig(BaseModel):
+    ylabel: str = None
+    

### 2024-01-20 index.qmd
update omni figures
update

@@
 -   The current intensity of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current intensity of IDs increases.
+
+## Figures
+
+::: {#fig-examples layout-nrow="1"}
+
+![](figures/examples/artemis_id_example)
+
+![](figures/examples/stereo_id_example)
+
+Examples of IDs from ARTEMIS, STEREO, and JUNO
+
+:::
+
+![Near-Earth' solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-omni_overview}
+
+[For code, see [noteboook](notebooks/20_omni_overview.ipynb).]{.aside}
+
+![Model validation](figures/model/juno_model_validation_full){#fig-model_validation}
+
+![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-ts_effect}

### 2024-01-20 notebooks/utils.py

@@ -1,10 +1,16 @@
 from pydantic import constr, BaseModel, root_validator
 from datetime import datetime, date
+from pytplot import tplot, get_data
 
+from xarray import DataArray
 
 class TplotConfig(BaseModel):
-    tvar: str
+    tvar: str = None
     trans: list[str] = None
+    
+class ProcessConfig(BaseModel):
+    tvar: str = None
+    trans: list[str] = list()
 
 
 class PanelConfig(BaseModel):
@@ -20,6 +26,7 @@ class PanelConfig(BaseModel):
     datatype: str = None
     probe: str = None
     
+    process: ProcessConfig = None
     tplot: TplotConfig = None
 
 
@@ -51,3 +58,16 @@ class Config(BaseModel):
 class GraphicalConfig(BaseModel):
     ylabel: str = None
     
+
+
+def export(config: OutputConfig, tvars2plot):
+    path = config.path
+    if config.display:
+        tplot(tvars2plot)
+    if "png" in config.formats:
+        tplot(tvars2plot, save_png=path, display=False)
+    if "svg" in config.formats:
+        tplot(tvars2plot, save_svg=path, display=False)
+    if "csv" in config.formats:
+        da: DataArray = get_data(tvars2plot, xarray=True)
+        da.to_pandas().to_csv(path + ".csv")

### 2024-01-21 presentations/AGU23_poster.qmd
update AGU23 poster

---
title: Solar wind discontinuities spatial evolution and energetic ion scattering
subtitle: AGU23 poster
abstract: Because solar wind plasma flow transports the entire spectrum of magnetic field fluctuations (from low-frequency inertial range to electron kinetic range), it is a natural laboratory for plasma turbulence investigation. Among the various wave modes and coherent plasma structures that contribute to this spectrum, one of the most important solar wind elements is ion-scale solar wind discontinuities. These structures, which carry very intense current, have been considered as a free energy source for plasma instabilities that contribute to solar wind heating. Investigations of such discontinuities have been mostly focused on their magnetic field signatures; much less is known about their role in scattering of energetic ions. In this studay, we consider observational-based model of ion dynamics and scattering in force-free rotational magnetic discontinuities. Focusing on quantification of the scattering effect, we demonstrate that background sheared magnetic field plays an important role in determining the efficiency of pitch angle scattering. We provide a model included statistical properties of solar wind discontinuities and providing estimates of ion scattering rate.
author:
  - name: Zijin Zhang
  - name: Anton Artemyev
  - name: Vassilis Angelopoulos
  - name: Shi Chen
bibliography: ../files/references.bib
date: 2023-12-11
code-links:
  - text: Poster PDF
    url: https://beforerr.github.io/ids_spatial_evolution_juno/presentations.AGU23_poster.pdf
---

## [Poster PDF](./AGU23_poster.pdf)

## Main findings {.main_findings}

- Solar wind discontinuities evolve in space with occurrence rate decreasing, **thickness increasing** and **current density decreasing** with distance from the Sun. And they are probably **generated locally** beyond 1 AU.
- Background sheared magnetic field plays an important role in determining the efficiency of ion pitch angle scattering, and characterize three ion populations: **transient, trapped, regular**.

## Introduction & Motivation

'Discontinuities' are discontinuous spatial changes in plasma parameters/characteristics and magnetic fields [@colburn1966].

![Current sheets in the heliosheath: Voyager 1, 2009](../images/jgra21162-fig-0009.png){width="48%"}
![Characteristics of magnetic field](https://github.com/Beforerr/ion_scattering_by_SWD/blob/385bfe5f1b147ef18d64e9507af77a38b5a9f091/figures/example_mva_noted.jpg?raw=true){width="48%"}

@söding2001 studied the radial distribution of discontinuities in the solar wind.

![Discontinuities between 0.3 and 19 AU](../images/söding2001_fig4.png){width=60%}
![Juno orbit](https://www.nasa.gov/wp-content/uploads/2023/03/575573main_Juno20110727-3-43_full.jpg){width=38%}

Joint observations of JUNO & ARTEMIS & Other missions really provides a unique opportunity!!!

## Method

- We use [@liu2022a] method to identify IDs, which has better compatibility for the IDs with minor field changes.
- Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features.
- Hamiltonian model is applied for investigation of ion dynamics in the solar wind discontinuity configuration.

The most generalized form of dimensionless hamiltonian equation for ions in force-free rotational magnetic discontinuities configuration is

$$
H=\frac{1}{2}\left(\frac{1}{6} \alpha^2 c_2 z^3-c_1 z+p_x\right)^2+\frac{p_z^2}{2}+\frac{1}{2}\left(\kappa x-\frac{\alpha z^2}{2}\right)^2
$$

With $B_l^2+B_m^2=\text { const }$, we have

$$
H=\frac{1}{2}\left(\frac{\alpha^2 z^3}{6 \sqrt{\kappa_m^2+1}}-z \sqrt{\kappa_m^2+1}+p_x\right)^2+\frac{p_z^2}{2}+\frac{1}{2}\left(\kappa_n x-\frac{\alpha z^2}{2}\right)^2
$$

The system has three parameters
$$
\kappa_n=\frac{B_n}{B_{l, \max }} 
\quad
\kappa_m=\frac{B_{m, 0}}{B_{l, \max }}
\quad
\alpha=\frac{l_0}{L}=\frac{\text { gyro radius }}{\text { system length }}
$$

## Results

![](../figures/ocr/ocr_time_cleaned.png){width=48%}

Normalized occurrence rate of IDs drops with the radial distance from the Sun, following 1/r law.

![](../figures/thickness/thickness_mn_dist.png){width=48%}
![](../figures/current/current_mn_dist.png){width=48%}

![](https://github.com/Beforerr/ion_scattering_by_SWD/blob/385bfe5f1b147ef18d64e9507af77a38b5a9f091/figures/example_traj.png?raw=true)

![](https://github.com/Beforerr/ion_scattering_by_SWD/blob/f6fbedc30f93bd799e2bb8cb6afe7aa31d58b98b/figures/example_scatter.png?raw=true){width=48%}

![](https://github.com/Beforerr/ion_scattering_by_SWD/blob/1728b9a32010b72e2ec6c156a76467fe25a51d88/figures/uncertainty_curve_length.png?raw=true){width=48%}

- High energy particle has higher chance to cross uncertainty curve
- High shear magnetic field will make separatrix vanishes and the geometrical jumps of the quasiadiabatic invariant disappear

### 2024-01-21 presentations/AGU23_poster.qmd
update

@@
   - text: Poster PDF
-    url: https://beforerr.github.io/ids_spatial_evolution_juno/presentations.AGU23_poster.pdf
+    href: ./AGU23_poster.pdf
 ---

### 2024-01-21 presentations/AGU23_poster.qmd
Built site for gh-pages

@@
   - text: Poster PDF
+    # href: https://beforerr.github.io/ids_spatial_evolution_juno/presentations.AGU23_poster.pdf
     href: ./AGU23_poster.pdf

### 2024-01-24 index.qmd
update AGU23 poster
update
add agu pdf format

--- 2024-01-15 index.qmd
@@
     name: University of California, Los Angeles
-bibliography: files/references.bib
 execute: 
@@
 
-## Background
+# Background
 
@@
 
-### Importance
+## Importance
 
@@
 
-### Motivations
+## Motivations
 
@@
 
-## Methods
+# Methods
 
@@
 
-### ID identification (limited feature extraction / anomaly detection)
+## ID identification (limited feature extraction / anomaly detection)
 
@@
 
-### Solar Wind Model {#solar-wind-model}
+## Solar Wind Model {#solar-wind-model}
 
@@
 
-## Results
+# Results
 
@@
 
-### Occurrence rates
+## Occurrence rates
 
@@
 
-### Properties
+## Properties
 
@@
 
-## Conclusion
+# Conclusion
 
--   We have collected 5 years of solar wind discontinuities from JUNO, ARTEMIS and STEREO.
+-   We have collected 5 years of solar wind discontinuities from JUNO, aMIS and STEREO.
 -   We have developed a pipeline to identify solar wind discontinuities. (Modular, Performant, Scalable)
@@
 -   The current intensity of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current intensity of IDs increases.
+
+# Figures
+
+::: {#fig-examples layout-nrow="1"}
+
+![](figures/examples/artemis_id_example.png)
+
+![](figures/examples/stereo_id_example.png)
+
+Examples of IDs from ARTEMIS, STEREO, and JUNO
+
+:::
+
+<!-- ![Near-Earth' solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-omni_overview} -->
+
+[For code, see [noteboook](notebooks/20_omni_overview.ipynb).]{.aside}
+
+![Model validation](figures/model/juno_model_validation_full){#fig-modelValidation}
+
+![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-tsEffect}

### 2024-01-24 notebooks/utils.py

@@ -66,6 +66,8 @@ def export(config: OutputConfig, tvars2plot):
         tplot(tvars2plot)
     if "png" in config.formats:
         tplot(tvars2plot, save_png=path, display=False)
+    if "pdf" in config.formats:
+        tplot(tvars2plot, save_pdf=path, display=False)
     if "svg" in config.formats:
         tplot(tvars2plot, save_svg=path, display=False)
     if "csv" in config.formats:

### 2024-01-25 index.qmd
better bib support

@@
 
-'Discontinuities' are discontinuous spatial changes in plasma parameters/characteristics and magnetic fields [@colburn1966].
+'Discontinuities' are discontinuous spatial changes in plasma parameters/characteristics and magnetic fields [@colburnDiscontinuitiesSolarWind1966].
 
-They are observed across the heliosphere from inner heliosphere [@liu2022] to the heliosheath [@burlaga2011].
+They are observed across the heliosphere from inner heliosphere [@liuCategorizingMHDDiscontinuities2022] to the heliosheath [@burlagaCurrentSheetsHeliosheath2011].
 
@@
 In (h), the cyan plane and arrow represent the RD and its motion vector, and the yellow curve shows the PSP orbit.
-In (j), both the colors and the curve correspond to the values of JM, and two vertical dashed lines indicate the area of |JM|>13max|JM| $\\vert {J}_{M}\\vert > \\frac{1}{3}\\text{max}\\left(\\vert {J}_{M}\\vert \\right)$ whose width is defined as the half thickness of the discontinuity.
+In (j), both the colors and the curve correspond to the values of JM, and two vertical dashed lines indicate the area of $\vert {J}_{M}\vert > \frac{1}{3}\text{max}\left(\vert {J}_{M}\vert \right)$ whose width is defined as the half thickness of the discontinuity.
 In (m), the solid lines present the actual upstream and downstream velocities, while the dashed lines show the theoretical downstream velocity to satisfy the Walén relation."}
@@
 
-@söding2001 studied the radial distribution of discontinuities in the solar wind between 0.3 and 19 AU during solar activity minimum.
-@liu2021 studied the spatial evolution of the discontinuities from 0.13-0.9 AU, using measurements from the Parker Solar Probe.
+@sodingRadialLatitudinalDependencies2001 studied the radial distribution of discontinuities in the solar wind between 0.3 and 19 AU during solar activity minimum.
+@liuCharacteristicsInterplanetaryDiscontinuities2021 studied the spatial evolution of the discontinuities from 0.13-0.9 AU, using measurements from the Parker Solar Probe.
 [Typical rate of occurrence is about 50 per day at 1AU]{.aside}
@@
 The discontinuity spectrum contains about half of the power of the full solar-wind magnetic ﬁeld over this 'inertial subrange'.
-[@borovsky2010]
-
-## Motivations
-
-Studying the radial distribution of occurrence rate, as well as the properties of solar wind discontinuities may help answer the following questions:
-
--   How does the discontinuities change with the radial distance from the Sun?
--   How is solar wind discontinuities formed? What is the physical mechanisms?
-    -   Generated at or near the sun?
-    -   Locally generated in the interplanetary space by turbulence?
-
-Joint observations of JUNO & ARTEMIS & Other missions really provides a unique opportunity!!!
-
-::: {#fig-juno_traj .column-page layout-ncol="2"}
-![](https://www.nasa.gov/wp-content/uploads/2023/03/575573main_Juno20110727-3-43_full.jpg)
-
-{{< video https://www.youtube.com/watch?v=sYp5p2oL51g title='Juno spacecraft trajectory animation' >}}
-
-Juno Spacecraft Cruise Trajectory
-:::
-
--   Five-year cruise to Jupiter from 2011 to 2016
--   One earth flyby in 2013
--   Nearly the same Heliographic latitude as Earth
-
-To eliminate the effect of the solar wind structure, we use data from other missions (mainly at 1AU) to provide a way of normalization.
-
-| Mission       | r \[AU\]  | $\delta t_B$        | $\delta t_{plasma}$                  | Data availability         |
-|---------------|---------------|---------------|---------------|---------------|
-| JUNO          | 1-5.5     | 1s averaged (64 Hz) | 1h **model** [\*](#solar-wind-model) | **2011 - 2016** - Today   |
-| ARTEMIS       | 1         | 1s averaged (8 Hz)  | 1h averaged                          | 2009 - Today (solar wind) |
-| STEREO-A      | 1         | 1s averaged (8 Hz)  | 1h averaged                          | 2006 - Today              |
-| STEREO-B      | 1         | 1s averaged (8 Hz)  | 1h averaged                          | 2006 - 2016.09            |
-| Wind          | 1         | 11 Hz               | 1h averaged                          | 1994 - 2004 -2020 - Today |
-| Solar Orbiter | 0.28-0.91 |                     |                                      | 2020 - Today              |
-| Ulysis        |           |                     |                                      |                           |
+[@borovskyContributionStrongDiscontinuities2010]
 
@@
 
-- We use [@liu2022a] method to identify IDs, which has better compatibility for the IDs with minor field changes.
+- We use [@liuMagneticDiscontinuitiesSolar2022] method to identify IDs, which has better compatibility for the IDs with minor field changes.
 - Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features.
@@
 
-$$ \textrm{Index}_1 = \frac{\sigma(\vec{B})}{Max(\sigma(\vec{B}_-),\sigma(\vec{B}_+))} $$
+$$ 
+\textrm{Index}_1 = \frac{\sigma(\vec{B})}{Max(\sigma(\vec{B}_-),\sigma(\vec{B}_+))} 
+$$
 
-$$ \textrm{Index}_2 = \frac{\sigma(\vec{B}_- + \vec{B}_+)} {\sigma(\vec{B}_-) + \sigma(\vec{B}_+)} $$
+$$
+\textrm{Index}_2 = \frac{\sigma(\vec{B}_- + \vec{B}_+)} {\sigma(\vec{B}_-) + \sigma(\vec{B}_+)}
+$$
 
-$$ \textrm{Index}_3 = \frac{| \Delta \vec{B} |}{|B_{bg}|} $$
+$$
+\textrm{Index}_3 = \frac{| \Delta \vec{B} |}{|B_{bg}|}
+$$
 
-$$ \textrm{Index}_1 \ge 2, \textrm{Index}_2 \ge 1, \textrm{Index}_3 \ge 0.1 $$
+$$ 
+\textrm{Index}_1 \ge 2, \textrm{Index}_2 \ge 1, \textrm{Index}_3 \ge 0.1 
+$$
 
@@
 
-We are using [Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/), which models the solar wind propagation in 2D using the BATSRUS MHD solver. [@keebler2022]
+We are using [Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/), which models the solar wind propagation in 2D using the BATSRUS MHD solver.
+@keeblerMSWIM2DTwodimensionalOuter2022
 
@@
 
-For model validation part, please see [JUNO Model Report](notebooks/analysis/20_model.ipynb).
-
-# Results
-
-For all results, see [results page](notebooks/results.qmd).
-
-## Occurrence rates
-
-[For code, see [noteboook](notebooks/analysis/01_occurence_rate.ipynb).]{.aside}
-
-::: {#fig-ocr_time layout-ncol="2"}
-![](figures/ocr/ocr_time_cleaned)
-
-![](figures/ocr/ocr_time_N2_cleaned)
-
-Occurrence rates with time
-:::
-
-::: {#fig-ocr_r layout-ncol="2"}
-![](figures/ocr/ocr_r_cleaned)
-
-![](figures/ocr/ocr_r_N2_cleaned)
-
-Occurrence rates with radial distance
-:::
-
-## Properties
-
-::: {#fig-thickness-distribution .column-page layout-ncol="2"}
-![MN thickness](figures/thickness/thickness_mn_dist)
-
-![MN current](figures/current/current_mn_dist)
-
-![MN normalized thickness](figures/thickness/thickness_mn_N1_dist)
-
-![MN normalized current](figures/current/current_mn_N1_dist)
-
-Thickness and current density distribution
-:::
+For model validation part, please see [JUNO Model Report](notebooks/20_model.ipynb).
 

### 2024-01-30 index.qmd
update

@@
 ---
-title: Solar wind discontinuities spatial evolution
+title: Solar wind discontinuities spatial evolution in the outer heliosphere
 author:
@@
     text: Tana
+  - href: https://www.overleaf.com/project/65b0a9c80a3616adf6e599e8
+    text: Overleaf
 ---
@@
 
+::: {.content-visible when-format="html"}
 ::: {#fig-ids_examples .column-page layout-ncol="2"}
@@
 :::
+:::
 
@@
 @liuCharacteristicsInterplanetaryDiscontinuities2021 studied the spatial evolution of the discontinuities from 0.13-0.9 AU, using measurements from the Parker Solar Probe.
+
+::: {.content-visible when-format="html"}
+
 [Typical rate of occurrence is about 50 per day at 1AU]{.aside}
@@
 Spatial distribution of the discontinuities
+:::
 :::

### 2024-02-02 index.qmd
update

@@
     text: Overleaf
+abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
+We identify and analyze the properties of the discontinuities at different radial distances from the Sun.
+By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of IDs drops with the radial distance from the Sun, following a $1/r$ law; (2) The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases; (3) The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
 ---
 
-# Background
+# Introduction
 
-'Discontinuities' are discontinuous spatial changes in plasma parameters/characteristics and magnetic fields [@colburnDiscontinuitiesSolarWind1966].
+Rapid variations in interplanetary magnetic fields, commonly recognized as solar wind magnetic discontinuities [@colburnDiscontinuitiesSolarWind1966], embody localized transient rotations or jumps of the magnetic field.
+Considered important for efficient plasma heating, they carry the most intense currents found in the solar wind and obserrved throughout the heliosphere from inner heliosphere [@liuCategorizingMHDDiscontinuities2022] to the heliosheath [@burlagaCurrentSheetsHeliosheath2011].
+Theoretical models [@lerchePropagationMagneticDisturbances1975, @medvedevDissipativeDynamicsCollisionless1997] and MHD simulations [@grecoIntermittentMHDStructures2008, @grecoStatisticalAnalysisDiscontinuities2009, @yangFormationRotationalDiscontinuities2015] suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence.
+These nonlinear processes can create significant isolated disturbances to the otherwise adiabatic evolution of the solar wind flow (?Reference?) and host many processes, including magnetic reconnection (?Reference?) and Fermi acceleration of particles [@wentzelMotionMagneticDiscontinuities1964].
+Moreover, they contribute significantly to the magnetic fluctuation spectra [@borovskyContributionStrongDiscontinuities2010] and can affect space weather [@tsurutaniReviewInterplanetaryDiscontinuities2011].
+Therefore, the study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind and test the local generation mechanism of discontinuities.
+However, previous study of solar wind discontinuities evolution [@sodingRadialLatitudinalDependencies2001] in the outer heliosphere were rarely in conjunction with measurements closer to the Sun.
+Moreover, the intervals in their study spread over multiple solar cycles though they are selected during solar activity minimum.
+Thus it is presently unclear whether their frequency and properties are the result of solar variability or due to the natural evolution of the discontinuities during their propagation and interaction with the ambient solar wind.
 
-They are observed across the heliosphere from inner heliosphere [@liuCategorizingMHDDiscontinuities2022] to the heliosheath [@burlagaCurrentSheetsHeliosheath2011].
+The goal of our paper is to investigate, statistically, discontinuities at different radial distance in the outer heliosphere to obtain a understanding of their formation and evolution.
+Our methodology involves integrating Juno measurements [@connerneyJunoMagneticField2017] between $1$ and $5$ AU with those at $1$ AU to distinguish temporal effect and spatial variations by examining the discontinuity characteristics at two radial distances simultaneously.
 
-::: {.content-visible when-format="html"}
-::: {#fig-ids_examples .column-page layout-ncol="2"}
-![Current sheets in the heliosheath: Voyager 1, 2009](images/jgra21162-fig-0009.png){fig-alt="Hodograms produced by means of a minimum variance analysis for the current sheets associated with the sector boundaries in Figures 8 and 10.
-(b, d, and f) The value of the component of B along the minimum variance direction (Bm) as a function of time, N.
-(a, c, and e) The components of B along the intermediate variance direction (Bi) and maximum variance direction (BM)."}
+First, the missions, instruments and data used are listed.
+Then, we brieﬂy describe the method used to identify the discontinuities and the model used to estimate the plasma state at Juno location due to the lack of plasma data during its cruise phase.
+Finally, we present the results of the spatial evolution of the discontinuities with respect to their characteristics (spatial scales and current density), and discuss the implications of our findings.
 
-![A rotational discontinuity (RD) detected at 0.126 AU](images/jgra57047-fig-0002-m.jpg){fig-alt="The properties of a rotational discontinuity (RD) detected at 0.126 AU on 28 January 2020.
-(a) The magnetic field magnitude and three components in Radial‐Tangential‐Normal (RTN) coordinate system, (b) the magnetic field in local magnetic normal (LMN) coordinate system, (c and d) the proton velocity in RTN and LMN coordinate systems, (e) the proton density, (f) the proton thermal pressure, the magnetic pressure and the sum, (g) the tangential components of the electric field in LMN coordinate system in the RD rest frame, (h) the position, orientation, and motion of the RD, (i–k) the distributions of BL, JM, and J · E across the RD, (l and m) the jump conditions across the RD.
-In (h), the cyan plane and arrow represent the RD and its motion vector, and the yellow curve shows the PSP orbit.
-In (j), both the colors and the curve correspond to the values of JM, and two vertical dashed lines indicate the area of $\vert {J}_{M}\vert > \frac{1}{3}\text{max}\left(\vert {J}_{M}\vert \right)$ whose width is defined as the half thickness of the discontinuity.
-In (m), the solid lines present the actual upstream and downstream velocities, while the dashed lines show the theoretical downstream velocity to satisfy the Walén relation."}
+:::: {.content-visible when-format="html"}
+::: {.callout-note collapse="false"}
 
-Discontinuities examples across the heliosphere
-:::
-:::
+## Related works
 
-@sodingRadialLatitudinalDependencies2001 studied the radial distribution of discontinuities in the solar wind between 0.3 and 19 AU during solar activity minimum.
-@liuCharacteristicsInterplanetaryDiscontinuities2021 studied the spatial evolution of the discontinuities from 0.13-0.9 AU, using measurements from the Parker Solar Probe.
-
-::: {.content-visible when-format="html"}
+- @sodingRadialLatitudinalDependencies2001 studied the radial distribution of discontinuities in the solar wind between 0.3 and 19 AU during solar activity minimum.
+- @liuCharacteristicsInterplanetaryDiscontinuities2021 studied the spatial evolution of the discontinuities from 0.13-0.9 AU, using measurements from the Parker Solar Probe.
 
@@
 :::
-
-## Importance
-
--   Contribution of Strong Discontinuities to the Power Spectrum
-
-    > The strong discontinuities produce a power-law spectrum in the 'inertial subrange' with a spectral index near the Kolmogorov -5/3 index.
-The discontinuity spectrum contains about half of the power of the full solar-wind magnetic ﬁeld over this 'inertial subrange'.
-[@borovskyContributionStrongDiscontinuities2010]
+::::
 
@@
 - Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features.
+
+::: {#fig-examples .column-page layout-nrow="1"}
+
+![](figures/examples/artemis_id_example)
+
+![](figures/examples/stereo_id_example)
+
+![](figures/examples/wind_id_example)
+
+Examples of IDs from ARTEMIS, STEREO, and Wind
+
+:::
+
+:::: {.content-visible when-format="html"}
+::: {.callout-note collapse="false"}
+::: {#fig-ids_examples layout-ncol="2"}
+![Current sheets in the heliosheath: Voyager 1, 2009](images/jgra21162-fig-0009.png){fig-alt="Hodograms produced by means of a minimum variance analysis for the current sheets associated with the sector boundaries in Figures 8 and 10.
+(b, d, and f) The value of the component of B along the minimum variance direction (Bm) as a function of time, N.
+(a, c, and e) The components of B along the intermediate variance direction (Bi) and maximum variance direction (BM)."}
+
+![A rotational discontinuity (RD) detected at 0.126 AU](images/jgra57047-fig-0002-m.jpg){fig-alt="The properties of a rotational discontinuity (RD) detected at 0.126 AU on 28 January 2020.
+(a) The magnetic field magnitude and three components in Radial‐Tangential‐Normal (RTN) coordinate system, (b) the magnetic field in local magnetic normal (LMN) coordinate system, (c and d) the proton velocity in RTN and LMN coordinate systems, (e) the proton density, (f) the proton thermal pressure, the magnetic pressure and the sum, (g) the tangential components of the electric field in LMN coordinate system in the RD rest frame, (h) the position, orientation, and motion of the RD, (i–k) the distributions of BL, JM, and J · E across the RD, (l and m) the jump conditions across the RD.
+In (h), the cyan plane and arrow represent the RD and its motion vector, and the yellow curve shows the PSP orbit.
+In (j), both the colors and the curve correspond to the values of JM, and two vertical dashed lines indicate the area of $\vert {J}_{M}\vert > \frac{1}{3}\text{max}\left(\vert {J}_{M}\vert \right)$ whose width is defined as the half thickness of the discontinuity.
+In (m), the solid lines present the actual upstream and downstream velocities, while the dashed lines show the theoretical downstream velocity to satisfy the Walén relation."}
+
+Discontinuities examples across the heliosphere
+:::
+:::
+::::
 
@@
 
-## Solar Wind Model {#solar-wind-model}
+## Solar Wind Model
 
@@
 
-::: {#fig-examples layout-nrow="1"}
+![Juno orbit](figures/juno_orbit_white){#fig-orbit}
 
-![](figures/examples/artemis_id_example.png)
+::: {#fig-examples .column-page layout-nrow="1"}
 
-![](figures/examples/stereo_id_example.png)
+![](figures/examples/artemis_id_example)
 
-Examples of IDs from ARTEMIS, STEREO, and JUNO
+![](figures/examples/stereo_id_example)
+
+![](figures/examples/wind_id_example)
+
+Examples of IDs from ARTEMIS, STEREO, and Wind
 
@@
 
-<!-- ![Near-Earth' solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-omni_overview} -->
+![Near-Earth's solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview}
+
+Overview of the solar wind at 1 AU
 

### 2024-02-02 _tex/index.tex
Built site for gh-pages

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{agujournal2019}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{sidenotes}{}{\usepackage{sidenotes}}
\@ifpackageloaded{marginnote}{}{\usepackage{marginnote}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Solar wind discontinuities spatial evolution in the outer heliosphere},
  pdfauthor={Zijin Zhang; Anton V. Artemyev; Vassilis Angelopoulos; Shi Chen},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\journalname{JGR: Space Physics}

\draftfalse

\begin{document}
\title{Solar wind discontinuities spatial evolution in the outer heliosphere}

\authors{Zijin Zhang\affil{1}, Anton V. Artemyev\affil{1}, Vassilis Angelopoulos\affil{1}, Shi Chen\affil{1}}
\affiliation{1}{University of California, Los Angeles, }
\correspondingauthor{Zijin Zhang}{zijin@ucla.edu}

\begin{abstract}
We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase. We identify and analyze the properties of the discontinuities at different radial distances from the Sun. By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of IDs drops with the radial distance from the Sun, following a \(1/r\) law; (2) The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases; (3) The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
\end{abstract}

\section{Introduction}\label{introduction}

Rapid variations in interplanetary magnetic fields, commonly recognized as solar wind magnetic discontinuities \citep{colburnDiscontinuitiesSolarWind1966}, embody localized transient rotations or jumps of the magnetic field. Considered important for efficient plasma heating, they carry the most intense currents found in the solar wind and obserrved throughout the heliosphere from inner heliosphere \citep{liuCategorizingMHDDiscontinuities2022} to the heliosheath \citep{burlagaCurrentSheetsHeliosheath2011}. Theoretical models \citep[\citet{medvedevDissipativeDynamicsCollisionless1997}]{lerchePropagationMagneticDisturbances1975} and MHD simulations \citep[\citet{grecoStatisticalAnalysisDiscontinuities2009}, \citet{yangFormationRotationalDiscontinuities2015}]{grecoIntermittentMHDStructures2008} suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence. These nonlinear processes can create significant isolated disturbances to the otherwise adiabatic evolution of the solar wind flow (?Reference?) and host many processes, including magnetic reconnection (?Reference?) and Fermi acceleration of particles \citep{wentzelMotionMagneticDiscontinuities1964}. Moreover, they contribute significantly to the magnetic fluctuation spectra \citep{borovskyContributionStrongDiscontinuities2010} and can affect space weather \citep{tsurutaniReviewInterplanetaryDiscontinuities2011}. Therefore, the study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind and test the local generation mechanism of discontinuities. However, previous study of solar wind discontinuities evolution \citep{sodingRadialLatitudinalDependencies2001} in the outer heliosphere were rarely in conjunction with measurements closer to the Sun. Moreover, the intervals in their study spread over multiple solar cycles though they are selected during solar activity minimum. Thus it is presently unclear whether their frequency and properties are the result of solar variability or due to the natural evolution of the discontinuities during their propagation and interaction with the ambient solar wind.

The goal of our paper is to investigate, statistically, discontinuities at different radial distance in the outer heliosphere to obtain a understanding of their formation and evolution. Our methodology involves integrating Juno measurements \citep{connerneyJunoMagneticField2017} between \(1\) and \(5\) AU with those at \(1\) AU to distinguish temporal effect and spatial variations by examining the discontinuity characteristics at two radial distances simultaneously.

First, the missions, instruments and data used are listed. Then, we brieﬂy describe the method used to identify the discontinuities and the model used to estimate the plasma state at Juno location due to the lack of plasma data during its cruise phase. Finally, we present the results of the spatial evolution of the discontinuities with respect to their characteristics (spatial scales and current density), and discuss the implications of our findings.

\section{Methods}\label{methods}

\begin{itemize}
\tightlist
\item
  We use \citep{liuMagneticDiscontinuitiesSolar2022} method to identify IDs, which has better compatibility for the IDs with minor field changes.
\item
  Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features.
\end{itemize}

\begin{figure*}

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/examples/artemis_id_example.pdf}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/examples/stereo_id_example.pdf}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/examples/wind_id_example.pdf}\end{minipage}%

\caption{\label{fig-examples}Examples of IDs from ARTEMIS, STEREO, and Wind}

\end{figure*}%

\subsection{ID identification (limited feature extraction / anomaly detection)}\label{id-identification-limited-feature-extraction-anomaly-detection}

Traditional methods for ID identiﬁcation, such as the criteria of

\begin{itemize}
\tightlist
\item
  Burlaga \& Ness (1969; B-criterion) : a directional change of the magnetic ﬁeld larger than 30° during 60 s
\item
  Tsurutani \& Smith (1979; TS-criterion) : \(|ΔB|/|B| \geq 0.5\) within 3 minutes
\end{itemize}

Mostly rely on magnetic ﬁeld variations with a certain time lag. B-criterion has, as its main condition.

In their methods, the IDs below the thresholds are artiﬁcially abandoned. Therefore, identiﬁcation criteria may affect the statistical results, and there is likely to be a discrepancy between the ﬁndings via B-criterion and TS- criterion.

Liu's method : The first two conditions guarantee that the field changes of the IDs identiﬁed are large enough to be distinguished from the stochastic fluctuations on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition.

\[ 
\textrm{Index}_1 = \frac{\sigma(\vec{B})}{Max(\sigma(\vec{B}_-),\sigma(\vec{B}_+))} 
\]

\[
\textrm{Index}_2 = \frac{\sigma(\vec{B}_- + \vec{B}_+)} {\sigma(\vec{B}_-) + \sigma(\vec{B}_+)}
\]

\[
\textrm{Index}_3 = \frac{| \Delta \vec{B} |}{|B_{bg}|}
\]

\[ 
\textrm{Index}_1 \ge 2, \textrm{Index}_2 \ge 1, \textrm{Index}_3 \ge 0.1 
\]

\subsection{Solar Wind Model}\label{solar-wind-model}

Sadly, JUNO does not provide plasma data during the cruise phase, so to estimate the plasma state we will use MHD model.

We are using \href{http://csem.engin.umich.edu/MSWIM2D/}{Michigan Solar WInd Model 2D (MSWIM2D)}, which models the solar wind propagation in 2D using the BATSRUS MHD solver. \citet{keeblerMSWIM2DTwodimensionalOuter2022}

Some key points about the model

\begin{itemize}
\tightlist
\item
  Representing the solar wind in the ecliptic plane from 1 to 75 AU
\item
  2D MHD model, using the BATSRUS MHD solver
\item
  Inclusion of neutral hydrogen (important for the outer heliosphere)
\item
  Inner boundary is filled by time-shifting in situ data from multiple spacecraft
\end{itemize}

For model validation part, please see \href{notebooks/20_model.ipynb}{JUNO Model Report}.

\section{Conclusion}\label{conclusion}

\begin{itemize}
\tightlist
\item
  We have collected 5 years of solar wind discontinuities from JUNO, aMIS and STEREO.
\item
  We have developed a pipeline to identify solar wind discontinuities. (Modular, Performant, Scalable)
\item
  The normalized occurrence rate of IDs drops with the radial distance from the Sun, following \(1/r\) law.
\item
  The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs decreases.
\item
  The current intensity of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current intensity of IDs increases.
\end{itemize}

\section{Figures}\label{figures}

\begin{figure}

\centering{

\includegraphics{figures/juno_orbit_white.pdf}

}

\caption{\label{fig-orbit}Juno orbit}

\end{figure}%

\begin{figure*}

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/examples/artemis_id_example.pdf}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/examples/stereo_id_example.pdf}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/examples/wind_id_example.pdf}\end{minipage}%

\caption{\label{fig-examples}Examples of IDs from ARTEMIS, STEREO, and Wind}

\end{figure*}%

\begin{figure}

\centering{

\includegraphics{figures/omni_overview.pdf}

}

\caption{\label{fig-overview}Near-Earth's solar wind plasma data during JUNO cruise phase}

\end{figure}%

Overview of the solar wind at 1 AU

{\marginnote{\begin{footnotesize}For code, see \href{notebooks/20_omni_overview.ipynb}{noteboook}.\end{footnotesize}}}

\begin{figure}

\centering{

\includegraphics{figures/model/juno_model_validation_full.pdf}

}

\caption{\label{fig-modelValidation}Model validation}

\end{figure}%

\begin{figure}

\centering{

\includegraphics{figures/ts_effect.pdf}

}

\caption{\label{fig-tsEffect}Effect of the time resolution on the discontinuity properties}

\end{figure}%

  \bibliography{files/bibexport.bib,../research.bib,files/bibliography/full\_anton.bib,files/bibliography/addon\_anton.bib}

\end{document}

### 2024-02-02 presentations/AGU23_poster.qmd
Built site for gh-pages

--- 2024-01-21 presentations/AGU23_poster.qmd
@@
   - name: Shi Chen
-bibliography: ../files/references.bib
 date: 2023-12-11

### 2024-02-02 index.qmd
update

@@
 Considered important for efficient plasma heating, they carry the most intense currents found in the solar wind and obserrved throughout the heliosphere from inner heliosphere [@liuCategorizingMHDDiscontinuities2022] to the heliosheath [@burlagaCurrentSheetsHeliosheath2011].
-Theoretical models [@lerchePropagationMagneticDisturbances1975, @medvedevDissipativeDynamicsCollisionless1997] and MHD simulations [@grecoIntermittentMHDStructures2008, @grecoStatisticalAnalysisDiscontinuities2009, @yangFormationRotationalDiscontinuities2015] suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence.
+Theoretical models [@lerchePropagationMagneticDisturbances1975; @medvedevDissipativeDynamicsCollisionless1997] and MHD simulations [@grecoIntermittentMHDStructures2008; @grecoStatisticalAnalysisDiscontinuities2009; @yangFormationRotationalDiscontinuities2015] suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence.
 These nonlinear processes can create significant isolated disturbances to the otherwise adiabatic evolution of the solar wind flow (?Reference?) and host many processes, including magnetic reconnection (?Reference?) and Fermi acceleration of particles [@wentzelMotionMagneticDiscontinuities1964].

### 2024-02-02 _tex/index.tex
Built site for gh-pages

@@
 Considered important for efficient plasma heating, they carry the most intense currents found in the solar wind and obserrved throughout the heliosphere from inner heliosphere \citep{liuCategorizingMHDDiscontinuities2022} to the heliosheath \citep{burlagaCurrentSheetsHeliosheath2011}.
-Theoretical models \citep[\citet{medvedevDissipativeDynamicsCollisionless1997}]{lerchePropagationMagneticDisturbances1975} and MHD simulations \citep[\citet{grecoStatisticalAnalysisDiscontinuities2009}, \citet{yangFormationRotationalDiscontinuities2015}]{grecoIntermittentMHDStructures2008} suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence.
+Theoretical models \citep{lerchePropagationMagneticDisturbances1975, medvedevDissipativeDynamicsCollisionless1997} and MHD simulations \citep{grecoIntermittentMHDStructures2008, grecoStatisticalAnalysisDiscontinuities2009, yangFormationRotationalDiscontinuities2015} suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence.
 These nonlinear processes can create significant isolated disturbances to the otherwise adiabatic evolution of the solar wind flow (?Reference?) and host many processes, including magnetic reconnection (?Reference?) and Fermi acceleration of particles \citep{wentzelMotionMagneticDiscontinuities1964}.

### 2024-02-02 index.qmd
update

@@
 
-:::: {.content-visible when-format="html"}
+::: {.content-visible when-format="html"}
 ::: {.callout-note collapse="false"}
-
 ## Related works
@@
 :::
-::::
+:::
 
-# Methods
+# Dataset, models, and methods
 
-- We use [@liuMagneticDiscontinuitiesSolar2022] method to identify IDs, which has better compatibility for the IDs with minor field changes.
-- Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features.
+{{< embed notes.ipynb#tbl-missions >}}
+
+## Methods
+
+We will use Liu's [@liu2022a] method to identify discontinuities in the solar wind.
+This method has better compatibility for the discontinuities with minor field changes, and is more robust to the situation encountered in the outer heliosphere.
+For each sampling instant $t$, we define three intervals: the pre-interval $[-1,-1/2]\cdot T+t$, the middle interval $[-1/,1/2]\cdot T+t$, and the post-interval $[1/2,1]\cdot T+t$, in which $T$ are time lags.
+Let time series of the magnetic field data in these three intervals are labeled ${\mathbf B}_-$, ${\mathbf B}_0$, ${\mathbf B}_+$, respectively.
+Then for an discontinuity, the following three conditions should be satisfied: (1) $\sigma({\mathbf B}_0)>2\max\left(\sigma({\mathbf B}_-, \sigma({\mathbf B}_+)\right)$, (2) $\sigma\left({\mathbf B}_-+{\mathbf B}_+\right)>\sigma({\mathbf B}_-)+\sigma({\mathbf B}_+)$, and (3) $|\Delta {\mathbf B}|>|{\mathbf B}_{bg}|/10$, in which $\sigma$ and ${\mathbf B}_{bg}$ represent the standard deviation and the background magnetic field magnitude, and $\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)$.
+The first two conditions guarantee that the field changes of the discontinuity identified are large enough to be distinguished from the stochastic fluctuations on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition.
+We also will use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to determine the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$.
+@fig-examples shows several examples of solar wind discontinuities detected by different spacecraft.
+
+<!-- - We use [@liuMagneticDiscontinuitiesSolar2022] method to identify IDs, which has better compatibility for the IDs with minor field changes.
+- Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features. -->
 
 ::: {#fig-examples .column-page layout-nrow="1"}
-
 ![](figures/examples/artemis_id_example)
@@
 Examples of IDs from ARTEMIS, STEREO, and Wind
-
 :::
 
-:::: {.content-visible when-format="html"}
+::: {.content-visible when-format="html"}
 ::: {.callout-note collapse="false"}
@@
 In (h), the cyan plane and arrow represent the RD and its motion vector, and the yellow curve shows the PSP orbit.
-In (j), both the colors and the curve correspond to the values of JM, and two vertical dashed lines indicate the area of $\vert {J}_{M}\vert > \frac{1}{3}\text{max}\left(\vert {J}_{M}\vert \right)$ whose width is defined as the half thickness of the discontinuity.
+In (j), both the colors and the curve correspond to the values of JM, and two vertical dashed lines indicate the area of $\\vert {J}_{M}\\vert > \\frac{1}{3}\\text{max}\\left(\\vert {J}_{M}\\vert \\right)$ whose width is defined as the half thickness of the discontinuity.
 In (m), the solid lines present the actual upstream and downstream velocities, while the dashed lines show the theoretical downstream velocity to satisfy the Walén relation."}
@@
 :::
-::::
+:::
 
@@
 
-::: {#fig-examples .column-page layout-nrow="1"}
-
+::: {.column-page layout-nrow="1"}
 ![](figures/examples/artemis_id_example)
@@
 Examples of IDs from ARTEMIS, STEREO, and Wind
-
 :::
@@
 
+::: {.column-screen-inset layout-nrow="1"}
+![](figures/thickness/thickness_k_dist)
+
+![](figures/thickness/thickness_k_N1_dist)
+
+![](figures/thickness/thickness_k_N1_r_dist)
+:::
+
+::: {.column-screen-inset layout-nrow="1"}
+
+![](figures/current/current_k_dist)
+
+![](figures/current/current_k_N1_dist)
+
+:::
+
 ![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-tsEffect}

### 2024-02-02 _tex/index.tex
Built site for gh-pages

@@
 
-\section{Methods}\label{methods}
+\section{Dataset, models, and methods}\label{dataset-models-and-methods}
 
-\begin{itemize}
-\tightlist
-\item
-  We use \citep{liuMagneticDiscontinuitiesSolar2022} method to identify IDs, which has better compatibility for the IDs with minor field changes.
-\item
-  Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features.
-\end{itemize}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1220}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0976}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1402}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1159}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1280}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.3963}}@{}}
+
+\caption{\label{tbl-missions}Missions info}
+
+\tabularnewline
+
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Mission
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\(\delta t_B\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\(\delta t_{plasma}\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Radial coverage
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Launch date
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+website
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Juno & 1 Hz & & 1 - 5.5 AU & 2011-08-05 00:00:00 &
+{[}`\href{https://science.nasa.gov/mission/juno}{NASA}'{]} \\
+ARTEMIS & 5 Hz, \ldots{} & & & 2007-02-17 00:00:00 & \\
+STEREO-A & 8 Hz & & & 2006-10-26 00:00:00 & \\
+WIND & 11 Hz & & & 1994-11-01 00:00:00 &
+{[}`\href{https://science.nasa.gov/mission/wind/}{NASA}'{]} \\
+Solar Orbiter & & & 0.28 - 0.9 AU & 2020-02-10 00:00:00 &
+{[}`\href{https://sci.esa.int/web/solar-orbiter}{ESA}'{]} \\
+Parker Solar Probe & & & 0.05 - 1 AU & 2018-08-12 00:00:00 &
+{[}`\href{https://science.nasa.gov/mission/parker-solar-probe}{NASA}'{]} \\
+
+\end{longtable}
+
+\textsubscript{Source: \href{https://Beforerr.github.io/ids_spatial_evolution_juno/notes.ipynb.html\#cell-tbl-missions}{Notes}}
+
+\subsection{Methods}\label{methods}
+
+We will use Liu's \citep{liu2022a} method to identify discontinuities in the solar wind.
+This method has better compatibility for the discontinuities with minor field changes, and is more robust to the situation encountered in the outer heliosphere.
+For each sampling instant \(t\), we define three intervals: the pre-interval \([-1,-1/2]\cdot T+t\), the middle interval \([-1/,1/2]\cdot T+t\), and the post-interval \([1/2,1]\cdot T+t\), in which \(T\) are time lags.
+Let time series of the magnetic field data in these three intervals are labeled \({\mathbf B}_-\), \({\mathbf B}_0\), \({\mathbf B}_+\), respectively.
+Then for an discontinuity, the following three conditions should be satisfied: (1) \(\sigma({\mathbf B}_0)>2\max\left(\sigma({\mathbf B}_-, \sigma({\mathbf B}_+)\right)\), (2) \(\sigma\left({\mathbf B}_-+{\mathbf B}_+\right)>\sigma({\mathbf B}_-)+\sigma({\mathbf B}_+)\), and (3) \(|\Delta {\mathbf B}|>|{\mathbf B}_{bg}|/10\), in which \(\sigma\) and \({\mathbf B}_{bg}\) represent the standard deviation and the background magnetic field magnitude, and \(\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)\).
+The first two conditions guarantee that the field changes of the discontinuity identified are large enough to be distinguished from the stochastic fluctuations on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition.
+We also will use the minimum or maximum variance analysis (MVA) analysis \citep{sonnerupMinimumMaximumVariance1998, sonnerupMagnetopauseStructureAttitude1967} to determine the main (most varying) magnetic field component, \(B_l\), and medium variation component, \(B_m\).
+Figure~\ref{fig-examples} shows several examples of solar wind discontinuities detected by different spacecraft.
 
@@
 
-\begin{minipage}{0.33\linewidth}
+\begin{minipage}{0.25\linewidth}
 \includegraphics{figures/examples/artemis_id_example.pdf}\end{minipage}%
 %
-\begin{minipage}{0.33\linewidth}
+\begin{minipage}{0.25\linewidth}
 \includegraphics{figures/examples/stereo_id_example.pdf}\end{minipage}%
 %
-\begin{minipage}{0.33\linewidth}
+\begin{minipage}{0.25\linewidth}
 \includegraphics{figures/examples/wind_id_example.pdf}\end{minipage}%
-
-\caption{\label{fig-examples}Examples of IDs from ARTEMIS, STEREO, and Wind}
+%
+\begin{minipage}{0.25\linewidth}
+Examples of IDs from ARTEMIS, STEREO, and Wind\end{minipage}%
 
@@
 
+\begin{figure*}
+
+\begin{minipage}{0.33\linewidth}
+\includegraphics{figures/thickness/thickness_k_dist.pdf}\end{minipage}%
+%
+\begin{minipage}{0.33\linewidth}
+\includegraphics{figures/thickness/thickness_k_N1_dist.pdf}\end{minipage}%
+%
+\begin{minipage}{0.33\linewidth}
+\includegraphics{figures/thickness/thickness_k_N1_r_dist.pdf}\end{minipage}%
+
+\end{figure*}%
+
+\begin{figure*}
+
+\begin{minipage}{0.50\linewidth}
+\includegraphics{figures/current/current_k_dist.pdf}\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+\includegraphics{figures/current/current_k_N1_dist.pdf}\end{minipage}%
+
+\end{figure*}%
+
 \begin{figure}

### 2024-02-05 article.qmd
update website

--- 2024-02-02 index.qmd
@@
 code-links:
+  - href: ../
+    text: Website
   - repo
@@
 Finally, we present the results of the spatial evolution of the discontinuities with respect to their characteristics (spatial scales and current density), and discuss the implications of our findings.
-
-::: {.content-visible when-format="html"}
-::: {.callout-note collapse="false"}
-## Related works
-
--   @sodingRadialLatitudinalDependencies2001 studied the radial distribution of discontinuities in the solar wind between 0.3 and 19 AU during solar activity minimum.
--   @liuCharacteristicsInterplanetaryDiscontinuities2021 studied the spatial evolution of the discontinuities from 0.13-0.9 AU, using measurements from the Parker Solar Probe.
-
-[Typical rate of occurrence is about 50 per day at 1AU]{.aside}
-
-::: {#fig-ids_distribution .column-page layout-ncol="2"}
-[![Discontinuities between 0.3 and 19 AU](images/söding2001_fig4.png){fig-alt="Distribution of DD per day over r with a bin size of 0.1 AU and the standard deviations as error bars on logarithmic scale; TS criterion at the top and B at the bottom; darker lines represent intervals in the ecliptic which are used for the given fit and lighter ones are out of the ecliptic; right Voyager 2 in detail on linear scale."}](https://www.researchgate.net/figure/Distribution-of-DD-per-day-over-r-with-a-bin-size-of-01-AU-and-the-standard-deviations_fig4_29624789)
-
-![Discontinuities between 0.13–0.9 AU](images/liu2021_fig2.png){fig-alt="Histograms as a function of heliocentric distance of (a) the number of events, (b) the PSP detection time, and (c)–(e) the occurrence rates of the total IDs, RDs and TDs.
-Panel (f) shows the ratio of RD occurrence rate to TD occurrence rate.
-The orange curves in panels (c) and (d) are the power-function fittings of ID and RD occurrence rates, with the coefficient of determination R2 being 0.983 and 0.985, respectively.
-The uncertainties of the power-law indices correspond to 95% confidence bounds."}
-
-Spatial distribution of the discontinuities
-:::
-:::
-:::
 
@@
 
+# Acknowledgements
+
+Sunspot data from the World Data Center SILSO, Royal Observatory of Belgium, Brussels
+
 # Figures

### 2024-02-05 index.qmd
update
update website

--- 2024-02-02 index.qmd
@@
 title: Solar wind discontinuities spatial evolution in the outer heliosphere
-author:
-  - name: Zijin Zhang
-    email: zijin@ucla.edu
-    orcid: 0000-0002-9968-067X
-    affiliation: University of California, Los Angeles
-    roles: writing
-    corresponding: true
-  - name: Anton V. Artemyev
-    email: aartemyev@igpp.ucla.edu
-    orcid: 0000-0001-8823-4474
-    affiliation: University of California, Los Angeles
-  - name: Vassilis Angelopoulos
-    orcid: 0000-0001-7024-1561
-    affiliation: University of California, Los Angeles
-  - name: Shi Chen
-    orcid: 0000-0002-2582-7085
-    affiliation: University of California, Los Angeles
-affiliations:
-  - id: ucla
-    name: University of California, Los Angeles
-execute: 
-  eval: false
-code-links:
-  - repo
-  - href: https://app.tana.inc?nodeid=Kmdzbyj-36NM
-    text: Tana
-  - href: https://www.overleaf.com/project/65b0a9c80a3616adf6e599e8
-    text: Overleaf
-abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
-We identify and analyze the properties of the discontinuities at different radial distances from the Sun.
-By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of IDs drops with the radial distance from the Sun, following a $1/r$ law; (2) The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases; (3) The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
 ---
 
-# Introduction
-
-Rapid variations in interplanetary magnetic fields, commonly recognized as solar wind magnetic discontinuities [@colburnDiscontinuitiesSolarWind1966], embody localized transient rotations or jumps of the magnetic field.
-Considered important for efficient plasma heating, they carry the most intense currents found in the solar wind and obserrved throughout the heliosphere from inner heliosphere [@liuCategorizingMHDDiscontinuities2022] to the heliosheath [@burlagaCurrentSheetsHeliosheath2011].
-Theoretical models [@lerchePropagationMagneticDisturbances1975; @medvedevDissipativeDynamicsCollisionless1997] and MHD simulations [@grecoIntermittentMHDStructures2008; @grecoStatisticalAnalysisDiscontinuities2009; @yangFormationRotationalDiscontinuities2015] suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence.
-These nonlinear processes can create significant isolated disturbances to the otherwise adiabatic evolution of the solar wind flow (?Reference?) and host many processes, including magnetic reconnection (?Reference?) and Fermi acceleration of particles [@wentzelMotionMagneticDiscontinuities1964].
-Moreover, they contribute significantly to the magnetic fluctuation spectra [@borovskyContributionStrongDiscontinuities2010] and can affect space weather [@tsurutaniReviewInterplanetaryDiscontinuities2011].
-Therefore, the study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind and test the local generation mechanism of discontinuities.
-However, previous study of solar wind discontinuities evolution [@sodingRadialLatitudinalDependencies2001] in the outer heliosphere were rarely in conjunction with measurements closer to the Sun.
-Moreover, the intervals in their study spread over multiple solar cycles though they are selected during solar activity minimum.
-Thus it is presently unclear whether their frequency and properties are the result of solar variability or due to the natural evolution of the discontinuities during their propagation and interaction with the ambient solar wind.
-
-The goal of our paper is to investigate, statistically, discontinuities at different radial distance in the outer heliosphere to obtain a understanding of their formation and evolution.
-Our methodology involves integrating Juno measurements [@connerneyJunoMagneticField2017] between $1$ and $5$ AU with those at $1$ AU to distinguish temporal effect and spatial variations by examining the discontinuity characteristics at two radial distances simultaneously.
-
-First, the missions, instruments and data used are listed.
-Then, we brieﬂy describe the method used to identify the discontinuities and the model used to estimate the plasma state at Juno location due to the lack of plasma data during its cruise phase.
-Finally, we present the results of the spatial evolution of the discontinuities with respect to their characteristics (spatial scales and current density), and discuss the implications of our findings.
-
-:::: {.content-visible when-format="html"}
 ::: {.callout-note collapse="false"}
-
 ## Related works
@@
 :::
-::::
-
-# Methods
-
-- We use [@liuMagneticDiscontinuitiesSolar2022] method to identify IDs, which has better compatibility for the IDs with minor field changes.
-- Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features.
-
-::: {#fig-examples .column-page layout-nrow="1"}
-
-![](figures/examples/artemis_id_example)
-
-![](figures/examples/stereo_id_example)
-
-![](figures/examples/wind_id_example)
-
-Examples of IDs from ARTEMIS, STEREO, and Wind
-
-:::
-
-:::: {.content-visible when-format="html"}
-::: {.callout-note collapse="false"}
-::: {#fig-ids_examples layout-ncol="2"}
-![Current sheets in the heliosheath: Voyager 1, 2009](images/jgra21162-fig-0009.png){fig-alt="Hodograms produced by means of a minimum variance analysis for the current sheets associated with the sector boundaries in Figures 8 and 10.
-(b, d, and f) The value of the component of B along the minimum variance direction (Bm) as a function of time, N.
-(a, c, and e) The components of B along the intermediate variance direction (Bi) and maximum variance direction (BM)."}
-
-![A rotational discontinuity (RD) detected at 0.126 AU](images/jgra57047-fig-0002-m.jpg){fig-alt="The properties of a rotational discontinuity (RD) detected at 0.126 AU on 28 January 2020.
-(a) The magnetic field magnitude and three components in Radial‐Tangential‐Normal (RTN) coordinate system, (b) the magnetic field in local magnetic normal (LMN) coordinate system, (c and d) the proton velocity in RTN and LMN coordinate systems, (e) the proton density, (f) the proton thermal pressure, the magnetic pressure and the sum, (g) the tangential components of the electric field in LMN coordinate system in the RD rest frame, (h) the position, orientation, and motion of the RD, (i–k) the distributions of BL, JM, and J · E across the RD, (l and m) the jump conditions across the RD.
-In (h), the cyan plane and arrow represent the RD and its motion vector, and the yellow curve shows the PSP orbit.
-In (j), both the colors and the curve correspond to the values of JM, and two vertical dashed lines indicate the area of $\vert {J}_{M}\vert > \frac{1}{3}\text{max}\left(\vert {J}_{M}\vert \right)$ whose width is defined as the half thickness of the discontinuity.
-In (m), the solid lines present the actual upstream and downstream velocities, while the dashed lines show the theoretical downstream velocity to satisfy the Walén relation."}
-
-Discontinuities examples across the heliosphere
-:::
-:::
-::::
-
-## ID identification (limited feature extraction / anomaly detection)
-
-Traditional methods for ID identiﬁcation, such as the criteria of
-
--   Burlaga & Ness (1969; B-criterion) : a directional change of the magnetic ﬁeld larger than 30° during 60 s
--   Tsurutani & Smith (1979; TS-criterion) : $|ΔB|/|B| \geq 0.5$ within 3 minutes
-
-Mostly rely on magnetic ﬁeld variations with a certain time lag. B-criterion has, as its main condition.
-
-In their methods, the IDs below the thresholds are artiﬁcially abandoned.
-Therefore, identiﬁcation criteria may affect the statistical results, and there is likely to be a discrepancy between the ﬁndings via B-criterion and TS- criterion.
-
-Liu's method : The first two conditions guarantee that the field changes of the IDs identiﬁed are large enough to be distinguished from the stochastic fluctuations on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition.
-
-$$ 
-\textrm{Index}_1 = \frac{\sigma(\vec{B})}{Max(\sigma(\vec{B}_-),\sigma(\vec{B}_+))} 
-$$
-
-$$
-\textrm{Index}_2 = \frac{\sigma(\vec{B}_- + \vec{B}_+)} {\sigma(\vec{B}_-) + \sigma(\vec{B}_+)}
-$$
-
-$$
-\textrm{Index}_3 = \frac{| \Delta \vec{B} |}{|B_{bg}|}
-$$
-
-$$ 
-\textrm{Index}_1 \ge 2, \textrm{Index}_2 \ge 1, \textrm{Index}_3 \ge 0.1 
-$$
-
-## Solar Wind Model
-
-Sadly, JUNO does not provide plasma data during the cruise phase, so to estimate the plasma state we will use MHD model.
-
-We are using [Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/), which models the solar wind propagation in 2D using the BATSRUS MHD solver.
-@keeblerMSWIM2DTwodimensionalOuter2022
-
-Some key points about the model
-
--   Representing the solar wind in the ecliptic plane from 1 to 75 AU
--   2D MHD model, using the BATSRUS MHD solver
--   Inclusion of neutral hydrogen (important for the outer heliosphere)
--   Inner boundary is filled by time-shifting in situ data from multiple spacecraft
-
-For model validation part, please see [JUNO Model Report](notebooks/20_model.ipynb).
-
-# Conclusion
-
--   We have collected 5 years of solar wind discontinuities from JUNO, aMIS and STEREO.
--   We have developed a pipeline to identify solar wind discontinuities. (Modular, Performant, Scalable)
--   The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
--   The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs decreases.
--   The current intensity of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current intensity of IDs increases.
-
-# Figures
-
-![Juno orbit](figures/juno_orbit_white){#fig-orbit}
-
-::: {#fig-examples .column-page layout-nrow="1"}
-
-![](figures/examples/artemis_id_example)
-
-![](figures/examples/stereo_id_example)
-
-![](figures/examples/wind_id_example)
-
-Examples of IDs from ARTEMIS, STEREO, and Wind
-
-:::
-
-![Near-Earth's solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview}
-
-Overview of the solar wind at 1 AU
-
-[For code, see [noteboook](notebooks/20_omni_overview.ipynb).]{.aside}
-
-![Model validation](figures/model/juno_model_validation_full){#fig-modelValidation}
-
-![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-tsEffect}

### 2024-02-06 article.qmd
update

@@
 
+::: {#fig-overview layout-ncol=1}
+![](figures/juno_orbit_white){}
+
+![](figures/juno-hg-loc_sunspot-number)
+
+Juno orbit, its longitudinal difference with Earth & STEREO missions and sunspot number during its cruise phase
+
+:::
+
 # Dataset, models, and methods
@@
 {{< embed notes.ipynb#tbl-missions >}}
+
+![Near-Earth's and STEREO-A solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview}
 
@@
 
-::: {#fig-examples .column-page layout-nrow="1"}
-![](figures/examples/artemis_id_example)
-
-![](figures/examples/stereo_id_example)
-
-![](figures/examples/wind_id_example)
-
-Examples of IDs from ARTEMIS, STEREO, and Wind
-:::
+![Examples of IDs from ARTEMIS, STEREO, and Wind](figures/fig_examples){#fig-examples}
 
@@
 
-![Juno orbit](figures/juno_orbit_white){#fig-orbit}
-
-::: {.column-page layout-nrow="1"}
-![](figures/examples/artemis_id_example)
-
-![](figures/examples/stereo_id_example)
-
-![](figures/examples/wind_id_example)
-
-Examples of IDs from ARTEMIS, STEREO, and Wind
-:::
-
-![Near-Earth's solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview}
-
 Overview of the solar wind at 1 AU

### 2024-02-06 notebooks/utils.py

@@ -54,22 +54,3 @@ class Config(BaseModel):
                 if not panel.get('timerange'):
                     panel['timerange'] = timerange
         return values
-
-class GraphicalConfig(BaseModel):
-    ylabel: str = None
-    
-
-
-def export(config: OutputConfig, tvars2plot):
-    path = config.path
-    if config.display:
-        tplot(tvars2plot)
-    if "png" in config.formats:
-        tplot(tvars2plot, save_png=path, display=False)
-    if "pdf" in config.formats:
-        tplot(tvars2plot, save_pdf=path, display=False)
-    if "svg" in config.formats:
-        tplot(tvars2plot, save_svg=path, display=False)
-    if "csv" in config.formats:
-        da: DataArray = get_data(tvars2plot, xarray=True)
-        da.to_pandas().to_csv(path + ".csv")

### 2024-02-06 article.qmd
update

@@
 
-![](figures/juno-hg-loc_sunspot-number)
+![](figures/juno-hg-loc_sunspot-number){#fig-hg-loc-sunspot}
 
@@
 
+## Dataset
+
+In this study we use datasets of four missions measuring solar wind magnetic field and plasma.
+Synergistic observations of these missions should advance our understanding of the solar wind discontinuities, their radial distribution and evolution [@velliUnderstandingOriginsHeliosphere2020].
+
 ![Near-Earth's and STEREO-A solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview}
+
+The solar wind plasma state, as evidenced by the sunspot number (referenced in @fig-hg-loc-sunspot and @fig-overview), plays a crucial role in understanding the dynamics of discontinuities.
+During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity.
+However, by the end of the mission's cruise phase, there was a significant decline in solar activity.
+This variation underscores the importance of calibrating the discontinuity properties in relation to solar activity levels to account for temporal fluctuations.
+
+Furthermore, an analysis of @fig-hg-loc-sunspot reveals the significance of the heliographic longitudinal difference between the Juno mission and Near-Earth missions (such as Wind and ARTEMIS) as well as STEREO-A missions.
+This longitudinal discrepancy ensures comprehensive coverage of the plasma en route to Juno.
+Specifically, when there is a substantial longitudinal difference between Juno and Earth, the difference between Juno and STEREO-A tends to be minimal, and vice versa.
+This relationship facilitates an extensive observation network for the plasma traveling towards Juno.
+
+June measurements do not include plasma characteristics, and to estimate discontinuity spatial scale (thicknesses) we will use solar wind speed obtained from the model of solar wind propagation.
+The hourly solar wind model data from the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keebler2022] will be employed to determine the ion bulk velocity $v$ and plasma density $n$ at the location of the Juno mission.
+Utilizing the BATSRUS MHD solver, this model is capable of simulating the propagation of the solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively encompassing the region of interest for our study.
+@fig-model shows comparison of magnetic field magnitudes obtained from MSWIM2D and measured by Juno.
+
+![Model validation](figures/model/juno_model_validation_full){#fig-model}
 
@@
 
-We will use Liu's [@liu2022a] method to identify discontinuities in the solar wind.
+We will use Liu's [@liuMagneticDiscontinuitiesSolar2022] method to identify discontinuities in the solar wind.
 This method has better compatibility for the discontinuities with minor field changes, and is more robust to the situation encountered in the outer heliosphere.
@@
 
-## Solar Wind Model
+# Results
 
-Sadly, JUNO does not provide plasma data during the cruise phase, so to estimate the plasma state we will use MHD model.
+The basic approach of this proposal is to use solar wind measurements at 1AU (STEREO, ARTEMIS, WIND) to compare with Juno and PSP measurements and distinguish effects of solar wind temporal variations and effects of spatial (with the radial distance from the Sun) variations of discontinuity occurrence rate and characteristics.
+The example of such comparison for the occurrence rate is shown in @fig-rate, where we plot number of discontinuities measured per day by different spacecraft missions (for the same temporal resolution of magnetic field data and the same criteria of discontinuity determination).
+The radial distance of Juno for 2011-2015 is shown in @fig-model, and the number of discontinuities measured by Juno per day coincides with the discontinuity number measured by STEREO, WIND, and ARTEMIS, when Juno is around $1$ AU.
+This number (occurrence rate) decreases with distance (with time after $\sim 2013$), as Juno moves from $1$ AU to $5$ AU.
+We will use the similar comparison for discontinuity characteristics and occurrence rate derived for PSP and Juno.
 
-We are using [Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/), which models the solar wind propagation in 2D using the BATSRUS MHD solver.
-@keeblerMSWIM2DTwodimensionalOuter2022
+::: {#fig-rate}
+![](figures/ocr/ocr_time_cleaned){width=45%}
 
-Some key points about the model
-
--   Representing the solar wind in the ecliptic plane from 1 to 75 AU
--   2D MHD model, using the BATSRUS MHD solver
--   Inclusion of neutral hydrogen (important for the outer heliosphere)
--   Inner boundary is filled by time-shifting in situ data from multiple spacecraft
-
-For model validation part, please see [JUNO Model Report](notebooks/20_model.ipynb).
+The number of discontinuities measured by Juno per day coincides with the discontinuity number measured by STEREO, WIND, and ARTEMIS, when Juno is around $1$ AU.
+This number (occurrence rate) decreases with distance (with time after $\sim 2013$), as Juno moves from $1$ AU to $5$ AU.
+We will use the similar comparison for discontinuity characteristics and occurrence rate derived for PSP and Juno.
+The radial distance of Juno for 2011-2015 is shown in @fig-model.
+:::
 
@@
 
--   We have collected 5 years of solar wind discontinuities from JUNO, aMIS and STEREO.
--   We have developed a pipeline to identify solar wind discontinuities. (Modular, Performant, Scalable)
+-   We have collected 5 years of solar wind discontinuities from JUNO, ARTEMIS and STEREO.
 -   The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
@@
 -   The current intensity of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current intensity of IDs increases.
+
+-   We have developed a pipeline to identify solar wind discontinuities. (Modular, Performant, Scalable)
 
@@
 
-# Figures
+# List of Figures
 
@@
 [For code, see [noteboook](notebooks/20_omni_overview.ipynb).]{.aside}
-
-![Model validation](figures/model/juno_model_validation_full){#fig-modelValidation}
 

### 2024-02-06 _manuscript/_tex/article.tex
Built site for gh-pages

--- 2024-02-02 _tex/index.tex
@@
 
+\begin{figure}
+
+\begin{minipage}{\linewidth}
+\includegraphics{figures/juno_orbit_white.pdf}\end{minipage}%
+\newline
+\begin{minipage}{\linewidth}
+\includegraphics{figures/juno-hg-loc_sunspot-number.pdf}\end{minipage}%
+
+\caption{\label{fig-overview}Juno orbit, its longitudinal difference with Earth \& STEREO missions and sunspot number during its cruise phase}
+
+\end{figure}%
+
 \section{Dataset, models, and methods}\label{dataset-models-and-methods}
@@
 
+\section{Acknowledgements}\label{acknowledgements}
+
+Sunspot data from the World Data Center SILSO, Royal Observatory of Belgium, Brussels
+
 \section{Figures}\label{figures}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{figures/juno_orbit_white.pdf}
-
-}
-
-\caption{\label{fig-orbit}Juno orbit}
-
-\end{figure}%
 
@@
 
-\begin{minipage}{0.25\linewidth}
+\begin{minipage}{\linewidth}
 \includegraphics{figures/examples/artemis_id_example.pdf}\end{minipage}%
-%
-\begin{minipage}{0.25\linewidth}
+\newline
+\begin{minipage}{\linewidth}
 \includegraphics{figures/examples/stereo_id_example.pdf}\end{minipage}%
-%
-\begin{minipage}{0.25\linewidth}
+\newline
+\begin{minipage}{\linewidth}
 \includegraphics{figures/examples/wind_id_example.pdf}\end{minipage}%
-%
-\begin{minipage}{0.25\linewidth}
+\newline
+\begin{minipage}{\linewidth}
 Examples of IDs from ARTEMIS, STEREO, and Wind\end{minipage}%

### 2024-02-08 index.qmd
update

@@
 
-::: {.callout-note collapse="false"}
+## Publications
+
+- manuscript please see [here](_manuscript/index.html)
+- AGU poster [here](presentations/AGU23_poster.qmd)
+
+## Updates
+
+::: {.column-screen layout-ncol="4"}
+![](figures/new/current/current_k_r_dist)
+
+![](figures/new/current/current_k_N1_r_dist)
+
+![](figures/new/thickness/thickness_k_r_dist)
+
+![](figures/new/thickness/thickness_k_N1_r_dist)
+
+New
+:::
+
+::: {.column-screen layout-ncol="4"}
+
+![](figures/current/current_r_dist)
+
+![](figures/current/current_N1_r_dist)
+
+![](figures/thickness/thickness_k_r_dist)
+
+![](figures/thickness/thickness_k_N1_r_dist)
+
+Old
+:::
+
+::: {.column-screen layout-nrow="1"}
+
+![Wind](figures/ts_method/wind)
+
+![Juno](figures/ts_method/juno)
+
+![Derivative method](figures/ts_method/derivative)
+
+![Fit method](figures/ts_method/fit)
+
+:::
+
+![](figures/ts_method/all)
+
+<!-- ::: {.column-screen layout-nrow="1"}
+
+![Effect of the time resolution on the discontinuity properties](figures/ts_effect_fit_new)
+
+![Effect of the time resolution on the discontinuity properties](figures/ts_effect)
+
+::: -->
+
 ## Related works
@@
 :::
-:::

### 2024-02-14 article.qmd
update

@@
 
-::: {#fig-overview layout-ncol=1}
-![](figures/juno_orbit_white){}
+:::: column-screen-inset
+::: {#fig-overview}
 
-![](figures/juno-hg-loc_sunspot-number){#fig-hg-loc-sunspot}
+<!-- ![](figures/juno_orbit_white){#fig-orbit width=85%} -->
 
-Juno orbit, its longitudinal difference with Earth & STEREO missions and sunspot number during its cruise phase
+<!-- ![](figures/juno-hg-loc_sunspot-number){#fig-hg-loc-sunspot} -->
+
+![](figures/fig_overview)
+
+Juno orbit, its longitudinal difference with Earth & STEREO missions, sunspot number during its cruise phase and near-Earth’s and STEREO-A solar wind plasma data during JUNO cruise phase
 
 :::
+::::
 
@@
 
-![Near-Earth's and STEREO-A solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview}
+<!-- ![Near-Earth's and STEREO-A solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview} -->
 

### 2024-02-15 article.qmd
refactor mission pipeline

@@
 
+# Plain Language Summary
+
+- **What I did:** I studied the solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
+I identified and analyzed the properties of the discontinuities at different radial distances from the Sun.
+I differentiated the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance).
+
+- **What I found:** The normalized occurrence rate of IDs drops with the radial distance from the Sun, following a $1/r$ law.
+The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases.
+The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
+
+- **What it means:** The results of this study provide a better understanding of the solar wind discontinuities in the outer heliosphere and their spatial evolution.
+This information is important for understanding the dynamics of the solar wind and testing the local generation mechanism of discontinuities.
+
 # Introduction
@@
 
-:::: column-screen-inset
 ::: {#fig-overview}
@@
 
-Juno orbit, its longitudinal difference with Earth & STEREO missions, sunspot number during its cruise phase and near-Earth’s and STEREO-A solar wind plasma data during JUNO cruise phase
+Overview.
+**a,** Juno orbit during its cruise phase (2011-206).
+**b,** Difference of heliographic longitude of Juno and 1-AU missions.
+**c,** monthly and smoothed sunspot number.
+**d-g,** Near-Earth (OMNI) and STEREO-A solar wind plasma density and speed.
 
 :::
-::::
 
 # Dataset, models, and methods
-
-{{< embed notes.ipynb#tbl-missions >}}
 
@@
 
-The solar wind plasma state, as evidenced by the sunspot number (referenced in @fig-hg-loc-sunspot and @fig-overview), plays a crucial role in understanding the dynamics of discontinuities.
+The solar wind plasma state, as evidenced by the sunspot number (referenced in @fig-overview), plays a crucial role in understanding the dynamics of discontinuities.
 During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity.
@@
 
-Furthermore, an analysis of @fig-hg-loc-sunspot reveals the significance of the heliographic longitudinal difference between the Juno mission and Near-Earth missions (such as Wind and ARTEMIS) as well as STEREO-A missions.
+Furthermore, an analysis of @fig-overview reveals the significance of the heliographic longitudinal difference between the Juno mission and Near-Earth missions (such as Wind and ARTEMIS) as well as STEREO-A missions.
 This longitudinal discrepancy ensures comprehensive coverage of the plasma en route to Juno.
@@
 
+The time resolution of the magnetic field and plasma data for Juno, Wind, ARTEMIS, STEREO is summarized in the table below.
+
+{{< embed notes.ipynb#tbl-missions >}}
+
+## Model
+
 June measurements do not include plasma characteristics, and to estimate discontinuity spatial scale (thicknesses) we will use solar wind speed obtained from the model of solar wind propagation.
-The hourly solar wind model data from the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keebler2022] will be employed to determine the ion bulk velocity $v$ and plasma density $n$ at the location of the Juno mission.
+The hourly solar wind model data from the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] will be employed to determine the ion bulk velocity $v$ and plasma density $n$ at the location of the Juno mission.
 Utilizing the BATSRUS MHD solver, this model is capable of simulating the propagation of the solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively encompassing the region of interest for our study.
@@
 
-![Model validation](figures/model/juno_model_validation_full){#fig-model}
+The model time resolution is hourly. After averaging Juno data to the same time resolution, we see that the model data is consistent with the Juno magnetic field data.
+
+::: {#fig-model}
+
+![](figures/model/juno_model_validation_full)
+
+**a,** Magnetic field magnitude from MSWIM2D and Juno. **b-c,** Plasma speed and density from MSWIM2D model. **d,** Juno radial distance from the Sun.
+:::
 
@@
 
-We will use Liu's [@liuMagneticDiscontinuitiesSolar2022] method to identify discontinuities in the solar wind.
+We use Liu's [@liuMagneticDiscontinuitiesSolar2022] method to identify discontinuities in the solar wind.
 This method has better compatibility for the discontinuities with minor field changes, and is more robust to the situation encountered in the outer heliosphere.
@@
 Let time series of the magnetic field data in these three intervals are labeled ${\mathbf B}_-$, ${\mathbf B}_0$, ${\mathbf B}_+$, respectively.
-Then for an discontinuity, the following three conditions should be satisfied: (1) $\sigma({\mathbf B}_0)>2\max\left(\sigma({\mathbf B}_-, \sigma({\mathbf B}_+)\right)$, (2) $\sigma\left({\mathbf B}_-+{\mathbf B}_+\right)>\sigma({\mathbf B}_-)+\sigma({\mathbf B}_+)$, and (3) $|\Delta {\mathbf B}|>|{\mathbf B}_{bg}|/10$, in which $\sigma$ and ${\mathbf B}_{bg}$ represent the standard deviation and the background magnetic field magnitude, and $\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)$.
-The first two conditions guarantee that the field changes of the discontinuity identified are large enough to be distinguished from the stochastic fluctuations on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition.
-We also will use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to determine the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$.
+Then for an discontinuity, the following three conditions should be satisfied: (1) $\sigma({\mathbf B}_0) > 2\max\left(\sigma({\mathbf B}_-), \sigma({\mathbf B}_+)\right)$, (2) $\sigma\left({\mathbf B}_-+{\mathbf B}_+\right)>\sigma({\mathbf B}_-)+\sigma({\mathbf B}_+)$, and (3) $|\Delta {\mathbf B}|>|{\mathbf B}_{bg}|/10$, in which $\sigma$ and ${\mathbf B}_{bg}$ represent the standard deviation and the background magnetic field magnitude, and $\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)$.
+The first two conditions guarantee that the field changes of the discontinuity identified are large enough to be distinguished from the stochastic fluctuations or Alfven waves on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition.
+
+Then for each discontinuity identified, we calculate the distance matrix of the time series sequence (distance between each pair of magnetic field vectors) to determine the leading edge and trailing edge of the discontinuity.
+After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to get the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$.
+The maxium variance direction is then fitted by a step-like functions to extract the parameters to properly describe the discontinuity (we used logistic function here).
+Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.
+
+$$
+B(t; A, \mu, \sigma, {\mathrm{form=logistic}}) = A \left[1 - \frac{1}{1 + e^{\alpha}} \right]
+$$
+
+where $\alpha = (t - \mu)/{\sigma}$.
+
 @fig-examples shows several examples of solar wind discontinuities detected by different spacecraft.
@@
 
-::: {.content-visible when-format="html"}
-::: {.callout-note collapse="false"}
-::: {#fig-ids_examples layout-ncol="2"}
-![Current sheets in the heliosheath: Voyager 1, 2009](images/jgra21162-fig-0009.png){fig-alt="Hodograms produced by means of a minimum variance analysis for the current sheets associated with the sector boundaries in Figures 8 and 10.
-(b, d, and f) The value of the component of B along the minimum variance direction (Bm) as a function of time, N.
-(a, c, and e) The components of B along the intermediate variance direction (Bi) and maximum variance direction (BM)."}
-
-![A rotational discontinuity (RD) detected at 0.126 AU](images/jgra57047-fig-0002-m.jpg){fig-alt="The properties of a rotational discontinuity (RD) detected at 0.126 AU on 28 January 2020.
-(a) The magnetic field magnitude and three components in Radial‐Tangential‐Normal (RTN) coordinate system, (b) the magnetic field in local magnetic normal (LMN) coordinate system, (c and d) the proton velocity in RTN and LMN coordinate systems, (e) the proton density, (f) the proton thermal pressure, the magnetic pressure and the sum, (g) the tangential components of the electric field in LMN coordinate system in the RD rest frame, (h) the position, orientation, and motion of the RD, (i–k) the distributions of BL, JM, and J · E across the RD, (l and m) the jump conditions across the RD.
-In (h), the cyan plane and arrow represent the RD and its motion vector, and the yellow curve shows the PSP orbit.
-In (j), both the colors and the curve correspond to the values of JM, and two vertical dashed lines indicate the area of $\\vert {J}_{M}\\vert > \\frac{1}{3}\\text{max}\\left(\\vert {J}_{M}\\vert \\right)$ whose width is defined as the half thickness of the discontinuity.
-In (m), the solid lines present the actual upstream and downstream velocities, while the dashed lines show the theoretical downstream velocity to satisfy the Walén relation."}
-
-Discontinuities examples across the heliosphere
-:::
-:::
-:::
-
-## ID identification (limited feature extraction / anomaly detection)
-
-Traditional methods for ID identiﬁcation, such as the criteria of
-
--   Burlaga & Ness (1969; B-criterion) : a directional change of the magnetic ﬁeld larger than 30° during 60 s
--   Tsurutani & Smith (1979; TS-criterion) : $|ΔB|/|B| \geq 0.5$ within 3 minutes
-
-Mostly rely on magnetic ﬁeld variations with a certain time lag. B-criterion has, as its main condition.
-
-In their methods, the IDs below the thresholds are artiﬁcially abandoned.
-Therefore, identiﬁcation criteria may affect the statistical results, and there is likely to be a discrepancy between the ﬁndings via B-criterion and TS- criterion.
-
-Liu's method : The first two conditions guarantee that the field changes of the IDs identiﬁed are large enough to be distinguished from the stochastic fluctuations on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition.
-
-$$ 
-\textrm{Index}_1 = \frac{\sigma(\vec{B})}{Max(\sigma(\vec{B}_-),\sigma(\vec{B}_+))} 
-$$
-
-$$
-\textrm{Index}_2 = \frac{\sigma(\vec{B}_- + \vec{B}_+)} {\sigma(\vec{B}_-) + \sigma(\vec{B}_+)}
-$$
-
-$$
-\textrm{Index}_3 = \frac{| \Delta \vec{B} |}{|B_{bg}|}
-$$
-
-$$ 
-\textrm{Index}_1 \ge 2, \textrm{Index}_2 \ge 1, \textrm{Index}_3 \ge 0.1 
-$$
-
 # Results
 
-The basic approach of this proposal is to use solar wind measurements at 1AU (STEREO, ARTEMIS, WIND) to compare with Juno and PSP measurements and distinguish effects of solar wind temporal variations and effects of spatial (with the radial distance from the Sun) variations of discontinuity occurrence rate and characteristics.
+<!-- The basic approach of this proposal is to use solar wind measurements at 1AU (STEREO, ARTEMIS, WIND) to compare with Juno and PSP measurements and distinguish effects of solar wind temporal variations and effects of spatial (with the radial distance from the Sun) variations of discontinuity occurrence rate and characteristics.
 The example of such comparison for the occurrence rate is shown in @fig-rate, where we plot number of discontinuities measured per day by different spacecraft missions (for the same temporal resolution of magnetic field data and the same criteria of discontinuity determination).
@@
 We will use the similar comparison for discontinuity characteristics and occurrence rate derived for PSP and Juno.
+-->
 
-::: {#fig-rate}
-![](figures/ocr/ocr_time_cleaned){width=45%}
+## Occurrence rate
+
+The occurrence rate of IDs is investigated with regards of the radial distance from the Sun.
+
+Note the quantity of IDs per day is corrected with respect to data gap and the time the mission spent in the pristine solar wind. 
+ARTEMIS spacecrafts will only be exposed in the solar wind for a relative short time during its orbits around the Moon and the Moon would be in the magnetosphere for a long time as it orbits the earth.
+(The data is obtained from OMNIWEB, link: [omniweb.gsfc.nasa.gov/ftpbrowser/themis_b_sw.txt](https://omniweb.gsfc.nasa.gov/ftpbrowser/themis_b_sw.txt))
+
+The rate of occurrence depends linearly on the solar wind velocity [@sodingRadialLatitudinalDependencies2001], however the plasma velocity data in Juno mission is not available during its cruise phase.
+Therefore, we do not normalize the occurrence rate with respect to the solar wind speed.
+This influence of the solar wind speed on the occurrence rate might be mitigated by the fact all the spacecrafts are in the ecliptic plane, and the solar wind speed is not expected to change significantly with the radial distance from the Sun beyond $1$ AU.
+So the decrease of the occurrence rate with the radial distance from the Sun is expected to be a real effect of the radial distance from the Sun.
+
+::: {#fig-rate layout-nrow="1"}
+
+![](figures/ocr/ocr_time_cleaned)
+
+![](figures/ocr/ocr_r_N2_cleaned)
 
@@
 We will use the similar comparison for discontinuity characteristics and occurrence rate derived for PSP and Juno.
-The radial distance of Juno for 2011-2015 is shown in @fig-model.
+The radial distance of Juno for 2011-2016 is shown in @fig-model.
 :::
 
-# Conclusion
+## Thickness
 
--   We have collected 5 years of solar wind discontinuities from JUNO, ARTEMIS and STEREO.
--   The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
--   The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs decreases.
--   The current intensity of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current intensity of IDs increases.
+The thickness $d$ of a discontinuity is determined by
 
--   We have developed a pipeline to identify solar wind discontinuities. (Modular, Performant, Scalable)
+$$
+d = (v \cdot n) \Delta T
+$$
+
+with $v = v_{sw} - v_{s/c} + U$ , where $\Delta T$ is the transition time (a factor of the $sigma$ used in fitting) , $v_{sw}$ is the solar wind velocity.
+The velocity of the spacecraft $v_{s/c}$ and the propagation speed of the discontinuities $U$ are negligible in our case.
+
+The transition time $\Delta T$ is determined in one second resolution data for all our missions to reduce the system error.
+(Note that highest time resolution of the data is not needed for the transition time determination by fitting method, see discussion in the appendix).
+
+::: {#fig-thickness layout-nrow="1"}
+![](figures/new/thickness/thickness_k_fit_r_dist)
+
+![](figures/new/thickness/thickness_k_fit_N1_r_dist)
+
+**a,** Thickness of IDs as a function of the radial distance from the Sun. **b,** Thickness of IDs normalized to the ion inertial length as a function of the radial distance from the Sun. 
+:::
+
+## Current density
+
+The peak current density $J_m$ of a discontinuity is determined by
+
+$$
+J_m = - \frac{1}{\mu_0 V_n} \frac{d B_m}{d t},
+$$
+
+where $\mu_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
+
+::: {#fig-current layout-nrow="1"}
+![](figures/new/current/current_k_r_dist)
+
+![](figures/new/current/current_k_N1_r_dist)
+
+**a,** Current density of IDs as a function of the radial distance from the Sun. **b,** Current density of IDs normalized to the Alfven current as a function of the radial distance from the Sun.
+:::
+
+# Summary and discussion
+
+We have collected 5 years of solar wind discontinuities from JUNO, ARTEMIS and STEREO.
+
+## Occurrence rate
+The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
+
+## Thickness
+
+The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs decreases.
+
+## Current density
+
+The current density of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current density of IDs increases.
 
@@
 
-Sunspot data from the World Data Center SILSO, Royal Observatory of Belgium, Brussels
+Sunspot data from the World Data Center SILSO, Royal Observatory of Belgium, Brussels. ARTEMIS solar wind time interval data from the OMNI database.
 
 # List of Figures
-
-Overview of the solar wind at 1 AU
-
-[For code, see [noteboook](notebooks/20_omni_overview.ipynb).]{.aside}
 
@@
 
+# Appendix
+
 ![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-tsEffect}

### 2024-02-15 index.qmd
update
refactor mission pipeline

@@
 ## Updates
+
+::: {.column-screen layout-nrow="1"}
+
+![](figures/new/thickness/thickness_k_fit_r_dist)
+
+![](figures/new/thickness/thickness_k_fit_N1_r_dist)
+
+New Fit Width
+:::
 
@@
 
-::: {.column-screen layout-nrow="1"}
+::: {.column-screen layout-ncol="4"}
 
@@
 
-:::
+![](figures/ts_method/wind_fit)
 
 ![](figures/ts_method/all)
+
+:::
 
@@
 :::
+
+::: {.content-visible when-format="html"}
+::: {.callout-note collapse="false"}
+::: {#fig-ids_examples layout-ncol="2"}
+![Current sheets in the heliosheath: Voyager 1, 2009](images/jgra21162-fig-0009.png){fig-alt="Hodograms produced by means of a minimum variance analysis for the current sheets associated with the sector boundaries in Figures 8 and 10.
+(b, d, and f) The value of the component of B along the minimum variance direction (Bm) as a function of time, N.
+(a, c, and e) The components of B along the intermediate variance direction (Bi) and maximum variance direction (BM)."}
+
+![A rotational discontinuity (RD) detected at 0.126 AU](images/jgra57047-fig-0002-m.jpg){fig-alt="The properties of a rotational discontinuity (RD) detected at 0.126 AU on 28 January 2020.
+(a) The magnetic field magnitude and three components in Radial‐Tangential‐Normal (RTN) coordinate system, (b) the magnetic field in local magnetic normal (LMN) coordinate system, (c and d) the proton velocity in RTN and LMN coordinate systems, (e) the proton density, (f) the proton thermal pressure, the magnetic pressure and the sum, (g) the tangential components of the electric field in LMN coordinate system in the RD rest frame, (h) the position, orientation, and motion of the RD, (i–k) the distributions of BL, JM, and J · E across the RD, (l and m) the jump conditions across the RD.
+In (h), the cyan plane and arrow represent the RD and its motion vector, and the yellow curve shows the PSP orbit.
+In (j), both the colors and the curve correspond to the values of JM, and two vertical dashed lines indicate the area of $\\vert {J}_{M}\\vert > \\frac{1}{3}\\text{max}\\left(\\vert {J}_{M}\\vert \\right)$ whose width is defined as the half thickness of the discontinuity.
+In (m), the solid lines present the actual upstream and downstream velocities, while the dashed lines show the theoretical downstream velocity to satisfy the Walén relation."}
+
+Discontinuities examples across the heliosphere
+:::
+:::
+:::

### 2024-02-15 notebooks/_missions/index.qmd
refactor mission pipeline

---
title: Missions
---

This module includes helpful functions for working with mission (magnetic field and plasma) data. We currently support the following missions:

- [Parker Solar Probe](psp/index.qmd)
- [Juno](juno/index.ipynb)
- [Wind](wind/index.ipynb)
- [THEMIS/ARTEMIS](themis/index.ipynb)
- [STEREO](stereo/index.ipynb)

Note: `speasy` and `pyspedas` are not suitable for processing large datasets, although they are useful for downloading and processing small datasets.

- `speasy` cache file and data are not persistent
- `pyspedas` loads the entire dataset into memory

### 2024-02-15 notebooks/utils.py

@@ -1,56 +1,49 @@
-from pydantic import constr, BaseModel, root_validator
-from datetime import datetime, date
-from pytplot import tplot, get_data
+def get_and_process_data(
+    mag_dataset, mag_parameters, plasma_dataset, plasma_parameters, timerange, tau, ts,
+    provider = 'archive/local'
+):
+    # define variables
+    mag_vars = Variables(
+        provider = provider,
+        dataset=mag_dataset,
+        parameters=mag_parameters,
+        timerange=timerange,
+    ).retrieve_data()
 
-from xarray import DataArray
+    plasma_vars = Variables(
+        provider = provider,
+        dataset=plasma_dataset,
+        parameters=plasma_parameters,
+        timerange=timerange,
+    ).retrieve_data()
 
-class TplotConfig(BaseModel):
-    tvar: str = None
-    trans: list[str] = None
-    
-class ProcessConfig(BaseModel):
-    tvar: str = None
-    trans: list[str] = list()
+    # get column names
+    bcols = mag_vars.data[0].columns
+    density_col = plasma_vars.data[0].columns[0]
+    vec_cols = plasma_vars.data[1].columns
+    temperature_col = plasma_vars.data[2].columns[0]
 
+    # get data
+    mag_data = mag_vars.to_polars()
+    plasma_data = (
+        plasma_vars.to_polars()
+        .with_columns(plasma_speed=pl_norm(vec_cols))
+        .rename({density_col: "plasma_density"})
+    )
+    # process temperature data
+    if plasma_vars.data[2].unit == "km/s":
+        plasma_data = plasma_data.pipe(df_thermal_spd2temp, temperature_col)
+    else:
+        plasma_data = plasma_data.rename({temperature_col: "plasma_temperature"})
 
-class PanelConfig(BaseModel):
-
-    timerange: list[datetime | date] = None
-    
-    id: str = None
-    name: str = None
-    units: str = None
-    
-    satellite: constr(to_lower=True)
-    instrument: constr(to_lower=True)
-    datatype: str = None
-    probe: str = None
-    
-    process: ProcessConfig = None
-    tplot: TplotConfig = None
-
-
-class OutputConfig(BaseModel):
-    path : str = None
-    filename: str = None
-    
-    formats: list[str] = list()
-    display: bool = False
-
-
-class Config(BaseModel):
-    panels: list[PanelConfig]
-    timerange: list[datetime | date] = None
-    output: OutputConfig = None
-    backend: str = None
-    
-    @root_validator(pre=True)
[…]

### 2024-02-16 notebooks/utils.R
refactor mission

@@ -51,7 +51,10 @@ calculate_summary <- function(data, x_col, y_col, x_seq) {
 }
 
 
-plot_binned_data <- function(data, x_col, y_col, x_bins, y_bins, y_lim = NULL, log_y = FALSE) {
+plot_binned_data <- function(
+    data, x_col, y_col, x_bins, y_bins,
+    y_lim = NULL, log_y = FALSE,
+    add_mode = TRUE, add_mean = TRUE, add_sd = TRUE) {
   # If y_lim is provided, filter the data
   if (!is.null(y_lim)) {
     data <- data %>%
@@ -83,12 +86,14 @@ plot_binned_data <- function(data, x_col, y_col, x_bins, y_bins, y_lim = NULL, l
     geom_tile(data = data_binned_normalized, aes(x = .data[[x_col]], y = .data[[y_col]], fill = n))
 
   # Calculate mode for each x-bin
-  modes <- data_binned_normalized %>%
-    group_by(.data[[x_col]]) %>%
-    slice_max(n, n = 1)
+  if (add_mode) {
+    modes <- data_binned_normalized %>%
+      group_by(.data[[x_col]]) %>%
+      slice_max(n, n = 1)
 
-  # Add the mode line
-  plot <- plot + geom_line(data = modes, aes(x = .data[[x_col]], y = .data[[y_col]], group = 1), linetype = "dashed")
+    # Add the mode line
+    plot <- plot + geom_line(data = modes, aes(x = .data[[x_col]], y = .data[[y_col]], group = 1), linetype = "dashed")
+  }
 
   data_xbinned <- calculate_summary(data, x_col, y_col, x_seq)
 
@@ -101,8 +106,7 @@ plot_binned_data <- function(data, x_col, y_col, x_bins, y_bins, y_lim = NULL, l
   plot +
     scale_fill_viridis_c() +
     theme_pubr(base_size = 16, legend = "r") +
-    coord_cartesian(ylim = y_lim) +
-    guides(fill = guide_colourbar(title = "p"))
+    coord_cartesian(ylim = y_lim)
 }
 
 
@@ -111,13 +115,15 @@ plot_dist <- function(
     y, ylab, y_lim = NULL, y_log = TRUE,
     x_bins = 8,
     y_bins = 16,
+    df1 = JNO_events_l1,
+    df2 = other_events_l1,
     p1title = "Juno",
[…]

### 2024-02-19 index.qmd
update
feat: high ts Juno processing

@@
 ## Updates
+
+### 02/19/2024
+
+{{< embed notebooks/04_properties.ipynb#fig-jno-8hz-tau-20-der >}}
+
+### 02/18/2024
+
+![](figures/new/duration/duration_dist_ts_comparison)
+
+#### Thickness
+::: {.column-screen layout-nrow="1"}
+![](figures/new/thickness/thickness_k_dist)
+
+![](figures/new/thickness/thickness_k_dist-8hz)
+
+![](figures/new/thickness/thickness_k_dist-8hz-tau_20)
+:::
+
+#### Current Density
+
+::: {.column-screen layout-nrow="1"}
+![](figures/new/current/current_k_dist)
+
+![](figures/new/current/current_k_dist-8hz)
+
+![](figures/new/current/current_k_dist-8hz-tau_20)
+
+:::
+
+### 02/17/2024
+
+::: {.column-screen layout-nrow="1"}
+
+![](figures/new/duration/duration_dist)
+
+![](figures/new/thickness/thickness_k_fit_dist)
+
+![](figures/new/current/current_k_dist)
+:::
 

### 2024-02-19 notebooks/utils.R

@@ -9,7 +9,12 @@ if (!requireNamespace("ggmagnify", quietly = TRUE)) {
   pak::pkg_install("hughjonesd/ggmagnify")
 }
 
+if (!requireNamespace("curry", quietly = TRUE)) {
+  pak::pkg_install("curry")
+}
+
 library(dplyr)
+library(purrr)
 
 library(ggplot2)
 library(ggdensity)
@@ -30,6 +35,26 @@ save_plot <- function(filename = NULL) {
   }
 }
 
+# partial that change default argument of function
+# see https://community.rstudio.com/t/how-to-change-default-argument-of-function-so-that-it-can-be-specified-again-when-use/79919 # nolint
+partial2 <- function(func, recursive = FALSE, ...) {
+  cl <- as.call(c(list(quote(func)), list(...)))
+  cl <- match.call(func,cl)
+  args <- as.list(cl)[-1]
+
+  function(...) {
+    new_cl <- as.call(c(list(quote(func)), list(...)))
+    new_cl <- match.call(func,new_cl)
+    new_args <- as.list(new_cl)[-1]
+    if (recursive) {
+      new_args <- modifyList(args, new_args, keep.null = TRUE)
+    }  else {
+      keep_args <- setdiff(names(args), names(new_args))
+      new_args <- c(args[keep_args], new_args)
+    }
+    do.call(func, new_args)
+  }
+}
 
 # Plotting function for Level 1 data.
 # Similar to the `geom_bin2d` function, but with added functionality
@@ -41,28 +66,34 @@ library(scales)
 # Helper function to calculate summary statistics for x-binned data
 calculate_summary <- function(data, x_col, y_col, x_seq) {
   data %>%
-    mutate(!!x_col := x_seq[findInterval(data[[x_col]], x_seq, rightmost.closed = TRUE)]) %>%
+    mutate(!!x_col := x_seq[
+      findInterval(data[[x_col]], x_seq, rightmost.closed = TRUE)
+    ]) %>%
     group_by(.data[[x_col]]) %>%
     summarise(
       mean_y = mean(.data[[y_col]], na.rm = TRUE),
[…]

### 2024-02-19 notebooks/utils/__init__.py

@@ -1,0 +1,43 @@
+import polars as pl
+from beforerr.polars import pl_norm
+
+PARAMETERS = ['j0_k', 'j0_k_norm',  'L_k', 'L_k_norm']
+
+def load_events(
+    name: str,
+    ts: float,
+    tau: float,
+    method="derivative",
+    format="arrow",
+    parameters=PARAMETERS,
+) -> pl.DataFrame:
+
+    data_dir = "../data"
+
+    match format:
+        case "arrow":
+            load_func = pl.scan_ipc
+        case "parquet":
+            load_func = pl.scan_parquet
+
+    if method == "derivative":
+        filepath = f"{data_dir}/05_reporting/events.{name}.derivative.ts_{ts:.2f}s_tau_{tau}s.{format}"
+    elif method == "fit":
+        filepath = (
+            f"{data_dir}/05_reporting/events.{name}.ts_{ts:.2f}s_tau_{tau}s.{format}"
+        )
+
+    df = load_func(filepath)
+    return (
+        df.drop_nulls()
+        .with_columns(
+            pl.col(parameters).abs(),
+            sat=pl.lit(name),
+            ts=pl.lit(f"{ts}s"),
+            method=pl.lit(method),
+            ts_method=pl.lit(f"{ts}s {method}"),
+            label=pl.lit(f"{name} {ts}s {method}"),
+            index_d_diff=pl_norm("dB_x", "dB_y", "dB_z") / pl.col("b_mag"),
+        )
+        .collect()
+    )

### 2024-03-15 index.qmd
update

@@
 ## Updates
+
+### 02/27/2024
+
+::: {.column-screen}
+::: {#fig-evolution-juno layout-nrow="1"}
+![Evolution of plamsa property using fitting method](figures/l_j_r_fit.png)
+
+![Evolution of plamsa property using derivative method](figures/l_j_r_der.png)
+
+From top to bottom is Juno observation in 1,2,3,4,5 AU
+:::
+:::
+
+### 02/26/2024
+
+::: {.column-screen layout-nrow="1"}
+{{< embed notebooks/06_corr_julia.ipynb#fig-l-comp >}}
+:::
+
+::: {.column-screen layout-nrow="1"}
+{{< embed notebooks/06_corr_julia.ipynb#fig-l-j-r-der >}}
+:::
+
+::: {.column-screen layout-nrow="1"}
+{{< embed notebooks/06_corr_julia.ipynb#fig-l-r-fit >}}
+
+{{< embed notebooks/06_corr_julia.ipynb#fig-l-r-der >}}
+:::
+
+### 02/25/2024
+
+::: {.column-screen layout-nrow="1"}
+{{< embed notebooks/05_sea.ipynb#fig-fit >}}
+
+{{< embed notebooks/05_sea.ipynb#fig-fit-params >}}
+:::
+
+### 02/22/2024
+
+::: {.column-screen layout-nrow="1"}
+![First Year](figures/sea/sea_juno_first_year_high.png)
+
+![Last Year](figures/sea/sea_juno_last_year_high.png)
+:::
+
+### 02/20/2024
 

### 2024-03-15 notebooks/ids_example.py

@@ -1,0 +1,32 @@
+# Examples of discontinuities (publication plot)
+
+# %%
+import sys
+import yaml
+
+from space_analysis.ds.tplot import Config, export, process_panel
+
+import matplotlib.pyplot as plt
+import scienceplots
+
+plt.style.use(["science", "nature", "notebook"])
+plt.rc("savefig", dpi=300)
+plt.rc('figure.subplot', wspace = 0, hspace = 0)
+
+# %%
+file_path = sys.argv[1]
+
+# %%
+config = yaml.load(open(file_path), Loader=yaml.FullLoader)
+config = Config(**config)
+tvars2plot = []
+
+# %%
+for p_config in config.panels:
+    tvar2plot = process_panel(p_config)
+    tvars2plot.append(tvar2plot)
+
+# %%
+export(tvars2plot, config)
+
+

### 2024-03-15 notebooks/utils.R

@@ -13,6 +13,10 @@ if (!requireNamespace("curry", quietly = TRUE)) {
   pak::pkg_install("curry")
 }
 
+if (!requireNamespace("egg", quietly = TRUE)) {
+  pak::pkg_install("egg")
+}
+
 library(dplyr)
 library(purrr)
 
@@ -20,6 +24,7 @@ library(ggplot2)
 library(ggdensity)
 library(ggpubr)
 library(patchwork)
+library(egg)
 library(see)
 
 library(glue)
@@ -28,10 +33,10 @@ library(gaussplotR)
 library(scales)
 
 # Save the plot, if filename is provided
-save_plot <- function(filename = NULL) {
+save_plot <- function(filename, ...) {
   if (!is.null(filename)) {
-    ggsave(filename = glue("../figures/{filename}.png"))
-    ggsave(filename = glue("../figures/{filename}.pdf"))
+    ggsave(filename = glue("../figures/{filename}.png"), ...)
+    ggsave(filename = glue("../figures/{filename}.pdf"), ...)
   }
 }
 
@@ -159,11 +164,18 @@ plot_binned_data <- function(
 }
 
 ## Common labels
-ylab_j_log <- expression(Log ~ J ~ (nA ~ m^-2))
-ylab_j_norm_log <- expression(Log ~ Normalized ~ J ~ (J[A]))
-ylab_l <- "Log Thickness (km)"
-ylab_l_norm <- expression(Log ~ Thickness ~ (d[i]))
+
+lab_j <- expression("Current Density " (nA ~ m^-2))
+lab_j_norm <- expression(Normalized ~ Current ~ Density ~ (J[A]))
+lab_l <- "Thickness (km)"
+lab_l_norm <- expression("Normalized Thickness " (d[i]))
 xlab_r <- "Radial Distance (AU)"
+
+
+lab_j_log <- expression(Log ~ J ~ (nA ~ m^-2))
+lab_j_norm_log <- expression(Log ~ Normalized ~ J ~ (J[A]))
+lab_l_log <- glue("Log {lab_l}")
+lab_l_norm_log <- expression(Log ~ Normalized ~ Thickness ~ (d[i]))
 
 ## Plotting function for quantity and normalized quantity
 
[…]

### 2024-03-15 notebooks/utils.jl

@@ -1,0 +1,65 @@
+using Printf
+
+function load(path::String)
+    df = path |> Arrow.Table |> DataFrame |> dropmissing
+    
+    # if 'radial_distance' is in the dataframe, round it
+    if "radial_distance" in names(df)
+        df = @chain df begin
+            @transform :r = string.(round.(Int, :radial_distance))
+        end
+    end
+
+    df = @chain df begin
+        @transform(
+            :j0_k = abs.(:j0_k),
+            :j0_k_norm = abs.(:j0_k_norm),
+        )
+    end
+
+    # Iterate through each column in the DataFrame
+    filter(row -> all(x -> !(x isa Number && isnan(x)), row), df)
+end
+
+function load(;tau = 60, ts = 1.00, name = "JNO", method = "fit", dir = "../data/05_reporting")
+    ts_str = @sprintf "ts_%.2fs" ts
+    df = load(joinpath(dir, "events.$name.$method.$(ts_str)_tau_$(tau)s.arrow"))
+    df.tau .= tau
+    df.ts .= ts
+    df
+end
+
+# %%
+# Define the labels for the plots
+r_lab = L"Radial Distance ($AU$)"
+j_lab = L"Current Density ($nA/m^2$)"
+l_lab = L"Thickness ($km$)"
+
+l_norm_lab = L"Normalized Thickness ($d_i$)"
+j_norm_lab = L"Normalized Current Density ($J_A$)"
+
+di_lab = L"Ion Inertial Length ($km$)"
+jA_lab = L"Alfvénic Current Density ($nA/m^2$)"
+
+# %%
+# Define the mappings
+di_map = :ion_inertial_length => di_lab
+di_log_map = :ion_inertial_length => log10 => L"Log %$di_lab"
+
+jA_map = :j_Alfven => jA_lab
+jA_log_map = :j_Alfven => log10 => L"Log %$jA_lab"
+
+l_map = :L_k => l_lab
+l_norm_map = :L_k_norm => l_norm_lab
+l_log_map = :L_k => log10 => L"Log %$l_lab"
+l_norm_log_map = :L_k_norm => log10 => L"Log %$l_norm_lab"
+
+
+current_map = :j0_k => j_lab
+current_norm_map = :j0_k_norm => j_norm_lab
+
+
+j_map = :j0_k => j_lab
+j_norm_map = :j0_k_norm => j_norm_lab
[…]

### 2024-03-15 notebooks/utils/__init__.py

@@ -1,7 +1,12 @@
 import polars as pl
 from beforerr.polars import pl_norm
 
-PARAMETERS = ['j0_k', 'j0_k_norm',  'L_k', 'L_k_norm']
+data_dir = "../data"
+
+PARAMETERS = ['j0_k', 'j0_k_norm',  'L_k', 'L_k_norm']    
+
+def keep_good_fit(df: pl.DataFrame, rsquared = 0.95):
+    return df.filter(pl.col('fit.stat.rsquared') > rsquared)
 
 def load_events(
     name: str,

### 2024-03-15 notebooks/utils/config.py

@@ -1,0 +1,157 @@
+from pydantic import Field
+import polars as pl
+
+from datetime import timedelta, datetime
+
+from space_analysis.ds.meta import Meta, PlasmaMeta
+from discontinuitypy.datasets import IDsDataset
+from discontinuitypy.config import IDsConfig as IDsConfigBase
+from discontinuitypy.config import SpeasyIDsConfig as SpeasyIDsConfigBase
+
+from .juno import get_mag_paths
+from math import ceil
+from pathlib import Path
+
+
+def _split_list(lst, n):
+    step = ceil(len(lst) / n)
+    for i in range(0, len(lst), step):
+        yield lst[i : i + step]
+
+
+def split_list(lst, n):
+    return list(_split_list(lst, n))
+
+
+def standardize_plasma_data(data: pl.LazyFrame, meta: PlasmaMeta):
+    """
+    Standardize plasma data columns across different datasets.
+    
+    Notes: meta will be updated with the new column names
+    """
+
+    if meta.density_col:
+        data = data.rename({meta.density_col: "plasma_density"})
+        meta.density_col = "plasma_density"
+    return data
+
+
+class IDsConfig(IDsConfigBase):
+    tau: timedelta = timedelta(seconds=60)
+    ts: timedelta = timedelta(seconds=1)
+    timerange: list[datetime] = Field(
+        ["2011-08-25", "2016-06-30"], validate_default=True
+    )
+    
+    _data_dir = Path("../data/05_reporting")
+
+    split: int = 8
+
+
+class JunoConfig(IDsConfig):
+    name: str = "JNO"
+
+    plasma_meta: PlasmaMeta = PlasmaMeta(
+        density_col="plasma_density", velocity_cols=["v_x", "v_y", "v_z"]
+    )
+
+    _sparse_num = 10
+    _plasma_df_path = "../data/03_primary/JNO_STATE_ts_3600s.parquet"
+
+    def model_post_init(self, __context):
+        self.plasma_data = pl.scan_parquet(self._plasma_df_path).sort("time")
+        self.data = self.mag_df
+
+    @property
+    def mag_df(self):
+        """Magnetic field data in a single dataframe"""
+        return pl.scan_ipc(self.mag_paths).sort("time").unique("time")
+
+    @property
+    def mag_dfs(self):
+        s_paths = split_list(self.mag_paths, self.split)
[…]

### 2024-03-15 notebooks/utils/juno.py

@@ -1,0 +1,48 @@
+from space_analysis.missions.juno.fgm import download_data
+from discontinuitypy.utils.basic import resample
+from pipe import select
+from fastcore.utils import mkdir
+import os
+import polars as pl
+from intake.source.utils import reverse_formats
+from datetime import datetime
+from . import data_dir
+from datetime import timedelta
+
+
+def preprocess(
+    fp,
+    every=timedelta(seconds=0.125),
+    dir_path=f"{data_dir}/02_intermediate/JNO_MAG_8hz",
+    update=False,
+):
+    fname = fp.split("/")[-1]
+
+    output_path = f"{dir_path}/{fname}"
+
+    if not os.path.exists(output_path) or update:
+        mkdir(dir_path, parents=True, exist_ok=True)
+        df = pl.scan_ipc(fp).sort("time").pipe(resample, every=every)
+        df.collect().write_ipc(output_path)
+    return output_path
+
+
+def get_mag_paths(
+    timerange: list[datetime],
+    freq: float,
+):
+    if freq == 1:
+        files = download_data()
+        url_pattern = "fgm_jno_l3_{date:%Y%j}se_r1s_v01.arrow"
+    if freq == 8:
+        files = list(download_data(datatype="FULL") | select(preprocess))
+        url_pattern = "fgm_jno_l3_{date:%Y%j}se_v01.arrow"
+
+    dates = reverse_formats(url_pattern, [file.split("/")[-1] for file in files]).get(
+        "date"
+    )
+
+    start = timerange[0].replace(tzinfo=None)
+    end = timerange[1].replace(tzinfo=None)
+    # filter by timerange
+    return [file for file, date in zip(files, dates) if date >= start and date <= end]

### 2024-03-16 index.qmd
update

@@
 ## Updates
+
+### 03/15/2024
+
+![Discontinuities in log-log scale](figures/l_j_fit_xscale_log)
+
+![Same as above but with multiple time resolutions and time windows](figures/l_j_r_fit_xscale_log)
 
@@
 ::: {.column-screen layout-nrow="1"}
-{{< embed notebooks/06_corr_julia.ipynb#fig-l-comp >}}
+{{< embed notebooks/01_results_julia.ipynb#fig-l-comp >}}
 :::
@@
 ::: {.column-screen layout-nrow="1"}
-{{< embed notebooks/06_corr_julia.ipynb#fig-l-j-r-der >}}
+{{< embed notebooks/01_results_julia.ipynb#fig-l-j-r-der >}}
 :::
@@
 ::: {.column-screen layout-nrow="1"}
-{{< embed notebooks/06_corr_julia.ipynb#fig-l-r-fit >}}
-
-{{< embed notebooks/06_corr_julia.ipynb#fig-l-r-der >}}
+{{< embed notebooks/01_results_julia.ipynb#fig-l-r-fit >}}
 :::
@@
 ::: {.column-screen layout-nrow="1"}
-{{< embed notebooks/05_sea.ipynb#fig-fit >}}
+{{< embed notebooks/archive/05_sea.ipynb#fig-fit >}}
 
-{{< embed notebooks/05_sea.ipynb#fig-fit-params >}}
+{{< embed notebooks/archive/05_sea.ipynb#fig-fit-params >}}
 :::

### 2024-05-13 index.qmd
chore: Update publication section and remove unnecessary files

--- 2024-02-19 index.qmd
@@
 
-## Publications
+# Publications
 
@@
 
-## Updates
+# Introduction
 
-### 02/19/2024
+Juno Orbit
 
-{{< embed notebooks/04_properties.ipynb#fig-jno-8hz-tau-20-der >}}
+- Five-year cruise to Jupiter from 2011 to 2016
+- One earth flyby in 2013
+- Nearly the same Heliographic latitude as Earth
 
-### 02/18/2024
+## Motivations
 
-![](figures/new/duration/duration_dist_ts_comparison)
+Studying the radial distribution of occurrence rate, as well as the properties of solar wind discontinuities may help answer the following questions:
 
-#### Thickness
-::: {.column-screen layout-nrow="1"}
-![](figures/new/thickness/thickness_k_dist)
+- How does the discontinuities change with the radial distance from the Sun?
 
-![](figures/new/thickness/thickness_k_dist-8hz)
+- How is solar wind discontinuities formed? What is the physical mechanisms?
 
-![](figures/new/thickness/thickness_k_dist-8hz-tau_20)
-:::
+  - Generated at or near the sun?
 
-#### Current Density
+  - Locally generated in the interplanetary space by turbulence?
 
-::: {.column-screen layout-nrow="1"}
-![](figures/new/current/current_k_dist)
+Joint observations of JUNO & ARTEMIS & Other missions really provides a unique opportunity!!!
 
-![](figures/new/current/current_k_dist-8hz)
+![](https://www.nasa.gov/wp-content/uploads/2023/03/575573main_Juno20110727-3-43_full.jpg)
 
-![](figures/new/current/current_k_dist-8hz-tau_20)
+{{< video https://www.youtube.com/watch?v=sYp5p2oL51g title='Juno spacecraft trajectory animation' >}}
 
-:::
+To eliminate the effect of the solar wind structure, we use data from other missions (mainly at 1AU) to provide a way of normalization.
 
-### 02/17/2024
+# Results
 
-::: {.column-screen layout-nrow="1"}
+# Related works
 
-![](figures/new/duration/duration_dist)
-
-![](figures/new/thickness/thickness_k_fit_dist)
-
-![](figures/new/current/current_k_dist)
-:::
-
-::: {.column-screen layout-nrow="1"}
-
-![](figures/new/thickness/thickness_k_fit_r_dist)
-
-![](figures/new/thickness/thickness_k_fit_N1_r_dist)
-
-New Fit Width
-:::
-
-::: {.column-screen layout-ncol="4"}
-![](figures/new/current/current_k_r_dist)
-
-![](figures/new/current/current_k_N1_r_dist)
-
-![](figures/new/thickness/thickness_k_r_dist)
-
-![](figures/new/thickness/thickness_k_N1_r_dist)
-
-New
-:::
-
-::: {.column-screen layout-ncol="4"}
-
-![](figures/current/current_r_dist)
-
-![](figures/current/current_N1_r_dist)
-
-![](figures/thickness/thickness_k_r_dist)
-
-![](figures/thickness/thickness_k_N1_r_dist)
-
-Old
-:::
-
-::: {.column-screen layout-ncol="4"}
-
-![Wind](figures/ts_method/wind)
-
-![Juno](figures/ts_method/juno)
-
-![Derivative method](figures/ts_method/derivative)
-
-![Fit method](figures/ts_method/fit)
-
-![](figures/ts_method/wind_fit)
-
-![](figures/ts_method/all)
-
-:::
-
-<!-- ::: {.column-screen layout-nrow="1"}
-
-![Effect of the time resolution on the discontinuity properties](figures/ts_effect_fit_new)
-
-![Effect of the time resolution on the discontinuity properties](figures/ts_effect)
-
-::: -->
-
-## Related works
-
+- Radial distribution
     -   @sodingRadialLatitudinalDependencies2001 studied the radial distribution of discontinuities in the solar wind between 0.3 and 19 AU during solar activity minimum.
     -   @liuCharacteristicsInterplanetaryDiscontinuities2021 studied the spatial evolution of the discontinuities from 0.13-0.9 AU, using measurements from the Parker Solar Probe.
+- Properties
+    -   @vaskoKineticscaleCurrentSheets2022
 

### 2024-05-13 notes.qmd
chore: Update publication section and remove unnecessary files

## Updates

### 03/15/2024

![Discontinuities in log-log scale](figures/l_j_fit_xscale_log)

![Same as above but with multiple time resolutions and time windows](figures/l_j_r_fit_xscale_log)

### 02/27/2024

::: {.column-screen}
::: {#fig-evolution-juno layout-nrow="1"}
![Evolution of plamsa property using fitting method](figures/l_j_r_fit.png)

![Evolution of plamsa property using derivative method](figures/l_j_r_der.png)

From top to bottom is Juno observation in 1,2,3,4,5 AU
:::
:::

### 02/26/2024

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/01_results_julia.ipynb#fig-l-comp >}}
:::

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/01_results_julia.ipynb#fig-l-j-r-der >}}
:::

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/01_results_julia.ipynb#fig-l-r-fit >}}
:::

### 02/25/2024

::: {.column-screen layout-nrow="1"}
{{< embed notebooks/archive/05_sea.ipynb#fig-fit >}}

{{< embed notebooks/archive/05_sea.ipynb#fig-fit-params >}}
:::

### 02/22/2024

::: {.column-screen layout-nrow="1"}
![First Year](figures/sea/sea_juno_first_year_high.png)

![Last Year](figures/sea/sea_juno_last_year_high.png)
:::

### 02/20/2024

### 02/19/2024

{{< embed notebooks/04_properties.ipynb#fig-jno-8hz-tau-20-der >}}

### 02/18/2024

![](figures/new/duration/duration_dist_ts_comparison)

#### Thickness
::: {.column-screen layout-nrow="1"}
![](figures/new/thickness/thickness_k_dist)

![](figures/new/thickness/thickness_k_dist-8hz)

![](figures/new/thickness/thickness_k_dist-8hz-tau_20)
:::

#### Current Density

::: {.column-screen layout-nrow="1"}
![](figures/new/current/current_k_dist)

![](figures/new/current/current_k_dist-8hz)

![](figures/new/current/current_k_dist-8hz-tau_20)

:::

### 02/17/2024

::: {.column-screen layout-nrow="1"}

![](figures/new/duration/duration_dist)

![](figures/new/thickness/thickness_k_fit_dist)

![](figures/new/current/current_k_dist)
:::

::: {.column-screen layout-nrow="1"}

![](figures/new/thickness/thickness_k_fit_r_dist)

![](figures/new/thickness/thickness_k_fit_N1_r_dist)

New Fit Width
:::

::: {.column-screen layout-ncol="4"}
![](figures/new/current/current_k_r_dist)

![](figures/new/current/current_k_N1_r_dist)

![](figures/new/thickness/thickness_k_r_dist)

![](figures/new/thickness/thickness_k_N1_r_dist)

New
:::

::: {.column-screen layout-ncol="4"}

![](figures/current/current_r_dist)

![](figures/current/current_N1_r_dist)

![](figures/thickness/thickness_k_r_dist)

![](figures/thickness/thickness_k_N1_r_dist)

Old
:::

::: {.column-screen layout-ncol="4"}

![Wind](figures/ts_method/wind)

![Juno](figures/ts_method/juno)

![Derivative method](figures/ts_method/derivative)

![Fit method](figures/ts_method/fit)

![](figures/ts_method/wind_fit)

![](figures/ts_method/all)

:::

<!-- ::: {.column-screen layout-nrow="1"}

![Effect of the time resolution on the discontinuity properties](figures/ts_effect_fit_new)

![Effect of the time resolution on the discontinuity properties](figures/ts_effect)

::: -->

### 2024-05-13 presentations/rMeeting.qmd
chore: Update publication section and remove unnecessary files

---
title: "Current Sheets in the Solar Wind: JUNO Observations in the Outer Heliosphere"
subtitle: SPARTHB
author:
  - name: Zijin Zhang
  - name: Anton V. Artemyev
  - name: Vassilis Angelopoulos
format:
  html: default
  pptx: default
slide-number: true
---

<!-- 
See [share notes](../../beforerr/docs/research/topics/swd/index.qmd) for
- introduction
- formation mechanisms
-->

# References

### 2024-05-13 article.qmd
update

@@
 
+Because the discontinuities may have different spatial scale at different radial distances from the Sun, we repeat the search procedure with time lags $T = 10, 20, 30, 40, 50, 60$ s, and combine the identified ID events together to establish the event list.
+Discontinuities with spatial scales larger than $60$ s are not considered in this study, however it could be argued that they are not significant in the outer heliosphere if they follow the trend with decreasing number of IDs with increasing spatial scale.
+@fig-ljFit also indicates that the spatial scale of IDs does not vary significantly with the radial distance from the Sun.
+
+Then for each discontinuity identified, we calculate the distance matrix of the time series sequence (distance between each pair of magnetic field vectors) to determine the leading edge and trailing edge of the discontinuity.
+After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to get the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$.
+The maxium variance direction is then fitted by a step-like functions to extract the parameters to properly describe the discontinuity (we used logistic function here).
+Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.
+
+> To cover IDs at different spatial scales, we repeat the search procedure with time lags T = 10, 20, 30, 40, 50, 60s, and combine the identiﬁed ID events together to establish the event list.
+
 Then for each discontinuity identified, we calculate the distance matrix of the time series sequence (distance between each pair of magnetic field vectors) to determine the leading edge and trailing edge of the discontinuity.
@@
 -->
+
+![](figures/l_j_fit)
+
+![](figures/l_j_fit_xscale_log.png){#fig-ljFit}
 
@@
 
+In @vaskoKineticscaleCurrentSheets2022 paper, CS thickness is estimated by the formula $d = \frac{\Delta B_l}{2 \mu_0 < J_m> }$.
+Because of @eq-j, $d = \frac{\Delta B_l}{2 \mu_0 < J_m> } = \frac{\Delta B_l V_n }{2 <\frac{d B_m}{ d t} >}$
+
 The transition time $\Delta T$ is determined in one second resolution data for all our missions to reduce the system error.
@@
 J_m = - \frac{1}{\mu_0 V_n} \frac{d B_m}{d t},
-$$
+$$ {#eq-j}
 
@@
 
+![](figures/l_j_fit_taus)
+
+![](figures/l_j_fit_taus_xscale_log)
+
 # Acknowledgements

### 2024-05-13 notebooks/utils.jl
update

@@ -1,41 +1,3 @@
-using Printf
-
-function load(path::String)
-    df = path |> Arrow.Table |> DataFrame |> dropmissing
-    
-    # if 'radial_distance' is in the dataframe, round it
-    if "radial_distance" in names(df)
-        df = @chain df begin
-            @transform :r = string.(round.(Int, :radial_distance))
-        end
-    end
-
-    df = @chain df begin
-        @transform(
-            :j0_k = abs.(:j0_k),
-            :j0_k_norm = abs.(:j0_k_norm),
-        )
-        
-    end
-
-    # Iterate through each column in the DataFrame
-    filter(row -> all(x -> !(x isa Number && isnan(x)), row), df)
-end
-
-function load(;tau = 60, ts = 1.00, name = "JNO", method = "fit", dir = "../data/05_reporting")
-    ts_str = @sprintf "ts_%.2fs" ts
-    df = load(joinpath(dir, "events.$name.$method.$(ts_str)_tau_$(tau)s.arrow"))
-    df.tau .= tau
-    df.ts .= ts
-    
-    if method == "fit"
-        df = @chain df begin
-            filter(:"fit.stat.rsquared" => >(0.95), _)
-        end
-    end
-    df
-end
-
 # %%
 # Define the labels for the plots
 r_lab = L"Radial Distance ($AU$)"

### 2024-05-13 notebooks/utils/io.jl

@@ -1,0 +1,48 @@
+using Printf
+using Arrow
+
+data_path = "$(@__DIR__)/../../data/05_reporting"
+
+function load(path::String)
+    df = path |> Arrow.Table |> DataFrame |> dropmissing
+    
+    # if 'radial_distance' is in the dataframe, round it
+    if "radial_distance" in names(df)
+        df = @chain df begin
+            @transform :r = string.(round.(Int, :radial_distance))
+        end
+    end
+
+    df = @chain df begin
+        @transform(
+            :j0_k = abs.(:j0_k),
+            :j0_k_norm = abs.(:j0_k_norm),
+        )
+        
+    end
+
+    # Iterate through each column in the DataFrame
+    filter(row -> all(x -> !(x isa Number && isnan(x)), row), df)
+end
+
+function load(;tau = 60, ts = 1.00, name = "JNO", method = "fit", dir = data_path)
+    ts_str = @sprintf "ts_%.2fs" ts
+    df = load(joinpath(dir, "events.$name.$method.$(ts_str)_tau_$(tau)s.arrow"))
+    df.tau .= tau
+    df.ts .= ts
+    
+    if method == "fit"
+        df = @chain df begin
+            filter(:"fit.stat.rsquared" => >(0.95), _)
+        end
+    end
+    df
+end
+
+
+function load_tau(tau)
+    df = load(tau=tau)
+    df.label .= "$tau s"
+    println("Number of events: ", size(df, 1))
+    df
+end

### 2024-05-13 notebooks/utils/plot.jl

@@ -1,0 +1,13 @@
+using AlgebraOfGraphics,
+    CairoMakie
+using DataFrames,
+    DataFramesMeta,
+    CategoricalArrays
+
+using Statistics
+using LinearAlgebra
+using beforerr
+using LaTeXStrings
+using PartialFunctions
+
+set_aog_theme!()

### 2024-05-13 notes.qmd
update figure

@@
 
+<!-- 
 ### 02/26/2024
@@
 ::: 
+-->
 
@@
 
-{{< embed notebooks/04_properties.ipynb#fig-jno-8hz-tau-20-der >}}
+<!-- {{< embed notebooks/04_properties.ipynb#fig-jno-8hz-tau-20-der >}} -->
 
@@
 
-<!-- ::: {.column-screen layout-nrow="1"}
-
+<!-- 
+::: {.column-screen layout-nrow="1"}
 ![Effect of the time resolution on the discontinuity properties](figures/ts_effect_fit_new)
@@
 ![Effect of the time resolution on the discontinuity properties](figures/ts_effect)
-
-::: -->
+:::
+-->

### 2024-05-13 presentations/rMeeting.qmd
update
update figure

@@
 
-# References
+## Motivation
+
+Studying the radial evolution of solar wind discontinuities from observations of PSP (0.1 AU – 1 AU) and JUNO (1AU – 5AU) with Earth-orbiting missions (ARTEMIS, Wind) during aligned intervals.
+
+## Methods
+
+![Time resolution effect](../figures/method/time_res_effect.png)
+
+![Tau effect](../figures/method/tau_effect.png)
+
+## References

### 2024-05-15 notebooks/utils/config.py
chore: Remove unnecessary files and update notebooks

@@ -7,6 +7,7 @@ from space_analysis.ds.meta import Meta, PlasmaMeta
 from discontinuitypy.datasets import IDsDataset
 from discontinuitypy.config import IDsConfig as IDsConfigBase
 from discontinuitypy.config import SpeasyIDsConfig as SpeasyIDsConfigBase
+from discontinuitypy.missions import WindMeta
 
 from .juno import get_mag_paths
 from math import ceil
@@ -26,7 +27,7 @@ def split_list(lst, n):
 def standardize_plasma_data(data: pl.LazyFrame, meta: PlasmaMeta):
     """
     Standardize plasma data columns across different datasets.
-    
+
     Notes: meta will be updated with the new column names
     """
 
@@ -36,17 +37,20 @@ def standardize_plasma_data(data: pl.LazyFrame, meta: PlasmaMeta):
     return data
 
 
+tau: timedelta = timedelta(seconds=60)
+timerange: list[datetime] = Field(["2011-08-25", "2016-06-30"], validate_default=True)
+
 class IDsConfig(IDsConfigBase):
     tau: timedelta = timedelta(seconds=60)
-    ts: timedelta = timedelta(seconds=1)
-    timerange: list[datetime] = Field(
-        ["2011-08-25", "2016-06-30"], validate_default=True
-    )
-    
+    # ts: timedelta = timedelta(seconds=1)
+    timerange: list[datetime] = timerange
+
     _data_dir = Path("../data/05_reporting")
 
     split: int = 8
 
+class SpeasyIDsConfig(IDsConfig, SpeasyIDsConfigBase):
+    pass
 
 class JunoConfig(IDsConfig):
     name: str = "JNO"
@@ -91,31 +95,25 @@ class JunoConfig(IDsConfig):
             ).update_candidates_with_plasma_data().events
 
 
-class SpeasyIDsConfig(IDsConfig, SpeasyIDsConfigBase):
-    # timerange: list[datetime] = Field(
-    #     ["2011-08-25", "2012-01-01"], validate_default=True
-    # )
+class WindConfig(WindMeta, SpeasyIDsConfig):
     pass
+    
 
-class WindConfig(SpeasyIDsConfig):
-    name: str = "Wind"
+    # mag_meta: Meta = Meta(
+    #     provider="archive/local",
+    #     dataset="WI_H4-RTN_MFI",
+    #     parameters=["BRTN"],
+    # )
 
[…]

### 2024-05-16 notebooks/utils/config.py
refactoring...

@@ -8,6 +8,7 @@ from discontinuitypy.datasets import IDsDataset
 from discontinuitypy.config import IDsConfig as IDsConfigBase
 from discontinuitypy.config import SpeasyIDsConfig as SpeasyIDsConfigBase
 from discontinuitypy.missions import WindMeta
+from discontinuitypy.missions import wind_mag_h4_rtn_meta, wind_plasma_k0_swe_meta
 
 from .juno import get_mag_paths
 from math import ceil
@@ -40,17 +41,24 @@ def standardize_plasma_data(data: pl.LazyFrame, meta: PlasmaMeta):
 tau: timedelta = timedelta(seconds=60)
 timerange: list[datetime] = Field(["2011-08-25", "2016-06-30"], validate_default=True)
 
+
 class IDsConfig(IDsConfigBase):
     tau: timedelta = timedelta(seconds=60)
     # ts: timedelta = timedelta(seconds=1)
     timerange: list[datetime] = timerange
 
-    _data_dir = Path("../data/05_reporting")
+    split: int = 16
+    test: bool = False
 
-    split: int = 8
+    def model_post_init(self, __context):
+        if self.test:
+            self.timerange = [datetime(2012, 1, 1), datetime(2012, 1, 2)]
+        super().model_post_init(__context)
+
 
 class SpeasyIDsConfig(IDsConfig, SpeasyIDsConfigBase):
     pass
+
 
 class JunoConfig(IDsConfig):
     name: str = "JNO"
@@ -96,24 +104,10 @@ class JunoConfig(IDsConfig):
 
 
 class WindConfig(WindMeta, SpeasyIDsConfig):
-    pass
-    
-
-    # mag_meta: Meta = Meta(
-    #     provider="archive/local",
-    #     dataset="WI_H4-RTN_MFI",
-    #     parameters=["BRTN"],
-    # )
-
-    # plasma_meta: PlasmaMeta = PlasmaMeta(
-    #     provider="archive/local",
-    #     dataset="WI_K0_SWE",
-    #     parameters=[
-    #         "Np",
-    #         "V_GSM",
-    #     ],
-    #     # TODO: is GSM close to RTN coordinates???
-    # )
+    provider: str = "archive/local"
+    mag_meta: Meta = wind_mag_h4_rtn_meta
+    plasma_meta: PlasmaMeta = wind_plasma_k0_swe_meta
+    split: int = 32
 
 
 class StereoConfig(IDsConfig):

### 2024-05-22 article.qmd
update figure
chore: Update notebooks, remove unnecessary files

@@
   - repo
-  - href: https://app.tana.inc?nodeid=Kmdzbyj-36NM
-    text: Tana
   - href: https://www.overleaf.com/project/65b0a9c80a3616adf6e599e8
     text: Overleaf
+
 abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
@@
 
-<!-- ![](figures/juno_orbit_white){#fig-orbit width=85%} -->
-
-<!-- ![](figures/juno-hg-loc_sunspot-number){#fig-hg-loc-sunspot} -->
-
 ![](figures/fig_overview)
@@
 
+<!-- 
 {{< embed notes.ipynb#tbl-missions >}}
+ -->
 

### 2024-05-22 index.qmd
update
update figure
chore: Update notebooks, remove unnecessary files

@@
 title: Solar wind discontinuities spatial evolution in the outer heliosphere
+code-links:
+  - href: zotero://select/library/collections/WS2YQQZB
+    text: Zotero
+  - href: https://app.tana.inc?nodeid=Kmdzbyj-36NM
+    text: Tana
 ---
@@
 
+# Dataset, models, and methods
+
 # Results
+
+## Occurrence rate
+
+![](figures/ocr/ocr_time_cleaned)
+
+## Properties
+
+![](figures/l_j_fit_xscale_log.png)
+
+# Appendix
+
+![Time resolution effect](figures/method/time_res_effect.png)
+
+![Tau effect](figures/method/tau_effect.png)
 

### 2024-05-24 notes.qmd
chore: Update dependencies and remove unnecessary files

@@
+---
+title: Notes
+jupyter: python3
+---
+
 ## Updates
@@
 
+## Solar Wind Model
+
+Sadly, JUNO does not provide plasma data during the cruise phase, so to estimate the plasma state we will use MHD model.
+
+We are using [Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/), which models the solar wind propagation in 2D using the BATSRUS MHD solver.
+@keeblerMSWIM2DTwodimensionalOuter2022
+
+Some key points about the model
+
+-   Representing the solar wind in the ecliptic plane from 1 to 75 AU
+-   2D MHD model, using the BATSRUS MHD solver
+-   Inclusion of neutral hydrogen (important for the outer heliosphere)
+-   Inner boundary is filled by time-shifting in situ data from multiple spacecraft
+
+For model validation part, please see [JUNO Model Report](notebooks/20_model.ipynb).
+
 <!-- 
@@
 -->
+
+# TODOs
+
+Science part
+
+-   Analysis
+    -   [ ] Contribution of discontinuities to the power spectrum
+    -   [ ] Check Datagap
+    -   [ ] Check `ARTEMIS-B` data in different states (solar wind, magnetosheath, magnetotail, moon wake)
+    -   [ ] Distribution of \|B\| over radius
+    -   [ ] JUNO from 2012-09\~2012-10 lack of IDS and extreme large thickness
+    -   [ ] Wind data
+    -   [ ] Add error bar
+    -   [ ] Validate the effects of calibrate candidate duration
+    -   [ ] Validate model density with `Voyager`
+-   Identifaction
+    -   [ ] Ensemble forest?
+    -   [ ] Smoothing is important?
+    -   [ ] Check change point algorithm
+-   Visualize data gaps
+-   Features
+    -   [ ] Thickness in N direction
+    -   [ ] Use high resolution data for feature extraction
+-   Compare with other methods of identifying IDs
+    -   [ ] Verify with other methods of identifying IDs
+-   [x] Incorporate solar wind propagation model
+    -   [x] Verify with solar wind propagation model
+        -   [x] Coordinate transformation
+
+## Infos
+
+```{python}
+# | label: tbl-missions
+# | tbl-cap: Missions info
+import yaml
+import polars as pl
+from functools import reduce
+from great_tables import GT
+
+with open("data/info.yml", "r") as file:
+    data = yaml.safe_load(file)
+
+# Recursive function to find magnetometers
+def find_instrument(instruments, ins_type):
+    instrument = {}
+    for key, value in instruments.items():
+        if value.get("type") == ins_type:
+            instrument = value
+        elif "instruments" in value:
+            instrument = find_instrument(value["instruments"], ins_type)
+    return instrument
+
+def parse_yaml(data, info, ins_type=None):
+    rows = []
+
+    for mission, details in data["missions"].items():
+        if ins_type is None:
+            rows.append([mission, details.get(info)])
+            continue
+        instruments = details.get("instruments", {})
+        instrument = find_instrument(instruments, ins_type)
+        rows.append([mission, instrument.get(info)])
+
+    return pl.DataFrame(rows, schema=["Mission", info])
+
+# Define the merge function
+def merge_dfs(left: pl.DataFrame, right, on="Mission", how="outer_coalesce"):
+    return left.join(right, on=on, how=how)
+
+# Parse and display the table
+df_mag = parse_yaml(data, "time_resolutions", "magnetometer").rename(
+    {"time_resolutions": "δt(B)"}
+)
+df_plasma = parse_yaml(data, "time_resolutions", "plasma").rename(
+    {"time_resolutions": "δt(plasma)"}
+)
+df_r = parse_yaml(data, "radial_coverage")
+df_time = parse_yaml(data, "launch_date")
+df_link = parse_yaml(data, "website")
+
+df_list = [df_mag, df_plasma, df_r, df_time, df_link]  # Replace with your DataFrames
+
+df_merged = reduce(merge_dfs, df_list).with_columns(pl.col("website").list.join(", "))
+
+GT(df_merged.to_pandas()).fmt_markdown("website").cols_label(
+    radial_coverage="Radial coverage",
+    launch_date="Launch date",
+)
+```

### 2024-05-25 article.qmd
chore: Update dependencies and remove unnecessary files
writing paper...

@@
     text: Overleaf
-
 abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
@@
 
-<!-- 
-{{< embed notes.ipynb#tbl-missions >}}
- -->
-
 ## Model
@@
 
-Then for each discontinuity identified, we calculate the distance matrix of the time series sequence (distance between each pair of magnetic field vectors) to determine the leading edge and trailing edge of the discontinuity.
-After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to get the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$.
-The maxium variance direction is then fitted by a step-like functions to extract the parameters to properly describe the discontinuity (we used logistic function here).
-Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.
-
-> To cover IDs at different spatial scales, we repeat the search procedure with time lags T = 10, 20, 30, 40, 50, 60s, and combine the identiﬁed ID events together to establish the event list.
-
+TODO:
+More than ?
+IDs are identified in the solar wind data from Juno, with ?
+IDs identified in 5 AU.
 Then for each discontinuity identified, we calculate the distance matrix of the time series sequence (distance between each pair of magnetic field vectors) to determine the leading edge and trailing edge of the discontinuity.
@@
 B(t; A, \mu, \sigma, {\mathrm{form=logistic}}) = A \left[1 - \frac{1}{1 + e^{\alpha}} \right]
-$$
+$${#eq-fit}
 
@@
 
-![](figures/l_j_fit)
-
-![](figures/l_j_fit_xscale_log.png){#fig-ljFit}
-
 ## Occurrence rate
 
-The occurrence rate of IDs is investigated with regards of the radial distance from the Sun.
-
-Note the quantity of IDs per day is corrected with respect to data gap and the time the mission spent in the pristine solar wind. 
-ARTEMIS spacecrafts will only be exposed in the solar wind for a relative short time during its orbits around the Moon and the Moon would be in the magnetosphere for a long time as it orbits the earth.
-(The data is obtained from OMNIWEB, link: [omniweb.gsfc.nasa.gov/ftpbrowser/themis_b_sw.txt](https://omniweb.gsfc.nasa.gov/ftpbrowser/themis_b_sw.txt))
+The occurrence rate of IDs is investigated with regards of the radial distance from the Sun for Juno, ARTEMIS, STEREO, and Wind.
+Number of discontinuities measured per day by different spacecraft missions (for the same temporal resolution of magnetic field data and the same criteria of discontinuity determination) is shown in @fig-rate.
+Because data is not continuously available and ARTEMIS spacecrafts will only be exposed in the solar wind for a relative short time during its orbits around the Moon (the Moon would be in the magnetosphere for a long time as it orbits the earth), the occurrence rate (numbder of IDs per day) is corrected with respect to data gap and the time the mission spent in the pristine solar wind.
+The occurrence rate of IDs observed by Juno is consistent with the occurrence rate observed by 1AU missions, when Juno is around $1$ AU.
+This number (occurrence rate) decreases with distance as Juno moves from $1$ AU to $5$ AU (corresponding to time after $\sim 2013$, the radial distance of Juno for 2011-2015 is shown in @fig-model)
 
@@
 This influence of the solar wind speed on the occurrence rate might be mitigated by the fact all the spacecrafts are in the ecliptic plane, and the solar wind speed is not expected to change significantly with the radial distance from the Sun beyond $1$ AU.
-So the decrease of the occurrence rate with the radial distance from the Sun is expected to be a real effect of the radial distance from the Sun.
+We normalize the occurrence rate from Juno to the occurrence rate from 1AU missions to account for the effect of solar wind structures on the occurrence rate.
+The normalized occurrence rate is shown in panel (b) of @fig-rate.
+The occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
+So the decrease of the occurrence rate with increasing radial distance from the Sun is expected to be a real effect of the radial distance from the Sun and this confirms the former results [@sodingRadialLatitudinalDependencies2001].
 
@@
 
-## Thickness
+## Current density and thickness
+
+The peak current density $J_m$ of a discontinuity is determined by
+
+$$
+J_m = - \frac{1}{\mu_0 V_n} \frac{d B_m}{d t},
+$$ {#eq-j}
+
+where $\mu_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
+For fitting method, the derivative of the magnetic field could be estimated as $d B_m / d t = A / 4 σ$.
+This estimate is more robust than the direct calculation of the derivative of the magnetic field, because the fitting method is less sensitive to the noise in the data and the time resolution of the data (see discussion in the appendix).
 
@@
 
-with $v = v_{sw} - v_{s/c} + U$ , where $\Delta T$ is the transition time (a factor of the $sigma$ used in fitting) , $v_{sw}$ is the solar wind velocity.
+with $v = v_{sw} - v_{s/c} + U$ , where $\Delta T$ is the transition time (a fixed factor of the $\sigma$ used in fitting) , $v_{sw}$ is the solar wind velocity.
 The velocity of the spacecraft $v_{s/c}$ and the propagation speed of the discontinuities $U$ are negligible in our case.
 
-In @vaskoKineticscaleCurrentSheets2022 paper, CS thickness is estimated by the formula $d = \frac{\Delta B_l}{2 \mu_0 < J_m> }$.
-Because of @eq-j, $d = \frac{\Delta B_l}{2 \mu_0 < J_m> } = \frac{\Delta B_l V_n }{2 <\frac{d B_m}{ d t} >}$
+To understand the relationship between the discontinuity and the local plasma, we normalize the thickness of the discontinuity by the initial ion length and the current density by the Alfven current density $J_A = e N_p V_A$ (corresponding to the drift between protons and electrons of local Alfén speed $V_A$).
+Figure @junoDistribution presents the statistical distribution of the (un)normalized thickness and current density of IDs grouped by the radial distance from the Sun collected by Juno.
+Panel (a,b) shows that the thickness increases with radial distance.
+However, after normalization, the thickness slightly decreases, with the most probable value around 4-2 $d_i$.
+With increasing radial distance, larger fraction of IDs have thickness less than 1 $d_i$, becombing sub-proton scale structures.
+Panel (c,d) shows that the current density decreases with increasing radial distance.
+However, after normalization, it slightly increases, with the most probable value around 0.05-0.15 $J_A$.
+It should be noted that for the normalized thickness and current density, the change is not significant compared to the spread of the distribution.
+
+The distribution of the thickness and current density of IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) during the five year of Juno cruise phase are shown in @fig-windDistribution.
+The distribution are grouped by the year of observation.
+Panel (a,b) shows that both the thickness and normalized thickness distribution of IDs remains almost constant with the year of observation.
+Most of the discontinuities have thickness around 350-3500 km, with the most probable value around 1000 km.
+Panel (c,d) shows that the current density slightly increases with the year of observation, with the most probable value around 5 $nA m^{-2}$, in consistence with previous studies [@vaskoKineticscaleCurrentSheets2022].
+However, after normalization, the current density distribution remains identical across the five years.
+The change in the current density could be explained by the change in the solar wind properties with the solar cycle, as shown in @fig-swParameters.
+Density and magnetic field asscoiated with the discontinuities increases with the solar cycle approaching the solar minimum, which could lead to the increase of the current density of the discontinuities with fixed normalized current density.
+
+::: {#fig-ljFit}
+![](figures/juno_distribution_r){#fig-ljFit}
+
+![](figures/l_j_fit_xscale_log)
+
+Distribution of various properties of IDs observed by Juno grouped by the radial distance from the Sun.
+Panel (a) thickness, (b) normalized thickness, (c) current density, (d) normalized current density.
+:::
+
+::: {#fig-windDistribution}
+![](figures/wind_distribution_time)
+
+Distribution of various properties of IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) grouped by the year of observation.
+Panel (a) thickness, (b) normalized thickness, (c) current density, (d) normalized current density.
+:::
+
+::: {#fig-swParameters}
+![](figures/sw_paramters_time)
+
+Solar wind parameters associated with the IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) grouped by the year of observation.
+Panel (a) solar wind density, (b) magnetic field, (c) fitted magnetic field $A$ in @eq-fit.
+:::
+
+# Discussion
+
+## Dependences of occurrence rate
+
+@marianiStatisticalStudyMagnetohydrodynamic1983
+@marianiVariationsOccurrenceRate1973
+
+TODO:
+
+# Conclusion
+
+We have collected 5 years of solar wind discontinuities from JUNO, ARTEMIS and STEREO. The results can be summarized as follows:
+
+1. The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
+2.
+The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs slightly decreases.
+The thickness distribution of IDs remains almost constant with the year of observation.
+3.
+The current density of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current density of IDs slightly increases.
+The current density distribution of IDs slightly increases with the year of observation, but after normalization, the current density distribution remains identical across the five years.
+
+# Acknowledgements
+
+Sunspot data from the World Data Center SILSO, Royal Observatory of Belgium, Brussels.
+ARTEMIS solar wind time interval data from the OMNI database.
+ARTEMIS solar wind time interval data from OMNIWEB, link: [omniweb.gsfc.nasa.gov/ftpbrowser/themis_b_sw.txt](https://omniweb.gsfc.nasa.gov/ftpbrowser/themis_b_sw.txt).
+
+# Appendix
+
+## Effect of the time resolution on the discontinuity properties
 
 The transition time $\Delta T$ is determined in one second resolution data for all our missions to reduce the system error.
-(Note that highest time resolution of the data is not needed for the transition time determination by fitting method, see discussion in the appendix).
+(Note that highest time resolution of the data is not needed for the transition time determination by fitting method).
+
+![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-tsEffect}
+
+# Archived Figures
+
+::: {#fig-current layout-nrow="1"}
+![](figures/new/current/current_k_r_dist)
+
+![](figures/new/current/current_k_N1_r_dist)
+
+**a,** Current density of IDs as a function of the radial distance from the Sun. **b,** Current density of IDs normalized to the Alfven current as a function of the radial distance from the Sun.
+:::
 
@@
 
-## Current density
-
-The peak current density $J_m$ of a discontinuity is determined by
-
-$$
-J_m = - \frac{1}{\mu_0 V_n} \frac{d B_m}{d t},
-$$ {#eq-j}
-
-where $\mu_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
-
-::: {#fig-current layout-nrow="1"}
-![](figures/new/current/current_k_r_dist)
-
-![](figures/new/current/current_k_N1_r_dist)
-
-**a,** Current density of IDs as a function of the radial distance from the Sun. **b,** Current density of IDs normalized to the Alfven current as a function of the radial distance from the Sun.
-:::
-
-# Summary and discussion
-
-We have collected 5 years of solar wind discontinuities from JUNO, ARTEMIS and STEREO.
-
-## Occurrence rate
-The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
-
-## Thickness
-
-The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs decreases.
-
-## Current density
-
-The current density of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current density of IDs increases.
-
 ![](figures/l_j_fit_taus)
@@
 ![](figures/l_j_fit_taus_xscale_log)
-
-# Acknowledgements
-
-Sunspot data from the World Data Center SILSO, Royal Observatory of Belgium, Brussels. ARTEMIS solar wind time interval data from the OMNI database.
-
-# List of Figures
 
@@
 :::
-
-# Appendix
-
-![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-tsEffect}

### 2024-05-25 index.qmd
writing paper...

@@
     text: Tana
+draft: true
 ---

### 2024-05-28 article.qmd
update

@@
     orcid: 0000-0001-7024-1561
-    affiliation: University of California, Los Angeles
-  - name: Shi Chen
-    orcid: 0000-0002-2582-7085
     affiliation: University of California, Los Angeles
@@
 @marianiStatisticalStudyMagnetohydrodynamic1983
+@tsurutaniInterplanetaryDiscontinuitiesTemporal1979
 @marianiVariationsOccurrenceRate1973
@@
 The current density of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current density of IDs slightly increases.
-The current density distribution of IDs slightly increases with the year of observation, but after normalization, the current density distribution remains identical across the five years.
+The current density distribution of IDs slightly increases with the year of observation, but after normalization, the current density distribution remains identical across the five years, thus no effect of the long-term (i.e.
+solar cycle) temporal variations.
 

### 2024-05-30 notes.qmd
update

@@
 -   Analysis
+    -   [ ] Re-calculate the occurrence rate of IDs
     -   [ ] Contribution of discontinuities to the power spectrum

### 2024-05-30 notebooks/main.jl
chore: update envs

@@ -1,24 +1,0 @@
-using AlgebraOfGraphics,
-    CairoMakie
-using DataFrames,
-    DataFramesMeta,
-    CategoricalArrays
-
-using Statistics
-using LinearAlgebra
-using beforerr
-import beforerr: easy_save
-using LaTeXStrings
-using PartialFunctions
-
-set_aog_theme!()
-
-include("utils/io.jl")
-# include("utils/Discontinuity.jl")
-include("../../share/src/Discontinuity.jl/Discontinuity.jl")
-
-easy_save(fname) = beforerr.easy_save(fname; dir="../figures")
-
-# %%
-# Define the labels for the plots
-r_lab = L"Radial Distance ($AU$)"

### 2024-05-30 notebooks/utils/config.py

@@ -12,7 +12,6 @@ from discontinuitypy.missions import wind_mag_h4_rtn_meta, wind_plasma_k0_swe_me
 
 from .juno import get_mag_paths
 from math import ceil
-from pathlib import Path
 
 
 def _split_list(lst, n):

### 2024-05-30 notebooks/utils/io.jl

@@ -1,83 +1,0 @@
-using Printf
-using Dates
-
-data_path = "$(@__DIR__)/../../data/05_reporting"
-
-function load(path::String)
-    DiscontinuityIO.load(path) |> process
-end
-
-function load(;tau = 60, ts = 1.00, name = "JNO", method = "fit", dir = data_path)
-    ts_str = @sprintf "ts_%.2fs" ts
-    df =load(joinpath(dir, "events.$name.$method.$(ts_str)_tau_$(tau)s.arrow"))
-    df.tau .= tau
-    df.ts .= ts
-    
-    if method == "fit"
-        df = @chain df begin
-            filter(:"fit.stat.rsquared" => >(0.95), _)
-        end
-    end
-    df
-end
-
-
-function load_tau(tau)
-    df = load(tau=tau)
-    df.label .= "$tau s"
-    println("Number of events: ", size(df, 1))
-    df
-end
-
-function load_taus(taus)
-@chain begin
-    vcat(load_tau.(taus)...);
-    sort(:tau)
-    unique([:"t.d_start", :"t.d_end"]) # remove events that appear in multiple taus datasets
-end
-end
-
-
-function process(df)
-    df_tmp = @transform(df,
-        :year = year.(:time) |> categorical   
-    )
-
-    # if 'radial_distance' is in the dataframe, round it
-    if "radial_distance" in names(df_tmp)
-        @transform!(df_tmp, :r = string.(round.(Int, :radial_distance)))
-    end
-
-    return df_tmp
-end
-
-
-function test_load()
-    j_events_low_fit = load()
-    j_events_tau_20_fit = load(tau = 20)
-    j_events_high_fit = load(ts = 0.12)
-
-    # add a label column to the dataframes
-    j_events_low_fit.label .= "1 Hz (fit)"
-    j_events_high_fit.label .= "8 Hz (fit)"
-    j_events_tau_20_fit.label .= "1 Hz, 20s (fit)"
-
-    # filter high time resolution events
-    j_events_high_fit = @chain j_events_high_fit begin
-        filter(:len => >(240), _)
-    end
-
-    # combine the dataframes
-    j_events = reduce(vcat, [j_events_low_fit, j_events_high_fit, j_events_tau_20_fit])
-
-    j_events_taus = 60:-10:20 .|> load_tau |> x -> reduce(vcat, x);
-
-    println("Number of events: ", size(j_events, 1))
-
[…]

### 2024-05-30 src/io.jl

@@ -1,0 +1,77 @@
+using Printf
+using Dates
+using Discontinuity
+
+data_path = datadir("05_reporting")
+
+function load(path)
+    Discontinuity.load(path) |> process!
+end
+
+function load(; tau=60, ts=1.00, name="JNO", method="fit", dir=data_path)
+    ts_str = @sprintf "ts_%.2fs" ts
+    df = load(joinpath(dir, "events.$name.$method.$(ts_str)_tau_$(tau)s.arrow"))
+    df.tau .= tau
+    df.ts .= ts
+    df
+end
+
+function load_tau(tau)
+    df = load(tau=tau)
+    df.label .= "$tau s"
+    println("Number of events: ", size(df, 1))
+    df
+end
+
+function load_taus(taus)
+    @chain begin
+        vcat(load_tau.(taus)...)
+        sort(:tau)
+        unique([:"t.d_start", :"t.d_end"]) # remove events that appear in multiple taus datasets
+    end
+end
+
+
+function process!(df)
+    df_tmp = @transform(df,
+        :year = year.(:time) |> categorical
+    )
+
+    # if 'radial_distance' is in the dataframe, round it
+    if "radial_distance" in names(df_tmp)
+        @transform!(df_tmp, :r = string.(round.(Int, :radial_distance)))
+    end
+
+    return df_tmp
+end
+
+
+function test_load()
+    j_events_low_fit = load()
+    j_events_tau_20_fit = load(tau=20)
+    j_events_high_fit = load(ts=0.12)
+
+    # add a label column to the dataframes
+    j_events_low_fit.label .= "1 Hz (fit)"
+    j_events_high_fit.label .= "8 Hz (fit)"
+    j_events_tau_20_fit.label .= "1 Hz, 20s (fit)"
+
+    # filter high time resolution events
+    j_events_high_fit = @chain j_events_high_fit begin
+        filter(:len => >(240), _)
+    end
+
+    # combine the dataframes
+    j_events = reduce(vcat, [j_events_low_fit, j_events_high_fit, j_events_tau_20_fit])
+
+    j_events_taus = 60:-10:20 .|> load_tau |> x -> reduce(vcat, x)
+
+    println("Number of events: ", size(j_events, 1))
+
+    j_events_low_der = load(method="derivative")
+    j_events_high_der = load(ts=0.12, method="derivative")
+
+    j_events_low_der[!, :label] .= "1 Hz (derivative)"
[…]

### 2024-05-30 src/main.jl

@@ -1,0 +1,25 @@
+using DrWatson
+@quickactivate
+
+using AlgebraOfGraphics,
+    CairoMakie
+using DataFrames,
+    DataFramesMeta,
+    CategoricalArrays
+
+using Statistics
+using LinearAlgebra
+using beforerr
+import beforerr: easy_save
+using LaTeXStrings
+
+set_aog_theme!()
+
+include("io.jl")
+
+figure_dir = projectdir("figures")
+easy_save(fname) = beforerr.easy_save(fname; dir=figure_dir)
+
+# %%
+# Define the labels for the plots
+r_lab = L"Radial Distance ($AU$)"

### 2024-05-31 src/io.jl
refactoring codes

@@ -1,16 +1,10 @@
 using Printf
-using Dates
 using Discontinuity
-
 data_path = datadir("05_reporting")
-
-function load(path)
-    Discontinuity.load(path) |> process!
-end
 
 function load(; tau=60, ts=1.00, name="JNO", method="fit", dir=data_path)
     ts_str = @sprintf "ts_%.2fs" ts
-    df = load(joinpath(dir, "events.$name.$method.$(ts_str)_tau_$(tau)s.arrow"))
+    df = Discontinuity.load(joinpath(dir, "events.$name.$method.$(ts_str)_tau_$(tau)s.arrow"))
     df.tau .= tau
     df.ts .= ts
     df
@@ -30,21 +24,6 @@ function load_taus(taus)
         unique([:"t.d_start", :"t.d_end"]) # remove events that appear in multiple taus datasets
     end
 end
-
-
-function process!(df)
-    df_tmp = @transform(df,
-        :year = year.(:time) |> categorical
-    )
-
-    # if 'radial_distance' is in the dataframe, round it
-    if "radial_distance" in names(df_tmp)
-        @transform!(df_tmp, :r = string.(round.(Int, :radial_distance)))
-    end
-
-    return df_tmp
-end
-
 
 function test_load()
     j_events_low_fit = load()

### 2024-05-31 src/main.jl

@@ -1,6 +1,7 @@
 using DrWatson
 @quickactivate
 
+using Discontinuity
 using AlgebraOfGraphics,
     CairoMakie
 using DataFrames,
@@ -16,10 +17,9 @@ using LaTeXStrings
 set_aog_theme!()
 
 include("io.jl")
+include("plot.jl")
 
 figure_dir = projectdir("figures")
 easy_save(fname) = beforerr.easy_save(fname; dir=figure_dir)
 
-# %%
-# Define the labels for the plots
-r_lab = L"Radial Distance ($AU$)"
+

### 2024-05-31 src/plot.jl

@@ -1,0 +1,23 @@
+using AlgebraOfGraphics: density
+
+using Dates
+
+round_c(x) = round(Integer, x)
+
+# %%
+# Define the labels for the plots
+r_lab = L"Radial Distance ($AU$)"
+r_map = :radial_distance => nonnumeric ∘ round_c  => r_lab
+tau_map = :tau => nonnumeric => "τ (s)"
+year_map = :time => nonnumeric ∘ year  => "Year"
+
+function plot_duration(plt; 
+    datalimits_f = x -> quantile(x, [0.02, 0.98]),
+    axis = (; yscale=log10),
+    facet = (; linkxaxes=:none, linkyaxes=:none),
+    legend = NamedTuple()
+)
+    plt *= mapping(:duration) * (visual(Lines))
+    specs = plt * density(; datalimits=datalimits_f) 
+    draw(specs, axis=axis, facet=facet, legend=legend)
+end

### 2024-08-28 src/main.jl
update: env

@@ -9,9 +9,10 @@ using DataFrames,
 
 using Statistics
 using LinearAlgebra
-using beforerr
-import beforerr: easy_save
+using Beforerr
+import Beforerr: easy_save
 using LaTeXStrings
+using Discontinuity
 
 set_aog_theme!()
 
@@ -21,4 +22,5 @@ include("plot.jl")
 figure_dir = projectdir("figures")
 easy_save(fname) = beforerr.easy_save(fname; dir=figure_dir)
 
+datalimits_f = x -> quantile(x, [0.02, 0.98])
 

### 2024-08-29 src/main.jl
update: .gitignore

@@ -20,7 +20,7 @@ include("io.jl")
 include("plot.jl")
 
 figure_dir = projectdir("figures")
-easy_save(fname) = beforerr.easy_save(fname; dir=figure_dir)
+easy_save(fname) = Beforerr.easy_save(fname; dir=figure_dir)
 
 datalimits_f = x -> quantile(x, [0.02, 0.98])
 

### 2024-08-29 article.qmd
update: tables in manuscript

@@
 First, the missions, instruments and data used are listed.
-Then, we brieﬂy describe the method used to identify the discontinuities and the model used to estimate the plasma state at Juno location due to the lack of plasma data during its cruise phase.
+Then, we briefly describe the method used to identify the discontinuities and the model used to estimate the plasma state at Juno location due to the lack of plasma data during its cruise phase.
 Finally, we present the results of the spatial evolution of the discontinuities with respect to their characteristics (spatial scales and current density), and discuss the implications of our findings.
@@
 Overview.
-**a,** Juno orbit during its cruise phase (2011-206).
+**a,** Juno orbit during its cruise phase (2011-2016).
 **b,** Difference of heliographic longitude of Juno and 1-AU missions.
@@
 
-Furthermore, an analysis of @fig-overview reveals the significance of the heliographic longitudinal difference between the Juno mission and Near-Earth missions (such as Wind and ARTEMIS) as well as STEREO-A missions.
-This longitudinal discrepancy ensures comprehensive coverage of the plasma en route to Juno.
+Further analysis of @fig-overview highlights the significance of the heliographic longitudinal difference between the Juno mission and Earth as well as the STEREO-A mission.
 Specifically, when there is a substantial longitudinal difference between Juno and Earth, the difference between Juno and STEREO-A tends to be minimal, and vice versa.
-This relationship facilitates an extensive observation network for the plasma traveling towards Juno.
+This longitudinal discrepancy between Earth and STEREO-A ensures comprehensive coverage of the plasma en route to Juno.
 
 The time resolution of the magnetic field and plasma data for Juno, Wind, ARTEMIS, STEREO is summarized in the table below.
+
+| Mission             | δt(B)    | δt(plasma) |
+|---------------------|----------|------------|
+| Juno                | 1 Hz     | 1 hour     |
+| ARTEMIS             | 5 Hz     | 0.25 Hz    |
+| WIND                | 11 Hz    | 1 Hz       |
+| STEREO              | 8 Hz     | 1 min      |
 
@@
 ![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-tsEffect}
-
-# Archived Figures
-
-::: {#fig-current layout-nrow="1"}
-![](figures/new/current/current_k_r_dist)
-
-![](figures/new/current/current_k_N1_r_dist)
-
-**a,** Current density of IDs as a function of the radial distance from the Sun. **b,** Current density of IDs normalized to the Alfven current as a function of the radial distance from the Sun.
-:::
-
-::: {#fig-thickness layout-nrow="1"}
-![](figures/new/thickness/thickness_k_fit_r_dist)
-
-![](figures/new/thickness/thickness_k_fit_N1_r_dist)
-
-**a,** Thickness of IDs as a function of the radial distance from the Sun. **b,** Thickness of IDs normalized to the ion inertial length as a function of the radial distance from the Sun. 
-:::
-
-![](figures/l_j_fit_taus)
-
-![](figures/l_j_fit_taus_xscale_log)
-
-::: {.column-screen-inset layout-nrow="1"}
-![](figures/thickness/thickness_k_dist)
-
-![](figures/thickness/thickness_k_N1_dist)
-
-![](figures/thickness/thickness_k_N1_r_dist)
-:::
-
-::: {.column-screen-inset layout-nrow="1"}
-
-![](figures/current/current_k_dist)
-
-![](figures/current/current_k_N1_dist)
-
-:::

### 2024-08-29 notes.qmd
update: tables in manuscript

@@
 
-## Updates
+# Updates
 
@@
 
-## Infos
+# Archived Figures
 
-```{python}
-# | label: tbl-missions
-# | tbl-cap: Missions info
-import yaml
-import polars as pl
-from functools import reduce
-from great_tables import GT
+::: {#fig-current layout-nrow="1"}
+![](figures/new/current/current_k_r_dist)
 
-with open("data/info.yml", "r") as file:
-    data = yaml.safe_load(file)
+![](figures/new/current/current_k_N1_r_dist)
 
-# Recursive function to find magnetometers
-def find_instrument(instruments, ins_type):
-    instrument = {}
-    for key, value in instruments.items():
-        if value.get("type") == ins_type:
-            instrument = value
-        elif "instruments" in value:
-            instrument = find_instrument(value["instruments"], ins_type)
-    return instrument
+**a,** Current density of IDs as a function of the radial distance from the Sun. **b,** Current density of IDs normalized to the Alfven current as a function of the radial distance from the Sun.
+:::
 
-def parse_yaml(data, info, ins_type=None):
-    rows = []
+::: {#fig-thickness layout-nrow="1"}
+![](figures/new/thickness/thickness_k_fit_r_dist)
 
-    for mission, details in data["missions"].items():
-        if ins_type is None:
-            rows.append([mission, details.get(info)])
-            continue
-        instruments = details.get("instruments", {})
-        instrument = find_instrument(instruments, ins_type)
-        rows.append([mission, instrument.get(info)])
+![](figures/new/thickness/thickness_k_fit_N1_r_dist)
 
-    return pl.DataFrame(rows, schema=["Mission", info])
+**a,** Thickness of IDs as a function of the radial distance from the Sun. **b,** Thickness of IDs normalized to the ion inertial length as a function of the radial distance from the Sun. 
+:::
 
-# Define the merge function
-def merge_dfs(left: pl.DataFrame, right, on="Mission", how="outer_coalesce"):
-    return left.join(right, on=on, how=how)
+![](figures/l_j_fit_taus)
 
-# Parse and display the table
-df_mag = parse_yaml(data, "time_resolutions", "magnetometer").rename(
-    {"time_resolutions": "δt(B)"}
-)
-df_plasma = parse_yaml(data, "time_resolutions", "plasma").rename(
-    {"time_resolutions": "δt(plasma)"}
-)
-df_r = parse_yaml(data, "radial_coverage")
-df_time = parse_yaml(data, "launch_date")
-df_link = parse_yaml(data, "website")
+![](figures/l_j_fit_taus_xscale_log)
 
-df_list = [df_mag, df_plasma, df_r, df_time, df_link]  # Replace with your DataFrames
+::: {.column-screen-inset layout-nrow="1"}
+![](figures/thickness/thickness_k_dist)
 
-df_merged = reduce(merge_dfs, df_list).with_columns(pl.col("website").list.join(", "))
+![](figures/thickness/thickness_k_N1_dist)
 
-GT(df_merged.to_pandas()).fmt_markdown("website").cols_label(
-    radial_coverage="Radial coverage",
-    launch_date="Launch date",
-)
-```
+![](figures/thickness/thickness_k_N1_r_dist)
+:::
+
+::: {.column-screen-inset layout-nrow="1"}
+
+![](figures/current/current_k_dist)
+
+![](figures/current/current_k_N1_dist)
+
+:::

### 2024-08-29 article.qmd
WIP: manuscripts

@@
 
-The time resolution of the magnetic field and plasma data for Juno, Wind, ARTEMIS, STEREO is summarized in the table below.
+Datasets collected from missions such as STEREO, ARTEMIS, and WIND will complement observations from Juno, offering a broader contextual perspective on heliospheric conditions and enabling a multi-point analysis of discontinuity properties [@velliUnderstandingOriginsHeliosphere2020].
+The table below summarizes the time resolution of magnetic field and plasma data for PSP, Juno, Wind, ARTEMIS, and STEREO.
 
@@
 
-## Model
-
-June measurements do not include plasma characteristics, and to estimate discontinuity spatial scale (thicknesses) we will use solar wind speed obtained from the model of solar wind propagation.
-The hourly solar wind model data from the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] will be employed to determine the ion bulk velocity $v$ and plasma density $n$ at the location of the Juno mission.
-Utilizing the BATSRUS MHD solver, this model is capable of simulating the propagation of the solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively encompassing the region of interest for our study.
-@fig-model shows comparison of magnetic field magnitudes obtained from MSWIM2D and measured by Juno.
-
-The model time resolution is hourly. After averaging Juno data to the same time resolution, we see that the model data is consistent with the Juno magnetic field data.
+However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind speed derived from solar wind propagation models.
+Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location.
+This model, which utilizes the BATSRUS MHD solver, simulates the propagation of solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively covering the region pertinent to our study.
+The MSWIM2D model provides output data with an hourly time resolution as shown in @fig-model.
+The comparison of magnetic field magnitudes from MSWIM2D with those measured by Juno, after averaging to the same time resolution, reveals a strong correlation, confirming the model’s reliability.
 
@@
 After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to get the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$.
-The maxium variance direction is then fitted by a step-like functions to extract the parameters to properly describe the discontinuity (we used logistic function here).
+The maximum variance direction is then fitted by a step-like functions to extract the parameters to properly describe the discontinuity (we used logistic function here).
 Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.

### 2024-09-09 src/juno/config.py
fix: time resolution

@@ -97,7 +97,7 @@ class WindConfig(Config, WindConfigBase, SpeasyIDsConfig):
 
 
 class StereoConfig(Config, StereoConfigBase, SpeasyIDsConfig):
-    ts: timedelta = timedelta(seconds=1)
+    pass
 
 
 class THEMISConfig(ThemisConfigBase, SpeasyIDsConfig):

### 2024-09-09 article.qmd
feat: grpMeeting presentations

@@
 ---
-title: Solar wind discontinuities spatial evolution in the outer heliosphere
+title: Spatial evolution of solar wind discontinuities in the outer heliosphere
 author:
@@
 We identify and analyze the properties of the discontinuities at different radial distances from the Sun.
-By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of IDs drops with the radial distance from the Sun, following a $1/r$ law; (2) The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases; (3) The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
+By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of interplanetary discontinuities (IDs) decreases with radial distance from the Sun, following a $1/r$ relationship; (2) The thickness of IDs increases with radial distance, but when normalized to the ion inertial length, the thickness decreases; (3) The current density of IDs decreases with radial distance, but when normalized to the Alfvén current, the current density of IDs increases; (4) The distribution of the normalized thickness and current density of IDs remain constant over time at 1 AU on a yearly scale.
 ---
@@
 Overview.
-**a,** Juno orbit during its cruise phase (2011-2016).
-**b,** Difference of heliographic longitude of Juno and 1-AU missions.
-**c,** monthly and smoothed sunspot number.
-**d-g,** Near-Earth (OMNI) and STEREO-A solar wind plasma density and speed.
+**a,** Juno's orbit during its cruise phase (2011-2016).
+**b,** Difference in heliographic longitude between Juno and 1-AU missions.
+**c,** monthly and smoothed sunspot numbers.
+**d-g,** solar wind plasma density and speed from Near-Earth (OMNI) and STEREO-A missions.
 
@@
 
+TODO: how is the occurrence rate related to the formation mechanism?
+
+## Spatial variations of discontinuity properties
+
 TODO:

### 2024-09-09 index.qmd
feat: grpMeeting presentations

@@
 
+# Conclusion
+
+- The normalized occurrence rate of interplanetary discontinuities (IDs) decreases with radial distance from the Sun, following a $1/r$ relationship.
+
+- The thickness of IDs increases with radial distance, but when normalized to the ion inertial length, the thickness decreases.
+
+- The current density of IDs decreases with radial distance, but when normalized to the Alfvén current, the current density of IDs increases.
+
+- The distribution of the normalized thickness and current density of IDs remain constant over time at 1 AU on a yearly scale.
+
 # Appendix

### 2024-09-09 presentations/grpMeeting_Zijin_2024-09.qmd
feat: grpMeeting presentations

--- 2024-09-09 article.qmd
@@
 ---
-title: Spatial evolution of solar wind discontinuities in the outer heliosphere
+title: "Spatial Evolution of Solar Wind Discontinuities in the Outer Heliosphere: JUNO and 1AU-missions Observations"
 author:
   - name: Zijin Zhang
-    email: zijin@ucla.edu
-    orcid: 0000-0002-9968-067X
-    affiliation: University of California, Los Angeles
-    roles: writing
-    corresponding: true
   - name: Anton V. Artemyev
-    email: aartemyev@igpp.ucla.edu
-    orcid: 0000-0001-8823-4474
-    affiliation: University of California, Los Angeles
   - name: Vassilis Angelopoulos
-    orcid: 0000-0001-7024-1561
-    affiliation: University of California, Los Angeles
-affiliations:
-  - id: ucla
-    name: University of California, Los Angeles
-execute: 
-  eval: false
-code-links:
-  - href: ../
-    text: Website
-  - repo
-  - href: https://www.overleaf.com/project/65b0a9c80a3616adf6e599e8
-    text: Overleaf
-abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
-We identify and analyze the properties of the discontinuities at different radial distances from the Sun.
-By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of interplanetary discontinuities (IDs) decreases with radial distance from the Sun, following a $1/r$ relationship; (2) The thickness of IDs increases with radial distance, but when normalized to the ion inertial length, the thickness decreases; (3) The current density of IDs decreases with radial distance, but when normalized to the Alfvén current, the current density of IDs increases; (4) The distribution of the normalized thickness and current density of IDs remain constant over time at 1 AU on a yearly scale.
+format:
+  html: default
+  pptx: default
 ---
 
-# Plain Language Summary
+## Introduction
 
-- **What I did:** I studied the solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
-I identified and analyzed the properties of the discontinuities at different radial distances from the Sun.
-I differentiated the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance).
+![Examples of IDs from ARTEMIS, STEREO, and Wind](../figures/fig_examples.png){#fig-examples}
 
-- **What I found:** The normalized occurrence rate of IDs drops with the radial distance from the Sun, following a $1/r$ law.
-The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases.
-The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
+## Motivation
 
-- **What it means:** The results of this study provide a better understanding of the solar wind discontinuities in the outer heliosphere and their spatial evolution.
-This information is important for understanding the dynamics of the solar wind and testing the local generation mechanism of discontinuities.
+**How do solar wind discontinuities evolve over radial distances from the Sun?**
 
-# Introduction
+Juno during its five-year cruise phase (2011-2016) to Jupiter provides a unique opportunity!
 
-Rapid variations in interplanetary magnetic fields, commonly recognized as solar wind magnetic discontinuities [@colburnDiscontinuitiesSolarWind1966], embody localized transient rotations or jumps of the magnetic field.
-Considered important for efficient plasma heating, they carry the most intense currents found in the solar wind and obserrved throughout the heliosphere from inner heliosphere [@liuCategorizingMHDDiscontinuities2022] to the heliosheath [@burlagaCurrentSheetsHeliosheath2011].
-Theoretical models [@lerchePropagationMagneticDisturbances1975; @medvedevDissipativeDynamicsCollisionless1997] and MHD simulations [@grecoIntermittentMHDStructures2008; @grecoStatisticalAnalysisDiscontinuities2009; @yangFormationRotationalDiscontinuities2015] suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence.
-These nonlinear processes can create significant isolated disturbances to the otherwise adiabatic evolution of the solar wind flow (?Reference?) and host many processes, including magnetic reconnection (?Reference?) and Fermi acceleration of particles [@wentzelMotionMagneticDiscontinuities1964].
-Moreover, they contribute significantly to the magnetic fluctuation spectra [@borovskyContributionStrongDiscontinuities2010] and can affect space weather [@tsurutaniReviewInterplanetaryDiscontinuities2011].
-Therefore, the study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind and test the local generation mechanism of discontinuities.
-However, previous study of solar wind discontinuities evolution [@sodingRadialLatitudinalDependencies2001] in the outer heliosphere were rarely in conjunction with measurements closer to the Sun.
+=> **What are the physical mechanisms behind their formation and evolution?**
+
+<!-- However, previous study of solar wind discontinuities evolution [@sodingRadialLatitudinalDependencies2001] in the outer heliosphere were rarely in conjunction with measurements closer to the Sun.
 Moreover, the intervals in their study spread over multiple solar cycles though they are selected during solar activity minimum.
 Thus it is presently unclear whether their frequency and properties are the result of solar variability or due to the natural evolution of the discontinuities during their propagation and interaction with the ambient solar wind.
+-->
 
-The goal of our paper is to investigate, statistically, discontinuities at different radial distance in the outer heliosphere to obtain a understanding of their formation and evolution.
-Our methodology involves integrating Juno measurements [@connerneyJunoMagneticField2017] between $1$ and $5$ AU with those at $1$ AU to distinguish temporal effect and spatial variations by examining the discontinuity characteristics at two radial distances simultaneously.
-
-First, the missions, instruments and data used are listed.
-Then, we briefly describe the method used to identify the discontinuities and the model used to estimate the plasma state at Juno location due to the lack of plasma data during its cruise phase.
-Finally, we present the results of the spatial evolution of the discontinuities with respect to their characteristics (spatial scales and current density), and discuss the implications of our findings.
+## Overview
 
@@
 
-![](figures/fig_overview)
+![](../figures/fig_overview.png)
 
@@
 
-# Dataset, models, and methods
+<!-- During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity.
+However, by the end of the mission's cruise phase, there was a significant decline in solar activity.
+This variation underscores the importance of calibrating the discontinuity properties in relation to solar activity levels to account for temporal fluctuations.
+-->
+
+## Temporal variations of SWDs
+
+::: {#fig-windDistribution}
+![](../figures/wind_distribution_time.png)
+
+Distribution of various properties of IDs observed by Wind mission grouped by the year of observation.
+Panel (a) thickness, (b) normalized thickness, (c) current density, (d) normalized current density.
+:::
+
+::: {#fig-swParameters}
+![](../figures/sw_paramters_time.png)
+
+Solar wind parameters associated with the IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) grouped by the year of observation.
+Panel (a) solar wind density, (b) magnetic field, (c) fitted magnetic field $A$ in @eq-fit.
+:::
 
 ## Dataset
-
-In this study we use datasets of four missions measuring solar wind magnetic field and plasma.
-Synergistic observations of these missions should advance our understanding of the solar wind discontinuities, their radial distribution and evolution [@velliUnderstandingOriginsHeliosphere2020].
-
-<!-- ![Near-Earth's and STEREO-A solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview} -->
-
-The solar wind plasma state, as evidenced by the sunspot number (referenced in @fig-overview), plays a crucial role in understanding the dynamics of discontinuities.
-During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity.
-However, by the end of the mission's cruise phase, there was a significant decline in solar activity.
-This variation underscores the importance of calibrating the discontinuity properties in relation to solar activity levels to account for temporal fluctuations.
-
-Further analysis of @fig-overview highlights the significance of the heliographic longitudinal difference between the Juno mission and Earth as well as the STEREO-A mission.
-Specifically, when there is a substantial longitudinal difference between Juno and Earth, the difference between Juno and STEREO-A tends to be minimal, and vice versa.
-This longitudinal discrepancy between Earth and STEREO-A ensures comprehensive coverage of the plasma en route to Juno.
-
-Datasets collected from missions such as STEREO, ARTEMIS, and WIND will complement observations from Juno, offering a broader contextual perspective on heliospheric conditions and enabling a multi-point analysis of discontinuity properties [@velliUnderstandingOriginsHeliosphere2020].
-The table below summarizes the time resolution of magnetic field and plasma data for PSP, Juno, Wind, ARTEMIS, and STEREO.
 
@@
 
-However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind speed derived from solar wind propagation models.
+$$
+B(t; A, \mu, \sigma, {\mathrm{form=logistic}}) = A \left[1 - \frac{1}{1 + e^{\alpha}} \right]
+$${#eq-fit}
+
+<!-- However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind speed derived from solar wind propagation models.
 Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location.
@@
 The comparison of magnetic field magnitudes from MSWIM2D with those measured by Juno, after averaging to the same time resolution, reveals a strong correlation, confirming the model’s reliability.
+-->
 
@@
 
-![](figures/model/juno_model_validation_full)
+![](../figures/model/juno_model_validation_full.png)
 
@@
 
-## Methods
+## Results - Occurrence rate
 
-We use Liu's [@liuMagneticDiscontinuitiesSolar2022] method to identify discontinuities in the solar wind.
-This method has better compatibility for the discontinuities with minor field changes, and is more robust to the situation encountered in the outer heliosphere.
-For each sampling instant $t$, we define three intervals: the pre-interval $[-1,-1/2]\cdot T+t$, the middle interval $[-1/,1/2]\cdot T+t$, and the post-interval $[1/2,1]\cdot T+t$, in which $T$ are time lags.
-Let time series of the magnetic field data in these three intervals are labeled ${\mathbf B}_-$, ${\mathbf B}_0$, ${\mathbf B}_+$, respectively.
-Then for an discontinuity, the following three conditions should be satisfied: (1) $\sigma({\mathbf B}_0) > 2\max\left(\sigma({\mathbf B}_-), \sigma({\mathbf B}_+)\right)$, (2) $\sigma\left({\mathbf B}_-+{\mathbf B}_+\right)>\sigma({\mathbf B}_-)+\sigma({\mathbf B}_+)$, and (3) $|\Delta {\mathbf B}|>|{\mathbf B}_{bg}|/10$, in which $\sigma$ and ${\mathbf B}_{bg}$ represent the standard deviation and the background magnetic field magnitude, and $\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)$.
-The first two conditions guarantee that the field changes of the discontinuity identified are large enough to be distinguished from the stochastic fluctuations or Alfven waves on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition.
+::: {#fig-rate}
 
-Because the discontinuities may have different spatial scale at different radial distances from the Sun, we repeat the search procedure with time lags $T = 10, 20, 30, 40, 50, 60$ s, and combine the identified ID events together to establish the event list.
-Discontinuities with spatial scales larger than $60$ s are not considered in this study, however it could be argued that they are not significant in the outer heliosphere if they follow the trend with decreasing number of IDs with increasing spatial scale.
-@fig-ljFit also indicates that the spatial scale of IDs does not vary significantly with the radial distance from the Sun.
-
-TODO:
-More than ?
-IDs are identified in the solar wind data from Juno, with ?
-IDs identified in 5 AU.
-Then for each discontinuity identified, we calculate the distance matrix of the time series sequence (distance between each pair of magnetic field vectors) to determine the leading edge and trailing edge of the discontinuity.
-After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to get the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$.
-The maximum variance direction is then fitted by a step-like functions to extract the parameters to properly describe the discontinuity (we used logistic function here).
-Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.
-
-$$
-B(t; A, \mu, \sigma, {\mathrm{form=logistic}}) = A \left[1 - \frac{1}{1 + e^{\alpha}} \right]
-$${#eq-fit}
-
-where $\alpha = (t - \mu)/{\sigma}$.
-
-@fig-examples shows several examples of solar wind discontinuities detected by different spacecraft.
-
-<!-- - We use [@liuMagneticDiscontinuitiesSolar2022] method to identify IDs, which has better compatibility for the IDs with minor field changes.
-- Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features. -->
-
-![Examples of IDs from ARTEMIS, STEREO, and Wind](figures/fig_examples){#fig-examples}
-
-# Results
-
-<!-- The basic approach of this proposal is to use solar wind measurements at 1AU (STEREO, ARTEMIS, WIND) to compare with Juno and PSP measurements and distinguish effects of solar wind temporal variations and effects of spatial (with the radial distance from the Sun) variations of discontinuity occurrence rate and characteristics.
-The example of such comparison for the occurrence rate is shown in @fig-rate, where we plot number of discontinuities measured per day by different spacecraft missions (for the same temporal resolution of magnetic field data and the same criteria of discontinuity determination).
-The radial distance of Juno for 2011-2015 is shown in @fig-model, and the number of discontinuities measured by Juno per day coincides with the discontinuity number measured by STEREO, WIND, and ARTEMIS, when Juno is around $1$ AU.
-This number (occurrence rate) decreases with distance (with time after $\sim 2013$), as Juno moves from $1$ AU to $5$ AU.
-We will use the similar comparison for discontinuity characteristics and occurrence rate derived for PSP and Juno.
--->
-
-## Occurrence rate
-
-The occurrence rate of IDs is investigated with regards of the radial distance from the Sun for Juno, ARTEMIS, STEREO, and Wind.
-Number of discontinuities measured per day by different spacecraft missions (for the same temporal resolution of magnetic field data and the same criteria of discontinuity determination) is shown in @fig-rate.
-Because data is not continuously available and ARTEMIS spacecrafts will only be exposed in the solar wind for a relative short time during its orbits around the Moon (the Moon would be in the magnetosphere for a long time as it orbits the earth), the occurrence rate (numbder of IDs per day) is corrected with respect to data gap and the time the mission spent in the pristine solar wind.
-The occurrence rate of IDs observed by Juno is consistent with the occurrence rate observed by 1AU missions, when Juno is around $1$ AU.
-This number (occurrence rate) decreases with distance as Juno moves from $1$ AU to $5$ AU (corresponding to time after $\sim 2013$, the radial distance of Juno for 2011-2015 is shown in @fig-model)
-
-The rate of occurrence depends linearly on the solar wind velocity [@sodingRadialLatitudinalDependencies2001], however the plasma velocity data in Juno mission is not available during its cruise phase.
-Therefore, we do not normalize the occurrence rate with respect to the solar wind speed.
-This influence of the solar wind speed on the occurrence rate might be mitigated by the fact all the spacecrafts are in the ecliptic plane, and the solar wind speed is not expected to change significantly with the radial distance from the Sun beyond $1$ AU.
-We normalize the occurrence rate from Juno to the occurrence rate from 1AU missions to account for the effect of solar wind structures on the occurrence rate.
-The normalized occurrence rate is shown in panel (b) of @fig-rate.
-The occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
-So the decrease of the occurrence rate with increasing radial distance from the Sun is expected to be a real effect of the radial distance from the Sun and this confirms the former results [@sodingRadialLatitudinalDependencies2001].
-
-::: {#fig-rate layout-nrow="1"}
-
-![](figures/ocr/ocr_time_cleaned)
-
-![](figures/ocr/ocr_r_N2_cleaned)
+![](../figures/ocr/ocr_time_cleaned.png)
 
@@
 
-## Current density and thickness
-
-The peak current density $J_m$ of a discontinuity is determined by
-
-$$
-J_m = - \frac{1}{\mu_0 V_n} \frac{d B_m}{d t},
-$$ {#eq-j}
-
-where $\mu_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
-For fitting method, the derivative of the magnetic field could be estimated as $d B_m / d t = A / 4 σ$.
-This estimate is more robust than the direct calculation of the derivative of the magnetic field, because the fitting method is less sensitive to the noise in the data and the time resolution of the data (see discussion in the appendix).
-
-The thickness $d$ of a discontinuity is determined by
-
-$$
-d = (v \cdot n) \Delta T
-$$
-
-with $v = v_{sw} - v_{s/c} + U$ , where $\Delta T$ is the transition time (a fixed factor of the $\sigma$ used in fitting) , $v_{sw}$ is the solar wind velocity.
-The velocity of the spacecraft $v_{s/c}$ and the propagation speed of the discontinuities $U$ are negligible in our case.
-
-To understand the relationship between the discontinuity and the local plasma, we normalize the thickness of the discontinuity by the initial ion length and the current density by the Alfven current density $J_A = e N_p V_A$ (corresponding to the drift between protons and electrons of local Alfén speed $V_A$).
-Figure @junoDistribution presents the statistical distribution of the (un)normalized thickness and current density of IDs grouped by the radial distance from the Sun collected by Juno.
-Panel (a,b) shows that the thickness increases with radial distance.
-However, after normalization, the thickness slightly decreases, with the most probable value around 4-2 $d_i$.
-With increasing radial distance, larger fraction of IDs have thickness less than 1 $d_i$, becombing sub-proton scale structures.
-Panel (c,d) shows that the current density decreases with increasing radial distance.
-However, after normalization, it slightly increases, with the most probable value around 0.05-0.15 $J_A$.
-It should be noted that for the normalized thickness and current density, the change is not significant compared to the spread of the distribution.
-
-The distribution of the thickness and current density of IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) during the five year of Juno cruise phase are shown in @fig-windDistribution.
-The distribution are grouped by the year of observation.
-Panel (a,b) shows that both the thickness and normalized thickness distribution of IDs remains almost constant with the year of observation.
-Most of the discontinuities have thickness around 350-3500 km, with the most probable value around 1000 km.
-Panel (c,d) shows that the current density slightly increases with the year of observation, with the most probable value around 5 $nA m^{-2}$, in consistence with previous studies [@vaskoKineticscaleCurrentSheets2022].
-However, after normalization, the current density distribution remains identical across the five years.
-The change in the current density could be explained by the change in the solar wind properties with the solar cycle, as shown in @fig-swParameters.
-Density and magnetic field asscoiated with the discontinuities increases with the solar cycle approaching the solar minimum, which could lead to the increase of the current density of the discontinuities with fixed normalized current density.
+## Results - Current density and thickness
 
 ::: {#fig-ljFit}
-![](figures/juno_distribution_r){#fig-ljFit}
 
-![](figures/l_j_fit_xscale_log)
+![](../figures/l_j_fit_xscale_log.png)
 
@@
 
-::: {#fig-windDistribution}
-![](figures/wind_distribution_time)
+## Conclusion
 
-Distribution of various properties of IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) grouped by the year of observation.
-Panel (a) thickness, (b) normalized thickness, (c) current density, (d) normalized current density.
-:::
+- The normalized occurrence rate of interplanetary discontinuities (IDs) decreases with radial distance from the Sun, following a $1/r$ relationship.
 
-::: {#fig-swParameters}
-![](figures/sw_paramters_time)
+- The thickness of IDs increases with radial distance, but when normalized to the ion inertial length, the thickness decreases.
 
-Solar wind parameters associated with the IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) grouped by the year of observation.
-Panel (a) solar wind density, (b) magnetic field, (c) fitted magnetic field $A$ in @eq-fit.
-:::
+- The current density of IDs decreases with radial distance, but when normalized to the Alfvén current, the current density of IDs increases.
 
-# Discussion
-
-## Dependences of occurrence rate
-
-@marianiStatisticalStudyMagnetohydrodynamic1983
-@tsurutaniInterplanetaryDiscontinuitiesTemporal1979
-@marianiVariationsOccurrenceRate1973
-
-TODO: how is the occurrence rate related to the formation mechanism?
-
-## Spatial variations of discontinuity properties
-
-TODO:
-
-# Conclusion
-
-We have collected 5 years of solar wind discontinuities from JUNO, ARTEMIS and STEREO. The results can be summarized as follows:
-
-1. The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
-2.
-The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs slightly decreases.
-The thickness distribution of IDs remains almost constant with the year of observation.
-3.
-The current density of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current density of IDs slightly increases.
-The current density distribution of IDs slightly increases with the year of observation, but after normalization, the current density distribution remains identical across the five years, thus no effect of the long-term (i.e.
-solar cycle) temporal variations.
-
-# Acknowledgements
-
-Sunspot data from the World Data Center SILSO, Royal Observatory of Belgium, Brussels.
-ARTEMIS solar wind time interval data from the OMNI database.
-ARTEMIS solar wind time interval data from OMNIWEB, link: [omniweb.gsfc.nasa.gov/ftpbrowser/themis_b_sw.txt](https://omniweb.gsfc.nasa.gov/ftpbrowser/themis_b_sw.txt).
-
-# Appendix
-
-## Effect of the time resolution on the discontinuity properties
-
-The transition time $\Delta T$ is determined in one second resolution data for all our missions to reduce the system error.
-(Note that highest time resolution of the data is not needed for the transition time determination by fitting method).
-
-![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-tsEffect}
+- The distribution of the normalized thickness and current density of IDs remain constant over time at 1 AU on a yearly scale.

### 2024-09-09 presentations/grpMeeting_Zijin_2024-09.qmd
update: presentation time scale

@@
 
-![Examples of IDs from ARTEMIS, STEREO, and Wind](../figures/fig_examples.png){#fig-examples}
+"Discontinuous changes in plasmas parameters and magnetic fields"
+
+![Examples of IDs from Juno, ARTEMIS, STEREO, and Wind](../figures/fig_examples.png){#fig-examples}
 
@@
 
-<!-- During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity.
+::: {.notes}
+During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity.
 However, by the end of the mission's cruise phase, there was a significant decline in solar activity.
 This variation underscores the importance of calibrating the discontinuity properties in relation to solar activity levels to account for temporal fluctuations.
--->
+:::
 
@@
 ::: {#fig-windDistribution}
-![](../figures/wind_distribution_time.png)
+![](../figures/wind_distribution_time_year.svg)
 
@@
 Solar wind parameters associated with the IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) grouped by the year of observation.
-Panel (a) solar wind density, (b) magnetic field, (c) fitted magnetic field $A$ in @eq-fit.
+Panel (a) solar wind density, (b) magnetic field, (c) fitted magnetic field amplitude.
 :::
+
+::: {.notes}
+The change in the current density could be explained by the change in the solar wind properties with the solar cycle, as shown in @fig-swParameters.
+Density and magnetic field asscoiated with the discontinuities increases with the solar cycle approaching the solar minimum, which could lead to the increase of the current density of the discontinuities with fixed normalized current density.
+:::
+
+![Grouped by month for the year 2013](../figures/wind_distribution_time_month.svg)
+
+![Grouped by week for the first two months of 2013](../figures/wind_distribution_time_week.svg)
 
@@
 
-$$
-B(t; A, \mu, \sigma, {\mathrm{form=logistic}}) = A \left[1 - \frac{1}{1 + e^{\alpha}} \right]
-$${#eq-fit}
-
-<!-- However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind speed derived from solar wind propagation models.
-Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location.
-This model, which utilizes the BATSRUS MHD solver, simulates the propagation of solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively covering the region pertinent to our study.
-The MSWIM2D model provides output data with an hourly time resolution as shown in @fig-model.
-The comparison of magnetic field magnitudes from MSWIM2D with those measured by Juno, after averaging to the same time resolution, reveals a strong correlation, confirming the model’s reliability.
--->
-
 ::: {#fig-model}
@@
 **a,** Magnetic field magnitude from MSWIM2D and Juno. **b-c,** Plasma speed and density from MSWIM2D model. **d,** Juno radial distance from the Sun.
+:::
+
+::: {.notes}
+However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind speed derived from solar wind propagation models.
+Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location.
+This model, which utilizes the BATSRUS MHD solver, simulates the propagation of solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively covering the region pertinent to our study.
+The MSWIM2D model provides output data with an hourly time resolution as shown in @fig-model.
+The comparison of magnetic field magnitudes from MSWIM2D with those measured by Juno, after averaging to the same time resolution, reveals a strong correlation, confirming the model’s reliability.
 :::
@@
 This number (occurrence rate) decreases with distance (with time after $\sim 2013$), as Juno moves from $1$ AU to $5$ AU.
-We will use the similar comparison for discontinuity characteristics and occurrence rate derived for PSP and Juno.
-The radial distance of Juno for 2011-2016 is shown in @fig-model.
 :::
@@
 
-- The thickness of IDs increases with radial distance, but when normalized to the ion inertial length, the thickness decreases.
+- The thickness of IDs increases with radial distance, but when normalized to the ion inertial length, it decreases.
 
-- The current density of IDs decreases with radial distance, but when normalized to the Alfvén current, the current density of IDs increases.
+- The current density of IDs decreases with radial distance, but when normalized to the Alfvén current, it increases.
 
 - The distribution of the normalized thickness and current density of IDs remain constant over time at 1 AU on a yearly scale.
+
+## References

### 2024-09-09 src/main.jl

@@ -20,7 +20,7 @@ include("io.jl")
 include("plot.jl")
 
 figure_dir = projectdir("figures")
-easy_save(fname) = Beforerr.easy_save(fname; dir=figure_dir)
+easy_save(fname, fig) = Beforerr.easy_save(fname, fig; formats=[:svg], dir=figure_dir)
 
 datalimits_f = x -> quantile(x, [0.02, 0.98])
 

### 2024-09-09 src/juno/config.py
feat: add plasma beta statistics

@@ -36,7 +36,6 @@ class Config(BaseModel):
     model_config = ConfigDict(arbitrary_types_allowed=True, extra="allow")
 
     tau: timedelta = DEFAULT_TAU
-    ts: timedelta = DEFAULT_TS
     timerange: list[datetime] = DEFAULT_TIMERANGE
 
     data_dir: Path = datadir() / "05_reporting"
@@ -48,6 +47,7 @@ class Config(BaseModel):
 class JunoConfig(Config, IDsDataset):
     _sparse_num = 10
     name: str = "JNO"
+    ts: timedelta = DEFAULT_TS
     plasma_data: pl.DataFrame = pl.scan_parquet(JNO_PLASMA_DF_PATH).sort("time")
     plasma_meta: PlasmaDataset = PlasmaDataset(
         density_col="plasma_density", velocity_cols=["v_x", "v_y", "v_z"]

### 2024-09-09 src/main.jl

@@ -13,6 +13,7 @@ using Beforerr
 import Beforerr: easy_save
 using LaTeXStrings
 using Discontinuity
+using Discontinuity.DefaultMapping
 
 set_aog_theme!()
 
@@ -22,5 +23,10 @@ include("plot.jl")
 figure_dir = projectdir("figures")
 easy_save(fname, fig) = Beforerr.easy_save(fname, fig; formats=[:svg], dir=figure_dir)
 
+year_map = :time => nonnumeric ∘ year => "Year"
+beta_map = :β => log10 => L"Log Plasma Beta $\beta$"
+
 datalimits_f = x -> quantile(x, [0.02, 0.98])
 
+import Base.log10
+log10(x::Unitful.Quantity) = log10(ustrip(x))

### 2024-09-10 src/main.jl
fix: using Unitful

@@ -14,6 +14,7 @@ import Beforerr: easy_save
 using LaTeXStrings
 using Discontinuity
 using Discontinuity.DefaultMapping
+using Unitful
 
 set_aog_theme!()
 

### 2024-09-15 article.qmd
update: presentation time scale
update: add roam link

@@
     text: Overleaf
+  - text: Roam Research
+    href: https://roamresearch.com/#/app/zijin/page/1Q5Q5Q5Q5
 abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
@@
 Finally, we present the results of the spatial evolution of the discontinuities with respect to their characteristics (spatial scales and current density), and discuss the implications of our findings.
+
+<!-- 
+References::
+  - @sodingRadialLatitudinalDependencies2001
+-->
 
@@
 
-![Examples of IDs from ARTEMIS, STEREO, and Wind](figures/fig_examples){#fig-examples}
+![Examples of IDs from Juno, ARTEMIS, STEREO, and Wind](figures/fig_examples){#fig-examples}
 
@@
 
-## Dependences of occurrence rate
-
-@marianiStatisticalStudyMagnetohydrodynamic1983
-@tsurutaniInterplanetaryDiscontinuitiesTemporal1979
-@marianiVariationsOccurrenceRate1973
-
-TODO: how is the occurrence rate related to the formation mechanism?
-
 ## Spatial variations of discontinuity properties
@@
 TODO:
+
+## Dependences of occurrence rate
+
+@sodingRadialLatitudinalDependencies2001
+@leppingMagneticFieldDirectional1986
+@marianiStatisticalStudyMagnetohydrodynamic1983
+@marianiVariationsOccurrenceRate1973
+@tsurutaniInterplanetaryDiscontinuitiesTemporal1979
+
+TODO: how is the occurrence rate related to the formation mechanism?
 

### 2024-09-16 scripts/data.py
fix: Juno config

@@ -1,0 +1,4 @@
+#| hide
+from juno.config import JunoConfig
+
+JunoConfig().produce_or_load()

### 2024-09-16 src/juno/config.py

@@ -7,11 +7,10 @@ from pathlib import Path
 
 from beforerr.project import datadir
 from space_analysis.meta import PlasmaDataset
-from discontinuitypy.datasets import IDsDataset
-from discontinuitypy.config import SpeasyIDsConfig
+from discontinuitypy.config import SpeasyIDsConfig, IDsConfig
 from discontinuitypy.mission import WindConfigBase, ThemisConfigBase, StereoConfigBase
 
-from .juno import get_mag_paths
+from .juno import get_mag_data
 from math import ceil
 
 
@@ -44,50 +43,24 @@ class Config(BaseModel):
     test: bool = False
 
 
-class JunoConfig(Config, IDsDataset):
-    _sparse_num = 10
+class JunoConfig(Config, IDsConfig):
     name: str = "JNO"
     ts: timedelta = DEFAULT_TS
     plasma_data: pl.DataFrame = pl.scan_parquet(JNO_PLASMA_DF_PATH).sort("time")
     plasma_meta: PlasmaDataset = PlasmaDataset(
-        density_col="plasma_density", velocity_cols=["v_x", "v_y", "v_z"]
+        density_col="plasma_density",
+        velocity_cols=["v_x", "v_y", "v_z"],
+        temperature_col="plasma_temperature",
     )
 
-    def model_post_init(self, __context):
+    def get_data(self):
         self.data = self.mag_df
 
     @property
     def mag_df(self):
         """Magnetic field data in a single dataframe"""
-        return pl.scan_ipc(self.mag_paths).sort("time").unique("time")
-
-    @property
-    def mag_dfs(self):
-        s_paths = split_list(self.mag_paths, self.split)
-        return [pl.scan_ipc(paths).sort("time").unique("time") for paths in s_paths]
-
-    @property
-    def mag_paths(self):
         freq = 1 / self.ts.total_seconds()
-        return get_mag_paths(self.timerange, freq)
-
-    def _get_and_process_data(self, **kwargs):
-        for mag_df in self.mag_dfs:
-            yield (
-                IDsDataset(
-                    mag_data=mag_df,
-                    plasma_data=self.plasma_data,
-                    plasma_meta=self.plasma_meta,
-                    tau=self.tau,
-                    ts=self.ts,
-                    method=self.method,
-                )
-                .find_events(
-                    return_best_fit=False, sparse_num=self._sparse_num, **kwargs
-                )
-                .update_candidates_with_plasma_data()
[…]

### 2024-09-16 src/juno/juno.py

@@ -46,3 +46,11 @@ def get_mag_paths(
     end = timerange[1].replace(tzinfo=None)
     # filter by timerange
     return [file for file, date in zip(files, dates) if date >= start and date <= end]
+
+
+def get_mag_data(
+    timerange: list[datetime],
+    freq: float,
+):
+    paths = get_mag_paths(timerange, freq)
+    return pl.scan_ipc(paths).sort("time").unique("time")

### 2024-09-17 index.qmd
update: wt analysis

@@
     text: Tana
-draft: true
 ---

### 2024-09-17 scripts/plot.jl

@@ -1,0 +1,24 @@
+using DrWatson
+@quickactivate
+include("../src/main.jl")
+import Base.copy
+
+Base.copy(x::Figure) = x
+safe_produce(f, c; kwargs...) = produce_or_load(f, c, figure_dir; filename=hash, suffix="svg", loadfile=false, kwargs...)
+
+function plot_dist_r(config)
+    @unpack df = config
+    return plot_dist(
+        data(df) * mapping(color=r_map);
+        datalimits=datalimits_f,
+    )
+end
+
+function main()
+    # j_events_taus = load_taus(60:-10:20)
+    jno_df = load(datadir("updated_events_JNO_tr=20110825-20160630_method=fit_tau=0:01:00_ts=0:00:01.arrow"))
+    config = @dict df = jno_df
+    safe_produce(plot_dist_r, config; prefix="juno_distribution_r")
+end
+
+main()

### 2024-09-21 article.qmd
update: manuscript intro and importance

@@
 
+TODO: annihilation mechanisms and related references
+
 Rapid variations in interplanetary magnetic fields, commonly recognized as solar wind magnetic discontinuities [@colburnDiscontinuitiesSolarWind1966], embody localized transient rotations or jumps of the magnetic field.
-Considered important for efficient plasma heating, they carry the most intense currents found in the solar wind and obserrved throughout the heliosphere from inner heliosphere [@liuCategorizingMHDDiscontinuities2022] to the heliosheath [@burlagaCurrentSheetsHeliosheath2011].
-Theoretical models [@lerchePropagationMagneticDisturbances1975; @medvedevDissipativeDynamicsCollisionless1997] and MHD simulations [@grecoIntermittentMHDStructures2008; @grecoStatisticalAnalysisDiscontinuities2009; @yangFormationRotationalDiscontinuities2015] suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence.
-These nonlinear processes can create significant isolated disturbances to the otherwise adiabatic evolution of the solar wind flow (?Reference?) and host many processes, including magnetic reconnection (?Reference?) and Fermi acceleration of particles [@wentzelMotionMagneticDiscontinuities1964].
-Moreover, they contribute significantly to the magnetic fluctuation spectra [@borovskyContributionStrongDiscontinuities2010] and can affect space weather [@tsurutaniReviewInterplanetaryDiscontinuities2011].
-Therefore, the study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind and test the local generation mechanism of discontinuities.
+They are microscale structures observed throughout the heliosphere, from inner heliosphere [@liuCategorizingMHDDiscontinuities2022] to the heliosheath [@burlagaCurrentSheetsHeliosheath2011].
+Despite being discovered over half a century ago, the specific origins and circumstances of their formation remain subjects of ongoing debate.
+Historically, it has been believed that discontinuities originate inside 1 AU, probably near or at the Sun, and are then convected passively outward by the solar wind [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979; @sodingRadialLatitudinalDependencies2001; @borovskyFluxTubeTexture2008].
+However, the good agreement observed in the waiting-time analysis between solar wind data and magnetohydrodynamic (MHD) turbulence simulations [@grecoStatisticalAnalysisDiscontinuities2009] indicates that a significant portion of these discontinuities could be associated with flux-tube boundaries.
+These structures are likely intermittent, arising spontaneously and forming rapidly and locally within MHD turbulence.
+The annihilation mechanisms for these discontinuities are also uncertain.
+These discontinuities may be unstable features and some could rapidly wane or decay [@neugebauerTangentialDiscontinuitiesSolar1986].
+Conversely, they can be very stable and persist over time intervals comparable to the convection time or the solar rotation period.
+<!-- (?Reference?).
+-->
+Further complicating this picture is the presence of different types of discontinuities in interplanetary space—specifically tangential and rotational discontinuities, which are classically regarded as static solutions to the MHD equations.
+These distinct types may arise from different sources and may evolve in unique ways.
+Investigating discontinuities across large radial distances has the potential to address these fundamental questions regarding their origin and evolution.
+
+Discontinuities are not only an interesting topic in themselves but are also considered crucial for understanding the dynamics of the solar wind and cosmic rays.
+Theoretical models [@lerchePropagationMagneticDisturbances1975; @medvedevDissipativeDynamicsCollisionless1997] and MHD simulations [@grecoIntermittentMHDStructures2008; @yangFormationRotationalDiscontinuities2015] suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and Alfvénic turbulence.
+These nonlinear processes can create significant disturbances to the otherwise adiabatic evolution of the solar wind flow.
+These theoretical predictions are supported by spacecraft observations, which have revealed that the solar wind magnetic field follows the Parker model of the heliospheric current sheet only on average.
+Localized transient currents, which can be significantly more intense than those predicted by the Parker model, are carried by various discontinuities observed as strong variations in magnetic field components [@colburnDiscontinuitiesSolarWind1966; @burlagaMicroScaleStructuresInterplanetary1968; @turnerOrientationsRotationalTangential1971].
+These discontinuities contribute significantly to the magnetic fluctuation spectra [@borovskyContributionStrongDiscontinuities2010] and play an important role in energy dissipation processes such as plasma heating [@osmanIntermittencyLocalHeating2012] and particle acceleration [@wentzelMotionMagneticDiscontinuities1964; @dmitrukTestParticleEnergization2004; @tesseinAssociationSuprathermalParticles2013].
+More specifically, because tangential discontinuities act as boundaries separating different types of plasma and often involve oppositely directed magnetic fields on either side, they are potential regions where magnetic reconnection or merging can occur.
+Additionally, rotational discontinuities, being nonlinear large-amplitude Alfvén waves, are expected to significantly contribute to the diffusion coefficient for cosmic rays.
+Finally, these discontinuities can produce geomagnetic effects [@tsurutaniReviewInterplanetaryDiscontinuities2011] and impact space weather due to abrupt changes in external (solar wind) conditions.
+
 However, previous study of solar wind discontinuities evolution [@sodingRadialLatitudinalDependencies2001] in the outer heliosphere were rarely in conjunction with measurements closer to the Sun.

### 2024-09-21 article.qmd
update: intro purpose and previous study

@@
 TODO: annihilation mechanisms and related references
+TODO: References to stabliity and time scales
 
@@
 Conversely, they can be very stable and persist over time intervals comparable to the convection time or the solar rotation period.
-<!-- (?Reference?).
--->
 Further complicating this picture is the presence of different types of discontinuities in interplanetary space—specifically tangential and rotational discontinuities, which are classically regarded as static solutions to the MHD equations.
@@
 
-However, previous study of solar wind discontinuities evolution [@sodingRadialLatitudinalDependencies2001] in the outer heliosphere were rarely in conjunction with measurements closer to the Sun.
-Moreover, the intervals in their study spread over multiple solar cycles though they are selected during solar activity minimum.
-Thus it is presently unclear whether their frequency and properties are the result of solar variability or due to the natural evolution of the discontinuities during their propagation and interaction with the ambient solar wind.
+In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft during its cruise phases (2011-2016) ([[@boltonJunoMission2017]]).
+The primary goal of this paper is to investigate the radial dependence of the occurrence rate and other properties of discontinuities, in order to gain insights into their evolution and origin.
+Continuous measurements at 1 AU from missions such as Wind, ARTEMIS, and STEREO have been utilized to distinguish temporal effects from spatial variations by examining the characteristics of discontinuities at two radial distances simultaneously.
+This distinction is crucial because temporal variations could easily be misinterpreted as spatial variations ([[@tsurutaniInterplanetaryDiscontinuitiesTemporal1979]]).
+Due to the potential misidentification of the normal direction of the magnetic field when using the minimum variance analysis (MVA) method [@hausmanDeterminingNatureOrientation2004; @liuFailuresMinimumVariance2023], we do not differentiate between the types of discontinuities, whether they are tangential, rotational, or either [@neugebauerReexaminationRotationalTangential1984].
 
-The goal of our paper is to investigate, statistically, discontinuities at different radial distance in the outer heliosphere to obtain a understanding of their formation and evolution.
-Our methodology involves integrating Juno measurements [@connerneyJunoMagneticField2017] between $1$ and $5$ AU with those at $1$ AU to distinguish temporal effect and spatial variations by examining the discontinuity characteristics at two radial distances simultaneously.
+Previous studies on the radial dependencies of solar wind discontinuities have been conducted by several authors (e.g., [[@marianiVariationsOccurrenceRate1973]]; [[@tsurutaniInterplanetaryDiscontinuitiesTemporal1979]]; [[@sodingRadialLatitudinalDependencies2001]]).
+However, the data used in these studies were rarely obtained in conjunction with measurements at fixed radial distances, and the methods employed to identify discontinuities were not robust for situations involving weak magnetic fields and long durations encountered at large radial distances.
+Additionally, some measurements at different radial distances were significantly separated in time, with limited time ranges covered ([[@sodingRadialLatitudinalDependencies2001]]).
+Consequently, there remains ambiguity in interpreting the results of these studies.
 
-First, the missions, instruments and data used are listed.
-Then, we briefly describe the method used to identify the discontinuities and the model used to estimate the plasma state at Juno location due to the lack of plasma data during its cruise phase.
-Finally, we present the results of the spatial evolution of the discontinuities with respect to their characteristics (spatial scales and current density), and discuss the implications of our findings.
-
-<!-- 
-References::
-  - @sodingRadialLatitudinalDependencies2001
--->
+The paper is structured as follows.
+First, we outline the missions, instruments, and data utilized in this study.
+Next, we provide a brief description of the method used to identify discontinuities and the model employed to estimate the plasma state at the Juno location, necessitated by the absence of plasma data during its cruise phase.
+In the subsequent sections, we present the results concerning the spatial variation of discontinuities, focusing on their occurrence rate and characteristics, such as spatial scales and current density.
+Finally, we discuss the implications of our findings in the context of the origin and evolution of these discontinuities in the solar wind.
 

### 2024-09-21 article.qmd
update: bib format

@@
 
-In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft during its cruise phases (2011-2016) ([[@boltonJunoMission2017]]).
+In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft during its cruise phases (2011-2016) [@boltonJunoMission2017].
 The primary goal of this paper is to investigate the radial dependence of the occurrence rate and other properties of discontinuities, in order to gain insights into their evolution and origin.
 Continuous measurements at 1 AU from missions such as Wind, ARTEMIS, and STEREO have been utilized to distinguish temporal effects from spatial variations by examining the characteristics of discontinuities at two radial distances simultaneously.
-This distinction is crucial because temporal variations could easily be misinterpreted as spatial variations ([[@tsurutaniInterplanetaryDiscontinuitiesTemporal1979]]).
+This distinction is crucial because temporal variations could easily be misinterpreted as spatial variations [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979].
 Due to the potential misidentification of the normal direction of the magnetic field when using the minimum variance analysis (MVA) method [@hausmanDeterminingNatureOrientation2004; @liuFailuresMinimumVariance2023], we do not differentiate between the types of discontinuities, whether they are tangential, rotational, or either [@neugebauerReexaminationRotationalTangential1984].
 
-Previous studies on the radial dependencies of solar wind discontinuities have been conducted by several authors (e.g., [[@marianiVariationsOccurrenceRate1973]]; [[@tsurutaniInterplanetaryDiscontinuitiesTemporal1979]]; [[@sodingRadialLatitudinalDependencies2001]]).
+Previous studies on the radial dependencies of solar wind discontinuities have been conducted by several authors [e.g., @marianiVariationsOccurrenceRate1973; @tsurutaniInterplanetaryDiscontinuitiesTemporal1979; @sodingRadialLatitudinalDependencies2001].
 However, the data used in these studies were rarely obtained in conjunction with measurements at fixed radial distances, and the methods employed to identify discontinuities were not robust for situations involving weak magnetic fields and long durations encountered at large radial distances.
-Additionally, some measurements at different radial distances were significantly separated in time, with limited time ranges covered ([[@sodingRadialLatitudinalDependencies2001]]).
+Additionally, some measurements at different radial distances were significantly separated in time, with limited time ranges covered [@sodingRadialLatitudinalDependencies2001].
 Consequently, there remains ambiguity in interpreting the results of these studies.

### 2024-09-21 src/main.jl
update: time map

@@ -24,9 +24,6 @@ include("plot.jl")
 figure_dir = projectdir("figures")
 easy_save(fname, fig) = Beforerr.easy_save(fname, fig; formats=[:svg], dir=figure_dir)
 
-year_map = :time => nonnumeric ∘ year => "Year"
-beta_map = :β => log10 => L"Log Plasma Beta $\beta$"
-
 datalimits_f = x -> quantile(x, [0.02, 0.98])
 
 import Base.log10

### 2024-09-21 src/plot.jl

@@ -10,6 +10,9 @@ r_lab = L"Radial Distance ($AU$)"
 r_map = :radial_distance => nonnumeric ∘ round_c  => r_lab
 tau_map = :tau => nonnumeric => "τ (s)"
 year_map = :time => nonnumeric ∘ year  => "Year"
+month_map = :time => nonnumeric ∘ month  => "Month"
+week_map = :time => nonnumeric ∘ week => "Week";
+beta_map = :β => log10 => L"Log Plasma Beta $\beta$"
 
 function plot_duration(plt; 
     datalimits_f = x -> quantile(x, [0.02, 0.98]),

### 2024-09-23 article.qmd
update: occurrence rate analysis and consider different hypotheses

@@
 
-@sodingRadialLatitudinalDependencies2001
-@leppingMagneticFieldDirectional1986
-@marianiStatisticalStudyMagnetohydrodynamic1983
-@marianiVariationsOccurrenceRate1973
-@tsurutaniInterplanetaryDiscontinuitiesTemporal1979
+The observed increase in the average waiting time between discontinuities with radial distance prompts us to explore different hypotheses to explain this phenomenon.
+At any given radial distance, discontinuities may originate from two primary sources: those generated near the Sun and convected outward by the solar wind, and those formed locally.
+Since the solar wind speed is significantly higher than the Alfvén speed—which characterizes the propagation speed of rotational discontinuities (RDs)—the fraction of inward-propagating discontinuities is expected to be negligible.
+Additionally, when observations are made by a single spacecraft, some discontinuities may be missed due to unfavorable positioning or limitations in detection methods.
 
-TODO: how is the occurrence rate related to the formation mechanism?
+First, we consider the limitations of our current detection methods.
+An increase in the duration of discontinuities could render some of them unidentifiable if their duration becomes comparable to the time interval used in our analysis.
+Although we observe a slight increase in the average duration of discontinuities with radial distance, this increase is relatively small.
+The overall population of discontinuities is still predominantly characterized by those with short durations (see Figure X in the appendix).
+Since our method normalizes the change in the magnetic field by the surrounding magnetic field, a decrease in magnetic field variation with radial distance alone does not necessitate non-identification.
+Notably, our results differ from previous studies [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979], which reported typical durations of 2 to 3 seconds at 1 AU and 10 to 30 seconds at 5 AU.
+In our analysis, however, the observed durations remain below 10 seconds at 5 AU, suggesting that our method may be more effective at identifying shorter-duration events than those reported in prior studies.
+
+If the majority of distant discontinuities are generated locally, and assuming that the primary conditions for their generation do not change significantly with radial distance, we would expect them to be uniformly distributed throughout the hemisphere.
+Consequently, the occurrence rate should be independent of radial distance.
+To test this hypothesis, we examined the relationship between waiting time and plasma beta.
+However, even at a 99% statistical significance level, we could not reject the null hypothesis that these two variables are independent.
+Therefore, if discontinuities are primarily generated locally, there must be other factors influencing their generation rates.
+
+Alternatively, we consider the hypothesis that the majority of discontinuities are generated close to the Sun.
+If we assume that discontinuities are one-dimensional, infinitely extended structures, then without annihilation, all discontinuities passing through one location would also pass through other radial distances.
+However, a more realistic assumption is that discontinuities are three-dimensional curved surfaces with lengths and widths proportional to their thickness.
+In this scenario, the occurrence rate observed by a single spacecraft does not represent the total number of discontinuities within a given shell.
+Since our spacecraft travels within the ecliptic plane and the normal direction of most discontinuities lies within this plane, it is necessary to project the discontinuities onto a circular cross-section.
+The projected lengths should then be normalized by the circumference of the circle to estimate the total number of discontinuities within the cylindrical shell.
+The normalization factor is  $d \sin\theta_{n,v} / r$ , where $d$ is the thickness of the discontinuity, $\theta_{n,v}$ is the angle between the normal direction of the discontinuity and the solar wind velocity, and  $r$ is the radial distance from the Sun (the result is shown in the appendix).
+Accounting for this factor reduces the differences in the normalized occurrence rates observed by different spacecraft.
+However, we cannot rule out the possibility that some discontinuities may be annihilated as they convect outward with the solar wind.
+This annihilation process would result in a lower number of discontinuities observed by Juno at larger radial distances.
+Therefore, under this hypothesis, the annihilation process must play a significant role.
+(However, if we disregard changes in the thickness and only account for the factor of the circumference of the circle, the normalized discontinuities observed by Juno would be consistent with those observed at 1 AU.)
+
+![](figures/ocr/ocr_normalized_by_r.svg)
 

### 2024-09-23 src/trans.jl
feat: new orientation analysis

@@ -1,0 +1,22 @@
+using LinearAlgebra
+
+function rotation_angle(u, v)
+    cos_theta = dot(u, v) / (norm(u) * norm(v))
+    theta = acos(cos_theta)
+    return rad2deg(theta)
+end
+
+"""
+# Notes
+- en_cols = [:Vn_x, :Vn_y, :Vn_z] # unit vector of the normal from MVA
+- ek_cols = [:k_x, :k_y, :k_z] # unit vector of the normal from cross product
+- v_cols = [:v_x, :v_y, :v_z] # vector of the velocity
+"""
+function calc_rotation_angle!(df)
+    @rtransform!(
+        df,
+        :θ_vn = rotation_angle([:v_x, :v_y, :v_z], [:Vn_x, :Vn_y, :Vn_z]),
+        :θ_vk = rotation_angle([:v_x, :v_y, :v_z], [:k_x, :k_y, :k_z]),
+        :θ_nk = rotation_angle([:Vn_x, :Vn_y, :Vn_z], [:k_x, :k_y, :k_z]),
+    )
+end

### 2024-09-23 src/io.jl
update code

@@ -1,30 +1,57 @@
 using Printf
 using Discontinuity
-import Discontinuity: load
+using Discontinuity: load
+include("trans.jl")
 data_path = datadir("05_reporting")
 
-function Discontinuity.load(;tau=60, ts=1.00, name="JNO", method="fit", dir=data_path)
+function Discontinuity.load(path, name_cols::Pair{Symbol}...)
+    df = load(path)
+    insertcols!(df, name_cols...)
+    return df
+end
+
+function Discontinuity.load(; tau=60, ts=1.00, name="JNO", method="fit", dir=data_path)
     ts_str = @sprintf "ts_%.2fs" ts
-    df = Discontinuity.load(joinpath(dir, "events.$name.$method.$(ts_str)_tau_$(tau)s.arrow"))
+    df = load(joinpath(dir, "events.$name.$method.$(ts_str)_tau_$(tau)s.arrow"))
     df.tau .= tau
     df.ts .= ts
     return df
 end
 
 function load_tau(tau)
-    df = load(tau=tau)
+    df = Discontinuity.load(; tau=tau)
     df.label .= "$tau s"
     println("Number of events: ", size(df, 1))
     return df
 end
 
+WIND_PATH = "updated_events_Wind_tr=20110825-20160630_method=fit_tau=0:01:00_ts=0:00:00.090909.arrow"
+JNO_PATH = "updated_events_JNO_tr=20110825-20160630_method=fit_tau=0:01:00_ts=0:00:01.arrow"
+
+post_process!(df) = df |> calc_rotation_angle! |> Discontinuity.unitize! |> Discontinuity.calc_beta!
+
+function load_wind(; path=WIND_PATH)
+    df = load(datadir(path), :dataset => "Wind")
+    rename!(df, ["VX (GSE)", "VY (GSE)", "VZ (GSE)"] .=> ["v_x", "v_y", "v_z"])
+    Discontinuity.unitize!(df, "SW Vth", u"km/s")
+    Discontinuity.calc_T!(df, "SW Vth")
+    return df |> post_process!
+end
+
+function load_jno(; path=JNO_PATH)
+    df = load(datadir(path), :dataset => "Juno") 
+    rename!(df, :radial_distance => :r)
+    Discontinuity.unitize!(df, "T", u"K")
+    return df |> post_process!
+end
+
 """
-## Note
+# Notes
 
 This will remove events that appear in multiple taus datasets. 
[…]

### 2024-10-09 article.qmd
fix: figure format
update: rm Roam link

@@
     text: Overleaf
-  - text: Roam Research
-    href: https://roamresearch.com/#/app/zijin/page/1Q5Q5Q5Q5
 abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
@@
 ::: {#fig-windDistribution}
-![](figures/wind_distribution_time)
+![](figures/wind_distribution_time.svg)
 
@@
 ::: {#fig-swParameters}
-![](figures/sw_paramters_time)
+![](figures/sw_paramters_time.svg)
 

### 2024-10-09 notes.qmd
update: dist with time subsets
feat: add plasma beta statistics
feat: update data
update

@@
 title: Notes
-jupyter: python3
 ---
 
+# Data
+
+`updated_events_JNO_method=fit_tau=0:01:00_ts=0:00:01.arrow` and `events.JNO.fit.ts_1.00s_tau_60s.arrow` are the same data for backward compatibility.
+
+`updated_events_Wind_tr=20110825-20160630_method=fit_tau=0:01:00_ts=0:00:00.090909.arrow` and `events.Wind.fit.ts_0.09s_tau_60s.arrow`
+
 # Updates
+
+### 09/23/2024
+
+::: {.column-page}
+::: {#fig-ocr-v layout-nrow="1"}
+
+![Wind](figures/ocr/ocr_wind_daily_v.svg)
+
+![](images/söding2001_fig4.png)
+
+Distribution of daily averages of DD per day over v with the fit of an linear function.
+:::
+:::
 
@@
     -   [ ] Re-calculate the occurrence rate of IDs
-    -   [ ] Contribution of discontinuities to the power spectrum
+    -   [x] Distribution of $δB/B$ over radius (related to the alfvenicity, identification standard about neighboring fluctuations)
+    -   [x] $\theta_{n,v}$ distribution
+    -   [ ] Correlation between plasma beta and thickness / current density
+
     -   [ ] Check Datagap
@@
     -   [ ] Validate the effects of calibrate candidate duration
-    -   [ ] Validate model density with `Voyager`
+
+    -   ~~Contribution of discontinuities to the power spectrum~~
+    -   ~~Validate model density with `Voyager`~~
 -   Identifaction

### 2024-11-03 notebooks/01_results_julia.qmd
Update figures with better resolution

---
title: Results (Julia)
---

```{julia}
using DrWatson
using Discontinuity
@quickactivate
include("../src/main.jl");
M = var_mapping()
```

```{julia}
wind_df = load_wind();
jno_df = load_jno();
```

## Check the discontinuities properties with time and radial distance

```{julia}
maps1 = [M.l_log M.l_norm_log; M.j_log M.j_norm_log]
maps2 = [M.density_log M.B_log; beta_map M.bm0_log];
```

```{julia}
temp_plot(layer::Layer) = m -> plot_dist(layer, m; datalimits=datalimits_f)
temp_plot(df::DataFrame; color=year_map) = temp_plot(data(df) * mapping(color=color))

fs = temp_plot(wind_df).([maps1, maps2])
fnames = ["wind_distribution_time", "wind_sw_paramters"]
easy_save.(fnames, fs) .|> display;
```

```{julia}
let df = jno_df # let df = j_events_taus
    fs = temp_plot(df; color=r_map).([maps1, maps2])
    fnames = ["juno_distribution_r", "juno_sw_paramters"]
    easy_save.(fnames, fs)
    display.(fs)
end;
```

### 2024-11-03 src/io.jl
fix due to update

@@ -66,7 +66,7 @@ function load_jno(; path=JNO_PATH)
     return df |> post_process!
 end
 
-function Discontinuity.load(sym::Symbol = :wind; kw...)
+function Discontinuity.load(sym::Symbol; kw...)
     func = sym == :wind ? load_wind : load_jno
     func(;kw...)
 end

### 2024-11-03 src/plot.jl

@@ -7,7 +7,7 @@ round_c(x) = round(Integer, x)
 # %%
 # Define the labels for the plots
 r_lab = L"Radial Distance ($AU$)"
-r_map = :radial_distance => nonnumeric ∘ round_c  => r_lab
+r_map = :r => nonnumeric ∘ round_c  => r_lab
 tau_map = :tau => nonnumeric => "τ (s)"
 year_map = :time => nonnumeric ∘ year  => "Year"
 month_map = :time => nonnumeric ∘ month  => "Month"

### 2024-11-04 notebooks/01_results_julia.qmd
update

@@
 
-fs = temp_plot(wind_df).([maps1, maps2])
-fnames = ["wind_distribution_time", "wind_sw_paramters"]
-easy_save.(fnames, fs) .|> display;
+let df = wind_df, fnames = ["wind_distribution_time", "wind_sw_paramters"]
+    fs = temp_plot(df).([maps1, maps2])
+    easy_save.(fnames, fs)
+    display.(fs)
+end
 ```
@@
 ```{julia}
-let df = jno_df # let df = j_events_taus
-    fs = temp_plot(df; color=r_map).([maps1, maps2])
-    fnames = ["juno_distribution_r", "juno_sw_paramters"]
+# let df = j_events_taus
+let df = jno_df, color = r_map, fnames = ["juno_distribution_r", "juno_sw_paramters"]
+    fs = temp_plot(df; color).([maps1, maps2])
     easy_save.(fnames, fs)
     display.(fs)
-end;
+end
 ```

### 2024-11-04 src/main.jl

@@ -17,14 +17,11 @@ using Discontinuity.DefaultMapping
 using Unitful
 
 set_aog_theme!()
-theme = (;colormap = Reverse(:tokyo))
-update_theme!(; theme...)
+theme = Theme(;colormap = Reverse(:tokyo), figure_padding=2)
+update_theme!(theme)
 
 include("io.jl")
 include("plot.jl")
-
-figure_dir = projectdir("figures")
-easy_save(fname, fig) = Beforerr.easy_save(fname, fig; formats=[:svg], dir=figure_dir)
 
 datalimits_f = x -> quantile(x, [0.02, 0.98])
 

### 2024-11-04 article.qmd
fix: update fitting function and improve figure references in article

@@
 After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to get the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$.
-The maximum variance direction is then fitted by a step-like functions to extract the parameters to properly describe the discontinuity (we used logistic function here).
+The maximum variance direction is then fitted by a hyperbolic tangent functions to extract the parameters to properly describe the discontinuity @eq-fit.
 Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.
@@
 $$
-B(t; A, \mu, \sigma, {\mathrm{form=logistic}}) = A \left[1 - \frac{1}{1 + e^{\alpha}} \right]
+B_m(t) = B_{m0} \tanh\left(\frac{t - t_0}{\Delta T}\right) + c
 $${#eq-fit}
 
-where $\alpha = (t - \mu)/{\sigma}$.
+where $B_{m0}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_0$ is the time of discontinuity, $\Delta T$ is the transition time, and $c$ is the offset of the magnetic field change (in the case of an ideal discontinuity with perfect rotational symmetry, $c$ should theoretically be zero.
+However, in the context of data processing, incorporating $c$ can enhance the fitting accuracy).
 
@@
 where $\mu_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
-For fitting method, the derivative of the magnetic field could be estimated as $d B_m / d t = A / 4 σ$.
+For fitting method, the derivative of the magnetic field could be estimated as $d B_m / d t = B_{m0} / \Delta T$.
 This estimate is more robust than the direct calculation of the derivative of the magnetic field, because the fitting method is less sensitive to the noise in the data and the time resolution of the data (see discussion in the appendix).
@@
 ::: {#fig-windDistribution}
-![](figures/wind_distribution_time.svg)
+![](figures/wind_distribution_time)
 
@@
 ::: {#fig-swParameters}
-![](figures/sw_paramters_time.svg)
+![](figures/wind_sw_paramters)
 
@@
 
-![](figures/ocr/ocr_normalized_by_r.svg)
+![](figures/ocr/ocr_normalized_by_r)
 

### 2024-11-04 notebooks/00_overview.qmd
feat: use qmd for overview notebook and configure execution settings

---
title: Overview
description: Juno Orbits and Sunspot Numbers
jupyter: python3
---

```{python}
import matplotlib.pyplot as plt
from beforerr.matplotlib import unify_axes_fontsize, sync_legend_colors, set_linewidth, hide_legend_lines
```

```{python}
import pandas as pd
import polars as pl
import scienceplots as scienceplots
from matplotlib.pyplot import Axes
from space_analysis.plot.basic import savefig
from space_analysis.utils.cdas import Variables

plt.rc("savefig", dpi=300)
plt.rc('figure.subplot', wspace = 0, hspace = 0)
```

```{python}
timerange = ["2011-08-01", "2016-07-01"]
fname = "juno-hg-loc_sunspot-number"

datasets = ['JUNO_HELIO1DAY_POSITION', 'EARTH_HELIO1DAY_POSITION', 'STA_HELIO1DAY_POSITION']
names = ['JUNO', 'EARTH', 'STA']
```

## Plotting Juno and other mission location

```{python}
dfs = []

for dataset, name in zip(datasets, names):
    ds_variables = Variables(
        dataset=dataset,
        timerange=timerange,
    )
    df = ds_variables.to_pandas()
    df = df.rename(columns={c: f"{name}_{c}" for c in df.columns})
    dfs.append(df)
```

```{python}
df_concated = pd.concat(dfs, axis=1)
```

```{python}
df = pl.DataFrame(df_concated.reset_index()).with_columns(
    JUNO_EARTH_HGI_LON_diff = (pl.col("JUNO_HGI_LON") - pl.col("EARTH_HGI_LON")).abs(),
    JUNO_STA_HGI_LON_diff = (pl.col("JUNO_HGI_LON") - pl.col("STA_HGI_LON")).abs(),
    JUNO_EARTH_HG_LON_diff = (pl.col("JUNO_HG_LON") - pl.col("EARTH_HG_LON")).abs(),
    JUNO_STA_HG_LON_diff = (pl.col("JUNO_HG_LON") - pl.col("STA_HG_LON")).abs(),
).with_columns(
    JUNO_EARTH_HG_LON_diff = pl.when(pl.col("JUNO_EARTH_HG_LON_diff")>180).then(360-pl.col("JUNO_EARTH_HG_LON_diff")).otherwise(pl.col("JUNO_EARTH_HG_LON_diff")),
    JUNO_STA_HG_LON_diff = pl.when(pl.col("JUNO_STA_HG_LON_diff")>180).then(360-pl.col("JUNO_STA_HG_LON_diff")).otherwise(pl.col("JUNO_STA_HG_LON_diff")),
)
```

```{python}
def plot_lon_diff(df,ax: Axes):
    ax.plot(df["Epoch"], df["JUNO_EARTH_HG_LON_diff"], label="Earth")
    ax.plot(df["Epoch"], df["JUNO_STA_HG_LON_diff"], label="STA")
    ax.set_ylabel("HG Longitude\nDifference\n[deg]")
```

## Plotting a solar cycle index

https://docs.sunpy.org/en/stable/generated/gallery/plotting/solar_cycle_example.html

```{python}
import sunpy.timeseries as ts
from astropy.time import Time
from sunpy.net import Fido
from sunpy.net import attrs as a
from sunpy.time import TimeRange
```

The U.S. Dept. of Commerce, NOAA, Space Weather Prediction Center (SWPC) provides recent solar cycle indices which includes different sunspot numbers, radio flux, and geomagnetic index. They also provide predictions for how the sunspot number and radio flux will evolve. Predicted values are based on the consensus of the Solar Cycle 24 Prediction Panel.

We will first search for and then download the data.

```{python}
time_range = TimeRange(timerange)
result = Fido.search(a.Time(time_range), a.Instrument('noaa-indices'))
f_noaa_indices = Fido.fetch(result)

noaa = ts.TimeSeries(f_noaa_indices, source='noaaindices').truncate(time_range)
```

We then load them into individual `~sunpy.timeseries.TimeSeries` objects.

Finally, we plot both ``noaa`` and ``noaa_predict`` for the sunspot number. In this case we use the S.I.D.C. Brussels International Sunspot Number (RI). The predictions provide both a high and low values, which we plot below as ranges.

```{python}
def plot_sunspot_number(noaa_indices_ts, ax):

    time : Time = noaa_indices_ts.time
    time = time.to_datetime()

    ax.scatter(time, noaa_indices_ts.quantity('sunspot RI'))
    ax.plot(time, noaa_indices_ts.quantity('sunspot RI'), label='Monthly')
    ax.plot(
        time, noaa_indices_ts.quantity('sunspot RI smooth'), label='Smoothed'
    )

    ax.set_ylim(bottom=0)
    ax.set_ylabel('Sunspot\nNumber\n[#]')
```

```{python}
fig, axes = plt.subplots(nrows=2, ncols=1, sharex=True, figsize=(10, 6))

plot_lon_diff(df, axes[0])
plot_sunspot_number(noaa, axes[1])
```

## Plotting OMNI and STEREO plasma data

```{python}
import yaml
from space_analysis.ds.tplot.plot import Config, plot, process_panel

file_path = 'omni_stereo.yml'
config = yaml.load(open(file_path), Loader=yaml.FullLoader)
config = Config(**config)
tvars2plot = []
```

```{python}
for p_config in config.panels:
    tvar2plot = process_panel(p_config)
    tvars2plot.append(tvar2plot)
```

```{python}
fig, axes = plot(tvars2plot, config)
```

## Overview plot

```{python}
with plt.style.context(['science', 'nature', 'no-latex']):
    figsize=(3.5, 6)
    fig, axes = plt.subplots(nrows=6, ncols=1, sharex=True, figsize=figsize)

    plot_lon_diff(df, axes[0])
    plot_sunspot_number(noaa, axes[1])
    plot(tvars2plot=tvars2plot, fig=fig, axes=axes[2:], config=config)

    for ax in axes:
        if ax.get_legend_handles_labels()[0]:
            legend = ax.legend(handletextpad=0, handlelength=0)

    set_linewidth(0.8)
    sync_legend_colors()
    hide_legend_lines()
    unify_axes_fontsize(fontsize='large')
    # savefig(fname)
```

![](../figures/juno-hg-loc_sunspot-number.png)

### 2024-11-10 article.qmd
update manuscript

@@
 
-In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft during its cruise phases (2011-2016) [@boltonJunoMission2017].
+In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft [@boltonJunoMission2017] during its cruise phases (2011-2016), with its orbits shown in panel (a) of @fig-fig-overview.
 The primary goal of this paper is to investigate the radial dependence of the occurrence rate and other properties of discontinuities, in order to gain insights into their evolution and origin.
@@
 
+# Dataset, models, and methods
+
+The solar wind plasma state, as evidenced by the sunspot number (referenced in panel (c) of @fig-overview), plays a crucial role in understanding the dynamics of discontinuities.
+During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity.
+However, by the end of the mission's cruise phase, there was a significant decline in solar activity.
+This variation underscores the importance of calibrating the discontinuity properties in relation to solar activity levels to account for temporal fluctuations.
+
 ::: {#fig-overview}
@@
 
-# Dataset, models, and methods
+Further analysis of @fig-overview highlights the significance of the heliographic longitudinal difference between the Juno mission and Earth as well as the STEREO-A mission.
+Specifically, when there is a substantial longitudinal difference between Juno and Earth, the difference between Juno and STEREO-A tends to be minimal, and vice versa.
+This longitudinal discrepancy between Earth and STEREO-A ensures comprehensive coverage of the plasma en route to Juno.
 
@@
 
-The solar wind plasma state, as evidenced by the sunspot number (referenced in @fig-overview), plays a crucial role in understanding the dynamics of discontinuities.
-During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity.
-However, by the end of the mission's cruise phase, there was a significant decline in solar activity.
-This variation underscores the importance of calibrating the discontinuity properties in relation to solar activity levels to account for temporal fluctuations.
-
-Further analysis of @fig-overview highlights the significance of the heliographic longitudinal difference between the Juno mission and Earth as well as the STEREO-A mission.
-Specifically, when there is a substantial longitudinal difference between Juno and Earth, the difference between Juno and STEREO-A tends to be minimal, and vice versa.
-This longitudinal discrepancy between Earth and STEREO-A ensures comprehensive coverage of the plasma en route to Juno.
-
 Datasets collected from missions such as STEREO, ARTEMIS, and WIND will complement observations from Juno, offering a broader contextual perspective on heliospheric conditions and enabling a multi-point analysis of discontinuity properties [@velliUnderstandingOriginsHeliosphere2020].
-The table below summarizes the time resolution of magnetic field and plasma data for PSP, Juno, Wind, ARTEMIS, and STEREO.
+The table below summarizes the time resolution of magnetic field and plasma data for Juno, Wind, ARTEMIS, and STEREO.
 
@@
 Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location.
-This model, which utilizes the BATSRUS MHD solver, simulates the propagation of solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively covering the region pertinent to our study.
+This model, which utilizes the BATSRUS MHD solver[@tothAdaptiveNumericalAlgorithms2012], simulates the propagation of solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively covering the region pertinent to our study.
 The MSWIM2D model provides output data with an hourly time resolution as shown in @fig-model.
@@
 $$
-B_m(t) = B_{m0} \tanh\left(\frac{t - t_0}{\Delta T}\right) + c
+B_l(t) = B_{l0} \tanh\left(\frac{t - t_0}{\Delta T}\right) + c_l
 $${#eq-fit}
 
-where $B_{m0}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_0$ is the time of discontinuity, $\Delta T$ is the transition time, and $c$ is the offset of the magnetic field change (in the case of an ideal discontinuity with perfect rotational symmetry, $c$ should theoretically be zero.
-However, in the context of data processing, incorporating $c$ can enhance the fitting accuracy).
+where $B_{l0}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_0$ is the time of discontinuity, $\Delta T$ is the transition time, and $c_l$ is the offset of the magnetic field change (in the case of an ideal discontinuity with perfect rotational symmetry, $c_l$ should theoretically be zero.
+However, in the context of data processing, incorporating $c_l$ can enhance the fitting accuracy).
 

### 2024-11-10 article.qmd
update: add discussion about Bn, PVI comparison, references to mission and clarification...

@@
 These theoretical predictions are supported by spacecraft observations, which have revealed that the solar wind magnetic field follows the Parker model of the heliospheric current sheet only on average.
-Localized transient currents, which can be significantly more intense than those predicted by the Parker model, are carried by various discontinuities observed as strong variations in magnetic field components [@colburnDiscontinuitiesSolarWind1966; @burlagaMicroScaleStructuresInterplanetary1968; @turnerOrientationsRotationalTangential1971].
+Localized transient currents, which can be significantly more intense than those predicted by the Parker model, are carried by various discontinuities observed as strong variations in magnetic field components [@colburnDiscontinuitiesSolarWind1966; @burlagaMicroscaleStructuresInterplanetary1968; @turnerOrientationsRotationalTangential1971].
 These discontinuities contribute significantly to the magnetic fluctuation spectra [@borovskyContributionStrongDiscontinuities2010] and play an important role in energy dissipation processes such as plasma heating [@osmanIntermittencyLocalHeating2012] and particle acceleration [@wentzelMotionMagneticDiscontinuities1964; @dmitrukTestParticleEnergization2004; @tesseinAssociationSuprathermalParticles2013].
@@
 
-In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft [@boltonJunoMission2017] during its cruise phases (2011-2016), with its orbits shown in panel (a) of @fig-fig-overview.
+In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft [@boltonJunoMission2017] during its cruise phases (2011-2016), with its orbits shown in panel (a) of @fig-overview.
 The primary goal of this paper is to investigate the radial dependence of the occurrence rate and other properties of discontinuities, in order to gain insights into their evolution and origin.
@@
 
-In this study we use datasets of four missions measuring solar wind magnetic field and plasma.
-Synergistic observations of these missions should advance our understanding of the solar wind discontinuities, their radial distribution and evolution [@velliUnderstandingOriginsHeliosphere2020].
-
-<!-- ![Near-Earth's and STEREO-A solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview} -->
-
-Datasets collected from missions such as STEREO, ARTEMIS, and WIND will complement observations from Juno, offering a broader contextual perspective on heliospheric conditions and enabling a multi-point analysis of discontinuity properties [@velliUnderstandingOriginsHeliosphere2020].
-The table below summarizes the time resolution of magnetic field and plasma data for Juno, Wind, ARTEMIS, and STEREO.
+In this study, we analyze Juno observations during its cruise phase from August 25, 2011, to July 30, 2016, spanning approximately 1,800 days.
+Data collected from missions such as STEREO, ARTEMIS, and WIND complement Juno’s observations, providing a broader perspective on heliospheric conditions and enabling a multi-point analysis of discontinuity properties [@velliUnderstandingOriginsHeliosphere2020].
+Specifically, we utilize magnetic fields from Juno [@boltonJunoMission2017], measured by the Juno Fluxgate Magnetometer (MAG) [@connerneyJunoMagneticField2017], alongside ion bulk velocity and plasma density with hourly resolution from a solar wind model at Juno’s location (described below).
+For ARTEMIS [@angelopoulosARTEMISMission2011], we use magnetic field data from the Fluxgate Magnetometer [@austerTHEMISFluxgateMagnetometer2008] and ion bulk velocity and plasma density derived from the Electrostatic Analyzer [@mcfaddenTHEMISESAPlasma2009].
+For STEREO[@kaiserSTEREOMissionIntroduction2008], we incorporate magnetic fields from the magnetic field experiment on IMPACT [@acuñaSTEREOIMPACTMagnetic2008; @luhmannSTEREOIMPACTInvestigation2008] and ion bulk velocity and plasma density from PLASTIC [@galvinPlasmaSuprathermalIon2008].
+For WIND, we include magnetic fields from the Magnetic Field Investigation (MFI) [@leppingWINDMagneticField1995] and ion bulk velocity and plasma density from the Solar Wind Experiment (SWE) [@ogilvieSWEComprehensivePlasma1995].
+The table below summarizes the time resolution of magnetic field and plasma data for each mission.
+These synergistic observations are expected to enhance our understanding of solar wind discontinuities, including their radial distribution and evolution.
 
@@
 
-We use Liu's [@liuMagneticDiscontinuitiesSolar2022] method to identify discontinuities in the solar wind.
-This method has better compatibility for the discontinuities with minor field changes, and is more robust to the situation encountered in the outer heliosphere.
-For each sampling instant $t$, we define three intervals: the pre-interval $[-1,-1/2]\cdot T+t$, the middle interval $[-1/,1/2]\cdot T+t$, and the post-interval $[1/2,1]\cdot T+t$, in which $T$ are time lags.
-Let time series of the magnetic field data in these three intervals are labeled ${\mathbf B}_-$, ${\mathbf B}_0$, ${\mathbf B}_+$, respectively.
-Then for an discontinuity, the following three conditions should be satisfied: (1) $\sigma({\mathbf B}_0) > 2\max\left(\sigma({\mathbf B}_-), \sigma({\mathbf B}_+)\right)$, (2) $\sigma\left({\mathbf B}_-+{\mathbf B}_+\right)>\sigma({\mathbf B}_-)+\sigma({\mathbf B}_+)$, and (3) $|\Delta {\mathbf B}|>|{\mathbf B}_{bg}|/10$, in which $\sigma$ and ${\mathbf B}_{bg}$ represent the standard deviation and the background magnetic field magnitude, and $\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)$.
-The first two conditions guarantee that the field changes of the discontinuity identified are large enough to be distinguished from the stochastic fluctuations or Alfven waves on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition.
+We employ Liu’s method [@liuMagneticDiscontinuitiesSolar2022] to identify discontinuities in the solar wind.
+This approach provides better compatibility for discontinuities with small magnetic field changes and demonstrates greater robustness for conditions in the outer heliosphere compared to traditional methods, namely the B-criterion [@burlagaDirectionalDiscontinuitiesInterplanetary1969] and the TS-criterion [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979].
+For each sampling time $t$, we define three intervals: the pre-interval $[-1,-1/2]\cdot T+t$, the middle interval $[-1/2,1/2]\cdot T+t$, and the post-interval $[1/2,1]\cdot T+t$, where $T$ represents time lags.
+The magnetic field timeseries in these three intervals are labeled as ${\mathbf B}_-$, ${\mathbf B}_0$, and ${\mathbf B}_+$, respectively.
+To identify a discontinuity, the following three conditions must be met:
+
+$$
+\begin{aligned}
+\sigma({\mathbf B}_0) &> 2\max\left(\sigma({\mathbf B}_-), \sigma({\mathbf B}_+)\right) \\
+\sigma\left({\mathbf B}_-+{\mathbf B}_+\right) &>\sigma({\mathbf B}_-)+\sigma({\mathbf B}_+) \\
+|\Delta {\mathbf B}| &>|{\mathbf B}_{bg}|/10
+\end{aligned}
+$$
+
+Here, $\sigma$ denotes the standard deviation, ${\mathbf B}_{bg}$ represents the background magnetic field magnitude, and $\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)$.
+The first two conditions ensure that the field changes are distinguishable from stochastic fluctuations, while the third condition serves as a supplementary measure to reduce recognition uncertainty.
+
+Notably, this method shares certain similarities with the Partial Variance of Increments (PVI) approach for identifying coherent structures, as both calculate indices based on standard deviations (with this method focusing on the standard deviation of the magnetic field, and PVI on magnetic field increments).
+However, this method is better suited for discontinuity identification by comparing data within neighboring time windows rather than across a correlation scale (an unknown quantity that may vary with radial distance and solar wind conditions).
+As a result, this approach effectively excludes wave-like coherent structures, eliminating the need for manual inspection and bypassing the necessity of grouping continuous clusters of high-PVI points as in PVI analysis.
 
@@
 Discontinuities with spatial scales larger than $60$ s are not considered in this study, however it could be argued that they are not significant in the outer heliosphere if they follow the trend with decreasing number of IDs with increasing spatial scale.
-@fig-ljFit also indicates that the spatial scale of IDs does not vary significantly with the radial distance from the Sun.
+@fig-junoDistribution also indicates that the spatial scale of IDs does not vary significantly with the radial distance from the Sun.
 
-TODO:
+<!-- TODO: -->
+
 More than ?
@@
 Then for each discontinuity identified, we calculate the distance matrix of the time series sequence (distance between each pair of magnetic field vectors) to determine the leading edge and trailing edge of the discontinuity.
-After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to get the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$.
-The maximum variance direction is then fitted by a hyperbolic tangent functions to extract the parameters to properly describe the discontinuity @eq-fit.
+After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to transform the magnetic field into the boundary normal (LMN) coordinate system.
+The main (most varying) magnetic field component, $B_l$, is then fitted by a hyperbolic tangent functions to extract the parameters to properly describe the discontinuity @eq-fit.
 Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.
@@
 
+Previous studies have indicated that the minimum variance direction obtained through Minimum Variance Analysis (MVA) is frequently unreliable.
+Improved accuracy can be achieved by either using the cross product of the magnetic field measured at the boundaries as the normal direction [@knetterFourpointDiscontinuityObservations2004] or by enforcing conditions such as $Δ|B|/|B| > 0.05$ or $ω > 60°$ [@liuFailuresMinimumVariance2023].
+The former approach requires a small normal component in the magnetic field, while the latter approach limits the dataset to a subset that satisfies these conditions.
+In our analysis, we applied both methods and observed no significant differences in the results.
+
+<!-- TODO: use both methods to determine the normal direction of the discontinuity and compare the results. -->
+
 @fig-examples shows several examples of solar wind discontinuities detected by different spacecraft.
@@
 
-![Examples of IDs from Juno, ARTEMIS, STEREO, and Wind](figures/fig_examples){#fig-examples}
+::: {#fig-examples}
+![Examples of IDs from Juno, ARTEMIS, STEREO, and Wind](figures/fig_examples)
+
+Examples of solar wind discontinuities observed by various spacecraft at different heliocentric distances and times.
+Panels (a)–(c) display data from Juno at 1 AU (a), 3 AU (b), and 5 AU (c), showing magnetic field components $B_l$ (blue), $B_n$ (red), $B_m$ (green), and the magnetic field magnitude $B_{\text{total}}$ (black).
+Panels (d)–(f) show magnetic field and ion speed observations from other spacecraft: ARTEMIS on March 27, 2012 (d), STEREO on June 28, 2016 (e), and Wind on August 26, 2011 (f).
+:::
 
@@
 The example of such comparison for the occurrence rate is shown in @fig-rate, where we plot number of discontinuities measured per day by different spacecraft missions (for the same temporal resolution of magnetic field data and the same criteria of discontinuity determination).
-The radial distance of Juno for 2011-2015 is shown in @fig-model, and the number of discontinuities measured by Juno per day coincides with the discontinuity number measured by STEREO, WIND, and ARTEMIS, when Juno is around $1$ AU.
+The radial distance of Juno for 2011-2016 is shown in @fig-model, and the number of discontinuities measured by Juno per day coincides with the discontinuity number measured by STEREO, WIND, and ARTEMIS, when Juno is around $1$ AU.
 This number (occurrence rate) decreases with distance (with time after $\sim 2013$), as Juno moves from $1$ AU to $5$ AU.
@@
 The occurrence rate of IDs observed by Juno is consistent with the occurrence rate observed by 1AU missions, when Juno is around $1$ AU.
-This number (occurrence rate) decreases with distance as Juno moves from $1$ AU to $5$ AU (corresponding to time after $\sim 2013$, the radial distance of Juno for 2011-2015 is shown in @fig-model)
+This number (occurrence rate) decreases with distance as Juno moves from $1$ AU to $5$ AU (corresponding to time after $\sim 2013$, the radial distance of Juno for 2011-2016 is shown in @fig-model)
 
@@
 
-![](figures/ocr/ocr_r_N2_cleaned)
+![](figures/ocr/ocr_r_N2_cleaned_simplified.pdf)
 
@@
 
-The peak current density $J_m$ of a discontinuity is determined by
+The current density $J_m$ across a discontinuity is determined by
 
 $$
-J_m = - \frac{1}{\mu_0 V_n} \frac{d B_m}{d t},
+J_m = - \frac{1}{μ_0 V_n} \frac{d B_l}{d t},
 $$ {#eq-j}
 
-where $\mu_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
-For fitting method, the derivative of the magnetic field could be estimated as $d B_m / d t = B_{m0} / \Delta T$.
+where $μ_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
+For fitting method, the derivative of the magnetic field could be estimated as $\max(d B_l / d t) = B_{l0} / \Delta T$.
 This estimate is more robust than the direct calculation of the derivative of the magnetic field, because the fitting method is less sensitive to the noise in the data and the time resolution of the data (see discussion in the appendix).
+
+<!--  The proton flow velocity $v$ is expressed as $v = v_{sw} - v_{s/c} + U$, where $v_{sw}$ is the solar wind velocity, $v_{s/c}$ is the spacecraft velocity, and $U$  denotes the propagation speed of the discontinuities.
+In our case, the latter two velocities are negligible.
+-->
 
@@
 $$
-d = (v \cdot n) \Delta T
+d = V_n \Delta T
 $$
 
-with $v = v_{sw} - v_{s/c} + U$ , where $\Delta T$ is the transition time (a fixed factor of the $\sigma$ used in fitting) , $v_{sw}$ is the solar wind velocity.
-The velocity of the spacecraft $v_{s/c}$ and the propagation speed of the discontinuities $U$ are negligible in our case.
+where $\Delta T$ is the transition time derived from the fitting method.
 
 To understand the relationship between the discontinuity and the local plasma, we normalize the thickness of the discontinuity by the initial ion length and the current density by the Alfven current density $J_A = e N_p V_A$ (corresponding to the drift between protons and electrons of local Alfén speed $V_A$).
-Figure @junoDistribution presents the statistical distribution of the (un)normalized thickness and current density of IDs grouped by the radial distance from the Sun collected by Juno.
+Figure @fig-junoDistribution presents the statistical distribution of the (un)normalized thickness and current density of IDs grouped by the radial distance from the Sun collected by Juno.
 Panel (a,b) shows that the thickness increases with radial distance.
@@
 
-::: {#fig-ljFit}
-![](figures/juno_distribution_r){#fig-ljFit}
-
-![](figures/l_j_fit_xscale_log)
+::: {#fig-junoDistribution}
+![](figures/juno_distribution_r)
 

### 2024-11-10 notebooks/00_overview.qmd
update

@@
 jupyter: python3
+execute: 
+  freeze: auto
 ---
@@
 ```{python}
+from IPython.display import clear_output
+from juno import DEFAULT_TIMERANGE
 import matplotlib.pyplot as plt
 from beforerr.matplotlib import unify_axes_fontsize, sync_legend_colors, set_linewidth, hide_legend_lines
+```
+
+```{python}
+timespan = (DEFAULT_TIMERANGE[1] - DEFAULT_TIMERANGE[0]).days
+print(f"Time span: {timespan} days")
 ```
@@
     dfs.append(df)
+clear_output()
 ```
@@
     tvars2plot.append(tvar2plot)
+
+clear_output()
 ```
@@
 ```
-
-![](../figures/juno-hg-loc_sunspot-number.png)

### 2024-11-10 src/juno/__init__.py

@@ -1,1 +1,8 @@
+from datetime import datetime
+
 AVG_SATS = ["STA", "THB", "Wind"]
+
+# "2011-08-25", "2016-06-30"
+DEFAULT_TIMERANGE = [datetime(2011, 8, 25), datetime(2016, 6, 30)]
+# "2012-01-01", "2012-01-02"
+DEFAULT_TEST_TIMERANGE = [datetime(2012, 1, 1), datetime(2012, 1, 2)]

### 2024-11-10 src/juno/config.py

@@ -11,6 +11,7 @@ from discontinuitypy.config import SpeasyIDsConfig, IDsConfig
 from discontinuitypy.mission import WindConfigBase, ThemisConfigBase, StereoConfigBase
 
 from .juno import get_mag_data
+from ..juno import DEFAULT_TIMERANGE, DEFAULT_TEST_TIMERANGE
 from math import ceil
 
 
@@ -26,8 +27,8 @@ def split_list(lst, n):
 
 DEFAULT_TAU = timedelta(seconds=60)
 DEFAULT_TS = timedelta(seconds=1)
-DEFAULT_TIMERANGE = Field(["2011-08-25", "2016-06-30"], validate_default=True)
-DEFAULT_TEST_TIMERANGE = Field(["2012-01-01", "2012-01-02"], validate_default=True)
+DEFAULT_TIMERANGE_F = Field(DEFAULT_TIMERANGE, validate_default=True)
+DEFAULT_TEST_TIMERANGE_F = Field(DEFAULT_TEST_TIMERANGE, validate_default=True)
 JNO_PLASMA_DF_PATH = datadir() / "03_primary/JNO_STATE_ts_3600s.parquet"
 
 
@@ -35,7 +36,7 @@ class Config(BaseModel):
     model_config = ConfigDict(arbitrary_types_allowed=True, extra="allow")
 
     tau: timedelta = DEFAULT_TAU
-    timerange: list[datetime] = DEFAULT_TIMERANGE
+    timerange: list[datetime] = DEFAULT_TIMERANGE_F
 
     data_dir: Path = datadir() / "05_reporting"
 

### 2024-11-10 article.qmd
fix: remove for tex compilation
update: correct time lag notation from T to τ

@@
 This approach provides better compatibility for discontinuities with small magnetic field changes and demonstrates greater robustness for conditions in the outer heliosphere compared to traditional methods, namely the B-criterion [@burlagaDirectionalDiscontinuitiesInterplanetary1969] and the TS-criterion [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979].
-For each sampling time $t$, we define three intervals: the pre-interval $[-1,-1/2]\cdot T+t$, the middle interval $[-1/2,1/2]\cdot T+t$, and the post-interval $[1/2,1]\cdot T+t$, where $T$ represents time lags.
+For each sampling time $t$, we define three intervals: the pre-interval $[-1,-1/2]\cdot τ+t$, the middle interval $[-1/2,1/2]\cdot τ+t$, and the post-interval $[1/2,1]\cdot τ+t$, where $τ$ represents time lags.
 The magnetic field timeseries in these three intervals are labeled as ${\mathbf B}_-$, ${\mathbf B}_0$, and ${\mathbf B}_+$, respectively.
@@
 
-Here, $\sigma$ denotes the standard deviation, ${\mathbf B}_{bg}$ represents the background magnetic field magnitude, and $\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)$.
+Here, $\sigma$ denotes the standard deviation, ${\mathbf B}_{bg}$ represents the background magnetic field magnitude, and $\Delta {\mathbf B}={\mathbf B}(t+τ/2)-{\mathbf B}(t-τ/2)$.
 The first two conditions ensure that the field changes are distinguishable from stochastic fluctuations, while the third condition serves as a supplementary measure to reduce recognition uncertainty.
@@
 
-Because the discontinuities may have different spatial scale at different radial distances from the Sun, we repeat the search procedure with time lags $T = 10, 20, 30, 40, 50, 60$ s, and combine the identified ID events together to establish the event list.
+Because the discontinuities may have different spatial scale at different radial distances from the Sun, we repeat the search procedure with time lags $τ = 10, 20, 30, 40, 50, 60$ s, and combine the identified ID events together to establish the event list.
 Discontinuities with spatial scales larger than $60$ s are not considered in this study, however it could be argued that they are not significant in the outer heliosphere if they follow the trend with decreasing number of IDs with increasing spatial scale.
@@
 ::: {#fig-examples}
-![Examples of IDs from Juno, ARTEMIS, STEREO, and Wind](figures/fig_examples)
+![](figures/fig_examples)
 

### 2024-11-18 notes.qmd
feat: add notations

@@
 `updated_events_Wind_tr=20110825-20160630_method=fit_tau=0:01:00_ts=0:00:00.090909.arrow` and `events.Wind.fit.ts_0.09s_tau_60s.arrow`
+
+## Notation
+
+Data Level
+
+-   l0: unprocessed
+
+-   l1: cleaned data, fill null value, add useful columns
+
+-   l2: time-averaged data
+
+### Columns naming conventions
+
+-   `v_{x,y,z}` or `sw_vel_{X,Y,Z}`: solar wind plasma speed in the *ANY* coordinate system, in units of $km/s$
+
+    -   `sw_vel_{r,t,n}`: solar wind plasma speed in the RTN coordinate system, in units of $km/s$
+    -   `sw_vel_gse_{x,y,z}`: solar wind plasma speed in the GSE coordinate system, in units of $km/s$
+    -   `sw_vel_lmn_{x,y,z}`: solar wind plasma speed in the LMN coordinate system, in units of $km/s$
+        -   `v_l` or `sw_vel_l`: abbreviation for `sw_vel_lmn_1`
+        -   `v_mn` or `sw_vel_mn` (deprecated)
+
+-   `radial_distance`: radial distance of the spacecraft, in units of $AU$
+
+-   `sw_elevation`: solar wind elevation angle, in units of $\degree$
+
+-   `sw_azimuth`: solar wind azimuth angle, in units of $\degree$
+
+-   `b_rtn_{x,y,z}` or `b_{r,t,n}`: magnetic field in the RTN coordinate system
+
+-   `b_gse_{x,y,z}`: magnetic field in the GSE coordinate system
+
+-   `model_b_{r,t,n}`: modelled magnetic field in the RTN coordinate system
+
+-   `state` : *1* for *solar wind*, *0* for *non-solar wind*
 

### 2024-11-21 article.qmd
doc: update

@@
 
-However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind speed derived from solar wind propagation models.
+However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind plasma state data derived from solar wind propagation models.
 Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location.

### 2024-11-21 notes.qmd
doc: update

@@
 -   `state` : *1* for *solar wind*, *0* for *non-solar wind*
+
+## Solar Wind Model
+
+Sadly, JUNO does not provide plasma data during the cruise phase, so we use MHD model to estimate the plasma state.
+
+[Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/) models the solar wind propagation in 2D using the BATSRUS MHD solver [@keeblerMSWIM2DTwodimensionalOuter2022].
+
+Some key points about the model
+
+-   Representing the solar wind in the ecliptic plane from 1 to 75 AU
+-   2D MHD model, using the BATSRUS MHD solver
+-   Inclusion of neutral hydrogen (important for the outer heliosphere)
+-   Inner boundary is filled by time-shifting in situ data from multiple spacecraft
+
+For model validation part, please see [JUNO Model Report](notebooks/20_model.ipynb).
 
@@
 
-## Solar Wind Model
-
-Sadly, JUNO does not provide plasma data during the cruise phase, so to estimate the plasma state we will use MHD model.
-
-We are using [Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/), which models the solar wind propagation in 2D using the BATSRUS MHD solver.
-@keeblerMSWIM2DTwodimensionalOuter2022
-
-Some key points about the model
-
--   Representing the solar wind in the ecliptic plane from 1 to 75 AU
--   2D MHD model, using the BATSRUS MHD solver
--   Inclusion of neutral hydrogen (important for the outer heliosphere)
--   Inner boundary is filled by time-shifting in situ data from multiple spacecraft
-
-For model validation part, please see [JUNO Model Report](notebooks/20_model.ipynb).
-
 <!-- 
@@
 -   Analysis
+    -   [ ] Texts about waiting time distribution
     -   [ ] Re-calculate the occurrence rate of IDs
@@
 
-    -   [ ] Check Datagap
-    -   [ ] Check `ARTEMIS-B` data in different states (solar wind, magnetosheath, magnetotail, moon wake)
-    -   [ ] Distribution of \|B\| over radius
+    -   [ ] Check datagap and visualize the data gap
+    -   [x] Check `ARTEMIS-B` data in different states (solar wind, magnetosheath, magnetotail, moon wake)
     -   [ ] JUNO from 2012-09\~2012-10 lack of IDS and extreme large thickness
-    -   [ ] Wind data
-    -   [ ] Add error bar
-    -   [ ] Validate the effects of calibrate candidate duration
+    -   [x] Wind data
 
+    -   ~~Validate the effects of calibrate candidate duration~~
     -   ~~Contribution of discontinuities to the power spectrum~~
@@
     -   [ ] Ensemble forest?
-    -   [ ] Smoothing is important?
+    -   [x] Smoothing is important?
     -   [ ] Check change point algorithm
--   Visualize data gaps
--   Features
-    -   [ ] Thickness in N direction
-    -   [ ] Use high resolution data for feature extraction
 -   Compare with other methods of identifying IDs

### 2024-11-21 src/io.jl
refactor: Update code in src/io.jl and src/main.jl

@@ -1,88 +1,57 @@
 using Printf
 using Discontinuity
 using Discontinuity: load
-include("trans.jl")
+using Dates
+using Dates: AbstractTime
 data_path = datadir("05_reporting")
 
-function Discontinuity.load(path, name_cols::Pair{Symbol}...)
-    df = load(path)
-    insertcols!(df, name_cols...)
-    return df
+DEFAULT_TAUS = 60:-10:20
+
+post_process!(df) = begin
+    df |>
+    Discontinuity.keep_good_fit! |>
+    Discontinuity.standardize_df! |>
+    Discontinuity.compute_params! |>
+    Discontinuity.unitize! |>
+    Discontinuity.calc_beta! |>
+    assign_accuracy!
 end
 
-function Discontinuity.load(; tau=60, ts=1.00, name="JNO", method="fit", dir=data_path)
-    ts_str = @sprintf "ts_%.2fs" ts
-    df = load(joinpath(dir, "events.$name.$method.$(ts_str)_tau_$(tau)s.arrow"))
-    df.tau .= tau
-    df.ts .= ts
-    return df
-end
+function Discontinuity.load(; tau=60, ts=1, name="JNO", dir=data_path, verbose=false, kw...)
+    ts = !ismissing(ts) ? Second(ts) : ts
+    tau = !ismissing(tau) ? Second(tau) : tau
+    ds = DataSet(; name, ts, tau, kw...)
+    df = load(ds; dir)
 
-function load_tau(tau)
-    df = Discontinuity.load(; tau=tau)
-    df.label .= "$tau s"
-    println("Number of events: ", size(df, 1))
-    return df
-end
-
-WIND_PATH = "updated_events_Wind_tr=20110825-20160630_method=fit_tau=0:01:00_ts=0:00:00.090909.arrow"
-JNO_PATH = "updated_events_JNO_tr=20110825-20160630_method=fit_tau=0:01:00_ts=0:00:01.arrow"
-
-post_process!(df) = df |> calc_rotation_angle! |> Discontinuity.unitize! |> Discontinuity.calc_beta! |> assign_accuracy!
-
-function backwards_comp!(df)
-    @rtransform!(df, 
-        :"B.vec.before" = [:"B.vec.before.l", :"B.vec.before.m", :"B.vec.before.n"],
-        :"B.vec.after" = [:"B.vec.after.l", :"B.vec.after.m", :"B.vec.after.n"],
-    )
-end
-
[…]

### 2024-11-21 src/main.jl

@@ -13,11 +13,11 @@ using Beforerr
 import Beforerr: easy_save
 using LaTeXStrings
 using Discontinuity
-using Discontinuity.DefaultMapping
 using Unitful
+import Base.round
 
 set_aog_theme!()
-theme = Theme(;colormap = Reverse(:tokyo), figure_padding=2)
+theme = Theme(; colormap=Reverse(:tokyo), figure_padding=2)
 update_theme!(theme)
 
 include("io.jl")
@@ -30,5 +30,8 @@ foreach([:log10, :log2, :log]) do f
     @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
 end
 
-dfplot(layer, args...; axis = (;), kwargs...) = draw(layer * mapping(args...; kwargs...); axis)
-dfplot(df::AbstractDataFrame, args...; axis = (;), kwargs...) = draw(data(df) * mapping(args...; kwargs...); axis)
+# Generalize function to round float like time
+Base.round(x::Number, y::Number; kw...) = y * round(x / y; kw...)
+
+dfplot(layer, args...; axis=(;), kwargs...) = draw(layer * mapping(args...; kwargs...); axis)
+dfplot(df::AbstractDataFrame, args...; axis=(;), kwargs...) = draw(data(df) * mapping(args...; kwargs...); axis)

### 2024-11-22 article.qmd
doc: Add waiting time results

--- 2024-11-10 article.qmd
@@
 The solar wind plasma state, as evidenced by the sunspot number (referenced in panel (c) of @fig-overview), plays a crucial role in understanding the dynamics of discontinuities.
-During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity.
+During the initial phase of the JUNO mission, the sunspot number peaked, indicating a period of heightened solar activity.
 However, by the end of the mission's cruise phase, there was a significant decline in solar activity.
@@
 After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to transform the magnetic field into the boundary normal (LMN) coordinate system.
-The main (most varying) magnetic field component, $B_l$, is then fitted by a hyperbolic tangent functions to extract the parameters to properly describe the discontinuity @eq-fit.
+The main (most varying) magnetic field component, $B_l$, is then fitted by a hyperbolic tangent function to extract the parameters to properly describe the discontinuity @eq-fit.
 Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.
@@
 $$
-B_l(t) = B_{l0} \tanh\left(\frac{t - t_0}{\Delta T}\right) + c_l
+B_l(t) = B_{l0} \tanh\left(\frac{t - t_0}{\Delta t}\right) + c_l
 $${#eq-fit}
 
-where $B_{l0}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_0$ is the time of discontinuity, $\Delta T$ is the transition time, and $c_l$ is the offset of the magnetic field change (in the case of an ideal discontinuity with perfect rotational symmetry, $c_l$ should theoretically be zero.
+where $B_{l0}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_0$ is the time of discontinuity, $\Delta t$ is the transition time, and $c_l$ is the offset of the magnetic field change (in the case of an ideal discontinuity with perfect rotational symmetry, $c_l$ should theoretically be zero.
 However, in the context of data processing, incorporating $c_l$ can enhance the fitting accuracy).
@@
 -->
+
+## Waiting time
+
+To comprehensively understand the radial evolution of the occurrence rate, particularly the average occurrence rate, it is essential to determine the statistical distributions underlying the observed samples.
+This enables the derivation of meaningful inferences.
+In this context, we derived the probability distribution of the waiting time $τ$ (also referred to as the interarrival interval, as defined in @tsurutaniInterplanetaryDiscontinuitiesTemporal1979) at various radial distances.
+
+To model the data, we employ the Weibull distribution due to its flexibility in capturing varying occurrence rates.
+This choice allows for a more accurate representation and an improved fit compared to the exponential distribution previously used in @tsurutaniInterplanetaryDiscontinuitiesTemporal1979.
+The probability density function of the Weibull distribution is given as follows:
+
+$$
+f(τ; α, θ) = \frac{α}{θ} \left( \frac{τ}{θ} \right)^{α-1} e^{-(τ/θ)^α}, \quad τ \ge 0
+$$
+
+Here, $α$ and $θ$ represent the shape and scale parameters, respectively.
+The complementary cumulative distribution function of the Weibull distribution $F(τ; α, θ) = 1 - \mathrm{e}^{-(τ/θ)^α}$ is a stretched exponential function.
+
+::: {#fig-waitingTime}
+![](figures/waiting_time_distribution)
+
+Waiting time distribution, along with the fitted Weibull distribution at different radial distances.
+:::
+
+The observed waiting time distribution, along with the fitted Weibull distribution, is shown in @fig-waitingTime.
+For $α < 1$, the likelihood of an event occurring decreases with increasing waiting time.
+This behavior aligns with our expectations for the discontinuity occurrence rate in response to the evolving state of the solar wind.
+Across the largest range of waiting times, the observed probabilities exceed those predicted by the fitted distribution.
+This discrepancy may be attributed to data gaps, which artificially extend the observed waiting times between discontinuities.
+
+The mean waiting time $\bar{τ}$ can be determined by integrating the probability density function $\bar{τ} = \int_0^\infty τ f(τ) dτ$.
+The mean occurrence rate, in turn, is simply the reciprocal of the mean waiting time.
+Notably, the mean value derived from the fitted Weibull distribution is more reliable, as it mitigates the influence of unusually large waiting times caused by data gaps.
 
@@
 where $μ_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
-For fitting method, the derivative of the magnetic field could be estimated as $\max(d B_l / d t) = B_{l0} / \Delta T$.
+For fitting method, the derivative of the magnetic field could be estimated as $\max(d B_l / d t) = B_{l0} / \Delta t$.
 This estimate is more robust than the direct calculation of the derivative of the magnetic field, because the fitting method is less sensitive to the noise in the data and the time resolution of the data (see discussion in the appendix).
@@
 $$
-d = V_n \Delta T
+d = V_n \Delta t
 $$
 
-where $\Delta T$ is the transition time derived from the fitting method.
+where $\Delta t$ is the transition time derived from the fitting method.
 
@@
 
-The transition time $\Delta T$ is determined in one second resolution data for all our missions to reduce the system error.
+The transition time $\Delta t$ is determined in one second resolution data for all our missions to reduce the system error.
 (Note that highest time resolution of the data is not needed for the transition time determination by fitting method).

### 2024-11-23 article.qmd
feat: add waiting time figure

@@
 ::: {#fig-waitingTime}
-![](figures/waiting_time_distribution)
+![](figures/fig_wt_dist.pdf)
 
-Waiting time distribution, along with the fitted Weibull distribution at different radial distances.
+Waiting time probability density functions $p(\tau)$ for Juno at 1 AU in 2011 (top) and 5 AU in 2016 (bottom).
+Observed data (black) are fitted with Weibull (blue) and exponential (orange) distributions.
+In 2011, the Weibull distribution is characterized by parameters $\alpha = 0.99, \theta = 30.29$, and a mean waiting time of 30.41 minutes, while the exponential distribution has a mean of 30.42 minutes.
+In 2016, the Weibull distribution has parameters $\alpha = 0.65, \theta = 110.50$, and a mean of 150.96 minutes, whereas the exponential distribution has a mean of 165.02 minutes.
+Vertical dashed lines denote the mean waiting times for each fitted distribution.
 :::

### 2024-11-23 notebooks/02_waiting_time.qmd
feat: add waiting time figure

---
title: Waiting time analysis
---

[Archived notebook using Python and R](analysis/01_occurence_rate.ipynb)

## Notes

- Occurence rate is related to the waiting time distribution.
- Group the data by the radial distance for WT analysis is not good as the radial distance is not a monotonic function of time.

It is hard to remove duplicate events when combining multiple datasets with different τ. So when using the combined dataset, the occurence rate would be overestimated.

> An analysiswas carried out to determine the probability distribution governing the time interval between successive discontinuities. The times at which the discontinuities occurred,obtainedfromthe identificationprogram, were used to computethe time difference, $τ = T_j - T_{j-1}$, the so-called interarrival interval. The number of cases were then tabulated corresponding to discreteranges of τ, and a histogramwas prepared.By properly normalizing the numberof casesin each range a probability distribution function giving the relative frequency of occurrencewas obtained. A similar study was previously carried out by Burlaga[1969].

### References

- [Weibull distribution - Distributions.jl](https://juliastats.org/Distributions.jl/stable/univariate/#Distributions.Weibull)

$$
f(τ; α, θ) = \frac{α}{θ} \left( \frac{τ}{θ} \right)^{α-1} e^{-(τ/θ)^α}, \quad τ \ge 0
$$

```{julia}
using DrWatson
@quickactivate
include(srcdir("main.jl"))

using CairoMakie
```

```{julia}
wind_df = load(; name="Wind", ts=missing);
jno_df = load();
```

```{julia}
subset_jno(df, r) = subset(df, :radial_distance => x -> round_c.(x) .== r)
subset_time(df, t) = subset(df, :time => x -> x .< t)
```

```{julia}
df = wind_df;
df_s1 = subset(df, :time => t -> year.(t) .== 2013);
df_s2 = subset(df_s1, :time => t -> month.(t) .< 2);

jno_df_s1 = subset(jno_df, :time => t -> year.(t) .== 2011);
jno_df_s2 = subset(jno_df, :time => t -> year.(t) .== 2016);
```

## Waiting time distribution

```{julia}
using Distributions

function plot_wt_pdf_lim(df; xlims=(1, 1000), ylims=(1e-5, 8e-2), kwargs...)
    f = plot_wt_pdf(df; kwargs...)
    xlims!(xlims...)
    ylims!(ylims...)
    return f
end

using Printf
Base.show(io::IO, f::Float64) = @printf(io, "%.2f", f)

dists = (Weibull, Exponential)
step = 5
```

```{julia}
#| column: page
#| layout-ncol: 3
dfs = [jno_df, jno_df_s1, jno_df_s2]
fgs = plot_wt_pdf_lim.(dfs; dists)
display.(fgs);
```

```{julia}
using Beforerr: DistsFit

WaitingTimeDist(df, args...) = DistsFit(waiting_time(df), args...)
```

```{julia}
let step = 5
    limits = (0, 680, 5e-6, 5e-2)
    f = Figure()
    new_ax(pos; kw...) = Axis(f[pos...]; yscale=log10, xlabel="τ (minutes)", ylabel="p(τ)", limits, kw...)

    ax1 = new_ax((1, 1); xlabel="")
    plot!(WaitingTimeDist(jno_df_s1, dists, step))
    ax2 = new_ax((2, 1);)
    plot!(WaitingTimeDist(jno_df_s2, dists, step))
    axislegend(ax1, "Juno, 2011"; loc=:upperright)
    axislegend(ax2, "Juno, 2016"; loc=:upperright)
    easy_save("fig_wt_dist")
end
```

## Occurence rate

```{julia}
using Distributions

get_fit_params(x; dist=Weibull, func=mean) = func(fit(dist, x))
get_wt_fit_params(time; kwargs...) = get_fit_params(waiting_time(time); kwargs...)
```

```{julia}
jno_ρ_df = @chain jno_df begin
    @transform!(
        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
        :l = :L_k .* (abs ∘ cosd).(:θ_vn),
        :l_n = :L_k .* (abs ∘ cos ∘ atan).(:Vn_y ./ :Vn_x)
    )
end;
```

```{julia}
time_interval = Day(160)

jno_ρ_df = @chain jno_df begin
    @transform(
        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
        :l = :L_k .* (abs ∘ cosd).(:θ_vn),
        :l_n = :L_k .* (abs ∘ cos ∘ atan).(:Vn_y ./ :Vn_x)
    )
    @transform(
        :l_ratio = :l ./ :r,
        :l_n_ratio = :l_n ./ :r
    )
    groupby(:time_bin)
    combine(
        nrow,
        :time => get_wt_fit_params => :τ,
        [:r :l :l_ratio :l_n_ratio] .=> mean
    )
    # subset(:nrow => x -> x .> 2000)
    @transform(
        :ρ = 1 ./ :τ,
    )
    @transform(
        :ρ_l = :ρ ./ :l_ratio_mean * maximum(:l_ratio_mean),
    )
    sort(:r_mean)
end
```

```{julia}
wind_ρ_df = @chain wind_df begin
    @transform!(
        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
    )
    groupby(:time_bin)
    combine(
        nrow,
        :time => get_wt_fit_params => :τ,
    )
    @transform!(
        :ρ = 1 ./ :τ,
    )
end
```

```{julia}
df = leftjoin(jno_ρ_df, wind_ρ_df, on=:time_bin, makeunique=true)
df.ρ_ratio = @. df.ρ / df.ρ_1

@transform!(df,
    :ratio = :ρ_ratio ./ :l_ratio_mean,
    :ratio_n = :ρ_ratio ./ :l_n_ratio_mean,
)
@transform!(
    df,
    :ratio = :ratio ./ mean(:ratio),
    :ratio_n = :ratio_n ./ mean(:ratio_n)
)

df
```

```{julia}
x = :time_bin => "Time"
legends = ["Juno", "Wind"]
specs = data(df) * mapping(x, [:ρ_l, :ρ_1] .=> "Normalized Occurence rates") * mapping(color=dims(1) => renamer(legends))
draw(specs)
easy_save("ocr/ocr_normalized_by_r")
```

```{julia}
x = :r_mean => r_lab
specs = data(df) * mapping(x, :ρ)
draw(specs)
```

```{julia}
y = [:ratio_n, :ratio]
specs = data(df) * mapping(x) * mapping(y, color=dims(1) => renamer(string.(y)))
plt2 = draw(specs)
```

## Compare the exponential and Weibull fits for the waiting time distributions of Wind dataset

```{julia}
f1 = plot_wt_pdf_lim(wind_df, ylims=(1e-6, 1e-1),)
f2 = plot_wt_pdf_lim(wind_df, dist=Weibull, ylims=(1e-6, 1e-1))
display.([f1, f2]);
```

```{julia}
df1 = subset_time(jno_df, Date(2011, 9, 30))
df2 = subset_time(wind_df, Date(2011, 9, 30))
dfs = [df1, df2]
fgs = dfs .|> plot_wt_pdf_lim
display.(fgs);
```

### 2024-11-23 src/io.jl

@@ -9,7 +9,7 @@ DEFAULT_TAUS = 60:-10:20
 
 post_process!(df) = begin
     df |>
-    Discontinuity.keep_good_fit! |>
+    Discontinuity.keep_good_fit |>
     Discontinuity.standardize_df! |>
     Discontinuity.compute_params! |>
     Discontinuity.unitize! |>

### 2024-11-23 article.qmd
docs: open research

@@
 Here, $α$ and $θ$ represent the shape and scale parameters, respectively.
-The complementary cumulative distribution function of the Weibull distribution $F(τ; α, θ) = 1 - \mathrm{e}^{-(τ/θ)^α}$ is a stretched exponential function.
+The complementary cumulative distribution function of the Weibull distribution $F(τ; α, θ) = 1 - \mathrm{e}^{-(τ/θ)^α}$ is a stretched exponential function (The Weibull distribution reduces to the exponential distribution when $α = 1$).
 
@@
 
+# Open Research
+
+Codes and datasets used for the analysis are available in the GitHub repository https://github.com/Beforerr/ids_spatial_evolution_juno.
+
 # Appendix

### 2024-11-26 scripts/data.py
fix: update data scripts

@@ -1,4 +1,24 @@
-#| hide
-from juno.config import JunoConfig
+# %%
+from rich import print
+from juno.config import JunoConfig, WindConfig, StereoConfig
 
-JunoConfig().produce_or_load()
+from speasy.core.requests_scheduling.request_dispatch import init_archive
+
+init_archive()
+
+# %%
+for c in [JunoConfig, WindConfig, StereoConfig]:
+    c().produce_or_load()
+
+# Different time windows
+taus = range(60, 10, -10)
+
+for tau in taus:
+    JunoConfig(tau=tau).produce_or_load()
+# %%
+# Test
+w_conf = WindConfig(test=True)
+w_conf.get_data()
+w_conf.plasma_data
+print(w_conf)
+# %%

### 2024-11-26 src/juno/config.py

@@ -1,4 +1,3 @@
-from pydantic import Field
 from pydantic import BaseModel, ConfigDict
 import polars as pl
 
@@ -6,12 +5,13 @@ from datetime import timedelta, datetime
 from pathlib import Path
 
 from beforerr.project import datadir
+from space_analysis.core import MagVariable
 from space_analysis.meta import PlasmaDataset
 from discontinuitypy.config import SpeasyIDsConfig, IDsConfig
 from discontinuitypy.mission import WindConfigBase, ThemisConfigBase, StereoConfigBase
 
 from .juno import get_mag_data
-from ..juno import DEFAULT_TIMERANGE, DEFAULT_TEST_TIMERANGE
+from . import DEFAULT_TIMERANGE, DEFAULT_TEST_TIMERANGE
 from math import ceil
 
 
@@ -27,8 +27,6 @@ def split_list(lst, n):
 
 DEFAULT_TAU = timedelta(seconds=60)
 DEFAULT_TS = timedelta(seconds=1)
-DEFAULT_TIMERANGE_F = Field(DEFAULT_TIMERANGE, validate_default=True)
-DEFAULT_TEST_TIMERANGE_F = Field(DEFAULT_TEST_TIMERANGE, validate_default=True)
 JNO_PLASMA_DF_PATH = datadir() / "03_primary/JNO_STATE_ts_3600s.parquet"
 
 
@@ -36,21 +34,41 @@ class Config(BaseModel):
     model_config = ConfigDict(arbitrary_types_allowed=True, extra="allow")
 
     tau: timedelta = DEFAULT_TAU
-    timerange: list[datetime] = DEFAULT_TIMERANGE_F
-
-    data_dir: Path = datadir() / "05_reporting"
+    timerange: list[datetime] = DEFAULT_TIMERANGE
 
     split: int = 16
     test: bool = False
+
+    file_path: Path = datadir() / "05_reporting"
+
+    def model_post_init(self, __context):
+        super().model_post_init(__context)
+        self.detect_kwargs = {"tau": self.tau}
+        if self.test:
+            self.timerange = DEFAULT_TEST_TIMERANGE
+            self.split = 1
+
+
+# %%
+def juno_plasma_data(source=JNO_PLASMA_DF_PATH):
+    v_cols = ["v_x", "v_y", "v_z"]
[…]

### 2024-11-26 notebooks/01_results_julia.qmd
feat: effect of time lag on the discontinuity identification

@@
 using Discontinuity
+using AlgebraOfGraphics
+using DataFramesMeta
 @quickactivate
@@
 M = var_mapping()
+
 ```
@@
 ```{julia}
-wind_df = load_wind();
-jno_df = load_jno();
+jno_df = load();
+wind_df = load(; name="Wind", ts=missing);
 ```
+
+![](./02_waiting_time.ipynb)
 
@@
 ```
+
+## Effects of time lag on the discontinuity identification
+
+```{julia}
+df = load_taus(; unique_f=missing)
+```
+
+```{julia}
+normalize_by_max(x) = x / maximum(x)
+normalize_by_max(df, x; kw...) = transform(df, x => normalize_by_max; kw...)
+
+function plot_nrow(df, x, dx, color; xlabel=x, normalize=true, plottype=Stairs, kw...)
+    y = Symbol(nrow)
+    df = @chain df begin
+        transform(x => ByRow(v -> round(v, dx)); renamecols=false)
+        groupby([x, color]; sort=true)
+        combine(nrow)
+    end
+
+    # normalize the nrows by the largest value
+    if normalize
+        df = normalize_by_max(groupby(df, [x]), y; renamecols=false)
+        ylabel = "Relative percentage of events"
+    else
+        ylabel = "Number of events"
+    end
+
+    plt = data(df) * mapping(x => xlabel, y => ylabel; color) * visual(plottype)
+    draw(plt; kw...)
+end
+
+plot_nrow(df, :r, 0.5, :tau; xlabel=r_lab)
+easy_save("ocr/juno_tau_r")
+```
+
+## Rotation angle
+
+```{julia}
+layer = data(jno_df) * mapping(color=r_map)
+maps = [M.ω; M.ω_in]
+f = plot_dist(layer, maps)
+```
+
+```{julia}
+f = plot_dist(layer * (; col=:accuracy), [:θ_nk => "θ_nk"])
+```
+
+## Bn and Change in dB
+
+```{julia}
+let maps = [M.dB_norm_over_B, M.bn]
+    layer = data(jno_df) * mapping(color=r_map, col=:accuracy)
+    f = plot_dist(layer, maps)
+end
+```
+
+```{julia}
+let maps = [M.dB_norm_over_B, M.bn]
+    l = data(wind_df) * (; col=:accuracy)
+    f = plot_dist(l, maps)
+end
+```
+
+## Compression ratio
+
+```{julia}
+let maps = [:db_over_b_max=> L"\max(Δ B)/B" , :db_over_b=> L"|Δ B|/B"], datalimits=((0, 0.5),)
+    layer = data(jno_df) * mapping(color=r_map)
+    f = plot_dist(layer, maps; axis=(yscale=identity,), datalimits)
+end

### 2024-11-26 src/trans.jl
chore: remove unused codes

@@ -1,22 +1,0 @@
-using LinearAlgebra
-
-function rotation_angle(u, v)
-    cos_theta = dot(u, v) / (norm(u) * norm(v))
-    theta = acos(cos_theta)
-    return rad2deg(theta)
-end
-
-"""
-# Notes
-- en_cols = [:Vn_x, :Vn_y, :Vn_z] # unit vector of the normal from MVA
-- ek_cols = [:k_x, :k_y, :k_z] # unit vector of the normal from cross product
-- v_cols = [:v_x, :v_y, :v_z] # vector of the velocity
-"""
-function calc_rotation_angle!(df)
-    @rtransform!(
-        df,
-        :θ_vn = rotation_angle([:v_x, :v_y, :v_z], [:Vn_x, :Vn_y, :Vn_z]),
-        :θ_vk = rotation_angle([:v_x, :v_y, :v_z], [:k_x, :k_y, :k_z]),
-        :θ_nk = rotation_angle([:Vn_x, :Vn_y, :Vn_z], [:k_x, :k_y, :k_z]),
-    )
-end

### 2024-12-29 article.qmd
docs: incorporate Anton's revision

@@
 ---
-title: Spatial evolution of solar wind discontinuities in the outer heliosphere
+title: "Solar wind discontinuities in the outer heliosphere: spatial distribution between 1 and 5 AU"
 author:
@@
     affiliation: University of California, Los Angeles
+  - name: Ivan Vasko
+    affiliation: University of Texas at Dallas
 affiliations:
@@
     text: Overleaf
-abstract: We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
+abstract: Solar wind discontinuities (SWDs; also known as current sheets) are kinetic plasma structures contributing significantly to the spectrum of magnetic field fluctuations and to solar wind heating.
+Properties of SWDs varies significantly with the radial distance away from the Sun, and investigation of this radial evolution is important for revealing of SWD origin and their contribution to solar wind plasma processes.
+In this study we utilize quite unique dataset of Juno spacecraft observations of SWDs during cruise phase, when Juno was traveling from Earth ($\sim 1$AU) to Jupiter ($\sim 5$AU).
+We combine Juno measurements with Wind, ARTEMIS, and STEREO measurements of SWDs around $\sim 1$AU, and this combination allows us to separate temporal (with solar activity) and spatial (with radial distance) variations of SWD properties.
+We find that (1) the normalized to $1$AU occurrence rate of SWDs decreases with radial distance from the Sun, following a $1/r$ relationship; (2) the SWD thickness increases with radial distance, but when normalized to the ion inertial length, the thickness remains almost unchanged within $[1,5]$AU; (3) the SWD current density decreases with radial distance, but when normalized to the Alfvén current, the current density remains almost unchanged within $[1,5]$AU; (4) the distribution of SWD normalized thickness and current density remain constant over time (five year period of Juno cruise phase) at $1$ AU.
+We discuss these results in context of theories of SWD origin and dynamics.
+# We present a study of the spatial evolution of solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
 We identify and analyze the properties of the discontinuities at different radial distances from the Sun.
-By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of interplanetary discontinuities (IDs) decreases with radial distance from the Sun, following a $1/r$ relationship; (2) The thickness of IDs increases with radial distance, but when normalized to the ion inertial length, the thickness decreases; (3) The current density of IDs decreases with radial distance, but when normalized to the Alfvén current, the current density of IDs increases; (4) The distribution of the normalized thickness and current density of IDs remain constant over time at 1 AU on a yearly scale.
+By differentiating the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance), we find that (1) the normalized occurrence rate of interplanetary discontinuities (SWDs) decreases with radial distance from the Sun, following a $1/r$ relationship; (2) The thickness of SWDs increases with radial distance, but when normalized to the ion inertial length, the thickness decreases; (3) The current density of SWDs decreases with radial distance, but when normalized to the Alfvén current, the current density of SWDs increases; (4) The distribution of the normalized thickness and current density of SWDs remain constant over time at 1 AU on a yearly scale.
 ---
@@
 
-- **What I did:** I studied the solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
+<!-- - **What I did:** I studied the solar wind discontinuities in the outer heliosphere using data from the Juno spacecraft during its cruise phase.
 I identified and analyzed the properties of the discontinuities at different radial distances from the Sun.
 I differentiated the temporal effect (correlated with solar activity) and spatial variations (correlated with radial distance).
-
-- **What I found:** The normalized occurrence rate of IDs drops with the radial distance from the Sun, following a $1/r$ law.
-The thickness of IDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of IDs decreases.
-The current intensity of IDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of IDs increases.
-
+- **What I found:** The normalized occurrence rate of SWDs drops with the radial distance from the Sun, following a $1/r$ law.
+The thickness of SWDs increases with the radial distance from the Sun, but after normalization to the ion inertial length, the thickness of SWDs decreases.
+The current intensity of SWDs decreases with the radial distance from the Sun, but after normalization to the Alfven current, the current intensity of SWDs increases.
 - **What it means:** The results of this study provide a better understanding of the solar wind discontinuities in the outer heliosphere and their spatial evolution.
 This information is important for understanding the dynamics of the solar wind and testing the local generation mechanism of discontinuities.
-
+-->
 # Introduction
 
-TODO: annihilation mechanisms and related references
-TODO: References to stabliity and time scales
+<!-- TODO: annihilation mechanisms and related references
+TODO: References to stabliity and time scales -->
 
-Rapid variations in interplanetary magnetic fields, commonly recognized as solar wind magnetic discontinuities [@colburnDiscontinuitiesSolarWind1966], embody localized transient rotations or jumps of the magnetic field.
-They are microscale structures observed throughout the heliosphere, from inner heliosphere [@liuCategorizingMHDDiscontinuities2022] to the heliosheath [@burlagaCurrentSheetsHeliosheath2011].
-Despite being discovered over half a century ago, the specific origins and circumstances of their formation remain subjects of ongoing debate.
-Historically, it has been believed that discontinuities originate inside 1 AU, probably near or at the Sun, and are then convected passively outward by the solar wind [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979; @sodingRadialLatitudinalDependencies2001; @borovskyFluxTubeTexture2008].
-However, the good agreement observed in the waiting-time analysis between solar wind data and magnetohydrodynamic (MHD) turbulence simulations [@grecoStatisticalAnalysisDiscontinuities2009] indicates that a significant portion of these discontinuities could be associated with flux-tube boundaries.
-These structures are likely intermittent, arising spontaneously and forming rapidly and locally within MHD turbulence.
+Rapid variations in the interplanetary magnetic field, commonly recognized as solar wind magnetic discontinuities (SWDs) [@colburnDiscontinuitiesSolarWind1966], embody localized transient rotations or jumps of the magnetic field.
+They are micro (ion kinetic) scale plasma structures observed throughout the heliosphere, from the inner heliosphere [@liuCategorizingMHDDiscontinuities2022] to the heliosheath [@burlagaCurrentSheetsHeliosheath2011].
+Despite being discovered over half a century ago, the specific origins and circumstances of their formation remain subjects of ongoing debate \cite<see discussion in>[and references therein]{Vasko22:apjl,Vasko24:jgr}.
+Historically, SWDs have been believed to originate inside 1 AU, probably near or at the Sun, and are then passively convected outward by the solar wind [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979; @sodingRadialLatitudinalDependencies2001; @borovskyFluxTubeTexture2008].
+However, the good agreement observed in the waiting-time analysis between solar wind data and magnetohydrodynamic (MHD) turbulence simulations [@grecoStatisticalAnalysisDiscontinuities2009] indicates that a significant portion of these discontinuities could be associated with flux-tube boundaries, intermittent structures, arising spontaneously and forming rapidly and locally within MHD turbulence.
 The annihilation mechanisms for these discontinuities are also uncertain.
 These discontinuities may be unstable features and some could rapidly wane or decay [@neugebauerTangentialDiscontinuitiesSolar1986].
-Conversely, they can be very stable and persist over time intervals comparable to the convection time or the solar rotation period.
-Further complicating this picture is the presence of different types of discontinuities in interplanetary space—specifically tangential and rotational discontinuities, which are classically regarded as static solutions to the MHD equations.
+Magnetic reconnection of SWDs is also considered a natural process that destroys them \cite{Gosling12,Wilson16:cs,else}.
+Conversely, SWDs can be very stable and persist over time intervals comparable to the convection time or the solar rotation period.
+Further complicating this picture is the presence of different types of discontinuities in interplanetary space -— specifically tangential and rotational discontinuities \cite<see discussion in>{Neugebauer06,Artemyev19:jgr:solarwind,wangSolarWindCurrent2024}, which are classically regarded as static solutions to the MHD equations [@hudsonDiscontinuitiesAnisotropicPlasma1970].
 These distinct types may arise from different sources and may evolve in unique ways.
@@
 
-Discontinuities are not only an interesting topic in themselves but are also considered crucial for understanding the dynamics of the solar wind and cosmic rays.
+Discontinuities are not only interesting because they are nonlinear plasma structures widely observed in the heliosphere,  but are also considered crucial for understanding the dynamics of the solar wind plasma and cosmic rays.
 Theoretical models [@lerchePropagationMagneticDisturbances1975; @medvedevDissipativeDynamicsCollisionless1997] and MHD simulations [@grecoIntermittentMHDStructures2008; @yangFormationRotationalDiscontinuities2015] suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and Alfvénic turbulence.
-These nonlinear processes can create significant disturbances to the otherwise adiabatic evolution of the solar wind flow.
-These theoretical predictions are supported by spacecraft observations, which have revealed that the solar wind magnetic field follows the Parker model of the heliospheric current sheet only on average.
-Localized transient currents, which can be significantly more intense than those predicted by the Parker model, are carried by various discontinuities observed as strong variations in magnetic field components [@colburnDiscontinuitiesSolarWind1966; @burlagaMicroscaleStructuresInterplanetary1968; @turnerOrientationsRotationalTangential1971].
-These discontinuities contribute significantly to the magnetic fluctuation spectra [@borovskyContributionStrongDiscontinuities2010] and play an important role in energy dissipation processes such as plasma heating [@osmanIntermittencyLocalHeating2012] and particle acceleration [@wentzelMotionMagneticDiscontinuities1964; @dmitrukTestParticleEnergization2004; @tesseinAssociationSuprathermalParticles2013].
-More specifically, because tangential discontinuities act as boundaries separating different types of plasma and often involve oppositely directed magnetic fields on either side, they are potential regions where magnetic reconnection or merging can occur.
-Additionally, rotational discontinuities, being nonlinear large-amplitude Alfvén waves, are expected to significantly contribute to the diffusion coefficient for cosmic rays.
-Finally, these discontinuities can produce geomagnetic effects [@tsurutaniReviewInterplanetaryDiscontinuities2011] and impact space weather due to abrupt changes in external (solar wind) conditions.
+These nonlinear processes can create significant disturbances to the otherwise adiabatic evolution of the solar wind flow [@matteiniIonKineticsSolar2012; @tsurutaniReviewAlfvenicTurbulence2018].
+These theoretical predictions are supported by spacecraft observations, which have revealed that the solar wind magnetic field follows the Parker model of the heliospheric current sheet only on average [@svirzhevskyHeliosphericMagneticField2021].
+Localized transient currents carried by SWDs and significantly more intense than those predicted by the Parker model, are observed as strong variations in magnetic field components [@colburnDiscontinuitiesSolarWind1966; @burlagaMicroscaleStructuresInterplanetary1968; @turnerOrientationsRotationalTangential1971].
+SWDs contribute significantly to magnetic fluctuation spectra [@borovskyContributionStrongDiscontinuities2010; @vaskoKineticScaleCurrentSheets2024] and play an important role in energy dissipation processes such as plasma heating [@osmanIntermittencyLocalHeating2012] and particle acceleration [@wentzelMotionMagneticDiscontinuities1964; @dmitrukTestParticleEnergization2004; @tesseinAssociationSuprathermalParticles2013].
+More specifically, because tangential discontinuities act as boundaries separating different types of plasma and often involve oppositely directed magnetic fields on either side, they are potential regions where magnetic reconnection or merging can occur \cite<see reviews by>{Gosling12,Paschmann13}.
+Additionally, rotational discontinuities, being nonlinear large-amplitude Alfvén waves, are expected to contribute significantly to the scattering of energetic particles [@artemyevSuperfastIonScattering2020].
+<!-- Finally, these discontinuities can produce geomagnetic effects [@tsurutaniReviewInterplanetaryDiscontinuities2011] and impact space weather due to abrupt changes in external (solar wind) conditions.
+-->
 
-In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft [@boltonJunoMission2017] during its cruise phases (2011-2016), with its orbits shown in panel (a) of @fig-overview.
-The primary goal of this paper is to investigate the radial dependence of the occurrence rate and other properties of discontinuities, in order to gain insights into their evolution and origin.
-Continuous measurements at 1 AU from missions such as Wind, ARTEMIS, and STEREO have been utilized to distinguish temporal effects from spatial variations by examining the characteristics of discontinuities at two radial distances simultaneously.
-This distinction is crucial because temporal variations could easily be misinterpreted as spatial variations [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979].
-Due to the potential misidentification of the normal direction of the magnetic field when using the minimum variance analysis (MVA) method [@hausmanDeterminingNatureOrientation2004; @liuFailuresMinimumVariance2023], we do not differentiate between the types of discontinuities, whether they are tangential, rotational, or either [@neugebauerReexaminationRotationalTangential1984].
-
-Previous studies on the radial dependencies of solar wind discontinuities have been conducted by several authors [e.g., @marianiVariationsOccurrenceRate1973; @tsurutaniInterplanetaryDiscontinuitiesTemporal1979; @sodingRadialLatitudinalDependencies2001].
+Investigation of the evolution of SWD properties with the radial distance (or alternatively, investigation of properties of SWD generation at different radial distances) has mostly been limited to comparison of SWD statistics collected by different missions during different intervals of solar activity [e.g., @marianiVariationsOccurrenceRate1973; @tsurutaniInterplanetaryDiscontinuitiesTemporal1979; @sodingRadialLatitudinalDependencies2001].
 However, the data used in these studies were rarely obtained in conjunction with measurements at fixed radial distances, and the methods employed to identify discontinuities were not robust for situations involving weak magnetic fields and long durations encountered at large radial distances.
 Additionally, some measurements at different radial distances were significantly separated in time, with limited time ranges covered [@sodingRadialLatitudinalDependencies2001].
-Consequently, there remains ambiguity in interpreting the results of these studies.
+Consequently, there remains an ambiguity in interpreting the results of these studies.
+In this study, we present a statistical analysis of discontinuities observed from Earth's orbit ($\sim 1$ AU) to Jupiter orbit ($\sim 5$ AU) by a single mission.
+We utilize data collected by the Juno spacecraft [@boltonJunoMission2017] during its cruise phases (2011-2016), with its orbits shown in panel (a) of @fig-overview.
+The primary goal of this study is to investigate the radial dependence of the SWD occurrence rate and properties, in order to gain insights into their evolution and origin.
+Continuous measurements of SWDs at 1 AU from missions such as Wind [@acunaGlobalGeospaceScience1995], ARTEMIS [@angelopoulosARTEMISMission2011], and STEREO [@kaiserSTEREOMissionIntroduction2008] have been utilized to distinguish temporal effects from spatial variations by examining the characteristics of discontinuities at two radial distances ($1$ AU and at Juno location) simultaneously.
+This distinction is crucial because temporal variations could easily be misinterpreted as spatial variations [see discussion in @tsurutaniInterplanetaryDiscontinuitiesTemporal1979].
+Due to the potential misidentification of the SWD normal plane with single spacecraft [see discussion in @hausmanDeterminingNatureOrientation2004; @liuFailuresMinimumVariance2023; @wangSolarWindCurrent2024], we do not differentiate between the types of discontinuities, whether they are tangential, rotational, or either [@neugebauerReexaminationRotationalTangential1984].
 
 The paper is structured as follows.
-First, we outline the missions, instruments, and data utilized in this study.
-Next, we provide a brief description of the method used to identify discontinuities and the model employed to estimate the plasma state at the Juno location, necessitated by the absence of plasma data during its cruise phase.
-In the subsequent sections, we present the results concerning the spatial variation of discontinuities, focusing on their occurrence rate and characteristics, such as spatial scales and current density.
-Finally, we discuss the implications of our findings in the context of the origin and evolution of these discontinuities in the solar wind.
+First, we outline the missions, instruments, and data utilized in this study (@sec-dataset).
+Next, we provide a brief description of the method used to identify discontinuities and the model employed to estimate the plasma state at the Juno location, necessitated by the absence of plasma data during its cruise phase (@sec-methods).
+In subsequent @sec-results, we present the results concerning the spatial variation of discontinuities, focusing on their occurrence rate and characteristics, such as spatial scales and current density.
+Finally, we discuss the implications of our findings in the context of the origin and evolution of these discontinuities in the solar wind (@sec-dependence).
 
@@
 The solar wind plasma state, as evidenced by the sunspot number (referenced in panel (c) of @fig-overview), plays a crucial role in understanding the dynamics of discontinuities.
-During the initial phase of the JUNO mission, the sunspot number peaked, indicating a period of heightened solar activity.
-However, by the end of the mission's cruise phase, there was a significant decline in solar activity.
+During the initial phase (2011) of the Juno mission [@boltonJunoMission2017], the sunspot number peaked, indicating a period of heightened solar activity.
+However, by the end of the mission's cruise phase in 2016, there was a significant decline in solar activity.
 This variation underscores the importance of calibrating the discontinuity properties in relation to solar activity levels to account for temporal fluctuations.
@@
 
-Further analysis of @fig-overview highlights the significance of the heliographic longitudinal difference between the Juno mission and Earth as well as the STEREO-A mission.
+Further analysis of @fig-overview highlights the significance of the heliographic longitudinal difference between the Juno mission and Earth as well as the STEREO-A mission [@kaiserSTEREOMissionIntroduction2008].
 Specifically, when there is a substantial longitudinal difference between Juno and Earth, the difference between Juno and STEREO-A tends to be minimal, and vice versa.
@@
 
-## Dataset
+## Dataset {#sec-dataset}
 
@@
 Data collected from missions such as STEREO, ARTEMIS, and WIND complement Juno’s observations, providing a broader perspective on heliospheric conditions and enabling a multi-point analysis of discontinuity properties [@velliUnderstandingOriginsHeliosphere2020].
-Specifically, we utilize magnetic fields from Juno [@boltonJunoMission2017], measured by the Juno Fluxgate Magnetometer (MAG) [@connerneyJunoMagneticField2017], alongside ion bulk velocity and plasma density with hourly resolution from a solar wind model at Juno’s location (described below).
+Specifically, we utilize magnetic fields from Juno [@boltonJunoMission2017], measured by the Juno Fluxgate Magnetometer (MAG) [@connerneyJunoMagneticField2017].
 For ARTEMIS [@angelopoulosARTEMISMission2011], we use magnetic field data from the Fluxgate Magnetometer [@austerTHEMISFluxgateMagnetometer2008] and ion bulk velocity and plasma density derived from the Electrostatic Analyzer [@mcfaddenTHEMISESAPlasma2009].
-For STEREO[@kaiserSTEREOMissionIntroduction2008], we incorporate magnetic fields from the magnetic field experiment on IMPACT [@acuñaSTEREOIMPACTMagnetic2008; @luhmannSTEREOIMPACTInvestigation2008] and ion bulk velocity and plasma density from PLASTIC [@galvinPlasmaSuprathermalIon2008].
-For WIND, we include magnetic fields from the Magnetic Field Investigation (MFI) [@leppingWINDMagneticField1995] and ion bulk velocity and plasma density from the Solar Wind Experiment (SWE) [@ogilvieSWEComprehensivePlasma1995].
+For STEREO[@kaiserSTEREOMissionIntroduction2008], we incorporate magnetic fields from the magnetic field experiment on IMPACT [@acunaSTEREOIMPACTMagnetic2008; @luhmannSTEREOIMPACTInvestigation2008] and ion bulk velocity and plasma density from PLASTIC [@galvinPlasmaSuprathermalIon2008].
+For WIND [@acunaGlobalGeospaceScience1995], we include magnetic fields from the Magnetic Field Investigation (MFI) [@leppingWINDMagneticField1995] and ion bulk velocity and plasma density from the Solar Wind Experiment (SWE) [@ogilvieSWEComprehensivePlasma1995].
 The table below summarizes the time resolution of magnetic field and plasma data for each mission.
@@
 
-However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind plasma state data derived from solar wind propagation models.
+Since Juno does not provide direct plasma measurements during the cruise phase, we will estimate the spatial scale (thickness) of discontinuities using solar wind plasma state data derived from solar wind propagation models.
 Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location.
@@
 
-## Methods
+## Methods {#sec-methods}
 
-We employ Liu’s method [@liuMagneticDiscontinuitiesSolar2022] to identify discontinuities in the solar wind.
-This approach provides better compatibility for discontinuities with small magnetic field changes and demonstrates greater robustness for conditions in the outer heliosphere compared to traditional methods, namely the B-criterion [@burlagaDirectionalDiscontinuitiesInterplanetary1969] and the TS-criterion [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979].
+We employ @liuMagneticDiscontinuitiesSolar2022 method to identify discontinuities in the solar wind.
+This method provides better compatibility for discontinuities with small magnetic field changes and demonstrates greater robustness for conditions in the outer heliosphere compared to traditional methods, namely the $B$-criterion [@burlagaDirectionalDiscontinuitiesInterplanetary1969] and the $TS$-criterion [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979].
 For each sampling time $t$, we define three intervals: the pre-interval $[-1,-1/2]\cdot T+t$, the middle interval $[-1/2,1/2]\cdot T+t$, and the post-interval $[1/2,1]\cdot T+t$, where $T$ represents time lags.
-The magnetic field timeseries in these three intervals are labeled as ${\mathbf B}_-$, ${\mathbf B}_0$, and ${\mathbf B}_+$, respectively.
+The magnetic field time series in these three intervals are labeled as ${\mathbf B}_-$, ${\mathbf B}_0$, and ${\mathbf B}_+$, respectively.
 To identify a discontinuity, the following three conditions must be met:
-
 $$
@@
 $$
+Here, $\sigma$ denotes the standard deviation, ${\mathbf B}_{bg}$ represents the background magnetic field magnitude, and $\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)$.
+The first two conditions ensure that the field changes are distinguishable from stochastic fluctuations, while the third condition serves as a supplementary measure to reduce recognition uncertainty [see discussion in @liuMagneticDiscontinuitiesSolar2022].
 
-Here, $\sigma$ denotes the standard deviation, ${\mathbf B}_{bg}$ represents the background magnetic field magnitude, and $\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)$.
-The first two conditions ensure that the field changes are distinguishable from stochastic fluctuations, while the third condition serves as a supplementary measure to reduce recognition uncertainty.
-
-Notably, this method shares certain similarities with the Partial Variance of Increments (PVI) approach for identifying coherent structures, as both calculate indices based on standard deviations (with this method focusing on the standard deviation of the magnetic field, and PVI on magnetic field increments).
-However, this method is better suited for discontinuity identification by comparing data within neighboring time windows rather than across a correlation scale (an unknown quantity that may vary with radial distance and solar wind conditions).
+Notably, this method shares certain similarities with the Partial Variance of Increments (PVI) approach [@grecoPartialVarianceIncrements2017] for identifying coherent structures, as both calculate indices based on standard deviations (with this method focusing on the standard deviation of the magnetic field, and PVI on magnetic field increments).
+However, @liuMagneticDiscontinuitiesSolar2022 method is better suited for discontinuity identification by comparing data within neighboring time windows rather than across a correlation scale (an unknown quantity that may vary with radial distance and solar wind conditions).
 As a result, this approach effectively excludes wave-like coherent structures, eliminating the need for manual inspection and bypassing the necessity of grouping continuous clusters of high-PVI points as in PVI analysis.
 
-Because the discontinuities may have different spatial scale at different radial distances from the Sun, we repeat the search procedure with time lags $T = 10, 20, 30, 40, 50, 60$ s, and combine the identified ID events together to establish the event list.
-Discontinuities with spatial scales larger than $60$ s are not considered in this study, however it could be argued that they are not significant in the outer heliosphere if they follow the trend with decreasing number of IDs with increasing spatial scale.
-@fig-junoDistribution also indicates that the spatial scale of IDs does not vary significantly with the radial distance from the Sun.
+Because the discontinuities may have different spatial scale at different radial distances from the Sun, we repeat the search procedure with time lags $T = 10, 20, 30, 40, 50, 60$ s, and combine the identified SWD events together to establish the event list.
+Discontinuities with spatial scales larger than $60$ s are not considered in this study, however it could be argued that they are not significant in the outer heliosphere if they follow the trend with decreasing number of SWDs with increasing spatial scale [see @Vasko22:apjl; @Vasko24:jgr].
+<!-- @fig-junoDistribution also indicates that the spatial scale of SWDs does not vary significantly with the radial distance from the Sun. -->
 
@@
 More than ?
-IDs are identified in the solar wind data from Juno, with ?
-IDs identified in 5 AU.
+SWDs are identified in the solar wind data from Juno, with ?
+SWDs identified within $[4, 5]$ AU.
 Then for each discontinuity identified, we calculate the distance matrix of the time series sequence (distance between each pair of magnetic field vectors) to determine the leading edge and trailing edge of the discontinuity.
-After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to transform the magnetic field into the boundary normal (LMN) coordinate system.
+After that, we use the minimum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to transform the magnetic field into the boundary normal ($LMN$) coordinate system.
 The main (most varying) magnetic field component, $B_l$, is then fitted by a hyperbolic tangent function to extract the parameters to properly describe the discontinuity @eq-fit.
-Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.
-
+Then we combine the magnetic field data and plasma data (from model) to obtain the thickness and the current density of the discontinuity.
 $$
@@
 $${#eq-fit}
-
-where $B_{l0}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_0$ is the time of discontinuity, $\Delta t$ is the transition time, and $c_l$ is the offset of the magnetic field change (in the case of an ideal discontinuity with perfect rotational symmetry, $c_l$ should theoretically be zero.
+where $B_{l0}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_0$ is the time of discontinuity detection, $\Delta t$ is the transition time, and $c_l$ is the offset of the magnetic field change (in the case of an ideal discontinuity with perfect rotational symmetry, $c_l$ should theoretically be zero.
 However, in the context of data processing, incorporating $c_l$ can enhance the fitting accuracy).
 
-Previous studies have indicated that the minimum variance direction obtained through Minimum Variance Analysis (MVA) is frequently unreliable.
-Improved accuracy can be achieved by either using the cross product of the magnetic field measured at the boundaries as the normal direction [@knetterFourpointDiscontinuityObservations2004] or by enforcing conditions such as $Δ|B|/|B| > 0.05$ or $ω > 60°$ [@liuFailuresMinimumVariance2023].
-The former approach requires a small normal component in the magnetic field, while the latter approach limits the dataset to a subset that satisfies these conditions.
+Previous studies have indicated that the minimum variance direction obtained through MVA is frequently unreliable \cite<see discussion in>{knetterFourpointDiscontinuityObservations2004,wangSolarWindCurrent2024}.
+Improved accuracy can be achieved by either using the cross product of the magnetic field measured at the boundaries as the normal direction [@knetterFourpointDiscontinuityObservations2004] or by enforcing conditions such as $Δ|B|/|B| > 0.05$ or $ω > 60°$ [@liuFailuresMinimumVariance2023], where $\Delta |{\mathbf B}|$ is the change in the magnitude of the magnetic field and $\omega$ is the field rotation angle across the discontinuity.
+The former approach requires a small normal component (component along the normal to SWD plane) in the magnetic field, while the latter approach limits the dataset to a subset that satisfies these conditions.
 In our analysis, we applied both methods and observed no significant differences in the results.
@@
 @fig-examples shows several examples of solar wind discontinuities detected by different spacecraft.
+Panels (a-c) show three examples of SWDs observed by Juno at 1, 3, and 5 AU distances, whereas panels (d-f) show three examples of SWDs observed by WIND, ARTEMIS, and STEREO-A (for these discontinuities we also show solar wind flow speed).
+All discontinuities share the same magnetic field configuration (in local $LMN$ coordinates): the main magnetic field component, $B_l$, reverses across the discontinuity, whereas the decrease of the magnetic pressure, $\sim B_l^2/2\mu_0$, is compensated by local enhancement of $B_m$ component.
+Such magnetic field rotation across the discontinuity keeps $|{\bf B}|$ almost constant \cite<typical magnetic field configuration for SWDs, see>{Artemyev19:grl:solarwind,vaskoKineticscaleCurrentSheets2022,Lotekar22,vaskoKineticScaleCurrentSheets2024}.
+The solar wind flow speed (three panels for WIND, ARTEMIS, and STEREO-A) shows typical jump across the discontinuities \cite<see discussion in>{Artemyev20:apjl}.
 
-<!-- - We use [@liuMagneticDiscontinuitiesSolar2022] method to identify IDs, which has better compatibility for the IDs with minor field changes.
-- Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features. -->
+<!-- - We use [@liuMagneticDiscontinuitiesSolar2022] method to identify SWDs, which has better compatibility for the SWDs with minor field changes.
+- Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract SWDs' features. -->
 
@@
 
-# Results
+# Results {#sec-results}
 
@@
 
-To comprehensively understand the radial evolution of the occurrence rate, particularly the average occurrence rate, it is essential to determine the statistical distributions underlying the observed samples.
+To comprehensively understand the radial evolution of the SWD occurrence rate, particularly the average occurrence rate, it is essential to determine the statistical distributions underlying the observed samples.
 This enables the derivation of meaningful inferences.
-In this context, we derived the probability distribution of the waiting time $τ$ (also referred to as the interarrival interval, as defined in @tsurutaniInterplanetaryDiscontinuitiesTemporal1979) at various radial distances.
+In this context, we derived the probability distribution of the waiting time $τ = t_{0,i} - t_{0,i-1}$, where $t_{0,i}$ is the time of detection of the $i$-th discontinuity event at various radial distances ($τ$ is also referred to as the interarrival interval in @tsurutaniInterplanetaryDiscontinuitiesTemporal1979).
 
-To model the data, we employ the Weibull distribution due to its flexibility in capturing varying occurrence rates.
+To model the data, we employ the Weibull distribution [@weibullStatisticalDistributionFunction1951] due to its flexibility in capturing varying occurrence rates.
 This choice allows for a more accurate representation and an improved fit compared to the exponential distribution previously used in @tsurutaniInterplanetaryDiscontinuitiesTemporal1979.
 The probability density function of the Weibull distribution is given as follows:
-
 $$
@@
 $$
-
-Here, $α$ and $θ$ represent the shape and scale parameters, respectively.
+where $α$ and $θ$ represent the shape and scale parameters, respectively.
 The complementary cumulative distribution function of the Weibull distribution $F(τ; α, θ) = 1 - \mathrm{e}^{-(τ/θ)^α}$ is a stretched exponential function (The Weibull distribution reduces to the exponential distribution when $α = 1$).
@@
 
-The occurrence rate of IDs is investigated with regards of the radial distance from the Sun for Juno, ARTEMIS, STEREO, and Wind.
-Number of discontinuities measured per day by different spacecraft missions (for the same temporal resolution of magnetic field data and the same criteria of discontinuity determination) is shown in @fig-rate.
-Because data is not continuously available and ARTEMIS spacecrafts will only be exposed in the solar wind for a relative short time during its orbits around the Moon (the Moon would be in the magnetosphere for a long time as it orbits the earth), the occurrence rate (numbder of IDs per day) is corrected with respect to data gap and the time the mission spent in the pristine solar wind.
-The occurrence rate of IDs observed by Juno is consistent with the occurrence rate observed by 1AU missions, when Juno is around $1$ AU.
+The occurrence rate of SWDs is investigated with regard to the radial distance from the Sun for Juno, ARTEMIS, STEREO, and Wind.
+The number of discontinuities measured per day by different spacecraft missions (for the same temporal resolution of the magnetic field data and the same criteria of discontinuity determination) is shown in @fig-rate.
+Because data is not continuously available and ARTEMIS spacecrafts will only be exposed in the solar wind for a relative short time during its orbits around the Moon (the Moon would be in the magnetosphere for a $\sim 30$% of it orbital time), the occurrence rate (number of SWDs per day) is corrected with respect to data gap and the time the mission spent in the pristine solar wind.
+The occurrence rate of SWDs observed by Juno is consistent with the occurrence rate observed by 1AU missions, when Juno is around $1$ AU.
 This number (occurrence rate) decreases with distance as Juno moves from $1$ AU to $5$ AU (corresponding to time after $\sim 2013$, the radial distance of Juno for 2011-2016 is shown in @fig-model)
@@
 The normalized occurrence rate is shown in panel (b) of @fig-rate.
-The occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
+The occurrence rate of SWDs drops with the radial distance from the Sun, following $1/r$ law.
 So the decrease of the occurrence rate with increasing radial distance from the Sun is expected to be a real effect of the radial distance from the Sun and this confirms the former results [@sodingRadialLatitudinalDependencies2001].
@@
 This number (occurrence rate) decreases with distance (with time after $\sim 2013$), as Juno moves from $1$ AU to $5$ AU.
-We will use the similar comparison for discontinuity characteristics and occurrence rate derived for PSP and Juno.
 The radial distance of Juno for 2011-2016 is shown in @fig-model.
@@
 
-The current density $J_m$ across a discontinuity is determined by
-
+The current density $J_m$ supporting the main magnetic field reversal across a discontinuity is determined by 
 $$
@@
 $$ {#eq-j}
-
 where $μ_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
 For fitting method, the derivative of the magnetic field could be estimated as $\max(d B_l / d t) = B_{l0} / \Delta t$.
-This estimate is more robust than the direct calculation of the derivative of the magnetic field, because the fitting method is less sensitive to the noise in the data and the time resolution of the data (see discussion in the appendix).
+This estimate is more robust than the direct calculation of the derivative of the magnetic field, because the fitting method is less sensitive to the noise in the data and the time resolution of the data (see discussion in the Appendix).
 
@@
 
-To understand the relationship between the discontinuity and the local plasma, we normalize the thickness of the discontinuity by the initial ion length and the current density by the Alfven current density $J_A = e N_p V_A$ (corresponding to the drift between protons and electrons of local Alfén speed $V_A$).
-Figure @fig-junoDistribution presents the statistical distribution of the (un)normalized thickness and current density of IDs grouped by the radial distance from the Sun collected by Juno.
+To understand the relationship between the discontinuity and the local plasma, we normalize the thickness of the discontinuity by the ion (proton) inertial length $d_i=c/w_{pi}$ and the current density by the Alfven current density $J_A = e N_p V_A$ (corresponding to the drift between protons and electrons of local Alfén speed $V_A$).
+@fig-junoDistribution presents the statistical distribution of the (un)normalized thickness and current density of SWDs grouped by the radial distance from the Sun collected by Juno.
 Panel (a,b) shows that the thickness increases with radial distance.
 However, after normalization, the thickness slightly decreases, with the most probable value around 4-2 $d_i$.
-With increasing radial distance, larger fraction of IDs have thickness less than 1 $d_i$, becombing sub-proton scale structures.
+With increasing radial distance, larger fraction of SWDs have thickness less than 1 $d_i$, becoming sub-proton scale structures.
 Panel (c,d) shows that the current density decreases with increasing radial distance.
 However, after normalization, it slightly increases, with the most probable value around 0.05-0.15 $J_A$.
-It should be noted that for the normalized thickness and current density, the change is not significant compared to the spread of the distribution.
+It should be noted that for the normalized thickness and current density, the change  with the radial distance is not significant compared to the spread of the distribution [see also discussion in @vaskoKineticScaleCurrentSheets2024].
 
-The distribution of the thickness and current density of IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) during the five year of Juno cruise phase are shown in @fig-windDistribution.
+The distribution of the thickness and current density of SWDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) during the five year of Juno cruise phase are shown in @fig-windDistribution.
 The distribution are grouped by the year of observation.
-Panel (a,b) shows that both the thickness and normalized thickness distribution of IDs remains almost constant with the year of observation.
-Most of the discontinuities have thickness around 350-3500 km, with the most probable value around 1000 km.
-Panel (c,d) shows that the current density slightly increases with the year of observation, with the most probable value around 5 $nA m^{-2}$, in consistence with previous studies [@vaskoKineticscaleCurrentSheets2022].
+Panels (a,b) show that both the thickness and normalized thickness distribution of SWDs remains almost constant with the year of observation.
+Most of the discontinuities have thickness around 350-3500 km at $1$ AU, with the most probable value around 1000 km.
+Panels (c,d) show that the current density slightly increases with the year of observation, with the most probable value around 5 $nA m^{-2}$, in consistence with previous studies [@vaskoKineticscaleCurrentSheets2022].
 However, after normalization, the current density distribution remains identical across the five years.
 The change in the current density could be explained by the change in the solar wind properties with the solar cycle, as shown in @fig-swParameters.
-Density and magnetic field asscoiated with the discontinuities increases with the solar cycle approaching the solar minimum, which could lead to the increase of the current density of the discontinuities with fixed normalized current density.
+Density and magnetic field associated with the discontinuities increases with the solar cycle approaching the solar minimum, which could lead to the increase of the current density of the discontinuities with fixed normalized current density.
 
@@
 
-Distribution of various properties of IDs observed by Juno grouped by the radial distance from the Sun.
+Distribution of various properties of SWDs observed by Juno grouped by the radial distance from the Sun.
 Panel (a) thickness, (b) normalized thickness, (c) current density, (d) normalized current density.
@@
 
-Distribution of various properties of IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) grouped by the year of observation.
+Distribution of various properties of SWDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) grouped by the year of observation.
 Panel (a) thickness, (b) normalized thickness, (c) current density, (d) normalized current density.
@@
 
-Solar wind parameters associated with the IDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) grouped by the year of observation.
+Solar wind parameters associated with the SWDs observed by 1AU satellites (Wind, ARTEMIS and STEREO-A) grouped by the year of observation.
 Panel (a) solar wind density, (b) magnetic field, (c) fitted magnetic field $A$ in @eq-fit.
@@
 
-## Dependences of occurrence rate
+## Dependence of occurrence rate {#sec-dependence}
 
@@
 At any given radial distance, discontinuities may originate from two primary sources: those generated near the Sun and convected outward by the solar wind, and those formed locally.
-Since the solar wind speed is significantly higher than the Alfvén speed—which characterizes the propagation speed of rotational discontinuities (RDs)—the fraction of inward-propagating discontinuities is expected to be negligible.
+Since the solar wind speed is significantly higher than the Alfvén speed—which characterizes the propagation speed of rotational discontinuities—the fraction of inward-propagating discontinuities is expected to be negligible.
 Additionally, when observations are made by a single spacecraft, some discontinuities may be missed due to unfavorable positioning or limitations in detection methods.
@@
 First, we consider the limitations of our current detection methods.
-An increase in the duration of discontinuities could render some of them unidentifiable if their duration becomes comparable to the time interval used in our analysis.
+An increase in the duration of discontinuities could render some of them unidentifiable if their duration becomes comparable to the time interval used in our analysis, $T$.
 Although we observe a slight increase in the average duration of discontinuities with radial distance, this increase is relatively small.
-The overall population of discontinuities is still predominantly characterized by those with short durations (see Figure X in the appendix).
+The overall population of discontinuities is still predominantly characterized by those with short durations (see @fig-TEffect in the Appendix).
 Since our method normalizes the change in the magnetic field by the surrounding magnetic field, a decrease in magnetic field variation with radial distance alone does not necessitate non-identification.
 Notably, our results differ from previous studies [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979], which reported typical durations of 2 to 3 seconds at 1 AU and 10 to 30 seconds at 5 AU.
-In our analysis, however, the observed durations remain below 10 seconds at 5 AU, suggesting that our method may be more effective at identifying shorter-duration events than those reported in prior studies.
+In our analysis, however, the observed durations remain below 10 seconds at 5 AU, suggesting that our method may be more effective at identifying shorter-duration events than those reported before.
 
@@
 Alternatively, we consider the hypothesis that the majority of discontinuities are generated close to the Sun.
-If we assume that discontinuities are one-dimensional, infinitely extended structures, then without annihilation, all discontinuities passing through one location would also pass through other radial distances.
-However, a more realistic assumption is that discontinuities are three-dimensional curved surfaces with lengths and widths proportional to their thickness.
-In this scenario, the occurrence rate observed by a single spacecraft does not represent the total number of discontinuities within a given shell.
-Since our spacecraft travels within the ecliptic plane and the normal direction of most discontinuities lies within this plane, it is necessary to project the discontinuities onto a circular cross-section.
-The projected lengths should then be normalized by the circumference of the circle to estimate the total number of discontinuities within the cylindrical shell.
-The normalization factor is  $d \sin\theta_{n,v} / r$ , where $d$ is the thickness of the discontinuity, $\theta_{n,v}$ is the angle between the normal direction of the discontinuity and the solar wind velocity, and  $r$ is the radial distance from the Sun (the result is shown in the appendix).
+A realistic assumption is that discontinuities are three-dimensional curved surfaces with lengths and widths proportional to their thickness.
+In this scenario, the occurrence rate observed by a single spacecraft does not represent the total number of discontinuities within a given shell (radial distance).
+Since spacecraft travels within the ecliptic plane and the normal direction of most discontinuities lies within this plane, it is necessary to project the discontinuities onto a circular cross-section.
+The projected lengths should then be normalized by the circumference of the circle to estimate the total number of discontinuities within the cylindrical shell surrounded Sun at given radial distance.
+The normalization factor is  $d \sin\theta_{n,v} / r$ , where $d$ is the thickness of the discontinuity, $\theta_{n,v}$ is the angle between the normal direction of the discontinuity and the solar wind velocity, and $r$ is the radial distance from the Sun (the result is shown in the Appendix).
 Accounting for this factor reduces the differences in the normalized occurrence rates observed by different spacecraft.
@@
 
-We have collected 5 years of solar wind discontinuities from JUNO, ARTEMIS and STEREO. The results can be summarized as follows:
+We have collected 5 years of solar wind discontinuities from Juno, Wind, ARTEMIS and STEREO. The results of analysis of these datasets can be summarized as follows:
 
-1. The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
+1. The normalized occurrence rate of SWDs drops with the radial distance from the Sun, following $1/r$ law within $[1,5]$AU.
 2.
-The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs slightly decreases.
-The thickness distribution of IDs remains almost constant with the year of observation.
+The thickness of SWDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of SWDs slightly decreases or remains almost constant within the scale of thickness distribution.
+The thickness distribution of SWDs remains almost constant with the time scale of one year of observation.
 3.
-The current density of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current density of IDs slightly increases.
-The current density distribution of IDs slightly increases with the year of observation, but after normalization, the current density distribution remains identical across the five years, thus no effect of the long-term (i.e.
-solar cycle) temporal variations.
+The current density of SWDs decrease with the radial distance from the Sun, but after normalization to the Alfven current, the current density of SWDs slightly increases or remains almost constant within the scale of thickness distribution.
+The current density distribution of SWDs slightly increases with the year of observation from 2011 to 2016, but after normalization, the current density distribution remains identical across the five years, thus no effect of the long-term (i.e.
+solar cycle) temporal variations is detected for normalized current density.
 
@@
 ![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-tsEffect}
+
+![The relative percentage of events as a function of radial distance (in AU) for different values of the parameter $T$ (20s, 30s, 40s, 50s, and 60s).
+The relative percentage of events is normalized to the number of events using $T=20$s.](figures/ocr/juno_tau_r.pdf){#fig-TEffect}

### 2025-01-01 article.qmd
docs: explain Vn accuracy

@@
 $$ {#eq-j}
-where $μ_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
+where $\μ_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity.
 For fitting method, the derivative of the magnetic field could be estimated as $\max(d B_l / d t) = B_{l0} / \Delta t$.
 This estimate is more robust than the direct calculation of the derivative of the magnetic field, because the fitting method is less sensitive to the noise in the data and the time resolution of the data (see discussion in the Appendix).
+Since the normal direction of the current sheet cannot be accurately determined using the MVA method, we also use the more reliable velocity $V_{nm} = \sqrt{V^2 - V_l^2}$ as an upper limit for $V_n$ to estimate $J_m$ and the subsequent $d$.
+Notably, this adjustment does not significantly affect the results presented here.
 

### 2025-01-02 notebooks/01_results_julia.qmd
feat: add combine and remove_duplicates figure for waiting time

@@
 ```{julia}
+df = load_taus(; unique_f=missing)
 jno_df = load();
 wind_df = load(; name="Wind", ts=missing);
+```
+
+```{julia}
+udf = Discontinuity.remove_duplicates(df)
+@info nrow(udf)
+@info nrow(subset(udf, :r => x -> x.>=4))
 ```
@@
 ```{julia}
-df = load_taus(; unique_f=missing)
-```
-
-```{julia}
 normalize_by_max(x) = x / maximum(x)
 normalize_by_max(df, x; kw...) = transform(df, x => normalize_by_max; kw...)
+normalize_by_all(x) = x / sum(x)
+normalize_by_all(df, x; kw...) = transform(df, x => normalize_by_all; kw...)
 
-function plot_nrow(df, x, dx, color; xlabel=x, normalize=true, plottype=Stairs, kw...)
+function plot_nrow(df, x, dx, color; xlabel=x, clabel=color, normalize=normalize_by_max, plottype=Stairs, kw...)
     y = Symbol(nrow)
@@
 
-    # normalize the nrows by the largest value
-    if normalize
-        df = normalize_by_max(groupby(df, [x]), y; renamecols=false)
+    if normalize isa Function
+        df = normalize(groupby(df, [x]), y; renamecols=false)
         ylabel = "Relative percentage of events"
@@
 
-    plt = data(df) * mapping(x => xlabel, y => ylabel; color) * visual(plottype)
+    plt = data(df) * mapping(x => xlabel, y => ylabel; color = color => clabel) * visual(plottype)
     draw(plt; kw...)
@@
 
-plot_nrow(df, :r, 0.5, :tau; xlabel=r_lab)
+let tdf = df
+    plot_nrow(tdf, :r, 0.5, :tau; xlabel=r_lab, clabel="T")
     easy_save("ocr/juno_tau_r")
+end
+
+let tdf = Discontinuity.remove_duplicates(df)
+    plot_nrow(tdf, :r, 0.5, :tau; normalize = normalize_by_all, xlabel=r_lab, clabel="T")
+    easy_save("ocr/juno_tau_r")
+end
 ```

### 2025-01-02 notebooks/02_waiting_time.qmd
feat: add combine and remove_duplicates figure for waiting time

@@
 ```{julia}
-let step = 5
+function plot_fig_wt_dist(; step=5, df1=jno_df_s1, df2=jno_df_s2)
     limits = (0, 680, 5e-6, 5e-2)
@@
     ax1 = new_ax((1, 1); xlabel="")
-    plot!(WaitingTimeDist(jno_df_s1, dists, step))
+    plot!(WaitingTimeDist(df1, dists, step))
     ax2 = new_ax((2, 1);)
-    plot!(WaitingTimeDist(jno_df_s2, dists, step))
+    plot!(WaitingTimeDist(df2, dists, step))
     axislegend(ax1, "Juno, 2011"; loc=:upperright)
     axislegend(ax2, "Juno, 2016"; loc=:upperright)
-    easy_save("fig_wt_dist")
+    return f
+end
+
+# let 
+#     plot_fig_wt_dist()
+#     easy_save("fig_wt_dist")
+# end
+
+let tdf = Discontinuity.remove_duplicates(df)
+    df1 = subset(tdf, :time => t -> year.(t) .== 2011)
+    df2 = subset(tdf, :time => t -> year.(t) .== 2016)
+    plot_fig_wt_dist(; df1, df2)
+    easy_save("fig_wt_dist_no_duplicates")
 end

### 2025-01-02 src/io.jl

@@ -48,9 +48,9 @@ This will remove events that appear in multiple taus datasets.
 However, this may not remove all "duplicates" that may have little duration differences, since "t_us", :"t_ds" are determined by the maximum distance, and they may vary across different taus for one "event".
 """
 function load_taus(; taus=DEFAULT_TAUS, unique_f=["t_us", "t_ds"])
-    df = vcat(load_tau.(taus)...)
+    df = vcat(load_tau.(taus)...; cols=:union)
     ismissing(unique_f) || unique!(df, unique_f)
-    df.tau = categorical(df.tau)
+    # df.tau = categorical(df.tau)
     return sort(df, :tau)
 end
 

### 2025-01-07 notebooks/01_results_julia.qmd
feat: update effect of time lag T

@@
 jno_df = load();
-wind_df = load(; name="Wind", ts=missing);
+wind_df = load(; name="Wind", ts=nothing);
 ```
@@
     plot_nrow(tdf, :r, 0.5, :tau; normalize = normalize_by_all, xlabel=r_lab, clabel="T")
-    easy_save("ocr/juno_tau_r")
+    ylims!(0, 0.7)
+    easy_save("ocr/juno_T_r")
 end

### 2025-03-11 notebooks/102_results_scattering.qmd
refactor: remove unused scattering function and add new results notebook

---
title: Ion Scattering by Solar Wind Discontinuities
---

```{julia}
include("../src/main.jl")
using Dates
using Beforerr
using FHist
using AlgebraOfGraphics: aog_theme

M = var_mapping()
```

Loading the data

```{julia}
name = "Wind"
df = load(; name);
```

```{julia}
# velocity v is normalized to $v0 = l Ω$, where $l$ represents the width of the RD and $Ω = q B/(mpc)$ is the cyclotron frequency.
using Unitful: ε0, μ0, mp
q_G = q / sqrt(4π * ε0)
B_G_factor = sqrt(4π / μ0)

function transform_scattering!(df::AbstractDataFrame)
    # gyrofrequency
    @chain df begin
        @transform!(
            :θ = acosd.(:bn_over_b),
            :E_norm = @. (q_G * :L_n_cross * :"B.mean" * B_G_factor / (mp * c^2)) |> NoUnits
        )
    end
end

transform_scattering!(df);
```

```{julia}
binedges = (-6:1, 0:10:180, 0:10:180)
hist3dbin(df) = Hist3D(
    (log10.(df[!, :E_norm]), df[!, :ω_in], df[!, :θ]); binedges
)

to_endpoints(binedges) = (first(binedges), last(binedges))

let
    h3d1 = hist3dbin(subset(df, :accuracy))
    h3d2 = hist3dbin(subset(df, :accuracy => ByRow(!)))
    z = zeros(eltype(bincounts(h3d1)))
    axis = (; aspect=:equal, xlabel="Log10 (He)", ylabel="In-plane rotation angle", zlabel="Azimuthal angle")

    f = Figure(; size=(600, 300), figure_padding=0)
    ax1 = Axis3(f[1, 1]; axis..., title="Reliable", protrusions=(30, 0, 60, 30))
    volume!(ax1, to_endpoints.(h3d1.binedges)..., replace(bincounts(h3d1), z => NaN))
    ax2 = Axis3(f[1, 2]; axis..., title="unreliable", protrusions=0)
    volume!(ax2, to_endpoints.(h3d2.binedges)..., replace(bincounts(h3d2), z => NaN))
    f
end

easy_save("scatter/$(name)_hist3d"; formats=[:png])
```

![](../figures/scatter/wind_hist3d.png)

```{julia}
# Volume plot type support in AOG
# https://github.com/MakieOrg/AlgebraOfGraphics.jl/pull/572

θ = :θ => "azimuthal angle"
Bn = :bn_over_b => abs => L"B_N/B";
v0 = :v0 => log10 => "Log v0";

layer = data(df) * mapping(layout=:accuracy);

xyz = (:E_norm, M.ω_in, θ)
datalimits = ((1, 14), (0, 180), (0, 180))
axis = (type=Axis3, width=400)
v = histogram(; datalimits, normalization=:pdf)
plt = data(df) * mapping(xyz...; layout=:accuracy) * v
fg = draw(plt; axis)
colorbar!(fg)
fg
```

```{julia}
datalimits = (2, 14)
axis = (; yscale=log10)
v = histogram(; normalization=:pdf, bins=20, datalimits)
dfplot(layer * v, v0; axis)
```

```{julia}
using FHist
using LinearAlgebra

function get_data(df; x=:v0, y=:ω_in, z=:θ)
    x = df[!, x] .|> ustrip .|> log2
    y = df[!, y]
    z = df[!, z] .|> abs
    return x, y, z
end

function get_hist3d(df)
    return Hist3D(
        get_data(df);
        binedges=(1.5:14.5, 20:10:180, 0:10:90),
    ) |> normalize
end

function plot_hist3d(df)
    h = get_hist3d(df)
    fig = Figure()
    ax = Axis3(fig[1, 1]; width=400, xlabel="log2(v0)", ylabel="ω_in", zlabel="θ")
    plot!(h)
    fig
end

using GLMakie
GLMakie.activate!()
plot_hist3d(filter_low_accuracy(df))
```

## Export

```{julia}
using HDF5

filename = datadir("$(name)_hist3d.h5")
h = get_hist3d(filter_low_accuracy(df))

function save(filename, h::Hist3D)
    # delete file if it exists
    isfile(filename) && rm(filename)
    h5writehist(filename, "hist", h)
end

save(filename, h)
```

```{julia}
*(size(bincounts(h))...) |> println
bincenters(h)
```

### 2025-03-11 src/io.jl

@@ -1,6 +1,6 @@
 using Printf
 using Discontinuity
-using Discontinuity: load
+using Discontinuity: load, unitize!
 using Dates
 using Dates: AbstractTime
 data_path = datadir("05_reporting")
@@ -18,9 +18,9 @@ post_process!(df) = begin
 end
 
 function Discontinuity.load(; tau=60, ts=1, name="JNO", dir=data_path, verbose=false, kw...)
-    ts = !ismissing(ts) ? Second(ts) : ts
-    tau = !ismissing(tau) ? Second(tau) : tau
-    ds = DataSet(; name, ts, tau, kw...)
+    ts = !isnothing(ts) ? Second(ts) : ts
+    tau = !isnothing(tau) ? Second(tau) : tau
+    ds = Discontinuity.DataSet(; name, ts, tau, kw...)
     df = load(ds; dir)
 
     if name == "JNO"
@@ -28,9 +28,12 @@ function Discontinuity.load(; tau=60, ts=1, name="JNO", dir=data_path, verbose=f
         df.T = df.T .* u"K"
     elseif name == "Wind"
         Discontinuity.calc_T!(df, "T")
+    elseif name == "STEREO"
+        nothing
     end
 
     df = df |> post_process!
+    :"B.mean" in names(df) && unitize!(df, :"B.mean", u"nT")
     verbose && println("Number of events: ", size(df, 1))
     insertcols!(df, :tau => tau, :ts => ts)
 end

### 2025-03-11 src/scattering.jl

@@ -1,18 +1,0 @@
-using PlasmaFormulary: ion_gyrofrequency
-using DataFramesMeta
-
-# velocity v is normalized to $v0 = l Ω$, where $l$ represents the width of the RD and $Ω = q B/(mpc)$ is the cyclotron frequency.
-function v_norm!(df::AbstractDataFrame)
-    # gyrofrequency
-    @chain df begin
-        @transform!(
-            :Ω = ion_gyrofrequency.(:"B.mean"),
-            :θ = acosd.(abs.(:bn_over_b))
-        )
-        @transform!(:v0 = :L_k .* :Ω)
-    end
-end
-
-θ = :θ => "azimuthal angle"
-Bn = :bn_over_b => abs => L"B_N/B";
-v0 = :v0 => log10 => "Log v0";

### 2025-03-13 notebooks/102_results_scattering.qmd
update scattering

@@
 using Beforerr
+using GLMakie
 using FHist
@@
 # velocity v is normalized to $v0 = l Ω$, where $l$ represents the width of the RD and $Ω = q B/(mpc)$ is the cyclotron frequency.
-using Unitful: ε0, μ0, mp
+using Unitful: ε0, μ0, mp, q, c
 q_G = q / sqrt(4π * ε0)
@@
     z = zeros(eltype(bincounts(h3d1)))
-    axis = (; aspect=:equal, xlabel="Log10 (He)", ylabel="In-plane rotation angle", zlabel="Azimuthal angle")
+    # axis = (; aspect=:equal, xlabel=L"\log (ṽ_B)", ylabel="In-plane rotation angle", zlabel="Azimuthal angle")
+    axis = (; aspect=:equal, xlabel=L"\log (ṽ_B)", ylabel=L"ω_{in}", zlabel=L"θ")
 
@@
     volume!(ax1, to_endpoints.(h3d1.binedges)..., replace(bincounts(h3d1), z => NaN))
-    ax2 = Axis3(f[1, 2]; axis..., title="unreliable", protrusions=0)
-    volume!(ax2, to_endpoints.(h3d2.binedges)..., replace(bincounts(h3d2), z => NaN))
+    # volume!(ax1, h3d1)
+    ax2 = Axis3(f[1, 2]; axis..., title="Unreliable", protrusions=0)
+    p = volume!(ax2, to_endpoints.(h3d2.binedges)..., replace(bincounts(h3d2), z => NaN))
+    Colorbar(f[1, 3], p)
+    # volume!(ax2, h3d2)
     f

### 2025-04-03 notebooks/01_results_julia.qmd
figure: polish

@@
 using DataFramesMeta
+using Beforerr
 @quickactivate
 include("../src/main.jl");
-M = var_mapping()
+M = var_mapping(; log_str="")
 
@@
 maps1 = [M.l_log M.l_norm_log; M.j_log M.j_norm_log]
-maps2 = [M.density_log M.B_log; beta_map M.bm0_log];
+maps2 = [M.density_log M.B_log; M.beta M.bm0_log];
+```
+
+```{julia}
+figure = (; size=Beforerr.figsize(7))
+
+"""
+    Strip trailing zeros from decimal numbers
+"""
+function _round(v;kw...)
+    rounded = string(round(v; digits=1, kw...))
+    # If it contains a decimal point, remove trailing zeros
+    if contains(rounded, ".")
+        # Remove trailing zeros
+        rounded = replace(rounded, r"\.?0+$" => "")
+        # If we removed everything after the decimal point, remove the decimal point too
+        rounded = replace(rounded, r"\.$" => "")
+    end
+    return rounded
+end
+
+axis = (; 
+    xticks = WilkinsonTicks(5),
+    xtickformat = values -> [L"10^{%$(_round(v))}" for v in values],
+    yscale=log10,
+)
 ```
@@
 let df = wind_df, fnames = ["wind_distribution_time", "wind_sw_paramters"]
-    fs = temp_plot(df).([maps1, maps2])
+    spec = data(df) * mapping(color=year_map)
+    fs = map([maps1, maps2]) do m
+        plot_dist(spec, m; 
+            datalimits=datalimits_f,
+            axis,
+            figure
+        )
+    end
     easy_save.(fnames, fs)
@@
 
+![](../figures/wind_distribution_time.png)
+
+![](../figures/wind_sw_paramters.png)
+
 ```{julia}
@@
 let df = jno_df, color = r_map, fnames = ["juno_distribution_r", "juno_sw_paramters"]
-    fs = temp_plot(df; color).([maps1, maps2])
+    spec = data(df) * mapping(; color)
+    fs = map([maps1, maps2]) do m
+        plot_dist(spec, m; 
+            datalimits=datalimits_f,
+            axis,
+            figure
+        )
+    end
+    resize_to_layout!.(fs)
     easy_save.(fnames, fs)
@@
 ```
+
+![](../figures/juno_distribution_r.png)
+![](../figures/juno_sw_paramters.png)
 
@@
 
+## Magnetic field magnitude and radial dependency
+
+```{julia}
+rfunc(r) = sqrt(1/r^2 + 1/r^4)
+rfunc(B,r) = B / rfunc(r)
+B_r_scaled= (:"B.mean", :r) => (log10 ∘ rfunc)
+B_m0_scaled= (:"fit.vars.amplitude", :r)  => (log10 ∘ abs ∘ rfunc)
+let df = jno_df, color = r_map, m = [M.B_log M.bm0_log; B_r_scaled B_m0_scaled]
+    spec = data(df) * mapping(; color)
+    f = plot_dist(spec, m; 
+            datalimits=datalimits_f,
+            axis
+        )
+    display(f)
+end
+```
+
 ## Bn and Change in dB

### 2025-04-03 src/main.jl

@@ -17,7 +17,14 @@ using Unitful
 import Base.round
 
 set_aog_theme!()
-theme = Theme(; colormap=Reverse(:tokyo), figure_padding=2)
+theme = Theme(;
+    colormap=Reverse(:tokyo),
+    figure_padding=2,
+    Axis=(
+        xminorticksvisible=true,
+        yminorticksvisible=true
+    )
+)
 update_theme!(theme)
 
 include("io.jl")

### 2025-04-24 notebooks/21_model.qmd
feat:  MHD Model and Juno solar wind parameters comparison

# MHD Model and Juno solar wind parameters comparison

@wilsonSolarWindProperties2018

```{julia}
using DrWatson
using Discontinuity
using Discontinuity: Alfven_current
using DataFramesMeta
using PlasmaFormulary: inertial_length

@quickactivate
include("../src/main.jl")
```

```{julia}
using CSV
using DataFrames

function HAPIDateTime(t::AbstractString)
    # Check if the string ends with Z and remove it for parsing
    t = rstrip(t, ['Z'])
    # Split into date and time parts if T is present
    parts = split(t, "T", limit=2)
    date_part = parts[1]
    time_part = length(parts) > 1 ? parts[2] : ""

    # Parse date part
    date = @something(
        tryparse(Date, date_part),
        tryparse_doy_date(date_part),
    )

    # Create DateTime with or without time
    if isempty(time_part)
        dt = DateTime(date)
    else
        dt = date + Time(time_part)
    end

    return dt
end

"""
Parse a date in Day of Year format (YYYY-DDD)
"""
function tryparse_doy_date(date_str::AbstractString)
    doy_regex = r"^(\d{4})-(\d{3})$"

    if occursin(doy_regex, date_str)
        m = match(doy_regex, date_str)
        year = parse(Int, m[1])
        doy = parse(Int, m[2])
        return Date(year) + Day(doy - 1)
    end

    return nothing
end

"""
    read_sw_params_csv(file="jgra54158-sup-0001-supinfo.csv")

Reads the solar wind parameters CSV file and returns a DataFrame.
"""
function read_sw_params_csv(file=datadir("jgra54158-sup-0001-supinfo.csv"))
    df = CSV.read(file, DataFrame)
    df[!, :UTC] = HAPIDateTime.(String.(df[!, :UTC]))
    return df
end

jno_sw_params = read_sw_params_csv()

# jno_df = load()
```

```{julia}
using FlexiJoins
using Distances
using Dates
using Unitful: μ0

jno_df_with_params = innerjoin(
    (jno_df, jno_sw_params),
    by_pred(x -> x.time .. (x.time + Minute(1)), ∋, :UTC);
)

@chain jno_df_with_params begin
    @transform! begin
        :N_PROTONS_CC = :N_PROTONS_CC .* u"cm^-3"
        :d_star = :d_star .* u"nT/s"
        :duration = :duration .* u"s"
        :V_KMPS = :V_KMPS .* u"km/s"
    end
    @transform! begin
        :V_n_cross_sw = @. abs(first(:n_cross) * :V_KMPS)
        :d_i_sw = inertial_length.(:N_PROTONS_CC, Unitful.q, Unitful.mp)
        :j_Alfven_sw = Alfven_current.(:b_mag, :N_PROTONS_CC)
    end
    @transform! begin
        :L_n_cross_sw = :V_n_cross_sw .* :duration
        :j0_k_sw = @. abs(:d_star / :V_n_cross_sw / μ0) |> u"nA/m^2"
    end
    @transform! begin
        :L_n_cross_sw_norm = @. :L_n_cross_sw / :d_i_sw |> NoUnits
        :j0_k_sw_norm = @. :j0_k_sw / :j_Alfven_sw |> NoUnits
    end
end
```

```{julia}
using CairoMakie
using UnitfulLatexify: latexroundunitlabel as lru

let df = jno_df_with_params, xlabel = "Model", ylabel = "Juno"
    f = Figure()
    ax = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel)
    scatter!(ax, norm.(df[!, :V]), ustrip.(df[!, :V_KMPS]))

    ax2 = f[1, 2] = Axis(f; title=lru("n", u"cm^-3"), xscale=log10, yscale=log10)
    scatter!(ax2, ustrip.(df[!, :n]), ustrip.(df[!, :N_PROTONS_CC]))
    ax3 = Axis(f[2, 1]; title=lru("L", u"km"), ylabel, xscale=log10, yscale=log10)
    scatter!(ax3, ustrip.(df[!, :L_n_cross]), ustrip.(df[!, :L_n_cross_sw]))
    ax4 = f[2, 2] = Axis(f; title=lru("J", u"nA/m^2"), xscale=log10, yscale=log10)
    scatter!(ax4, ustrip.(df[!, :j0_k]), ustrip.(df[!, :j0_k_sw]))
    ax5 = f[3, 1] = Axis(f; title=L"L/d_i", xlabel, ylabel, xscale=log10, yscale=log10)
    scatter!(ax5, df[!, :L_n_cross_norm], df[!, :L_n_cross_sw_norm])
    ax6 = f[3, 2] = Axis(f; title=L"J/J_{Alfven}", xlabel, xscale=log10, yscale=log10)
    scatter!(ax6, df[!, :j0_k_norm], df[!, :j0_k_sw_norm])
    for ax in (ax,)
        ablines!(ax, 0, 1, color=:red, linestyle=:dash)
    end

    lines!(ax2, exp10.(-1:0), exp10.(-1:0), color=:red, linestyle=:dash)
    lines!(ax3, exp10.([2, 4.5]), exp10.([2, 4.5]), color=:red, linestyle=:dash)
    lines!(ax4, exp10.(-2:1), exp10.(-2:1), color=:red, linestyle=:dash)
    lines!(ax5, exp10.(-1:2), exp10.(-1:2), color=:red, linestyle=:dash)
    lines!(ax6, exp10.(-2:1), exp10.(-2:1), color=:red, linestyle=:dash)

    easy_save("model/juno_sw_comparision")
end
```

![](../figures/model/juno_sw_comparision.png)

### 2025-04-24 src/plot.jl

@@ -7,20 +7,19 @@ round_c(x) = round(Integer, x)
 # %%
 # Define the labels for the plots
 r_lab = L"Radial Distance ($AU$)"
-r_map = :r => nonnumeric ∘ round_c  => r_lab
+r_map = :r => nonnumeric ∘ round_c => r_lab
 tau_map = :tau => nonnumeric => "τ (s)"
-year_map = :time => nonnumeric ∘ year  => "Year"
-month_map = :time => nonnumeric ∘ month  => "Month"
+year_map = :time => nonnumeric ∘ year => "Year"
+month_map = :time => nonnumeric ∘ month => "Month"
 week_map = :time => nonnumeric ∘ week => "Week";
-beta_map = :β => log10 => L"Log Plasma Beta $\beta$"
 
-function plot_duration(plt; 
-    datalimits_f = x -> quantile(x, [0.02, 0.98]),
-    axis = (; yscale=log10),
-    facet = (; linkxaxes=:none, linkyaxes=:none),
-    legend = (; position=:top, titleposition=:left)
+function plot_duration(plt;
+    datalimits_f=x -> quantile(x, [0.02, 0.98]),
+    axis=(; yscale=log10),
+    facet=(; linkxaxes=:none, linkyaxes=:none),
+    legend=(; position=:top, titleposition=:left)
 )
     plt *= mapping(:duration) * (visual(Lines))
-    specs = plt * density(; datalimits=datalimits_f) 
+    specs = plt * density(; datalimits=datalimits_f)
     draw(specs, axis=axis, facet=facet, legend=legend)
 end

### 2025-04-25 notebooks/02_waiting_time.qmd
docs: update

@@
 
+using Discontinuity: remove_duplicates
 using CairoMakie
@@
 ```{julia}
+df = load_taus(; unique_f=missing)
+
 wind_df = load(; name="Wind", ts=missing);
@@
 using Distributions
+import DataFrames: groupby
 
@@
 get_wt_fit_params(time; kwargs...) = get_fit_params(waiting_time(time); kwargs...)
+
+function groupby(df::AbstractDataFrame, dt::Period; col=:time)
+    @chain df begin
+        @transform!(:time_bin = round.(:time, dt),)
+        groupby(:time_bin)
+    end
+end
+
+begin
+    dt = Day(50)
+    tdf = @chain df begin
+        remove_duplicates
+        groupby(dt)
+        combine(
+            nrow,
+            :time => get_wt_fit_params => :τ,
+            [:r] .=> mean
+        )
+        @transform(:ρ = 1 ./ :τ)
+    end
+
+    x = :time_bin => "Time"
+    specs = data(tdf) * mapping(x, :ρ => "Occurence rates")
+    draw(specs)
+end
 ```
 
-```{julia}
-jno_ρ_df = @chain jno_df begin
-    @transform!(
-        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
-        :l = :L_k .* (abs ∘ cosd).(:θ_vn),
-        :l_n = :L_k .* (abs ∘ cos ∘ atan).(:Vn_y ./ :Vn_x)
-    )
-end;
-```
+### Normalization by thickness
 

### 2025-04-25 notebooks/21_model.qmd
docs: update

@@
 using PlasmaFormulary: inertial_length
+using SpaceDataModel: tryparse_datetime
 
@@
 using DataFrames
-
-function HAPIDateTime(t::AbstractString)
-    # Check if the string ends with Z and remove it for parsing
-    t = rstrip(t, ['Z'])
-    # Split into date and time parts if T is present
-    parts = split(t, "T", limit=2)
-    date_part = parts[1]
-    time_part = length(parts) > 1 ? parts[2] : ""
-
-    # Parse date part
-    date = @something(
-        tryparse(Date, date_part),
-        tryparse_doy_date(date_part),
-    )
-
-    # Create DateTime with or without time
-    if isempty(time_part)
-        dt = DateTime(date)
-    else
-        dt = date + Time(time_part)
-    end
-
-    return dt
-end
-
-"""
-Parse a date in Day of Year format (YYYY-DDD)
-"""
-function tryparse_doy_date(date_str::AbstractString)
-    doy_regex = r"^(\d{4})-(\d{3})$"
-
-    if occursin(doy_regex, date_str)
-        m = match(doy_regex, date_str)
-        year = parse(Int, m[1])
-        doy = parse(Int, m[2])
-        return Date(year) + Day(doy - 1)
-    end
-
-    return nothing
-end
+using Unitful
 
@@
     df = CSV.read(file, DataFrame)
-    df[!, :UTC] = HAPIDateTime.(String.(df[!, :UTC]))
+    @chain df begin
+        @transform! @byrow begin
+            :time = tryparse_datetime(String(:UTC))
+            :N_PROTONS_CC = :N_PROTONS_CC * u"cm^-3"
+            :V_KMPS = :V_KMPS * u"km/s"
+        end
+    end
     return df
@@
 
-jno_sw_params = read_sw_params_csv()
+@b read_sw_params_csv()
 
@@
     @transform! begin
-        :N_PROTONS_CC = :N_PROTONS_CC .* u"cm^-3"
+
         :d_star = :d_star .* u"nT/s"

### 2025-04-26 notebooks/21_model.qmd
update

@@
 ```{julia}
-using DrWatson
 using Discontinuity
 using Discontinuity: Alfven_current
-using DataFramesMeta
 using PlasmaFormulary: inertial_length
-using SpaceDataModel: tryparse_datetime
-
 @quickactivate
@@
 ```{julia}
+using DrWatson: datadir
 using CSV
-using DataFrames
+using DataFrames, DataFramesMeta
 using Unitful
+using SpaceDataModel: parse_doy_datetime
 
-"""
-    read_sw_params_csv(file="jgra54158-sup-0001-supinfo.csv")
-
-Reads the solar wind parameters CSV file and returns a DataFrame.
-"""
+"""Reads the solar wind parameters CSV file and returns a DataFrame."""
 function read_sw_params_csv(file=datadir("jgra54158-sup-0001-supinfo.csv"))
@@
         @transform! @byrow begin
-            :time = tryparse_datetime(String(:UTC))
+            :time = parse_doy_datetime(:UTC)
             :N_PROTONS_CC = :N_PROTONS_CC * u"cm^-3"
@@
 
-@b read_sw_params_csv()
-
-# jno_df = load()
+jno_sw_params = read_sw_params_csv()
 ```
@@
     @transform! begin
-
         :d_star = :d_star .* u"nT/s"

### 2025-04-30 notebooks/01_results_julia.qmd
update

@@
 title: Results (Julia)
+engine: julia
 ---
@@
 ```{julia}
+using Juno
+using Juno: r_map, datalimits_f
+using CairoMakie: WilkinsonTicks
+using CairoMakie.Makie: resize_to_layout!
 using DrWatson
@@
 using Beforerr
-@quickactivate
-include("../src/main.jl");
+import Beforerr: easy_save
+using LaTeXStrings
 M = var_mapping(; log_str="")
 
+set_aog_theme!()
 ```
@@
 # let df = j_events_taus
-let df = jno_df, color = r_map, fnames = ["juno_distribution_r", "juno_sw_paramters"]
+let color = r_map, fnames = ["juno_distribution_r", "juno_sw_paramters"]
+    df = subset_by_quantiles(udf, [:L_n_cross, :j0_k, :j0_k_norm])
     spec = data(df) * mapping(; color)
@@
     resize_to_layout!.(fs)
-    easy_save.(fnames, fs)
+    # easy_save.(fnames, fs)
     display.(fs)
@@
 ![](../figures/juno_sw_paramters.png)
+
+## Correlation analysis of SWDs observed by 1-AU satellites
+
+Correlation analysis on the current density and solar wind parameters (J-Ne, J-beta, J-|B|, etc.)
+
+```{julia}
+using DataStructures: nlargest
+let scols = [:j0_k,:j0_k_norm]
+    @info "Before subsetting" nlargest.(10, eachcol(wind_df[!, scols]))
+    sdf = subset_by_quantiles(wind_df, scols)
+    @info "After subsetting"  nlargest.(10, eachcol(sdf[!, scols]))
+end
+```
+
+```{julia}
+using PairPlots
+
+log_df(df) = log.(df)
+select_cols(df, cols) = df[!, cols]
+
+begin df = wind_df
+    @transform! df :year = year.(:time)
+    j_params = ["j0_k", "j0_k_norm", "j_Alfven", "n.mean", "B.mean", "β"]
+    cols = intersect(j_params, names(df))
+    sdf = subset_by_quantiles(ustrip.(df[!, cols]), Symbol.(cols), lower=0.01, upper=0.99)
+    corr_matrix = cor(Matrix(log_df(sdf)))
+    @info "Correlation Matrix" corr_matrix
+
+    fig = Figure()
+    gs = GridLayout(fig[1,1])
+    f = pairplot(gs[1:6,1:6], log_df(sdf))
+    # dfs = collect(groupby(df[!, [cols; "year"]], :year))
+    # f = pairplot(gs[1:6,2:7], log_df.(select_cols.(dfs, Ref(cols)))..., bottomleft=false, topright=true)
+    easy_save("temp/wind_pairplot")
+end
+```
+
+```julia
+┌ Info: Correlation Matrix
+│   corr_matrix =
+│    6×6 Matrix{Float64}:
+│     1.0         0.878214   0.240162   0.126952   0.267604   0.0864104
+│     0.878214    1.0       -0.253355  -0.247737  -0.160763   0.154384
+│     0.240162   -0.253355   1.0        0.759608   0.867571  -0.138572
+│     0.126952   -0.247737   0.759608   1.0        0.345521   0.233941
+│     0.267604   -0.160763   0.867571   0.345521   1.0       -0.36578
+└     0.0864104   0.154384  -0.138572   0.233941  -0.36578    1.0
+```
 

### 2025-04-30 src/Juno.jl

@@ -1,0 +1,68 @@
+module Juno
+using DrWatson
+using AlgebraOfGraphics,
+    CairoMakie
+using DataFrames,
+    DataFramesMeta,
+    CategoricalArrays
+
+using NaNStatistics: nanpctile
+using Statistics: quantile
+using Beforerr
+using LaTeXStrings
+using Discontinuity
+using Unitful
+import Base.round
+
+export subset_by_quantiles
+export load_taus
+
+set_aog_theme!()
+theme = Theme(;
+    colormap=Reverse(:tokyo),
+    figure_padding=2,
+    Axis=(
+        xminorticksvisible=true,
+        yminorticksvisible=true
+    )
+)
+update_theme!(theme)
+
+include("io.jl")
+include("plot.jl")
+
+datalimits_f = x -> quantile(x, [0.02, 0.98])
+
+foreach([:log10, :log2, :log]) do f
+    @eval import Base: $f
+    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
+end
+
+# Generalize function to round float like time
+Base.round(x::Number, y::Number; kw...) = y * round(x / y; kw...)
+
+struct Bound{T}
+    lower::T
+    upper::T
+end
+Bound(nt) = Bound(nt[1], nt[2])
+Base.in(x, bound::Bound) = bound.lower ≤ x ≤ bound.upper
+Base.in(::Missing, ::Bound) = false
+
+"""
+    subset_by_quantiles(df, cols; lower=0.01, upper=0.99)
+
+Returns a subset of `df` containing only rows where, for each column `col` in `cols`,
+the values lie between the `lower` and `upper` quantiles of `col`.
+"""
+function subset_by_quantiles(df, cols; lower=0.01, upper=0.99)
+    bounds = map(cols) do col
+        Bound(quantile.(Ref(skipmissing(df[!, col])), (lower, upper)))
+    end
+    f(row) = all(in(row[cols[i]], bounds[i]) for i in eachindex(cols))
+    return filter(f, df)
+end
+
+dfplot(layer, args...; axis=(;), kwargs...) = draw(layer * mapping(args...; kwargs...); axis)
+dfplot(df::AbstractDataFrame, args...; axis=(;), kwargs...) = draw(data(df) * mapping(args...; kwargs...); axis)
+end

### 2025-04-30 src/main.jl

@@ -1,44 +1,0 @@
-using DrWatson
-@quickactivate
-
-using AlgebraOfGraphics,
-    CairoMakie
-using DataFrames,
-    DataFramesMeta,
-    CategoricalArrays
-
-using Statistics
-using LinearAlgebra
-using Beforerr
-import Beforerr: easy_save
-using LaTeXStrings
-using Discontinuity
-using Unitful
-import Base.round
-
-set_aog_theme!()
-theme = Theme(;
-    colormap=Reverse(:tokyo),
-    figure_padding=2,
-    Axis=(
-        xminorticksvisible=true,
-        yminorticksvisible=true
-    )
-)
-update_theme!(theme)
-
-include("io.jl")
-include("plot.jl")
-
-datalimits_f = x -> quantile(x, [0.02, 0.98])
-
-foreach([:log10, :log2, :log]) do f
-    @eval import Base: $f
-    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
-end
-
-# Generalize function to round float like time
-Base.round(x::Number, y::Number; kw...) = y * round(x / y; kw...)
-
-dfplot(layer, args...; axis=(;), kwargs...) = draw(layer * mapping(args...; kwargs...); axis)
-dfplot(df::AbstractDataFrame, args...; axis=(;), kwargs...) = draw(data(df) * mapping(args...; kwargs...); axis)

### 2025-04-30 notebooks/30_data.qmd
feat: load Juno data

---
title: Data Processing (Julia)
---

```{julia}
using Parquet2
using DrWatson
using DataFrames
using DimensionalData

function get_juno_data(; dir=datadir(), cols=["BX SE", "BY SE", "BZ SE"])
    ds = Parquet2.Dataset(dir * "/2011.parquet")
    data = reduce(hcat, Parquet2.load(ds, col) for col in cols)
    times = Parquet2.load(ds, "time")
    dims = (Ti(times), Y())
    return DimArray(data, dims)
end

b = get_juno_data()
```

```{julia}
using Discontinuity
using Dates
period = Second(60)

# this is to speed up the detection
# also Juno data is of low precision
_float16(x) = convert(Array{Float16,ndims(x)}, x)

detect_variance(_float16(b), t, period, 10, Val(1))
```

### 2025-05-01 notebooks/30_data.qmd
update

@@
 ```{julia}
-using Parquet2
-using DrWatson
-using DataFrames
+using Juno.Data
 using DimensionalData
 
-function get_juno_data(; dir=datadir(), cols=["BX SE", "BY SE", "BZ SE"])
-    ds = Parquet2.Dataset(dir * "/2011.parquet")
-    data = reduce(hcat, Parquet2.load(ds, col) for col in cols)
-    times = Parquet2.load(ds, "time")
-    dims = (Ti(times), Y())
-    return DimArray(data, dims)
-end
-
-b = get_juno_data()
+n, V, T, r = get_state_data()
+b = get_mag_data()
 ```
@@
 
-# this is to speed up the detection
-# also Juno data is of low precision
-_float16(x) = convert(Array{Float16,ndims(x)}, x)
+ds = ids_finder(b, period, V, n)
 
-detect_variance(_float16(b), t, period, 10, Val(1))
+ds.r = r[Ti(Near(ds.time))]
 ```
+
+Diagnose the missing values
+
+```{julia}
+using SPEDAS
+
+@kwdef struct JunoEvent{D} <: AbstractEvent
+    data::D
+    start
+    stop
+    metadata = Dict()
+end
+
+JunoEvent(df::DataFrame, i) = Event(df[i, :], df.tstart[i], df.tstop[i])
+JunoEvent(df::DataFrame) = (i = rand(1:size(df, 1)); @info i; Event(df, i))
+
+df.time[isnan.(df.grad)]
+function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
+    tmin, tmax = t_us_ds(event)
+    f = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
+    tlines!(f, [tmin, tmax])
+    f
+end
+tplot(Product(b, tview), "2011-08-28T06:42:00", "2011-08-28T06:43:00")
+```
+
+```{julia}
+using Discontinuity: var_mapping
+
+M = var_mapping(; j=:J_m_max_mva)
+maps1 = [M.l_log M.l_norm_log; M.j_log M.j_norm_log]
+maps2 = [M.density_log M.B_log; M.beta M.bm0_log];
+df
+begin
+    color = r_map
+    fnames = ["juno_distribution_r", "juno_sw_paramters"]
+    # df = subset_by_quantiles(ds, [:L_n_cross, :j0_k, :j0_k_norm])
+    df = dropmissing(ds)
+    spec = data(df) * mapping(; color)
+    fs = map([maps1, maps2]) do m
+        plot_dist(spec, m;
+            datalimits=datalimits_f,
+            axis,
+            figure
+        )
+    end
+    resize_to_layout!.(fs)
+    # easy_save.(fnames, fs)
+    display.(fs)
+end
+```

### 2025-05-01 scripts/data.py

@@ -21,4 +21,9 @@ w_conf = WindConfig(test=True)
 w_conf.get_data()
 w_conf.plasma_data
 print(w_conf)
+
+s_conf = StereoConfig(test=True)
+s_conf.get_data()
+s_conf.plasma_data
+
 # %%

### 2025-05-01 src/Juno.jl

@@ -30,6 +30,7 @@ update_theme!(theme)
 
 include("io.jl")
 include("plot.jl")
+include("data.jl")
 
 datalimits_f = x -> quantile(x, [0.02, 0.98])
 

### 2025-05-01 src/data.jl

@@ -1,0 +1,41 @@
+module Data
+using Parquet2
+using DimensionalData
+using DimensionalData: DimArray, Ti, Y, ForwardOrdered, Unordered
+
+export get_mag_data, get_state_data
+
+data_dir = homedir() * "/data"
+
+_nonmissingtype(::AbstractArray{T}) where {T} = Array{nonmissingtype(T)}
+nonmissing(x) = convert(_nonmissingtype(x), x)
+
+load(ds, col) = Parquet2.load(ds, col) |> nonmissing
+
+function get_mag_data(file="2011.parquet"; dir="data/03_primary/JNO_MAG_ts_1s", cols=["BX SE", "BY SE", "BZ SE"])
+    ds = Parquet2.Dataset(dir * "/" * file)
+    data = reduce(hcat, load(ds, col) for col in cols)
+    times = load(ds, "time")
+    t_dim = Ti(times)
+    dims = (t_dim, Y())
+    return DimArray(data, dims)
+end
+
+function get_state_data(file="JNO_STATE_ts_3600s.parquet"; dir="./data/03_primary", cols=["BX SE", "BY SE", "BZ SE"])
+    path = dir * "/" * file
+    v_cols = ("v_x", "v_y", "v_z")
+
+    ds = Parquet2.Dataset(path)
+    times = load(ds, "time")
+    t_dim = Ti(times)
+
+    n = DimArray(load(ds, "plasma_density"), (t_dim,))
+    v_data = reduce(hcat, load(ds, col) for col in v_cols)
+    v = DimArray(v_data, (t_dim, Y()))
+    T = DimArray(load(ds, "plasma_temperature"), (t_dim,))
+    r = DimArray(load(ds, "radial_distance"), (t_dim,))
+    return (; n, v, T, r)
+end
+
+
+end

### 2025-05-01 src/juno/config.py

@@ -92,6 +92,14 @@ wi_k0_swe_ds = PlasmaDataset(
     dataset="WI_K0_SWE", parameters=["Np", "V_GSE", "THERMAL_SPD"]
 )
 
+sta_l1_mag_rtn = MagVariable(
+    dataset="STA_L1_MAG_RTN",
+    parameter=["BFIELD"],
+    B_cols=["BR", "BT", "BN"],
+    ts=timedelta(seconds=0.125),
+)
+
+# sta_l2_impact_magplasma = PlasmaDataset()
 
 class WindConfig(Config, WindConfigBase, SpeasyIDsConfig):
     provider: str = "archive/local"
@@ -100,7 +108,8 @@ class WindConfig(Config, WindConfigBase, SpeasyIDsConfig):
 
 
 class StereoConfig(Config, StereoConfigBase, SpeasyIDsConfig):
-    pass
+    provider: str = "archive/local"
+    mag_meta: MagVariable = sta_l1_mag_rtn
 
 
 class THEMISConfig(ThemisConfigBase, SpeasyIDsConfig):

### 2025-05-01 src/juno/juno.py

@@ -6,14 +6,14 @@ import os
 import polars as pl
 from intake.source.utils import reverse_formats
 from datetime import datetime
-from beforerr.project import datadir
+from pathlib import Path
 from datetime import timedelta
 
 
 def preprocess(
     fp,
     every=timedelta(seconds=0.125),
-    dir_path=datadir() / "02_intermediate/JNO_MAG_8hz",
+    dir_path=Path.home() / "data/02_intermediate/JNO_MAG_8hz",
     update=False,
 ):
     fname = fp.split("/")[-1]

### 2025-05-01 notebooks/30_data.qmd
update

@@
 using Dates
+using DataFrames
 period = Second(60)
@@
 ds.r = r[Ti(Near(ds.time))]
+
+df = dropmissing(ds)
 ```
@@
 using SPEDAS
-
-@kwdef struct JunoEvent{D} <: AbstractEvent
-    data::D
-    start
-    stop
-    metadata = Dict()
-end
+using Discontinuity: mva_transform, tanh_model
 
@@
 
-df.time[isnan.(df.grad)]
-function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
-    tmin, tmax = t_us_ds(event)
-    f = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
-    tlines!(f, [tmin, tmax])
+B_product = Product(b, tview)
+
+struct FitProduct{F,P} <: Function
+    f::F
+    param::P
+    t_fit::DateTime
+end
+
+function (p::FitProduct)(t0, t1)
+    tspan = DateTime(t0):Millisecond(10):DateTime(t1)
+    xspan = (tspan .- p.t_fit) / Millisecond(1)
+    data = p.f.(xspan, Ref(p.param))
+    return DimVector(data, Ti(tspan))
+end
+
+FitProduct(row) = FitProduct(tanh_model, row.fit_param, row.t_us_ds[1])
+FitProduct(df::DataFrame, i) = FitProduct(df[i, :])
+
+struct MVAProduct <: Function
+    V
+    B
+    B_tspan
+end
+
+(p::MVAProduct)(t0, t1) = mva(p.V(t0, t1), p.B(p.B_tspan...))
+
+function plot_candidate(df::DataFrame, i, toffset=Second(0); kwargs...)
+    row = df[i, :]
+    B_mva = MVAProduct(B_product, B_product, row.t_us_ds)
+    Bl_fit_product = FitProduct(row)
+
+    tmin, tmax = row.tstart, row.tstop
+    f = tplot([B_product, B_mva, Bl_fit_product], tmin - toffset, tmax + toffset; kwargs...)
+    tlines!(f, collect(row.t_us_ds))
     f
 end
-tplot(Product(b, tview), "2011-08-28T06:42:00", "2011-08-28T06:43:00")
+```
+
+```{julia}
+# 740, 1508, 4004, 4805
+for i in [740, 1508, 4805]
+    display(plot_candidate(df, i))
+end
 ```

### 2025-05-01 src/data.jl

@@ -21,7 +21,7 @@ function get_mag_data(file="2011.parquet"; dir="data/03_primary/JNO_MAG_ts_1s", 
     return DimArray(data, dims)
 end
 
-function get_state_data(file="JNO_STATE_ts_3600s.parquet"; dir="./data/03_primary", cols=["BX SE", "BY SE", "BZ SE"])
+function get_state_data(file="JNO_STATE_ts_3600s.parquet"; dir="./data/03_primary")
     path = dir * "/" * file
     v_cols = ("v_x", "v_y", "v_z")
 

### 2025-05-02 notebooks/21_model.qmd
feat: juno dist with real solar wind data

@@
 using DrWatson: datadir
-using CSV
 using DataFrames, DataFramesMeta
 using Unitful
-using SpaceDataModel: parse_doy_datetime
-
-"""Reads the solar wind parameters CSV file and returns a DataFrame."""
-function read_sw_params_csv(file=datadir("jgra54158-sup-0001-supinfo.csv"))
-    df = CSV.read(file, DataFrame)
-    @chain df begin
-        @transform! @byrow begin
-            :time = parse_doy_datetime(:UTC)
-            :N_PROTONS_CC = :N_PROTONS_CC * u"cm^-3"
-            :V_KMPS = :V_KMPS * u"km/s"
-        end
-    end
-    return df
-end
+using Juno.Data: read_sw_params_csv
 

### 2025-05-02 notebooks/30_data.qmd
feat: juno dist with real solar wind data

@@
 n, V, T, r = get_state_data()
-b = get_mag_data()
+jno_sw_params = read_sw_params_csv()
 ```
@@
 
-ds = ids_finder(b, period, V, n)
+ds = mapreduce(vcat, 2011:2016) do year
+    b = get_mag_data(year)
+    ids_finder(b, period, V, n)
+end
+```
 
+```{julia}
+using FlexiJoins
+using StaticArrays
 ds.r = r[Ti(Near(ds.time))]
+ds.T = T[Ti(Near(ds.time))] * u"K"
 
 df = dropmissing(ds)
+
+df_sw = innerjoin(
+    (ds, jno_sw_params),
+    by_pred(x -> x.time .. (x.time + Minute(1)), ∋, :time);
+)
+@transform! df_sw @byrow begin
+    :n = :N_PROTONS_CC
+    :V = SA[:V_KMPS, 0, 0] * u"km/s"
+    :T = :T_PROTONS_EV * u"eV"
+    :r = "5 (Data)"
+end
 ```
@@
     param::P
-    t_fit::DateTime
+    t0::DateTime
 end
@@
     tspan = DateTime(t0):Millisecond(10):DateTime(t1)
-    xspan = (tspan .- p.t_fit) / Millisecond(1)
+    xspan = @. (tspan - p.t0) / Millisecond(1)
     data = p.f.(xspan, Ref(p.param))
@@
     B
-    B_tspan
+    mva_tspan
 end
 
-(p::MVAProduct)(t0, t1) = mva(p.V(t0, t1), p.B(p.B_tspan...))
+(p::MVAProduct)(t0, t1) = mva(p.V(t0, t1), p.B(p.mva_tspan...))
 
@@
 ```{julia}
+indices = eachindex(df.grad)[isnan.(df.grad)]
+```
+
+```{julia}
 # 740, 1508, 4004, 4805
-for i in [740, 1508, 4805]
+# 3094
+for i in [4805]
     display(plot_candidate(df, i))
@@
 ```{julia}
-using Discontinuity: var_mapping
+using Discontinuity: var_mapping, compute_params!
 
-M = var_mapping(; j=:J_m_max_mva)
+M = var_mapping(; log_str="", j=:J_m_max_mva, n=:n, B=:B_mag)
 maps1 = [M.l_log M.l_norm_log; M.j_log M.j_norm_log]
-maps2 = [M.density_log M.B_log; M.beta M.bm0_log];
-df
-begin
+maps2 = [M.density_log M.B_log; M.beta :V_mag];
+let df = vcat(df, df_sw, cols=:intersect)
     color = r_map
@@
     # df = subset_by_quantiles(ds, [:L_n_cross, :j0_k, :j0_k_norm])
-    df = dropmissing(ds)
+    df = compute_params!(dropmissing(df))
     spec = data(df) * mapping(; color)
-    fs = map([maps1, maps2]) do m
+    fs = map([maps1]) do m
         plot_dist(spec, m;
@@
 end
+easy_save("juno_distribution_r_sw")
 ```

### 2025-05-02 src/data.jl

@@ -1,9 +1,13 @@
 module Data
 using Parquet2
+using CSV
+using Unitful
+using DataFrames, DataFramesMeta
 using DimensionalData
 using DimensionalData: DimArray, Ti, Y, ForwardOrdered, Unordered
+using SpaceDataModel: parse_doy_datetime
 
-export get_mag_data, get_state_data
+export get_mag_data, get_state_data, read_sw_params_csv
 
 data_dir = homedir() * "/data"
 
@@ -12,7 +16,8 @@ nonmissing(x) = convert(_nonmissingtype(x), x)
 
 load(ds, col) = Parquet2.load(ds, col) |> nonmissing
 
-function get_mag_data(file="2011.parquet"; dir="data/03_primary/JNO_MAG_ts_1s", cols=["BX SE", "BY SE", "BZ SE"])
+function get_mag_data(time; dir="data/03_primary/JNO_MAG_ts_1s", cols=["BX SE", "BY SE", "BZ SE"])
+    file = "$time.parquet"
     ds = Parquet2.Dataset(dir * "/" * file)
     data = reduce(hcat, load(ds, col) for col in cols)
     times = load(ds, "time")
@@ -37,5 +42,14 @@ function get_state_data(file="JNO_STATE_ts_3600s.parquet"; dir="./data/03_primar
     return (; n, v, T, r)
 end
 
+"""Reads the solar wind parameters CSV file and returns a DataFrame."""
+function read_sw_params_csv(file="./data/jgra54158-sup-0001-supinfo.csv")
+    @transform! CSV.read(file, DataFrame) @byrow begin
+        :time = parse_doy_datetime(:UTC)
+        # :N_PROTONS_CC = :N_PROTONS_CC * u"cm^-3"
+        # :V_KMPS = :V_KMPS * u"km/s"
+        # :T_PROTONS_EV = :T_PROTONS_EV * u"eV"
+    end
+end
 
 end

### 2025-05-02 src/plot.jl

@@ -2,12 +2,13 @@ using AlgebraOfGraphics: density
 
 using Dates
 
-round_c(x) = round(Integer, x)
+nonnumeric_r(x::Number) = string(round(Integer, x))
+nonnumeric_r(x) = x
 
 # %%
 # Define the labels for the plots
 r_lab = L"Radial Distance ($AU$)"
-r_map = :r => nonnumeric ∘ round_c => r_lab
+r_map = :r => nonnumeric_r => r_lab
 tau_map = :tau => nonnumeric => "τ (s)"
 year_map = :time => nonnumeric ∘ year => "Year"
 month_map = :time => nonnumeric ∘ month => "Month"

### 2025-05-03 notebooks/01_results_julia.qmd
update

@@
 using Juno
-using Juno: r_map, datalimits_f
+using Juno: r_map, datalimits_f, produce_or_load_juno
+using CairoMakie
 using CairoMakie: WilkinsonTicks
@@
 using Discontinuity
+using Discontinuity: var_mapping, compute_params!, compute_orientation_params!, filter_low_mva_quality!
 using AlgebraOfGraphics
@@
 using LaTeXStrings
+using Unitful
 M = var_mapping(; log_str="")
@@
 ![](../figures/juno_sw_paramters.png)
+
+### Orientation
+
+```{julia}
+# ds = produce_or_load_juno()
+let df= dropmissing(ds), color = r_map
+    @chain df begin
+        compute_orientation_params!
+        filter_low_mva_quality!
+    end
+    f = Figure()
+    spec = data(df) * mapping(:B_n_mva_norm, :B_n_cross_norm) * AlgebraOfGraphics.density()
+    draw!(f[1,1],spec)
+    spec2 = data(df) * mapping(:θ_mva_cross) * AlgebraOfGraphics.density()
+    draw!(f[1,2],spec2)
+    f
+end
+```
 

### 2025-05-03 notebooks/21_model.qmd
update

@@
 using Discontinuity
-using Discontinuity: Alfven_current
-using PlasmaFormulary: inertial_length
-@quickactivate
-include("../src/main.jl")
+using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current
+using Juno: produce_or_load_juno
+using PlasmaFormulary: CurrentDensity, NumberDensity
 ```
@@
 ```{julia}
-using DrWatson: datadir
 using DataFrames, DataFramesMeta
@@
 
-jno_sw_params = read_sw_params_csv()
+jno_df = produce_or_load_juno()
+jno_sw_params = read_sw_params_csv(; add_unit=true)
 ```
@@
 using FlexiJoins
-using Distances
 using Dates
@@
     (jno_df, jno_sw_params),
-    by_pred(x -> x.time .. (x.time + Minute(1)), ∋, :UTC);
+    by_pred(x -> x.time .. (x.time + Minute(1)), ∋, :time);
 )
@@
 @chain jno_df_with_params begin
-    @transform! begin
-        :d_star = :d_star .* u"nT/s"
-        :duration = :duration .* u"s"
-        :V_KMPS = :V_KMPS .* u"km/s"
-    end
+    compute_params!
     @transform! begin
         :V_n_cross_sw = @. abs(first(:n_cross) * :V_KMPS)
+        :V_n_mva_sw = @. abs(first(:n_mva) * :V_KMPS)
         :d_i_sw = inertial_length.(:N_PROTONS_CC, Unitful.q, Unitful.mp)
-        :j_Alfven_sw = Alfven_current.(:b_mag, :N_PROTONS_CC)
+        :J_A_sw = Alfven_current.(:B_mag, :N_PROTONS_CC)
     end
-    @transform! begin
+    @transform! @astable begin
         :L_n_cross_sw = :V_n_cross_sw .* :duration
-        :j0_k_sw = @. abs(:d_star / :V_n_cross_sw / μ0) |> u"nA/m^2"
-    end
-    @transform! begin
         :L_n_cross_sw_norm = @. :L_n_cross_sw / :d_i_sw |> NoUnits
-        :j0_k_sw_norm = @. :j0_k_sw / :j_Alfven_sw |> NoUnits
+        :L_n_mva_sw = :V_n_mva_sw .* :duration
+        :L_n_mva_sw_norm = @. :L_n_mva_sw / :d_i_sw |> NoUnits
+        :J_m_max_cross_sw = @. abs(gradient_current(:grad, :V_n_cross_sw))
+        :J_m_max_cross_sw_norm = @. :J_m_max_cross_sw / :J_A_sw |> NoUnits
+        :J_m_max_mva_sw = @. abs(gradient_current(:grad, :V_n_mva_sw))
+        :J_m_max_mva_sw_norm = @. :J_m_max_mva_sw / :J_A_sw |> NoUnits
     end
@@
 using UnitfulLatexify: latexroundunitlabel as lru
+using CairoMakie.GeometryBasics
 
-let df = jno_df_with_params, xlabel = "Model", ylabel = "Juno"
-    f = Figure()
-    ax = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel)
-    scatter!(ax, norm.(df[!, :V]), ustrip.(df[!, :V_KMPS]))
+p_big = decompose(Point2f, Circle(Point2f(0), 1))
+p_small = decompose(Point2f, Circle(Point2f(0), 0.5))
 
-    ax2 = f[1, 2] = Axis(f; title=lru("n", u"cm^-3"), xscale=log10, yscale=log10)
-    scatter!(ax2, ustrip.(df[!, :n]), ustrip.(df[!, :N_PROTONS_CC]))
-    ax3 = Axis(f[2, 1]; title=lru("L", u"km"), ylabel, xscale=log10, yscale=log10)
-    scatter!(ax3, ustrip.(df[!, :L_n_cross]), ustrip.(df[!, :L_n_cross_sw]))
-    ax4 = f[2, 2] = Axis(f; title=lru("J", u"nA/m^2"), xscale=log10, yscale=log10)
-    scatter!(ax4, ustrip.(df[!, :j0_k]), ustrip.(df[!, :j0_k_sw]))
-    ax5 = f[3, 1] = Axis(f; title=L"L/d_i", xlabel, ylabel, xscale=log10, yscale=log10)
-    scatter!(ax5, df[!, :L_n_cross_norm], df[!, :L_n_cross_sw_norm])
-    ax6 = f[3, 2] = Axis(f; title=L"J/J_{Alfven}", xlabel, xscale=log10, yscale=log10)
-    scatter!(ax6, df[!, :j0_k_norm], df[!, :j0_k_sw_norm])
-    for ax in (ax,)
+uless(x) = NoUnits(x)
+uless(x::NumberDensity) = NoUnits(x / u"cm^-3")
+uless(x::CurrentDensity) = NoUnits(x / u"nA/m^2")
+uless(x::Unitful.Length) = NoUnits(x / u"km")
+uless(x::Unitful.Velocity) = NoUnits(x / u"km/s")
+
+let df = jno_df_with_params, xlabel = "Model", ylabel = "Juno", xscale = log10, yscale = log10, plot = (; alpha=0.3)
+    f = Figure(; size=(600, 600))
+    ax1 = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel)
+    ax2 = Axis(f[1, 2]; title=lru("n", u"cm^-3"), xscale, yscale)
+    ax3 = Axis(f[2, 1]; title=lru("L", u"km"), ylabel, xscale, yscale)
+    ax4 = Axis(f[2, 2]; title=lru("J", u"nA/m^2"), xscale, yscale)
+    ax5 = Axis(f[3, 1]; title=L"L/d_i", xlabel, ylabel, xscale, yscale)
+    ax6 = Axis(f[3, 2]; title=L"J/J_{Alfven}", xlabel, xscale, yscale)
+
+    p1, p2 = @with df begin
+        scatter!(ax1, uless.(:V_mag), uless.(:V_KMPS))
+        scatter!(ax2, uless.(:n), uless.(:N_PROTONS_CC))
+
+        p1 = scatter!(ax3, uless.(:L_n_cross), uless.(:L_n_cross_sw), label="Cross"; plot...)
+        p2 = scatter!(ax3, uless.(:L_n_mva), uless.(:L_n_mva_sw), label="MVA"; plot...)
+
+        scatter!(ax4, uless.(:J_m_max_cross), uless.(:J_m_max_cross_sw), label="Cross"; plot...)
+        scatter!(ax4, uless.(:J_m_max_mva), uless.(:J_m_max_mva_sw), label="MVA"; plot...)
+
+        scatter!(ax5, uless.(:L_n_cross_norm), uless.(:L_n_cross_sw_norm); plot...)
+        scatter!(ax5, uless.(:L_n_mva_norm), uless.(:L_n_mva_sw_norm); plot...)
+        scatter!(ax6, uless.(:J_m_max_cross_norm), uless.(:J_m_max_cross_sw_norm); plot...)
+        scatter!(ax6, uless.(:J_m_max_mva_norm), uless.(:J_m_max_mva_sw_norm); plot...)
+        (p1, p2)
+    end
+
+    Legend(f[1, 3], [p1, p2], ["Cross", "MVA"])
+
+    for ax in (ax1,)
         ablines!(ax, 0, 1, color=:red, linestyle=:dash)
@@
 
+    limits!(ax1, 360, 550, 360, 550)
+
     easy_save("model/juno_sw_comparision")

### 2025-05-03 notebooks/30_data.qmd
update

@@
 ```{julia}
+using Juno: produce_or_load_juno
 using Juno.Data
@@
 using DataFrames
-period = Second(60)
 
-ds = mapreduce(vcat, 2011:2016) do year
-    b = get_mag_data(year)
-    ids_finder(b, period, V, n)
-end
+ds = produce_or_load_juno()
 ```
@@
 using StaticArrays
-ds.r = r[Ti(Near(ds.time))]
+ds.r = parent(r[Ti(Near(ds.time))])
 ds.T = T[Ti(Near(ds.time))] * u"K"

### 2025-05-03 src/data.jl

@@ -1,5 +1,6 @@
 module Data
 using Parquet2
+using Arrow
 using CSV
 using Unitful
 using DataFrames, DataFramesMeta
@@ -26,6 +27,17 @@ function get_mag_data(time; dir="data/03_primary/JNO_MAG_ts_1s", cols=["BX SE", 
     return DimArray(data, dims)
 end
 
+# '/Volumes/My Passport for Mac/data/02_intermediate/JNO_MAG_8hz/fgm_jno_l3_2016181se_v01.arrow'
+function get_mag_data(year, doy; dir=homedir() * "/data/02_intermediate/JNO_MAG_8hz", cols=["BX SE", "BY SE", "BZ SE"])
+    file = "fgm_jno_l3_$(year)$(string(doy, pad=3))se_v01.arrow"
+    ds = Arrow.Table(dir * "/" * file)
+    # data = reduce(hcat, load(ds, col) for col in cols)
+    # times = load(ds, "time")
+    # t_dim = Ti(times)
+    # dims = (t_dim, Y())
+    # return DimArray(data, dims)
+end
+
 function get_state_data(file="JNO_STATE_ts_3600s.parquet"; dir="./data/03_primary")
     path = dir * "/" * file
     v_cols = ("v_x", "v_y", "v_z")
@@ -43,13 +55,17 @@ function get_state_data(file="JNO_STATE_ts_3600s.parquet"; dir="./data/03_primar
 end
 
 """Reads the solar wind parameters CSV file and returns a DataFrame."""
-function read_sw_params_csv(file="./data/jgra54158-sup-0001-supinfo.csv")
-    @transform! CSV.read(file, DataFrame) @byrow begin
-        :time = parse_doy_datetime(:UTC)
-        # :N_PROTONS_CC = :N_PROTONS_CC * u"cm^-3"
-        # :V_KMPS = :V_KMPS * u"km/s"
-        # :T_PROTONS_EV = :T_PROTONS_EV * u"eV"
+function read_sw_params_csv(file="./data/jgra54158-sup-0001-supinfo.csv"; add_unit=false)
+    df = CSV.read(file, DataFrame)
+
+    @transform! df :time = parse_doy_datetime.(:UTC)
+
+    add_unit && @transform! df begin
+        :N_PROTONS_CC = :N_PROTONS_CC * u"cm^-3"
+        :V_KMPS = :V_KMPS * u"km/s"
+        :T_PROTONS_EV = :T_PROTONS_EV * u"eV"
     end
+    df
 end
 
 end

### 2025-05-03 src/io.jl

@@ -5,6 +5,27 @@ using Dates
 using Dates: AbstractTime
 data_path = datadir("05_reporting")
 
+function produce(d)
+    @unpack year, period = d
+    b = get_mag_data(year)
+    n, V = get_state_data()
+    d["ds"] = ids_finder(b, Second(period), V, n)
+    return d
+end
+
+function produce_or_load_juno()
+    allparams = Dict(
+        "id" => ["Juno"],
+        "period" => [60],
+        "year" => collect(2011:2016),
+    )
+    dicts = produce_or_load.(produce, dict_list(allparams), "data")
+    ds = mapreduce(vcat, dicts) do d
+        d[1]["ds"]
+    end
+    return ds
+end
+
 DEFAULT_TAUS = 60:-10:20
 
 post_process!(df) = begin

### 2025-05-03 notebooks/21_model.qmd
refactor: better plot

@@
 using Discontinuity
-using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current
+using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current, uless, plasma_beta
 using Juno: produce_or_load_juno
-using PlasmaFormulary: CurrentDensity, NumberDensity
+using Juno.Data: read_sw_params_csv
 ```
@@
 using Unitful
-using Juno.Data: read_sw_params_csv
 
@@
         :J_A_sw = Alfven_current.(:B_mag, :N_PROTONS_CC)
+        :β_sw = plasma_beta.(:T_PROTONS_EV, :N_PROTONS_CC, :B_mag)
     end
@@
         :L_n_cross_sw_norm = @. :L_n_cross_sw / :d_i_sw |> NoUnits
+        :J_m_max_cross_sw = @. abs(gradient_current(:grad, :V_n_cross_sw))
+        :J_m_max_cross_sw_norm = @. :J_m_max_cross_sw / :J_A_sw |> NoUnits
+
         :L_n_mva_sw = :V_n_mva_sw .* :duration
         :L_n_mva_sw_norm = @. :L_n_mva_sw / :d_i_sw |> NoUnits
-        :J_m_max_cross_sw = @. abs(gradient_current(:grad, :V_n_cross_sw))
-        :J_m_max_cross_sw_norm = @. :J_m_max_cross_sw / :J_A_sw |> NoUnits
         :J_m_max_mva_sw = @. abs(gradient_current(:grad, :V_n_mva_sw))
@@
 using CairoMakie
+import CairoMakie.Makie.SpecApi as S
 using UnitfulLatexify: latexroundunitlabel as lru
-using CairoMakie.GeometryBasics
 
-p_big = decompose(Point2f, Circle(Point2f(0), 1))
-p_small = decompose(Point2f, Circle(Point2f(0), 0.5))
+uless_plot!(ax, x, y; kw...) = scatter!(ax, uless.(x), uless.(y); kw...)
 
-uless(x) = NoUnits(x)
-uless(x::NumberDensity) = NoUnits(x / u"cm^-3")
-uless(x::CurrentDensity) = NoUnits(x / u"nA/m^2")
-uless(x::Unitful.Length) = NoUnits(x / u"km")
-uless(x::Unitful.Velocity) = NoUnits(x / u"km/s")
+let df = jno_df_with_params, xlabel = "Model", ylabel = "Juno", axis = (; xscale=log10, yscale=log10), plot = (; alpha=0.3)
+    f = Figure()
+    ax1 = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel)
+    ax2 = Axis(f[1, 2]; title=lru("n", u"cm^-3"), axis...)
 
-let df = jno_df_with_params, xlabel = "Model", ylabel = "Juno", xscale = log10, yscale = log10, plot = (; alpha=0.3)
-    f = Figure(; size=(600, 600))
-    ax1 = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel)
-    ax2 = Axis(f[1, 2]; title=lru("n", u"cm^-3"), xscale, yscale)
-    ax3 = Axis(f[2, 1]; title=lru("L", u"km"), ylabel, xscale, yscale)
-    ax4 = Axis(f[2, 2]; title=lru("J", u"nA/m^2"), xscale, yscale)
-    ax5 = Axis(f[3, 1]; title=L"L/d_i", xlabel, ylabel, xscale, yscale)
-    ax6 = Axis(f[3, 2]; title=L"J/J_{Alfven}", xlabel, xscale, yscale)
+    ax_T = Axis(f[2, 1]; title=lru("T", u"eV"), axis...)
+    ax_β = Axis(f[2, 2]; title=lru("β", u""), axis...)
 
-    p1, p2 = @with df begin
-        scatter!(ax1, uless.(:V_mag), uless.(:V_KMPS))
-        scatter!(ax2, uless.(:n), uless.(:N_PROTONS_CC))
+    ax3 = Axis(f[4, 1]; title=lru("L", u"km"), ylabel, axis...)
+    ax4 = Axis(f[4, 2]; title=lru("J", u"nA/m^2"), axis...)
+    ax5 = Axis(f[5, 1]; title=L"L/d_i", xlabel, ylabel, axis...)
+    ax6 = Axis(f[5, 2]; title=L"J/J_{Alfven}", xlabel, axis...)
 
-        p1 = scatter!(ax3, uless.(:L_n_cross), uless.(:L_n_cross_sw), label="Cross"; plot...)
-        p2 = scatter!(ax3, uless.(:L_n_mva), uless.(:L_n_mva_sw), label="MVA"; plot...)
+    @with df begin
+        uless_plot!(ax1, :V_mag, :V_KMPS)
+        uless_plot!(ax2, :n, :N_PROTONS_CC)
 
-        scatter!(ax4, uless.(:J_m_max_cross), uless.(:J_m_max_cross_sw), label="Cross"; plot...)
-        scatter!(ax4, uless.(:J_m_max_mva), uless.(:J_m_max_mva_sw), label="MVA"; plot...)
+        p1 = uless_plot!(ax3, :L_n_cross, :L_n_cross_sw, label="Cross"; plot...)
+        p2 = uless_plot!(ax3, :L_n_mva, :L_n_mva_sw, label="MVA"; plot...)
+        Legend(f[3, :], [p1, p2], ["Cross", "MVA"])
 
-        scatter!(ax5, uless.(:L_n_cross_norm), uless.(:L_n_cross_sw_norm); plot...)
-        scatter!(ax5, uless.(:L_n_mva_norm), uless.(:L_n_mva_sw_norm); plot...)
-        scatter!(ax6, uless.(:J_m_max_cross_norm), uless.(:J_m_max_cross_sw_norm); plot...)
-        scatter!(ax6, uless.(:J_m_max_mva_norm), uless.(:J_m_max_mva_sw_norm); plot...)
-        (p1, p2)
+        uless_plot!(ax_T, :T, :T_PROTONS_EV)
+        uless_plot!(ax_β, :β, :β)
+
+        uless_plot!(ax4, :J_m_max_cross, :J_m_max_cross_sw, label="Cross"; plot...)
+        uless_plot!(ax4, :J_m_max_mva, :J_m_max_mva_sw, label="MVA"; plot...)
+        uless_plot!(ax5, :L_n_cross_norm, :L_n_cross_sw_norm; plot...)
+        uless_plot!(ax5, :L_n_mva_norm, :L_n_mva_sw_norm; plot...)
+        uless_plot!(ax6, :J_m_max_cross_norm, :J_m_max_cross_sw_norm; plot...)
+        uless_plot!(ax6, :J_m_max_mva_norm, :J_m_max_mva_sw_norm; plot...)
     end
 
-    Legend(f[1, 3], [p1, p2], ["Cross", "MVA"])
+    color = :red
+    linestyle = :dash
 
     for ax in (ax1,)
-        ablines!(ax, 0, 1, color=:red, linestyle=:dash)
+        ablines!(ax, 0, 1; color, linestyle)
     end
 
-    lines!(ax2, exp10.(-1:0), exp10.(-1:0), color=:red, linestyle=:dash)
-    lines!(ax3, exp10.([2, 4.5]), exp10.([2, 4.5]), color=:red, linestyle=:dash)
-    lines!(ax4, exp10.(-2:1), exp10.(-2:1), color=:red, linestyle=:dash)
-    lines!(ax5, exp10.(-1:2), exp10.(-1:2), color=:red, linestyle=:dash)
-    lines!(ax6, exp10.(-2:1), exp10.(-2:1), color=:red, linestyle=:dash)
+    lines!(ax2, exp10.(-1:0), exp10.(-1:0); color, linestyle)
+    lines!(ax3, exp10.([2, 4.5]), exp10.([2, 4.5]); color, linestyle)
+    lines!(ax4, exp10.(-2:1), exp10.(-2:1); color, linestyle)
+    lines!(ax5, exp10.(-1:2), exp10.(-1:2); color, linestyle)
+    lines!(ax6, exp10.(-2:1), exp10.(-2:1); color, linestyle)
 

### 2025-05-03 notebooks/21_model.qmd
feat: fig_juno_sw_comparision

@@
 using Discontinuity
-using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current, uless, plasma_beta
+using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current, uless, plasma_beta, filter_low_mva_quality!
 using Juno: produce_or_load_juno
-using Juno.Data: read_sw_params_csv
+using Juno.Data: get_mag_data, get_state_data, read_sw_params_csv
+using CairoMakie
+using AlgebraOfGraphics
+import SPEDAS
+set_aog_theme!()
+theme = Theme(; figure_padding=(0, 6, 0, 0),
+    Legend=(padding=(0, 0, 0, 0), margin=(0, 0, 0, 0),)
+)
+update_theme!(theme)
 ```
@@
 ```{julia}
-using DataFrames, DataFramesMeta
+using DataFrames, DataFramesMeta, DimensionalData
 using Unitful
@@
 jno_df = produce_or_load_juno()
+n, V, T, r = get_state_data()
 jno_sw_params = read_sw_params_csv(; add_unit=true)
+
+selector = Ti(Near(jno_df.time))
+jno_df.r = parent(r[selector])
+jno_df.T = parent(T[selector]) * u"K"
 ```
@@
         :V_n_mva_sw = @. abs(first(:n_mva) * :V_KMPS)
-        :d_i_sw = inertial_length.(:N_PROTONS_CC, Unitful.q, Unitful.mp)
+        :d_i_sw = inertial_length.(:N_PROTONS_CC)
         :J_A_sw = Alfven_current.(:B_mag, :N_PROTONS_CC)
@@
 ```{julia}
-using CairoMakie
-import CairoMakie.Makie.SpecApi as S
 using UnitfulLatexify: latexroundunitlabel as lru
+using Beforerr
 
@@
 
-let df = jno_df_with_params, xlabel = "Model", ylabel = "Juno", axis = (; xscale=log10, yscale=log10), plot = (; alpha=0.3)
-    f = Figure()
-    ax1 = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel)
-    ax2 = Axis(f[1, 2]; title=lru("n", u"cm^-3"), axis...)
+let df = filter_low_mva_quality!(jno_df_with_params), xlabel = "Model", ylabel = "Juno", axis = (; xscale=log10, yscale=log10), plot = (; alpha=0.3)
+    f = Figure(;)
+    wh = (width=120, height=110)
+    ax1 = Axis(f[1, 1]; title=lru("V", u"km/s"), ylabel, wh...)
+    ax2 = Axis(f[1, 2]; title=lru("n", u"cm^-3"), wh..., axis...)
 
-    ax_T = Axis(f[2, 1]; title=lru("T", u"eV"), axis...)
-    ax_β = Axis(f[2, 2]; title=lru("β", u""), axis...)
+    ax_T = Axis(f[1, 3]; title=lru("T", u"eV"), wh..., axis...)
+    ax_β = Axis(f[1, 4]; title=L"β", wh..., axis...)
 
-    ax3 = Axis(f[4, 1]; title=lru("L", u"km"), ylabel, axis...)
-    ax4 = Axis(f[4, 2]; title=lru("J", u"nA/m^2"), axis...)
-    ax5 = Axis(f[5, 1]; title=L"L/d_i", xlabel, ylabel, axis...)
-    ax6 = Axis(f[5, 2]; title=L"J/J_{Alfven}", xlabel, axis...)
+    ax_L = Axis(f[2, 1]; title=lru("L", u"km"), xlabel, ylabel, wh..., axis...)
+    ax_J = Axis(f[2, 2]; title=lru("J", u"nA/m^2"), xlabel, wh..., axis...)
+    ax_Ln = Axis(f[2, 3]; title=L"L/d_i", xlabel, wh..., axis...)
+    ax_Jn = Axis(f[2, 4]; title=L"J/J_A", xlabel, wh..., axis...)
 
@@
         uless_plot!(ax2, :n, :N_PROTONS_CC)
+        uless_plot!(ax_T, :T, :T_PROTONS_EV)
+        uless_plot!(ax_β, :β, :β_sw)
 
-        p1 = uless_plot!(ax3, :L_n_cross, :L_n_cross_sw, label="Cross"; plot...)
-        p2 = uless_plot!(ax3, :L_n_mva, :L_n_mva_sw, label="MVA"; plot...)
-        Legend(f[3, :], [p1, p2], ["Cross", "MVA"])
+        p1 = uless_plot!(ax_L, :L_n_cross, :L_n_cross_sw, label="Cross"; plot...)
+        p2 = uless_plot!(ax_L, :L_n_mva, :L_n_mva_sw, label="MVA"; plot...)
+        axislegend(ax_L; padding=0, position=(^(:lt)), framevisible=true, framecolor=(^(:gray)))
 
-        uless_plot!(ax_T, :T, :T_PROTONS_EV)
-        uless_plot!(ax_β, :β, :β)
-
-        uless_plot!(ax4, :J_m_max_cross, :J_m_max_cross_sw, label="Cross"; plot...)
-        uless_plot!(ax4, :J_m_max_mva, :J_m_max_mva_sw, label="MVA"; plot...)
-        uless_plot!(ax5, :L_n_cross_norm, :L_n_cross_sw_norm; plot...)
-        uless_plot!(ax5, :L_n_mva_norm, :L_n_mva_sw_norm; plot...)
-        uless_plot!(ax6, :J_m_max_cross_norm, :J_m_max_cross_sw_norm; plot...)
-        uless_plot!(ax6, :J_m_max_mva_norm, :J_m_max_mva_sw_norm; plot...)
+        uless_plot!(ax_J, :J_m_max_cross, :J_m_max_cross_sw; plot...)
+        uless_plot!(ax_J, :J_m_max_mva, :J_m_max_mva_sw; plot...)
+        uless_plot!(ax_Ln, :L_n_cross_norm, :L_n_cross_sw_norm; plot...)
+        uless_plot!(ax_Ln, :L_n_mva_norm, :L_n_mva_sw_norm; plot...)
+        uless_plot!(ax_Jn, :J_m_max_cross_norm, :J_m_max_cross_sw_norm; plot...)
+        uless_plot!(ax_Jn, :J_m_max_mva_norm, :J_m_max_mva_sw_norm; plot...)
     end
@@
 
-    lines!(ax2, exp10.(-1:0), exp10.(-1:0); color, linestyle)
-    lines!(ax3, exp10.([2, 4.5]), exp10.([2, 4.5]); color, linestyle)
-    lines!(ax4, exp10.(-2:1), exp10.(-2:1); color, linestyle)
-    lines!(ax5, exp10.(-1:2), exp10.(-1:2); color, linestyle)
-    lines!(ax6, exp10.(-2:1), exp10.(-2:1); color, linestyle)
+    lines!(ax2, exp10.([-1.5, 0]), exp10.([-1.5, 0]); color, linestyle)
+    lines!(ax_L, exp10.([2, 5]), exp10.([2, 5]); color, linestyle)
+    lines!(ax_J, exp10.(-2:1), exp10.(-2:1); color, linestyle)
+    lines!(ax_Ln, exp10.([-1, 3]), exp10.([-1, 3]); color, linestyle)
+    lines!(ax_Jn, exp10.([-2, 2]), exp10.([-2, 2]); color, linestyle)
+    lines!(ax_T, exp10.([0.2, 1.5]), exp10.([0.2, 1.5]); color, linestyle)
+    lines!(ax_β, exp10.(-2:2), exp10.(-2:2); color, linestyle)
 
     limits!(ax1, 360, 550, 360, 550)
+    limits!(ax_L, 10^1.9, 10^5, 10^1.9, 10^5)
+    limits!(ax_J, 10^-2.1, 10^1.08, 10^-2.1, 10^1.08)
+    limits!(ax_Ln, 10^-1.1, 10^2.8, 10^-1.1, 10^2.8)
+    limits!(ax_Jn, 10^-2.5, 10^1.4, 10^-2.5, 10^1.4)
 
-    easy_save("model/juno_sw_comparision")
+    SPEDAS.add_labels!()
+    resize_to_layout!(f)
+    easy_save("fig_juno_sw_comparision")
 end
@@
 
+```{julia}
+function query(df, field, f=argmin)
+    inds = f(skipmissing(df[!, field]))
+    df[inds, :]
+end
+
+row = query(jno_df_with_params, :L_n_cross)
+```
+
+```{julia}
+using SPEDAS: Product, tview, tplot, tlines!
+using Discontinuity: MVAProduct
+# Juno_B_product = Product(
+#     get_mag_data(2016), tview
+# )
+Juno_B_mva_product = MVAProduct(Juno_B_product, Juno_B_product, row.t_us_ds)
+
+tplot([Juno_B_product, Juno_B_mva_product], row.tstart, row.tstop)
+tlines!([row.t_us_ds...])
+current_figure()
+```
+
 ![](../figures/model/juno_sw_comparision.png)

### 2025-05-03 notebooks/30_data.qmd
feat: fig_juno_sw_comparision

@@
 using StaticArrays
-ds.r = parent(r[Ti(Near(ds.time))])
-ds.T = T[Ti(Near(ds.time))] * u"K"
+selector = Ti(Near(ds.time))
+ds.r = parent(r[selector])
+ds.T = parent(T[selector]) * u"K"
 
@@
 
-struct FitProduct{F,P} <: Function
-    f::F
-    param::P
-    t0::DateTime
-end
-
-function (p::FitProduct)(t0, t1)
-    tspan = DateTime(t0):Millisecond(10):DateTime(t1)
-    xspan = @. (tspan - p.t0) / Millisecond(1)
-    data = p.f.(xspan, Ref(p.param))
-    return DimVector(data, Ti(tspan))
-end
-
 FitProduct(row) = FitProduct(tanh_model, row.fit_param, row.t_us_ds[1])
 FitProduct(df::DataFrame, i) = FitProduct(df[i, :])
-
-struct MVAProduct <: Function
-    V
-    B
-    mva_tspan
-end
-
-(p::MVAProduct)(t0, t1) = mva(p.V(t0, t1), p.B(p.mva_tspan...))
 

### 2025-05-10 src/Juno.jl
feat: THEMIS reprocessing

@@ -12,10 +12,36 @@ using Beforerr
 using LaTeXStrings
 using Discontinuity
 using Unitful
+using Dates: DateTime
 import Base.round
 
 export subset_by_quantiles
 export load_taus
+
+const START_TIME = DateTime(2011, 8, 25)
+const END_TIME = DateTime(2016, 6, 30)
+const TIME_RANGE = (START_TIME, END_TIME)
+const TEST_TIME_RANGE = (DateTime(2012, 1, 1), DateTime(2012, 1, 2))
+
+function get_time_range(yr, start=START_TIME, stop=END_TIME)
+    yr == year(start) && return (start, DateTime(yr + 1))
+    yr == year(stop) && return (DateTime(yr), stop)
+    yr < year(start) || yr > year(stop) && @info "Year $yr is outside the $TIME_RANGE"
+    return (DateTime(yr), DateTime(yr + 1))
+end
+
+using DimensionalData
+using DimensionalData: rebuild, setdims, _astuple
+const DD = DimensionalData
+
+function sort_data(A, dim=Ti)
+    time = parent(DD.dims(A, dim))
+    issorted(time) ? A : begin
+        newdata = sortslices(parent(A); dims=dimnum(A, dim))
+        newtime = dim(sort(time))
+        rebuild(A, newdata, setdims(DD.dims(A), newtime))
+    end
+end
 
 set_aog_theme!()
 theme = Theme(;
@@ -31,6 +57,7 @@ update_theme!(theme)
 include("io.jl")
 include("plot.jl")
 include("data.jl")
+include("THEMIS.jl")
 
 datalimits_f = x -> quantile(x, [0.02, 0.98])
 

### 2025-05-10 src/THEMIS.jl

@@ -1,0 +1,36 @@
+module THEMIS
+using ..Juno: get_time_range, sort_data
+using Dates: DateTime, Second
+using DrWatson: produce_or_load, dict_list, @unpack
+using Speasy: SpeasyProduct, init_cdaweb
+using Discontinuity: ids_finder
+
+__init__() = init_cdaweb()
+
+B_GSE = SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ")
+B_FGL_GSE = SpeasyProduct("THB_L2_FGM/thb_fgl_gseQ")
+
+SSE_STATE = SpeasyProduct("THB_L2_MERGED/XYZ_SSE")
+# THB_L1_STATE/thb_pos_sse
+
+function produce(d)
+    START_TIME = DateTime(2011, 9, 9) # There is an np.datetime64('NaT') which makes `Speasy` conversion fail
+    @unpack year, period = d
+    data = B_FGL_GSE(get_time_range(year, START_TIME)...)
+    d["ds"] = ids_finder(sort_data(data), Second(period))
+    return d
+end
+
+function produce()
+    allparams = Dict(
+        "id" => ["THB"],
+        "period" => [60],
+        "year" => collect(2011:2016),
+    )
+    dicts = produce_or_load.(produce, dict_list(allparams), "data")
+    ds = mapreduce(vcat, dicts) do d
+        d[1]["ds"]
+    end
+    return ds
+end
+end

### 2025-05-15 src/THEMIS.jl
refactor: generalize

@@ -1,36 +1,41 @@
-module THEMIS
-using ..Juno: get_time_range, sort_data
-using Dates: DateTime, Second
-using DrWatson: produce_or_load, dict_list, @unpack
-using Speasy: SpeasyProduct, init_cdaweb
-using Discontinuity: ids_finder
+using Speasy: init_cdaweb, init_archive
 
-__init__() = init_cdaweb()
+init_provider() = (init_cdaweb(); init_archive())
 
-B_GSE = SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ")
-B_FGL_GSE = SpeasyProduct("THB_L2_FGM/thb_fgl_gseQ")
-
-SSE_STATE = SpeasyProduct("THB_L2_MERGED/XYZ_SSE")
-# THB_L1_STATE/thb_pos_sse
-
-function produce(d)
-    START_TIME = DateTime(2011, 9, 9) # There is an np.datetime64('NaT') which makes `Speasy` conversion fail
-    @unpack year, period = d
-    data = B_FGL_GSE(get_time_range(year, START_TIME)...)
-    d["ds"] = ids_finder(sort_data(data), Second(period))
+function general_produce(d::Dict; split=Day(30), kw...)
+    @unpack year, period, B = d
+    timerange = get_time_range(year)
+    d["ds"] = ids_finder(B, timerange..., Second(period); split, kw...)
     return d
 end
 
-function produce()
+function general_produce(id, B; kw...)
     allparams = Dict(
-        "id" => ["THB"],
+        "id" => id,
         "period" => [60],
         "year" => collect(2011:2016),
+        "B" => B,
     )
-    dicts = produce_or_load.(produce, dict_list(allparams), "data")
+    dicts = produce_or_load.(general_produce, dict_list(allparams), "data")
     ds = mapreduce(vcat, dicts) do d
         d[1]["ds"]
     end
     return ds
 end
+
+module THEMIS
+using Speasy: SpeasyProduct, getdimarray
+using SPEDAS: tsort
+
+const B_GSE = SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ")
+const B_FGL_GSE = (args...; kw...) -> tsort(getdimarray("archive/local/THB_L2_FGM/thb_fgl_gse", args...; sanitize=true, kw...))
[…]

### 2025-05-16 notebooks/02_waiting_time.qmd
feat: OCR redo

--- 2025-01-02 notebooks/02_waiting_time.qmd
@@
 
-It is hard to remove duplicate events when combining multiple datasets with different τ. So when using the combined dataset, the occurence rate would be overestimated.
+It is hard to remove duplicate events *totally* when combining multiple datasets with different τ. So when using the combined dataset, the occurence rate would be overestimated.
 
@@
 ```{julia}
-using DrWatson
-@quickactivate
-include(srcdir("main.jl"))
+using Juno
+using Dates
+using Discontinuity
+using Discontinuity: waiting_time, remove_duplicates
+using Discontinuity: plot_wt_pdf, plot_wt_pdf!
+using CairoMakie
+using Beforerr: easy_save
+using AlgebraOfGraphics
+using Distributions, DataFramesMeta
+using Unitful
+using DimensionalData
 
-using CairoMakie
+hidexlabel!(ax) = ax.xlabelvisible = false
+hideylabel!(ax) = ax.ylabelvisible = false
+
+M = (
+    ρ=:ρ => "Occurence Rates (#/day)",
+    ρ_norm=:ρ_norm => "Normalized Occurence Rates",
+    tbin=:time_bin => "Time",
+    r=:r_mean => "Radial Distance (AU)",
+)
+
+Juno.setup_theme!()
 ```
 
+### Data
+
 ```{julia}
-wind_df = load(; name="Wind", ts=missing);
-jno_df = load();
+using Juno: general_produce, init_provider
+using Juno: THEMIS, Wind, STEREO
+using DataFrames, DataFramesMeta
+init_provider()
+wdf = general_produce("Wind", Wind.B_RTN)
+tdf = general_produce("THB", THEMIS.B_FGL_GSE)
+jdf = general_produce("Juno", Juno.Data.get_mag_data)
+sdf = general_produce("STA", STEREO.B_RTN3)
+
+wdf.id .= "Wind"
+tdf.id .= "THEMIS-B"
+jdf.id .= "Juno"
+sdf.id .= "STEREO-A"
+thb_sw_tranges = THEMIS.themis_b_sw()
+# thb_sse_state = THEMIS.SSE_STATE(Juno.TIME_RANGE)
+tdf_sw = mapreduce(vcat, eachrow(thb_sw_tranges)) do row
+    @subset(tdf, :time .> row.start, :time .< row.stop)
+end
+
+Juno.Data.add_state_info!(jdf)
 ```
@@
 ```{julia}
-df = wind_df;
-df_s1 = subset(df, :time => t -> year.(t) .== 2013);
-df_s2 = subset(df_s1, :time => t -> month.(t) .< 2);
-
-jno_df_s1 = subset(jno_df, :time => t -> year.(t) .== 2011);
-jno_df_s2 = subset(jno_df, :time => t -> year.(t) .== 2016);
+jno_df_s1 = subset(jdf, :time => t -> year.(t) .== 2011);
+jno_df_s2 = subset(jdf, :time => t -> year.(t) .== 2016);
 ```
@@
 ```{julia}
-using Distributions
-
 function plot_wt_pdf_lim(df; xlims=(1, 1000), ylims=(1e-5, 8e-2), kwargs...)
@@
 #| layout-ncol: 3
+if false
     dfs = [jno_df, jno_df_s1, jno_df_s2]
     fgs = plot_wt_pdf_lim.(dfs; dists)
-display.(fgs);
+    display.(fgs)
+end
 ```
+
+### Juno
+
+```{julia}
+_wt(df, tmax=1000) = filter!(<(tmax), waiting_time(df))
+
+let f = Figure()
+    ax1 = plot_wt_pdf!(f[1, 1], _wt(jno_df_s1); dists)
+    ax2 = plot_wt_pdf!(f[2, 1], _wt(jno_df_s2); dists)
+    ax3 = plot_wt_pdf!(f[1, 2], _wt(jno_df_s1, 600); dists)
+    ax4 = plot_wt_pdf!(f[2, 2], _wt(jno_df_s2, 600); dists)
+    axs = (ax1, ax2, ax3, ax4)
+    hideylabel!.(axs)
+    xlims!.(axs, 1, 500)
+    ylims!.(axs, 1e-5, 8e-2)
+    f
+end
+```
+
+### Wind and ARTEMIS
+
+```{julia}
+let f = Figure()
+    _wt(df, tmax=1000) = filter!(<(tmax), waiting_time(df))
+    ax1 = plot_wt_pdf!(f[1, 1], _wt(wdf); dists, legend_title="Wind")
+    ax2 = plot_wt_pdf!(f[2, 1], _wt(tdf_sw); dists, legend_title="ARTEMIS")
+    ax3 = plot_wt_pdf!(f[1, 2], _wt(wdf, 200); dists, legend_title="Wind")
+    ax4 = plot_wt_pdf!(f[2, 2], _wt(tdf_sw, 200); dists, legend_title="ARTEMIS")
+
+    axs = (ax1, ax2)
+    axs2 = (ax3, ax4)
+    hidexlabel!.((ax1, ax3))
+    hideylabel!.(axs2)
+    xlims!.(axs, 1, 500)
+    ylims!.(axs, 1e-5, 8e-2)
+    ylims!.(axs2, 1e-5, 8e-2)
+    easy_save("fig_wt_pdf_wind_thb")
+end
+```
+
+![](../figures/fig_wt_pdf_wind_thb.png)
 
@@
 
-# let 
-#     plot_fig_wt_dist()
-#     easy_save("fig_wt_dist")
-# end
-
 let tdf = Discontinuity.remove_duplicates(df)
@@
 ```{julia}
-using Distributions
+import DataFrames: groupby
+using PartialFunctions
 
-get_fit_params(x; dist=Weibull, func=mean) = func(fit(dist, x))
-get_wt_fit_params(time; kwargs...) = get_fit_params(waiting_time(time); kwargs...)
+function get_wt_fit_params(time; dist=Weibull, stat=mean, tmax=nothing, δt=1u"minute", kwargs...)
+    Δts = waiting_time(time)
+    isnothing(tmax) || filter!(x -> x < tmax, Δts)
+    stat(fit(dist, Δts; kwargs...)) * δt
+end
+
+function groupby(df::AbstractDataFrame, dt::Period, args...; col=:time)
+    @chain df begin
+        @transform!(:time_bin = round.(:time, dt),)
+        @groupby(:time_bin, args...)
+    end
+end
+
+function get_groupby_occurence_rate(df, dt::Period; tmax=nothing, combine=())
+    @chain df begin
+        groupby(dt, :id)
+        DataFrames.combine(nrow, :time => get_wt_fit_params$(; tmax) => :τ, combine...)
+        @transform(:ρ = NoUnits.(Day(1) ./ :τ))
+    end
+end
 ```
 
+## Figure: Occurence rate for time
+
 ```{julia}
-jno_ρ_df = @chain jno_df begin
-    @transform!(
-        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
-        :l = :L_k .* (abs ∘ cosd).(:θ_vn),
-        :l_n = :L_k .* (abs ∘ cos ∘ atan).(:Vn_y ./ :Vn_x)
-    )
-end;
+using LsqFit
+using LaTeXStrings
+using Beforerr: figsize
+
+@. model(r, p) = p[1] / r^p[2]
+label_model(p) = LaTeXString(@sprintf("y \\sim %.2f / r^{%.2f}", p[1], p[2]))
+
+begin
+    f = Figure(; size=(600, 300))
+    dt = Day(60)
+    ttdf = get_groupby_occurence_rate(tdf_sw, dt; tmax=120)
+    wtdf = get_groupby_occurence_rate(wdf, dt; tmax=1000)
+    stdf = @chain begin
+        get_groupby_occurence_rate(sdf, dt; tmax=500)
+        @rtransform(:ρ = ifelse(Date(2015, 3) < :time_bin < Date(2015, 8), missing, :ρ))
+    end
+    jtdf = get_groupby_occurence_rate(jdf, dt; tmax=1000, combine=([:r] .=> mean))
+    jtdf.ρ_norm = jtdf.ρ ./ @rsubset(wtdf, :time_bin in jtdf.time_bin).ρ
+
+    tticks = DateTime(2011):Year(1):DateTime(2016)
+    axis = (; yticks=0:20:100, xticks=datetimeticks(tticks, Dates.format.(tticks, "yyyy")))
+    specs = (data(wtdf) + data(stdf) + data(ttdf) + data(jtdf)) * mapping(M.tbin, M.ρ; color=:id => "") * visual(ScatterLines)
+    g1 = draw!(f[1, 1], specs; axis)
+    legend!(f[1, 1], g1; tellheight=false, tellwidth=false, valign=:bottom, halign=:left)
+    ylims!(10, 105)
+
+    g2 = draw!(f[1, 2], data(jtdf) * mapping(M.r, M.ρ_norm))
+    ax2 = g2[1].axis
+    rfit = curve_fit(model, jtdf.r_mean, jtdf.ρ_norm, [1.0, 1.0])
+    lines!(ax2, sort(jtdf.r_mean), model(sort(jtdf.r_mean), rfit.param); color=:gray, linestyle=:dash)
+    text!(ax2, (3, 0.8); text=label_model(rfit.param))
+    ylims!(ax2, 0.15, 1.05)
+    easy_save("fig_occurence_rate")
+end
 ```
+
+### Normalization by thickness
 

### 2025-05-16 notebooks/30_data.qmd
feat: THEMIS reprocessing
feat: OCR redo

@@
 jno_sw_params = read_sw_params_csv()
+```
+
+```{julia}
+using Speasy
+using Juno
+using Juno: THEMIS, Wind, STEREO
+using Juno: general_produce, init_provider
+init_provider()
+```
+
+```{julia}
+wdf = general_produce("Wind", Wind.B_RTN)
+tdf = general_produce("THB", THEMIS.B_FGL_GSE)
+tdf_sw = mapreduce(vcat, eachrow(thb_sw_tranges)) do row
+    @subset(tdf, :time .> row.start, :time .< row.stop)
+end
+tdf_sw.in_lunar_wake = parent(thb_sse_state[Ti(Near(tdf_sw.time)), Y(1)]) .< 0
+tdf_sw_pure = @subset(tdf_sw, :in_lunar_wake .== false)
+tdf_sw_pure.id .= "THB_SW_PURE"
+df = vcat(wdf, tdf, tdf_sw, tdf_sw_pure; cols=:intersect)
+```
+
+Inspect the data
+
+```{julia}
+using SPEDAS
+
+tplot(
+    Wind.B_RTN, "2015-08-07T14:50:54", "2015-08-07T14:51:30"
+)
 ```

### 2025-05-16 src/Juno.jl

@@ -43,16 +43,18 @@ function sort_data(A, dim=Ti)
     end
 end
 
-set_aog_theme!()
-theme = Theme(;
-    colormap=Reverse(:tokyo),
-    figure_padding=2,
-    Axis=(
-        xminorticksvisible=true,
-        yminorticksvisible=true
+function setup_theme!()
+    set_aog_theme!()
+    theme = Theme(;
+        colormap=Reverse(:tokyo),
+        figure_padding=2,
+        Axis=(
+            xminorticksvisible=true,
+            yminorticksvisible=true
+        )
     )
-)
-update_theme!(theme)
+    update_theme!(theme)
+end
 
 include("io.jl")
 include("plot.jl")

### 2025-05-16 src/THEMIS.jl

@@ -1,6 +1,7 @@
 using Speasy: init_cdaweb, init_archive
+using DataToolkit
 
-init_provider() = (init_cdaweb(); init_archive())
+init_provider() = (init_cdaweb(); init_archive(); loadcollection!("Data.toml"))
 
 function general_produce(d::Dict; split=Day(30), kw...)
     @unpack year, period, B = d
@@ -9,23 +10,26 @@ function general_produce(d::Dict; split=Day(30), kw...)
     return d
 end
 
-function general_produce(id, B; kw...)
+function general_produce(id, B; f=general_produce, kw...)
     allparams = Dict(
         "id" => id,
         "period" => [60],
         "year" => collect(2011:2016),
         "B" => B,
     )
-    dicts = produce_or_load.(general_produce, dict_list(allparams), "data")
+    dicts = produce_or_load.(f, dict_list(allparams), "data")
     ds = mapreduce(vcat, dicts) do d
         d[1]["ds"]
     end
+    ds.id .= id
     return ds
 end
 
 module THEMIS
 using Speasy: SpeasyProduct, getdimarray
 using SPEDAS: tsort
+using DataToolkit, DataFramesMeta
+using SpaceDataModel: parse_doy_datetime
 
 const B_GSE = SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ")
 const B_FGL_GSE = (args...; kw...) -> tsort(getdimarray("archive/local/THB_L2_FGM/thb_fgl_gse", args...; sanitize=true, kw...))
@@ -33,9 +37,24 @@ const B_FGS_GSE = (args...; kw...) -> tsort(getdimarray("archive/local/THB_L2_FG
 
 const SSE_STATE = SpeasyProduct("THB_L2_MERGED/XYZ_SSE")
 # THB_L1_STATE/thb_pos_sse
+
+themis_b_sw() = @select!(
+    d"themis_b_sw",
+    :start = parse_doy_datetime.(:start),
+    :stop = parse_doy_datetime.(:end)
+)
 end
 
 module Wind
 using Speasy: SpeasyProduct
 const B_RTN = SpeasyProduct("archive/local/WI_H4-RTN_MFI/BRTN")
+end
+
+module STEREO
+using Speasy: SpeasyProduct
+using SPEDAS: tsort
+preprocess(da) = @views tsort(da[:, 1:3])
+preprocess(::Nothing) = nothing
[…]

### 2025-05-16 src/data.jl

@@ -68,4 +68,10 @@ function read_sw_params_csv(file="./data/jgra54158-sup-0001-supinfo.csv"; add_un
     df
 end
 
+function add_state_info!(df, state=get_state_data())
+    selector = Ti(Near(df.time))
+    df.r = parent(state.r[selector])
+    df.T = parent(state.T[selector]) * u"K"
+end
+
 end

### 2025-05-19 notebooks/02_waiting_time.qmd
fig: add_labels

@@
 using CairoMakie
-using Beforerr: easy_save
+using Beforerr: easy_save, add_labels!
 using AlgebraOfGraphics
@@
     ylims!(ax2, 0.15, 1.05)
+    add_labels!()
     easy_save("fig_occurence_rate")

### 2025-05-23 notebooks/02_waiting_time.qmd
chore: cleanup

@@
 ```
+
+## Old codes
+
+```julia
+subset_jno(df, r) = subset(df, :radial_distance => x -> round_c.(x) .== r)
+subset_time(df, t) = subset(df, :time => x -> x .< t)
+
+bin(x, bin_size) = @. round(x / bin_size) * bin_size
+bin(bin_size) = x -> bin(x, bin_size)
+
+df = wind_df;
+df_s1 = subset(df, :time => t -> year.(t) .== 2013);
+df_s2 = subset(df_s1, :time => t -> month.(t) .< 2);
+
+jno_df_s1 = subset(jno_df, :time => t -> year.(t) .== 2011);
+jno_df_s2 = subset(jno_df, :time => t -> year.(t) .== 2016);
+
+jno_ρ_df = @chain jno_df begin
+    @transform!(
+        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
+        :l = :L_k .* (abs ∘ cosd).(:θ_vn),
+        :l_n = :L_k .* (abs ∘ cos ∘ atan).(:Vn_y ./ :Vn_x)
+    )
+end;
+
+time_interval = Day(160)
+
+jno_ρ_df = @chain jno_df begin
+    @transform(
+        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
+        :l = :L_k .* (abs ∘ cosd).(:θ_vn),
+        :l_n = :L_k .* (abs ∘ cos ∘ atan).(:Vn_y ./ :Vn_x)
+    )
+    @transform(
+        :l_ratio = :l ./ :r,
+        :l_n_ratio = :l_n ./ :r
+    )
+    groupby(:time_bin)
+    combine(
+        nrow,
+        :time => get_wt_fit_params => :τ,
+        [:r :l :l_ratio :l_n_ratio] .=> mean
+    )
+    # subset(:nrow => x -> x .> 2000)
+    @transform(
+        :ρ = 1 ./ :τ,
+    )
+    @transform(
+        :ρ_l = :ρ ./ :l_ratio_mean * maximum(:l_ratio_mean),
+    )
+    sort(:r_mean)
+end
+
+wind_ρ_df = @chain wind_df begin
+    @transform!(
+        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
+    )
+    groupby(:time_bin)
+    combine(
+        nrow,
+        :time => get_wt_fit_params => :τ,
+    )
+    @transform!(
+        :ρ = 1 ./ :τ,
+    )
+end
+
+df = leftjoin(jno_ρ_df, wind_ρ_df, on=:time_bin, makeunique=true)
+df.ρ_ratio = @. df.ρ / df.ρ_1
+
+@transform!(df,
+    :ratio = :ρ_ratio ./ :l_ratio_mean,
+    :ratio_n = :ρ_ratio ./ :l_n_ratio_mean,
+)
+@transform!(
+    df,
+    :ratio = :ratio ./ mean(:ratio),
+    :ratio_n = :ratio_n ./ mean(:ratio_n)
+)
+
+x = :time_bin => "Time"
+legends = ["Juno", "Wind"]
+specs = data(df) * mapping(x, [:ρ_l, :ρ_1] .=> "Normalized Occurence rates") * mapping(color=dims(1) => renamer(legends))
+draw(specs)
+easy_save("ocr/ocr_normalized_by_r")
+
+x = :r_mean => r_lab
+specs = data(df) * mapping(x, :ρ)
+draw(specs)
+
+y = [:ratio_n, :ratio]
+specs = data(df) * mapping(x) * mapping(y, color=dims(1) => renamer(string.(y)))
+plt2 = draw(specs)
+```

### 2025-06-21 notebooks/21_model.qmd
fig: mva and cross comparison

@@
 using Discontinuity
-using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current, uless, plasma_beta, filter_low_mva_quality!
+using Discontinuity: compute_params!, Alfven_current, inertial_length, gradient_current, uless, plasma_beta, filter_low_mva_quality
 using Juno: produce_or_load_juno
@@
 
-let df = filter_low_mva_quality!(jno_df_with_params), xlabel = "Model", ylabel = "Juno", axis = (; xscale=log10, yscale=log10), plot = (; alpha=0.3)
+let df = filter_low_mva_quality(jno_df_with_params), xlabel = "Model", ylabel = "Juno", axis = (; xscale=log10, yscale=log10), plot = (; alpha=0.3)
     f = Figure(;)
@@
 
+    # Compare L and J from MVA and cross methods
+    ax_L_comp = Axis(f[3, 2]; title=lru("L", u"km"), xlabel="MVA", ylabel="Cross", wh..., axis...)
+    ax_J_comp = Axis(f[3, 3]; title=lru("J", u"nA/m^2"), xlabel="MVA", wh..., axis...)
+
+    @with df begin
+        uless_plot!(ax_L_comp, :L_n_mva_sw, :L_n_cross_sw; plot...)
+        uless_plot!(ax_J_comp, :J_m_max_mva_sw, :J_m_max_cross_sw; plot...)
+    end
+
     color = :red
@@
     lines!(ax_β, exp10.(-2:2), exp10.(-2:2); color, linestyle)
+    lines!(ax_L_comp, exp10.([2, 5]), exp10.([2, 5]); color, linestyle)
+    lines!(ax_J_comp, exp10.([-2, 1]), exp10.([-2, 1]); color, linestyle)
 
@@
     limits!(ax_Jn, 10^-2.5, 10^1.4, 10^-2.5, 10^1.4)
+
+    limits!(ax_L_comp, 10^2.5, 10^5.1, 10^2.5, 10^5.1)
+    limits!(ax_J_comp, 10^-2.1, 10^1.1, 10^-2.1, 10^1.1)
 
